### 2016-02-16 misc/notes.tex
added miscellaneous files used for this project

\documentclass[11pt]{article}

%%% standard header
\usepackage[margin=1in]{geometry} % one inch margins
\usepackage{fancyhdr} % easier header and footer management
\pagestyle{fancyplain} % page formatting style
\usepackage{hyperref} % for linking references
\setlength{\parindent}{0cm} % don't indent new paragraphs...
\parskip 6pt % ... place a space between paragraphs instead
\usepackage[inline]{enumitem} % include for \setlist{}, use below
%\setlist{nolistsep} % more compact spacing between environments
\setlist[itemize]{leftmargin=*} % nice margins for itemize ...
\setlist[enumerate]{leftmargin=*} % ... and enumerate environments
\frenchspacing % add a single space after a period
\usepackage{lastpage} % for referencing last page
\cfoot{\thepage~of \pageref{LastPage}} % "x of y" page labeling

%%% symbols, notations, etc.
\usepackage{physics,braket,bm,commath,amssymb} % physics packages
\renewcommand{\t}{\text} % text in math mode
\newcommand{\f}[2]{\dfrac{#1}{#2}} % shorthand for fractions
\newcommand{\p}[1]{\left(#1\right)} % parenthesis
\renewcommand{\sp}[1]{\left[#1\right]} % square parenthesis
\renewcommand{\set}[1]{\left\{#1\right\}} % curly parenthesis
\renewcommand{\v}{\bm} % bold vectors
\newcommand{\uv}[1]{\hat{\v{#1}}} % unit vectors
\newcommand{\av}{\vec} % arrow vectors
\renewcommand{\del}{\nabla} % del operator
\renewcommand{\d}{\partial} % partial d
\renewcommand{\c}{\cdot} % inner product
\newcommand{\w}{\wedge} % wedge product
\newcommand{\bk}{\Braket} % shorthand for braket notation
\let\vepsilon\epsilon % remap normal epsilon to vepsilon
\let\vphi\phi % remap normal phi to vphi
\newcommand{\eps}{\varepsilon} % prettier epsilon
\renewcommand{\phi}{\varphi} % prettier phi
\renewcommand{\l}{\ell} % prettier l
\newcommand{\m}[1]{\begin{pmatrix}#1\end{pmatrix}} % matrix
\newcommand{\vm}[1]{\begin{vmatrix}#1\end{vmatrix}} % determinant

%%% sections
\usepackage{sectsty,titlesec} % section options
\sectionfont{\large} % section font size
\subsectionfont{\normalsize} % subsection font size

\renewcommand{\headrulewidth}{0.5pt} % horizontal line in header
\lhead{Michael A. Perlin}

\renewcommand{\u}{\uparrow}
\renewcommand{\d}{\downarrow}
\newcommand{\E}{\mathcal E}
\newcommand{\floor}[1]{\left\lfloor{#1}\right\rfloor}
\newcommand{\ceil}[1]{\left\lceil{#1}\right\rceil}

\begin{document}
\titlespacing{\section}{0pt}{6pt}{0pt} % section placement
\titlespacing{\subsection}{5mm}{6pt}{0pt} % subsection placement

\section*{Prefix}

\subsection*{Projections}

The projection operator $P\sp{\v v,I\v u}$ projects $\v v$ onto the
plane $I\v u$ (i.e. the plane orthogonal to $\v u$), and is is defined
by:
\begin{align}
  P\sp{\v v,I\v u}=\v v-\v v\c\uv u\uv u
\end{align}

\subsection*{Rotations}

The rotation operator $R\sp{\v v,I\v\phi}$ rotates the vector $\v v$
by $\phi$ in the plane $I\uv\phi$, and is defined by
\begin{align}
  R\sp{\v v,I\phi\uv z}=\p{v_x\cos\phi-v_y\sin\phi}\uv
  x+\p{v_y\cos\phi+v_x\sin\phi}\uv y+v_z\uv z.
\end{align}
which may also be written as
\begin{align}
  R\sp{\v v,I\v\phi}=P\sp{\v v,I\uv\phi}\cos\phi+\uv\phi\times\v
  v\sin\phi+\v v\c\uv\phi\uv\phi,
\end{align}
If we choose coordinates in which $\v v=v_x\uv x+v_z\uv z$,
i.e. $v_y=0$, then
\begin{align}
  R\sp{\v v,I\phi\uv z}=v_x\p{\cos\phi\uv x+\sin\phi\uv y}+v_z\uv z.
\end{align}

We will define the frequently used operator
\begin{align}
  P_\perp\sp{\v v,I\v u}=R\sp{P\sp{\v v,I\uv u},\f\pi2 I\uv u} =\uv
  u\times\v v.
\end{align}

\newpage
\section*{NV system}

We have the total system Hamiltonian
\begin{align}
  H_{\t{sys}}=H_{\t{NV}}^{\t{GS}}+H_{\t{hf}}+H_{\t{nZ}}+H_{\t{nn}},
\end{align}
where
\begin{align}
  H_{\t{NV}}^{\t{GS}}=D\p{\v S\c\uv z}^2-\gamma_e\v B\c\v S
\end{align}
is the ground state Hamiltonian of the NV center. Here $\uv z$ is the
natural axis of the NV center.

The hyperfine Hamiltonian is
\begin{align}
  H_{\t{hf}}=\sum_j\f{\gamma_e\gamma_j}{4\pi r_j^3} \sp{\v S\c\v I_j
    -3\p{\v S\c\v r_j}\p{\v I_j\c\v r_j}},
\end{align}
where $\gamma_j$ and $\v I_j$ are, respectively, the gyromagnetic
ratio and spin of nucleus $j$. This Hamiltonian accounts for the
interaction between the NV center and the spin of atomic nuclei.

The nuclear Zeeman Hamiltonian which accounts for the interaction
between the atomic nuclei and the external magnetic field is
\begin{align}
  H_{\t{nZ}}=-\sum_j\gamma_j\v B\c\v I_j.
\end{align}

Finally, the internuclear spin-spin interaction Hamiltonian is
\begin{align}
  H_{\t{nn}}=\sum_{j<k}\f{\gamma_j\gamma_k}{4\pi r_{jk}^3}\sp{\v
    I_j\c\v I_k-3\p{\v I_j\c\v r_{jk}}\p{\v I_k\c\v r_{jk}}}.
\end{align}

Letting $\v B=B_z\uv z$, the Hamiltonian $H_{\t{NV}}^{\t{GS}}$ becomes
\begin{align}
  H_{\t{NV}}^{\t{GS}}=DS_z^2-\gamma_eB_zS_z.
\end{align}
Changing into the frame of this $H_{\t{NV}}^{\t{GS}}$ affects only the
hyperfine Hamiltonian, which becomes
\begin{align}
  H_{\t{hf}}'\approx S_z\sum_j\v A_j\c\v I_j,
\end{align}
where we define the hyperfine field
\begin{align}
  \v A_j=\f{\gamma_e\gamma_j}{4\pi r_j^3}\sp{\uv z-3\p{\uv r_j\c\uv
      z}\uv r_j}.
\end{align}

When restricted to the subspace of $\set{\ket0,\ket{m_s}}$ for NV
center spins ($m_s=\pm1$), we can say that
\begin{align}
  S_z=\f12m_s\p{\sigma_z+1},
\end{align}
where $\sigma_z=\op{m_s}-\op0$. Defining the interaction Hamiltonian
\begin{align}
  H_{\t{int}}=\f12m_s\sigma_z\sum_j\v A_j\c\v I_j
\end{align}
and the effective nuclear Zeeman Hamiltonian
\begin{align}
  H_{\t{nZ}}^{\t{eff}}=-\sum_j\p{\gamma_jB_z\uv z-\f{m_s}2\v A_j}\c\v
  I_j \equiv-\sum_j\v\omega_j\c\v I_j,
\end{align}
we can say that
\begin{align}
  H_{\t{sys}}'=H_{\t{hf}}'+H_{\t{nZ}}+H_{\t{nn}}
  =H_{\t{int}}+H_{\t{nZ}}^{\t{eff}}+H_{\t{nn}}.
\end{align}

\newpage
\section*{Decoupling nuclear spins}

We add an auxiliary radio frequency decoupling field
\begin{align}
  \v B_{\t{rfd}}
  =V_{\t{rfd}}\cos\p{\omega_{\t{rfd}}t-\phi_{\t{rfd}}}\uv n_{\t{rfd}}
\end{align}
with $\omega_{\t{rfd}}\sim\gamma_jB_z\gg\gamma_jV_{\t{rfd}}$, so that
we get the additional Hamiltonian
\begin{align}
  H_\t{rfd}=\sum_j\gamma_jV_{\t{rfd}}\cos\p{\omega_{\t{rfd}}
    t-\phi_{\t{rfd}}}\uv n_{\t{rfd}}\c\v I_j.
\end{align}
Here we neglect the field's coupling to the NV center by the secular
approximation. Defining
\begin{align}
  H_{\t{n}}=H_{\t{nZ}}^{\t{eff}}+H_{\t{rfd}},
\end{align}
the propagator for $H_n$ can be written as
\begin{align}
  U_n=U_{\t{nZ}}^{\t{eff}}\tilde U_{\t{rfd}},
\end{align}
where, after making a rotating wave approximation for $H_{\t{rfd}}$,
changing into the frame of $H_{\t{nZ}}^{\t{eff}}$, and making a
secular approximation with $\omega_j\gg\gamma_jV_{\t{rfd}}$,
\begin{align}
  \tilde H_{\t{rfd}}\approx\sum_j\f12\gamma_jV_{\t{rfd}} R\sp{P\sp{\uv
      n_{\t{rfd}},I\uv\omega_j},
    \p{\phi_{\t{rfd}}-\sp{\omega_{\t{rfd}}-\omega_j}t}I\uv\omega_j}
  \c\v I_j.
\end{align}
The time dependence in $U_{\t{rfd}}$ can be removed in the frame of
\begin{align}
  H_f=-\sum_j\p{\omega_{\t{rfd}}-\omega_j}\uv\omega_j\c\v I_j,
\end{align}
such that
\begin{align}
  \tilde U_{\t{rfd}}=U_fU_\nu,
\end{align}
where
\begin{align}
  H_\nu=\sum_j\v\nu_j\c\v I_j
\end{align}
and
\begin{align}
  \v\nu_j=\f12\gamma_jV_{\t{rfd}} R\sp{P\sp{\uv n,
      I\uv\omega_j},\phi_{\t{rfd}}\uv\omega_j}
  +\p{\omega_{\t{rfd}}-\omega_j}\uv\omega_j\equiv\v\Omega_j+
  \epsilon_j\uv\omega_j,
\end{align}
where $\v\Omega_j\perp\uv\omega_j$. Note that
$\Omega_j=\f12\gamma_jV_{\t{rfd}}\sqrt{1-\abs{\uv
    n\c\uv\omega_j}^2}$. We finally have that
\begin{align}
  U_n=U_{\t{nZ}}^{\t{eff}}U_fU_\nu=U_\omega U_\nu,
\end{align}
with
\begin{align}
  H_\omega=-\omega_{\t{rfd}}\sum_j\uv\omega_j\c\v I_j.
\end{align}
In the fame of $H_\omega$, after making a secular approximation with
$\omega_{\t{rfd}}\gg\gamma_jV_{\t{rfd}}$ and $\gamma_jB_z\gg\abs{\v
  A_j}$ (so $\uv\omega_j\approx\uv z$), the internuclear coupling
Hamiltonian becomes
\begin{align}
  \tilde H_{\t{nn}}&\approx\sum_{j<k}\f{\gamma_j\gamma_k}{4\pi
    r_{jk}^3}
  \f12\sp{1-3\p{\uv r_{jk}\c\uv z}^2}\p{3I_j^zI_k^z-\v I_j\c\v I_k} \\
  &=\sum_{j<k}\f{\gamma_j\gamma_k}{4\pi r_{jk}^3} \f12\sp{1-3\p{\uv
      r_{jk}\c\uv z}^2} \sp{3\p{\v I_j\c\uv z}\p{\v I_k\c\uv z}-\v
    I_j\c\v I_k}.
\end{align}
This Hamiltonian vanishes in a frame where all $\v I_n$ rotate (at a
frequency much greater than the prefactors in $H_{\t{nn}}$) about an
axis which makes an angle $\arccos\p{1/\sqrt3}$ with the $\uv z$ axis,
so that $3\p{\tilde{\v I_j}\c\uv z}\p{\tilde{\v I_k}\c\uv z}=\v
I_j\c\v I_k$. This precession occurs precisely in the frame of $H_\nu$
if $\Omega_j\approx\sqrt2\p{\omega_{\t{rfd}}-\omega_j}$, such that
$\v\nu_j$ makes the necessary angle with the $\uv z$ axis and
$\nu_j\sim\gamma_jV_{\t{rfd}}$ is much greater than the prefactors in
$H_{\t{nn}}$. Alternately, we can say that if $\Delta=\Omega_j/\sqrt2$
and $\delta_j=\p{\omega_{\t{rfd}}-\omega_j}-\Delta$, the nuclear
coupling $H_{\t{nn}}$ vanishes so long as $\delta_j/\Delta\ll 1$.

\newpage
\section*{Dynamic decoupling of the NV center and single nuclear spin
  addressing}

To shield the NV center from environmental noise, we use dynamic
decoupling schemes which periodically flip the NV spin state
$\ket0\leftrightarrow\ket{m_s}$. This decoupling effectively prepends
a modulation function $F\p{t}\in\set{-1,1}$ to the interaction
Hamiltonian, so that
\begin{align}
  H_{\t{int}}=\f12F\p{t}m_s\sigma_z\sum_j\v A_j\c\v I_j.
\end{align}
In the frame of $H_n=H_{\t{nZ}}^{\t{eff}}+H_{\t{rfd}}$,
\begin{align}
  \tilde H_{\t{int}}=\f12F\p{t}m_s\sigma_z\sum_j\tilde{\v A_j}\c\v
  I_j,
\end{align}
where
\begin{align}
  \tilde{\v A_j}=R\sp{R\sp{\v A_j,\omega_{\t{rfd}}I\uv\omega_jt},
    -I\v\nu_jt}.
\end{align}
Expanding $F\p{t}$ in a Fourier series,
\begin{align}
  \tilde H_{\t{int}}=\f12m_s\sigma_z\sum_kf_k\cos\p{k\omega_{DD}t}
  \sum_j\tilde{\v A_j}\c\v I_j.
\end{align}
Defining
\begin{align}
  \v A_n^z=\v A_n\c\uv\omega_n\uv\omega_n, && \v A_n^x=P\sp{\v
    A_n,I\uv\omega_n}, && \v A_n^y=P_\perp\sp{\v A_n,I\uv\omega_n},
\end{align}
when some harmonic
\begin{align}
  k_{DD}\omega_{DD}=\omega_{\t{rfd}}\pm\nu_n
  =\omega_n+\p{1\pm\sqrt3}\Delta
\end{align}
and $\abs{\omega_n-\omega_j}\gg\abs{f_{k_{DD}}\v A_j}$ for all $j\ne
n$ (which we can achieve by making $f_{k_{DD}}$ arbitrarily small), we
get, by the rotating wave approximation, % fixme: prove
\begin{align}
  \tilde H_{\t{int}}\approx\f18m_sf_{k_{DD}}\sigma_z\v a_n^\pm\c\v
  I_j,
\end{align}
where
\begin{align}
  \v a_n^\pm=P\sp{\v A_n^x,I\uv\nu_n}\pm P_\perp\sp{\v
    A_n^y,I\uv\nu_n} =P\sp{P\sp{\v A_n,I\uv\omega_n},I\uv\nu_n}\pm
  P_\perp\sp{P_\perp\sp{\v A_n,I\uv\omega_n},I\uv\nu_n}.
\end{align}
If instead some harmonic $k_{DD}\omega_{DD}=\nu_n$, then
\begin{align}
  \tilde H_{\t{int}}\approx\f14m_sf_{k_{DD}}\sigma_z\v a_n^z\c\v I_n,
\end{align}
with
\begin{align}
  \v a_n^z=P\sp{\v A_n^z,I\uv\nu_n} =P\sp{\v
    A_n\c\uv\omega_n\uv\omega_n,I\uv\nu_n}.
\end{align}

Using this information, we can measure all $\v A_j$.

\newpage
\section*{Nuclear spin control}

We applying a radio frequency control field with the Hamiltonian
\begin{align}
  H_{\t{rfc}}=\sum_j\gamma_jV_{\t{rfc}}\cos\p{\omega_{\t{rfc}}t-\phi_{\t{rfc}}}
  \uv m_{\t{rfc}}\c\uv I_j.
\end{align}
Using
$\gamma_nV_{\t{rfc}}\ll\abs{\omega_{\t{rfd}}-\omega_n}\ll\omega_{\t{rfd}}$
and $\gamma_nV_{\t{rfc}}\ll\abs{\omega_n-\omega_j}$, when
\begin{align}
  \omega_{\t{rfc}}=\omega_{\t{rfd}}\pm\nu_n=\omega_n+\p{1\pm\sqrt3}\Delta
\end{align}
we effectively have
\begin{align}
  H_{\t{ctl}}\approx\f14\gamma_nV_{\t{rfc}}\v b_n^\pm\c\v I_n,
\end{align}
with
\begin{align}
  \v b_n^\pm=P\sp{\v m_n^x,I\uv\nu_n}\pm P_\perp\sp{\v m_n^y,
    I\uv\nu_n},
\end{align}
and
\begin{align}
  \v m_n^x=R\sp{P\sp{\uv m_{\t{rfc}},I\uv\omega_n},
    \phi_{\t{rfc}}I\uv\omega_n}, && \v m_n^y=R\sp{P_\perp\sp{\uv
      m_{\t{rfc}},I\uv\omega_n}, \phi_{\t{rfc}}I\uv\omega_n}, && \v
  m_n^z=\uv m_{\t{rfc}}\c\uv\omega_n\uv\omega_n.
\end{align}
Expanding,
\begin{align}
  \v b_n^\pm=P\sp{R\sp{P\sp{\uv m_{\t{rfc}},I\uv\omega_n}, \phi
      I\uv\omega_n},I\uv\nu_n}\pm P_\perp\sp{R\sp{P_\perp\sp{\uv
        m_{\t{rfc}},I\uv\omega_n},\phi I\uv\omega_n},I\uv\nu_n}.
\end{align}

If instead $\omega_{\t{rfc}}=\nu_n$, then
\begin{align}
  H_{\t{ctl}}\approx\f12\gamma_nV_{\t{rfc}}\v b_n^z\c\v I_n,
\end{align}
with
\begin{align}
  \v b_n^z=R\sp{P\sp{\v m_n^z,I\uv\nu_n},-\phi_{\t{rfc}}I\uv\nu_n}
  =R\sp{P\sp{\uv m_{\t{rfc}}\c\uv\omega_n\uv\omega_n,I\uv\nu_n},
    -\phi_{\t{rfc}}I\uv\nu_n}.
\end{align}

\newpage
\section*{Individual nuclear spin coupling and control summary}

To summarize, we have the following tools at hand to couple the NV
center to nuclei:
\begin{align}
  H_{\t{int}}^\pm=\f18m_sf_{k_{DD}}\sigma_z\v a_n^\pm\c\v I_n
  =\alpha_n^\pm\sigma_z\uv a_n^\pm\c\v I_n, &&
  H_{\t{int}}^z=\f14m_sf_{k_{DD}}\sigma_z\v a_n^z\c\v I_n,
  =\alpha_n^z\sigma_z\uv a_n^z\c\v I_n
\end{align}
where
\begin{align}
  \v a_n^\pm=P\sp{\v A_n^x,I\uv\nu_n}\pm P_\perp\sp{\v
    A_n^y,I\uv\nu_n} =P\sp{P\sp{\v A_n,I\uv\omega_n},I\uv\nu_n}\pm
  P_\perp\sp{P_\perp\sp{\v A_n,I\uv\omega_n},I\uv\nu_n}.
\end{align}
and
\begin{align}
  \v a_n^z=P\sp{\v A_n^z,I\uv\nu_n} =P\sp{\v
    A_n\c\uv\omega_n\uv\omega_n,I\uv\nu_n}.
\end{align}

In order to control individual nuclei, we have:
\begin{align}
  H_{\t{ctl}}\approx\f14\gamma_nV_{\t{rfc}}\v b_n^\pm\c\v I_n
  =\beta_n^\pm\uv b_n^\pm\c\v I_n, &&
  H_{\t{ctl}}\approx\f12\gamma_nV_{\t{rfc}}\v b_n^z\c\v I_n
  =\beta_n^z\uv b_n^\pm\c\v I_n,
\end{align}
where
\begin{multline}
  \v b_n^\pm=P\sp{\v m_n^x,I\uv\nu_n}\pm P_\perp\sp{\v m_n^y,
    I\uv\nu_n} \\
  =P\sp{R\sp{P\sp{\uv m_{\t{rfc}},I\uv\omega_n}, \phi
      I\uv\omega_n},I\uv\nu_n}\pm P_\perp\sp{R\sp{P_\perp\sp{\uv
        m_{\t{rfc}},I\uv\omega_n},\phi I\uv\omega_n},I\uv\nu_n},
\end{multline}
and
\begin{align}
  \v b_n^z=R\sp{P\sp{\v m_n^z,I\uv\nu_n},-\phi_{\t{rfc}}I\uv\nu_n}
  =R\sp{P\sp{\uv m_{\t{rfc}}\c\uv\omega_n\uv\omega_n,I\uv\nu_n},
    -\phi_{\t{rfc}}I\uv\nu_n}.
\end{align}

Here we have full control over the orientation of $\uv\nu_n$
($I\uv\nu_n$), with the restriction that it makes an angle
$\theta_m=\arccos\p{1/\sqrt3}\approx0.3\pi$ with $\uv z$ ($\uv x\uv
y$).

A choice of $\uv\nu_n$ fixes $\uv a_n^z$, which will always make an
angle $\pi/2-\theta_m\approx0.2\pi$ with $\uv z$. We can rotate
$\uv\nu_n$ in $\uv x\uv y$ to change the directions of $\uv a_n^\pm$,
both of which will always lie in $I\uv\nu_n$. Unless $P\sp{\v A_n,\uv
  x\uv y}=\v 0$, it should be possible to orient $\uv a_n^\pm$ in the
$\uv x\uv y$ plane, at an angle of $\pi/2$ with $\uv a_n^z$. We can
therefore effectively create an interaction Hamiltonian of the form
\begin{align}
  H_{\t{int},n}=h\sigma_z^{NV}\sigma_{z'}^n,
\end{align}
where $\uv z'$ lies in the $I\uv\nu_j$ plane. We can, however,
initially rotate one of the spin axes into the other, perform logical
operations, and then rotate back to get the effective Hamiltonian
\begin{align}
  \tilde H_{\t{int},n}=R^\dagger
  H_{\t{int},n}R=h\sigma_z^{NV}\sigma_z^n.
\end{align}

The directions of $\uv b_n^z$ and one of $\uv b_n^\pm$ may be
determined within $I\uv\nu_n$ at will, so we can effectively create a
control Hamiltonian
\begin{align}
  H_{\t{ctl},n}=h_{z'}\sigma_{z'}^n+h_{x'}\sigma_{x'}^n.
\end{align}
Finally, we have arbitrary control over the NV center with the
Hamiltonians
\begin{align}
  H_{NV}=h_z\sigma_z^{NV}+h_x\sigma_x^{NV}+h_y\sigma_y^{NV}.
\end{align}

\newpage
\section*{Single qubit logic gates}

In this section we work in the following basis:
\begin{align}
  \ket\u=\m{1\\0}, && \ket\d=\m{0\\1}.
\end{align}

We have Hamiltonians of the form $H_\alpha=h\sigma_\alpha$, with the
respective propagators $U_\alpha=\exp\p{-iH_\alpha t}$. We can use
these propagators to implement the rotation operators
\begin{align}
  R_z\p\phi=\m{e^{-i\phi/2}&0\\0&e^{i\phi/2}}=U_z\p{\f\phi2},
\end{align}
\begin{align}
  R_x\p\phi=\m{\cos\p{\phi/2}&-i\sin\p{\phi/2}\\
    -i\sin\p{\phi/2}&\cos\p{\phi/2}}=U_x\p{\f\phi2},
\end{align}
and
\begin{align}
  R_y\p\phi=\m{\cos\p{\phi/2}&-\sin\p{\phi/2}\\
    \sin\p{\phi/2}&\cos\p{\phi/2}}=U_y\p{\f\phi2}.
\end{align}
Particularly interesting special cases of these operators include the
phase shift and bit-flit gates
\begin{align}
  Z=\m{1&0\\0&-1}\cong R_z\p\pi, && X=\m{0&1\\1&0}\cong R_x\p\pi.
\end{align}

When we have $H_{\t{HG}}=h\p{\uv z+\uv x}/\sqrt2$, we get the
propagator
\begin{align}
  U_{\t{HG}}=\cos\p{ht}-i\sin\p{ht}\f{\sigma_z+\sigma_x}{\sqrt2}
\end{align}
which allows us to implement the Hadamard gate
\begin{align}
  \t{HG}=\f{1}{\sqrt2}\m{1&1\\1&-1}\cong U_{\t{HG}}\p{\f\pi2}.
\end{align}

\newpage
\section*{Two qubit logic gates}

In this section we work in the following basis:
\begin{align}
  \ket{\u\u}=\m{1\\0\\0\\0}, && \ket{\u\d}=\m{0\\1\\0\\0}, &&
  \ket{\d\u}=\m{0\\0\\1\\0}, && \ket{\d\d}=\m{0\\0\\0\\1}.
\end{align}

We have Hamiltonians of the form
$H_{\alpha\beta}=h\sigma_\alpha^1\sigma_\beta^2$, with the respective
propagators $U_{\alpha\beta}\p{ht}=\exp\p{-iH_{\alpha\beta}t}$. We can
use these propagators together with the single-qubit phase shift gates
to implement the controlled phase shift gates
\begin{align}
  \t{c}R_{\u\u}\p\phi
  &=\m{e^{i \phi} & 0 & 0 & 0 \\
    0 & 1 & 0 & 0 \\
    0 & 0 & 1 & 0 \\
    0 & 0 & 0 & 1}, & \t{c}R_{\u\d}\p\phi
  &=\m{1 & 0 & 0 & 0 \\
    0 & e^{i \phi} & 0 & 0 \\
    0 & 0 & 1 & 0 \\
    0 & 0 & 0 & 1}, \\
  \t{c}R_{\d\u}\p\phi
  &=\m{1 & 0 & 0 & 0 \\
    0 & 1 & 0 & 0 \\
    0 & 0 & e^{i \phi} & 0 \\
    0 & 0 & 0 & 1} & \t{c}R\p\phi\equiv\t{c}R_{\d\d}\p\phi
  &=\m{1 & 0 & 0 & 0 \\
    0 & 1 & 0 & 0 \\
    0 & 0 & 1 & 0 \\
    0 & 0 & 0 & e^{i \phi}}.
\end{align}
We also define the controlled phase flip ($\t{c}Z$) and controlled NOT
($\t{cNOT}$) gates
\begin{align}
  \t{c}Z&=\m{1 & 0 & 0 & 0 \\
    0 & 1 & 0 & 0 \\
    0 & 0 & 1 & 0 \\
    0 & 0 & 0 & -1}, &
  \t{cNOT}&=\m{1 & 0 & 0 & 0 \\
    0 & 1 & 0 & 0 \\
    0 & 0 & 0 & 1 \\
    0 & 0 & 1 & 0},
\end{align}
and, finally, the SWAP, $\sqrt{\t{SWAP}}$, $i$SWAP, and
$\sqrt{i\t{SWAP}}$ gates
\begin{align}
  \t{SWAP}
  &=\m{1 & 0 & 0 & 0 \\
    0 & 0 & 1 & 0 \\
    0 & 1 & 0 & 0 \\
    0 & 0 & 0 & 1}, & \sqrt{\t{SWAP}}
  &=\m{1 & 0 & 0 & 0 \\
    0 & \p{1+i}/2 & \p{1-i}/2 & 0 \\
    0 & \p{1-i}/2 & \p{1+i}/2 & 0\\
    0 & 0 & 0 & 1} \\
  i\t{SWAP}
  &=\m{1 & 0 & 0 & 0 \\
    0 & 0 & i & 0 \\
    0 & i & 0 & 0 \\
    0 & 0 & 0 & 1}, & \sqrt{i\t{SWAP}}
  &=\m{1 & 0 & 0 & 0 \\
    0 & 1/\sqrt2 & i/\sqrt2 & 0 \\
    0 & i/\sqrt2 & 1/\sqrt2 & 0 \\
    0 & 0 & 0 & 1}.
\end{align}

The swap gate can be used to generate any two-qubit operation
$\mathcal O_{m,n}$ between spins $n$ and $m$ through an intermediate
spin $p$ via
\begin{align}
  \mathcal O_{m,n}=\t{SWAP}_{p,m}\mathcal O_{p,n}\t{SWAP}_{p,m}.
\end{align}

\newpage
\section*{Gate generation}

We have a gate $G$, which is generated by the propagator
\begin{align}
  U\sp{G,t}=\exp\p{-i\int_0^tdt'H\sp{G,t'}}.
\end{align}
We wish to solve for $H\sp{G,t}$ so that $U\sp{G,t_0}=G$. If we assume
$H\sp{G}$ is independent of time, then
\begin{align}
  G=\exp\p{-it_0H\sp{G}},
\end{align}
and so
\begin{align}
  t_0H\sp{G}=i\ln G. \label{lnG}
\end{align}
Knowing that $t_0H\sp{G}$ takes the form
\begin{align}
  t_0H\sp{G}
  =\sum_{\alpha,\beta}h_{\alpha,\beta}^{1,2}\sigma_\alpha^1\sigma_\beta^2,
  \label{H_G}
\end{align}
where $\alpha,\beta\in\set{I,x,y,z}$ and $n\in\set{1,2}$ (with
$\sigma_I\equiv I_2$), we have reduced finding $H\sp{G}$ to a linear
algebra problem: pick a gate $G$, compute $i\ln G$, and find coupling
strengths $h_{\alpha,\beta}^{1,2}$ in (\ref{H_G}) which satisfy
(\ref{lnG}).

Using this technique, up to global phase we can find that
\begin{align}
  t_0H\sp{\t{c}R_{\u\u}\p\phi}&=-\f\phi4\p{\sigma_z^1+\sigma_z^2
    +\sigma_z^1\sigma_z^2}, &
  t_0H\sp{\t{c}R_{\u\d}\p\phi}&=\f\phi4\p{-\sigma_z^1+\sigma_z^2
    +\sigma_z^1\sigma_z^2}, \\
  t_0H\sp{\t{c}R_{\d\u}\p\phi}&=\f\phi4\p{\sigma_z^1-\sigma_z^2
    +\sigma_z^1\sigma_z^2}, & t_0H\sp{\t{c}R_{\d\d}\p\phi}
  &=\f\phi4\p{\sigma_z^1+\sigma_z^2 -\sigma_z^1\sigma_z^2},
\end{align}
\begin{align}
  t_0H\sp{\t{c}Z}
  &=\f\pi4\p{\sigma_z^1+\sigma_z^2-\sigma_z^1\sigma_z^2}, &
  t_0H\sp{\t{cNOT}}
  &=\f\pi4\p{\sigma_z^1+\sigma_x^2-\sigma_z^1\sigma_x^2},
\end{align}
\begin{align}
  t_0H\sp{\t{SWAP}}&=\f\pi4\p{\sigma_z^1\sigma_z^2
    +\sigma_x^1\sigma_x^2+\sigma_y^1\sigma_y^2}, &
  t_0H\sp{\sqrt{\t{SWAP}}}&=\f12t_0H\sp{\t{SWAP}}, \\
  t_0H\sp{i\t{SWAP}}&=-\f\pi4\p{\sigma_x^1\sigma_x^2
    +\sigma_y^1\sigma_y^2}, &
  t_0H\sp{\sqrt{i\t{SWAP}}}&=\f12t_0H\sp{i\t{SWAP}},
\end{align}

\newpage
\section*{Nuclear placement on a diamond lattice}

The positions $\v s$ of any nucleus in a diamond lattice can be
written in terms of a reduced position $\v r$ as
\begin{align}
  \v s=\f{a}2\v r=\f{a}2\p{b\v a_0+\l\v a_1+m\v a_2+n\v a_3} \equiv
  \f{a}2\sp{b\v a_0+\sum_ic_i\v a_i}
\end{align}
for $b\in\set{0,1}$; $\l,m,n\in\mathbb{Z}$;
\begin{align}
  \v a_0=\f12\p{\uv x+\uv y+\uv z}; && \v a_1=\uv y+\uv z; && \v
  a_2=\uv z+\uv x; && \v a_3=\uv x+\uv y;
\end{align}
and $a\approx0.35668~\t{nm}$. We will find it useful to note that:
\begin{align}
  \v a_0\c\v a_0=\f34, && \v a_0\c\v a_i=1, && \v a_i\c\v a_i=2, && \v
  a_i\c\v a_{j\ne i}=1.
\end{align}
The positions for which $\l=m=n=0$ are reserved for the NV center.

\section*{Conditions for larmor equality}

Two nuclei are said to be {\it larmor equal}, or a {\it larmor pair},
if they have the same effective larmor frequency
\begin{align}
  \omega_j=\abs{\gamma_j B_z\uv a_0-\f{m_s}2\v A_j}.
\end{align}
This equality occurs when the reduced positions $\v r$ and $\v s'$ of
two $^{13}$C nuclei simultaneously satisfy
\begin{align}
  \abs{\v r\c\v a_0}=\abs{\v r'\c\v a_0}, \label{condA0}
\end{align}
and
\begin{align}
  \abs{\v r-\v r\c\uv a_0\uv a_0}^2 =\abs{\v r'-\v r'\c\uv a_0\uv
    a_0}^2. \label{condB0}
\end{align}

Expanding condition (\ref{condA0}) yields
\begin{align}
  \abs{\f34b+\l+m+n}=\abs{\f34b'+\l'+m'+n'}. \label{condA}
\end{align}
The fact that all variables here are integers implies that
\begin{align}
  b=b', \label{condAa}
\end{align}
\begin{align}
  \abs{\l+m+n}=\abs{\l'+m'+n'}. \label{condAb}
\end{align}

We can expand part of (\ref{condB0}) as
\begin{align}
  \v r-\v r\c\uv a_0\uv a_0
  &=\v r-\v r\c\v a_0\v a_0a_0^{-2} \\
  &=b\v a_0+\sum_ic_i\v a_i-\p{\f34b+\sum_ic_i}\v a_0\f43 \\
  &=b\v a_0+\sum_ic_i\v a_i-b\v a_0-\f43\sum_ic_i\v a_0 \\
  &=\sum_ic_i\p{\v a_i-\f43\v a_0}.
\end{align}
Letting $\set{i,j,k}=\set{1,2,3}$, we can simplify this result to
\begin{align}
  \v r-\v r\c\uv a_0\uv a_0
  &=\sum_ic_i\sp{\uv x^j+\uv x^k-\f23\p{\uv x^i+\uv x^j+\uv x^k}} \\
  &=\f13\sum_ic_i\p{-2\uv x^i+\uv x^j+\uv x^k} \\
  &=\f13\sum_i\p{-2c_i+c_j+c_k}\uv x^i.
\end{align}
The squared magnitude of this quantity is
\begin{align}
  \abs{\v r-\v r\c\uv a_0\uv a_0}^2
  &=\f19\sum_i\p{-2c_i+c_j+c_k}^2 \\
  &=\f19\sum_i\p{4c_i^2+c_j^2+c_k^2-4c_ic_j-4c_ic_k+2c_jc_k} \\
  &=\f23\sp{\p{\l^2+m^2+n^2}-\p{mn+n\l+\l m}} \\
  &=\l^2+m^2+n^2-\f13\p{\l+m+n}^2.
\end{align}
Condition (\ref{condB0}) is therefore equivalently
\begin{align}
  \l^2+m^2+n^2-\f13\p{\l+m+n}^2
  ={\l'}^2+{m'}^2+{n'}^2-\f13\p{\l'+m'+n'}^2. \label{condB}
\end{align}
Larmor equality of two nuclei therefore equivalent to simultaneously
satisfying (\ref{condAa}), (\ref{condAb}), and (\ref{condB}).

\section*{Search space restrictions from a hyperfine cutoff}

We may wish to restrict our search for larmor pairs to nuclei for
which
\begin{align}
  \abs{\v A}>A_{\t{min}}, \label{condC0}
\end{align}
where
\begin{align}
  \v A=\f{\gamma_e\gamma_c}{4\pi s^3}\sp{\uv a_0-3\p{\uv s\c\uv
      a_0}\uv s} =\f{2\gamma_e\gamma_c}{\pi a^3r^3}\sp{\uv a_0-3\p{\uv
      r\c\uv a_0}\uv r}\equiv \f{\alpha}{r^3}\sp{\uv a_0-3\p{\uv
      r\c\uv a_0}\uv r}.
\end{align}
We can compute
\begin{align}
  \abs{\v A}^2=\f{\alpha^2}{r^6}\sp{1+9\p{\uv r\c\uv a_0}^2-6\p{\uv
      r\c\uv a_0}^2}=\f{\alpha^2}{r^6}\sp{1+3\p{\uv r\c\uv a_0}^2}.
\end{align}
This quantity is minimally
\begin{align}
  \floor{\abs{\v A}^2}=\f{\alpha^2}{r^6},
\end{align}
which means
\begin{align}
  \abs{\v A} \ge \f{\abs{\alpha}}{r^3} > A_{\t{min}}.
\end{align}
We can therefore restrict our search to nuclei for which
$\abs{\alpha}/r^3>A_{\t{min}}$, or equivalently
\begin{align}
  r^2<\p{\f{\abs{\alpha}}{A_{\t{min}}}}^{2/3}. \label{condC1}
\end{align}
We can expand $r^2$ as
\begin{align}
  r^2=\v r\c\v r
  &=\f34b^2+b\p{\l+m+n}+2\l^2+2m^2+2n^2+2mn+2n\l+2\l m \\
  &=b\p{\f34+\l+m+n}+\l^2+m^2+n^2+\p{\l+m+n}^2.
\end{align}
If $b=0$, then
\begin{align}
  r^2=\l^2+m^2+n^2+\p{\l+m+n}^2<\p{\f{\abs{\alpha}}{A_{\t{min}}}}^{2/3},
\end{align}
which means that each of $\l$, $m$, and $n$ must satisfy
\begin{align}
  \abs{c_i}<\p{\f{\abs{\alpha}}{A_{\t{min}}}}^{1/3}. \label{limit0}
\end{align}
If $b=1$, then
\begin{align}
  r^2&=\f34+\l+m+n+\l^2+m^2+n^2+\p{\l+m+n}^2 \\
  &=\p{\l+\f12}^2+\p{m+\f12}^2+\p{n+\f12}^2+\p{\l+m+n}^2,
\end{align}
and therefore each of $\l$, $m$, and $n$ must satisfy
\begin{align}
  \abs{c_i+\f12}<\p{\f{\abs{\alpha}}{A_{\t{min}}}}^{1/3},
\end{align}
which also implies
\begin{align}
  \abs{c_i}<\p{\f{\abs{\alpha}}{A_{\t{min}}}}^{1/3}+\f12.
  \label{limit1}
\end{align}
In performing a search for larmor pairs, we can use restriction
(\ref{limit1}) to limit our search space.

\section*{Computing the probability of occurrence}

If we have a set of $R$ lattice sites indexed by $(b,\l,m,n)$ mutually
satisfying (\ref{condA0}) and (\ref{condB0}), then the probability of
filling exactly $r$ of them with $^{13}$C nuclei is
\begin{align}
  P_{R,r}=p^r\p{1-p}^{R-r}\m{R\\r}=\f{R!~p^r\p{1-p}^{R-r}}{r!\p{R-r}!},
\end{align}
where $p$ is the probability that any particular site with a $^{13}$C
nucleus, i.e. the relative abundance of $^{13}$C. The probability of
having at least two $^{13}$C nuclei in these sites is therefore
\begin{align}
  P_{R,r\ge2}=\sum_{r=2}^RP_{R,r}=1-\p{P_{R,0}+P_{R,1}}.
\end{align}
If we have many such sets of lattice sites, then the total probability
$\bar P$ of having at least two sites filled within at least one set
of sites is
\begin{align}
  \bar P=1-\prod_R\p{1-P_{R,r\ge2}} =1-\prod_R\p{P_{R,0}+P_{R,1}}
  =1-\prod_R\p{1-p}^R\p{1+\f{Rp}{1-p}}.
\end{align}

\newpage
\section*{Singlet-triplet qubit initialization}

We can generate individual singlet and triplet-0 states via the
entanglement operator
\begin{align}
  \E=\f1{\sqrt2}
  \m{1 & 0 & 0 & 1 \\
    0 & 1 & 1 & 0 \\
    0 & -1 & 1 & 0 \\
    -1 & 0 & 0 & 1},
\end{align}
which maps $\ket{\u\d}\to\p{\ket{\u\d}-\ket{\d\u}}/\sqrt2\equiv\ket S$
and $\ket{\d\u}\to\p{\ket{\u\d}+\ket{\d\u}}/\sqrt2\equiv\ket T$. The
Hamiltonians to generate $\E$ and its inverse are
\begin{align}
  t_0H\sp{\mathcal E}&=-\f\pi4\sigma_y^1\sigma_x^2, & t_0H\sp{\mathcal
    E^\dag}&=\f\pi4\sigma_y^1\sigma_x^2.
\end{align}
We can generate superpositions of singlet and triplet-0 states of the
form
\begin{align}
  \ket\psi=\cos\theta\ket S+e^{i\phi}\sin\theta\ket T
\end{align}
via
\begin{align}
  \ket\psi=\E\sp{\cos\theta\ket{\u\d} +e^{i\phi}\sin\theta\ket{\d\u}},
\end{align}
which is in turn given by
\begin{align}
  \ket\psi\cong\E cR_{\d\u}\p{\phi}U_{yx}\p\theta\ket{\u\d}.
\end{align}
We therefore define the qubit initialization operator
\begin{multline}
  \mathcal Q\p{\theta,\phi}
  =\E cR_{\d\u}\p{\phi}U_{xx}\p\theta \\
  =\f{e^{-i\phi/4}}{\sqrt2}
  \m{ \cos\theta+\sin\theta & 0 & 0 & \cos\theta-\sin\theta \\
    0 & \cos\theta+e^{i\phi}\sin\theta &
    e^{i\phi}\cos\theta-\sin\theta & 0 \\
    0 & -\cos\theta+e^{i\phi}\sin\theta &
    e^{i\phi}\cos\theta+\sin\theta & 0 \\
    -\cos\theta+\sin\theta & 0 & 0 & \cos\theta+\sin\theta}
\end{multline}
so that
\begin{align}
  \mathcal Q\p{\theta,\phi}\ket{\u\d} \cong\cos\theta\ket S
  +e^{i\phi}\sin\theta\ket T.
\end{align}

\newpage
\section*{Singlet-triplet single qubit gates}

Letting $I_r=\op{\u\u}+\op{\d\d}$, we can implement the
singlet-triplet rotation gates
\begin{align}
  R_z^{ST}\p\phi=e^{-i\phi/2}\op S+e^{i\phi/2}\op T+I_r
  =\m{1 & 0 & 0 & 0 \\
    0 & \cos\p{\phi/2} & i \sin\p{\phi/2} & 0 \\
    0 & i \sin\p{\phi/2} & \cos\p{\phi/2} & 0 \\
    0 & 0 & 0 & 1},
\end{align}
\begin{multline}
  R_x^{ST}\p\phi=\cos\p{\f\phi2}\p{\op S+\op T}
  -i\sin\p{\f\phi2}\p{\op{T}{S}+\op{S}{T}}+I_r \\
  =\m{1 & 0 & 0 & 0 \\
    0 & e^{-i\phi/2} & 0 & 0 \\
    0 & 0 & e^{i\phi/2} & 0 \\
    0 & 0 & 0 & 1},
\end{multline}
\begin{multline}
  R_y^{ST}\p\phi=\cos\p{\f\phi2}\p{\op S+\op T}
  +\sin\p{\f\phi2}\p{-\op{S}{T}+\op{T}{S}}+I_r \\
  =\m{1 & 0 & 0 & 0 \\
    0 & \cos\p{\phi/2} & -\sin\p{\phi/2} & 0 \\
    0 & \sin\p{\phi/2} & \cos\p{\phi/2} & 0 \\
    0 & 0 & 0 & 1},
\end{multline}
which are generated by the Hamiltonians
\begin{align}
  t_0H\sp{R_z^{ST}\p\phi}=-\f\phi4\p{\sigma_x^1\sigma_x^2
    +\sigma_y^1\sigma_y^2},
\end{align}
\begin{align}
  t_0H\sp{R_x^{ST}\p\phi}=\f\phi4\p{\sigma_z^1-\sigma_z^2},
\end{align}
\begin{align}
  t_0H\sp{R_y^{ST}\p\phi}=\f\phi4\p{\sigma_y^1\sigma_x^2
    -\sigma_x^1\sigma_y^2}.
\end{align}
As the two terms in each of these Hamiltonians commute, the
corresponding operations may be applied sequentially.  The phase-flip,
bit-flip, and Hadamard gates are, respectively,
\begin{align}
  Z^{ST}=\op S-\op T+iI_r\cong R_z^{ST}\p\pi,
\end{align}
\begin{align}
  X^{ST}=\op{S}{T}+\op{T}{S}+iI_r\cong R_x^{ST}\p\pi,
\end{align}
\begin{align}
  \t{HG}^{ST}=\f1{\sqrt2}\sp{\p{\ket S+\ket T}\bra S +\p{\ket S-\ket
      T}\bra T}+iI_r\cong R_y^{ST}\p{\f\pi2}R_z^{ST}\p\pi.
\end{align}
Alternately, within the singlet-triplet subspace,
\begin{align}
  Z^{ST}\cong\t{SWAP}^{1,2}, && X^{ST}=Z^1, &&
  \t{HG}^{ST}=Z^1{\E^\dag}^{1,2}.
\end{align}

\newpage
\section*{Singlet-triplet / NV-center two qubit gates}

If we simply wish to read out a singlet-triplet qubit state, it is
sufficient to perform the operation
\begin{align}
  \mathcal R=\p{X\t{HG}}^{NV}\t{SWAP}^{NV,1}
\end{align}
and measure the state of the NV center. Here we can identify the
generating Hamiltonian
\begin{align}
  t_0H\sp{XHG}=\f\pi4\sigma_y.
\end{align}
This measurement procedure will leave one carbon nucleus in the
original state of the NV center, and will collapse the second carbon
nucleus onto an unknown state.

In order to perform coherent computations with the singlet-triplet
qubit, we construct an NV / singlet-triplet (ST) SWAP operation:
\begin{align}
  \t{SWAP}^{NV,ST}=\E^{1,2}\t{cNOT}^{1,2}
  \p{X\t{HG}}^{NV}\t{cNOT}^{NV,2}\t{SWAP}^{NV,1}.
\end{align}
In practice, we cannot couple nuclear spins directly, so we perform
the operation
\begin{align}
  \t{SWAP}^{NV,ST}=\t{SWAP}^{NV,1}\E^{NV,2}\t{cNOT}^{NV,2}
  \t{SWAP}^{NV,1}\p{X\t{HG}}^{NV}\t{cNOT}^{NV,2}\t{SWAP}^{NV,1}.
\end{align}
Wanting to replace SWAP operations with $i$SWAP operations, we can
equivalently rearrange the above to
\begin{align}
  \t{SWAP}^{NV,ST}=\p{X\t{HG}}^{NV}\t{SWAP}^{NV,1}\E^{NV,2}
  \t{cNOT}^{NV,2}{i\t{SWAP}^\dag}^{NV,1}\t{cNOT}^{NV,2}i\t{SWAP}^{NV,1},
\end{align}
and in turn
\begin{multline}
  \t{SWAP}^{NV,ST}\cong \\
  \exp\p{i\f\pi4\sigma_x^{NV}\sigma_x^{ST}}
  \p{X\t{HG}}^{NV}i\t{SWAP}^{NV,1}\E^{NV,2}
  \t{cNOT}^{NV,2}{i\t{SWAP}^\dag}^{NV,1}\t{cNOT}^{NV,2}i\t{SWAP}^{NV,1},
  \label{swap_no_zz}
\end{multline}
where
\begin{align}
  \sigma_x^{ST}=\op{S}{T}+\op{T}{S}+iI_r
  \cong\f12\p{\sigma_z^1-\sigma_z^2}.
\end{align}
The construction in (\ref{swap_no_zz}) avoids couplings of the form
$\sigma_z^{NV}\sigma_z^j$.

Alternately, we can construct the SWAP gate from controlled-NOT
operations as
\begin{align}
  \t{SWAP}^{NV,ST}=\t{cNOT}^{NV,ST}\t{cNOT}^{ST,NV}\t{cNOT}^{NV,ST},
\end{align}
where
\begin{align}
  \t{cNOT}^{NV,ST}=\t{c}Z^{NV,1}, &&
  \t{cNOT}^{ST,NV}=\E^{1,2}\t{cNOT}^{1,NV}{\E^\dag}^{1,2}.
\end{align}
We can expand
\begin{align}
  \t{cNOT}^{ST,NV}&=\t{SWAP}^{NV,1}\E^{NV,2}\t{SWAP}^{NV,1}\t{cNOT}^{1,NV}
  \t{SWAP}^{NV,1}{\E^\dag}^{NV,2}\t{SWAP}^{NV,1} \\
  &=\t{SWAP}^{NV,1}\E^{NV,2}\t{cNOT}^{NV,1}{\E^\dag}^{NV,2}\t{SWAP}^{NV,1}.
\end{align}
Therefore
\begin{align}
  \t{SWAP}^{NV,ST}=\t{c}Z^{NV,1}\t{SWAP}^{NV,1}
  \E^{NV,2}\t{cNOT}^{NV,1}{\E^\dag}^{NV,2}
  \t{SWAP}^{NV,1}\t{c}Z^{NV,1},
\end{align}
which can further be reduced to
\begin{multline}
  \t{SWAP}^{NV,ST}= \\
  R_z^{NV}\p{\f\pi2}R_z^1\p{\f\pi2}{i\t{SWAP}^\dag}^{NV,1}
  \E^{NV,2}\t{cNOT}^{NV,1}{\E^\dag}^{NV,2}
  i\t{SWAP}^{NV,1}R_z^1\p{-\f\pi2}R_z^{NV}\p{-\f\pi2}.
  \label{swap_no_zz_cnot}
\end{multline}
The constructions in (\ref{swap_no_zz}) and (\ref{swap_no_zz_cnot})
are theoretically equal (up to global phase), but may have different
fidelities in practice.

Note that in order to function properly, $\t{SWAP}^{NV,ST}$ requires
the target carbon nuclei to be in a singlet-triplet state prior to
operation.

\newpage
\section*{New notation for NV/ST operations}

We introduce a new notation for operations:
\begin{align}
  U\sp{t_0H}=\exp\p{-it_0 H}.
\end{align}
In this notation,
\begin{align}
  R_{\uv n}\p\phi=U\sp{\f\phi2\sigma_{\uv n}},
\end{align}
\begin{align}
  \t{cNOT}^{m,n}=U\sp{\f\pi4\p{\sigma_z^m+\sigma_x^n
      -\sigma_z^m\sigma_x^n}}
  =U\sp{\f\pi4\sigma_z^m}U\sp{\f\pi4\sigma_x^n}
  U\sp{-\f\pi4\sigma_z^m\sigma_x^n}
\end{align}
\begin{align}
  i\t{SWAP}^{m,n}=U\sp{-\f\pi4\p{\sigma_x^m\sigma_x^n
      +\sigma_y^m\sigma_y^n}} =U\sp{-\f\pi4\sigma_y^m\sigma_y^n}
  U\sp{-\f\pi4\sigma_x^m\sigma_x^n},
\end{align}
\begin{align}
  \E^{m,n}=U\sp{-\f\pi4\sigma_y^m\sigma_x^n},
\end{align}
and therefore
\begin{multline}
  \t{SWAP}^{NV,ST}= U\sp{\f\pi4\sigma_z^{NV}}U\sp{\f\pi4\sigma_z^1}
  U\sp{\f\pi4\sigma_x^{NV}\sigma_x^1}
  U\sp{\f\pi4\sigma_y^{NV}\sigma_y^1}
  U\sp{-\f\pi4\sigma_y^{NV}\sigma_x^2} \\
  U\sp{\f\pi4\sigma_z^{NV}}U\sp{\f\pi4\sigma_x^1}
  U\sp{-\f\pi4\sigma_z^{NV}\sigma_x^1}
  U\sp{\f\pi4\sigma_y^{NV}\sigma_x^2} \\
  U\sp{-\f\pi4\sigma_y^{NV}\sigma_y^1}
  U\sp{-\f\pi4\sigma_x^{NV}\sigma_x^1}
  U\sp{-\f\pi4\sigma_z^1}U\sp{-\f\pi4\sigma_z^{NV}}.
\end{multline}

\section*{Optimizations}

Individual nuclear control is a slow operation, whereas operations of
the form $U\sp{\phi\sum_j\sigma_{\uv n}^j}$ can be performed
relatively quickly and with high fidelity. We therefore modify the
above $\t{SWAP}^{NV,ST}$ decomposition as
\begin{multline}
  \t{SWAP}^{NV,ST}=
  U\sp{\f\pi4\sigma_z^{NV}}U\sp{\f\pi4\sum_j\sigma_z^j}
  U\sp{\f\pi4\sigma_x^{NV}\sigma_x^1}
  U\sp{\f\pi4\sigma_y^{NV}\sigma_y^1}
  U\sp{\f\pi4\sigma_y^{NV}\sigma_y^2} \\
  U\sp{\f\pi4\sigma_z^{NV}}U\sp{\f\pi4\sigma_x^1}
  U\sp{-\f\pi4\sigma_z^{NV}\sigma_x^1}
  U\sp{-\f\pi4\sigma_y^{NV}\sigma_y^2} \\
  U\sp{-\f\pi4\sigma_y^{NV}\sigma_y^1}
  U\sp{-\f\pi4\sigma_x^{NV}\sigma_x^1}
  U\sp{-\f\pi4\sum_j\sigma_z^j}U\sp{-\f\pi4\sigma_z^{NV}}.
\end{multline}

\newpage
\section*{NV decoupling for single nuclear control}

We require
\begin{align}
  \abs{k_m\omega_{DD}-\omega_\l}\gg A,
\end{align}
where $k_m$ is a positive odd integer minimizing
$\abs{k\omega_{DD}-\omega_\l}$. This requirement implies
\begin{align}
  \omega_{DD}\gg A,
\end{align}
so we let
\begin{align}
  \abs{k_m\omega_{DD}-\omega_\l}=s_\Delta A,
\end{align}
and
\begin{align}
  \omega_{DD}=s_{DD}A
\end{align}
for some $s_\Delta,s_{DD}\gg1$, and express
\begin{align}
  k_m\omega_{DD}=\omega_\l\pm s_\Delta A.
\end{align}

\subsection*{Case 1: $\omega_\l \le s_\Delta A$}
In this case, as $k_m\omega_{DD}>0$,
\begin{align}
  k_m\omega_{DD}=\omega_\l+s_\Delta A.
\end{align}
Given that $k_m\ge 1$ and $\omega_{DD}>0$,
\begin{align}
  \omega_{DD}-\omega_\l\le k_m\omega_{DD}-\omega_\l.
\end{align}
As $\omega_{DD}\ge\omega_\l$, we know that $\omega_{DD}-\omega_\l>0$,
so that
\begin{align}
  \abs{\omega_{DD}-\omega_\l}<\abs{k_m\omega_{DD}-\omega_\l}.
\end{align}
By the definition of $k_m$, we must therefore have that $k_m=1$, which
means that
\begin{align}
  \omega_{DD}=\omega_\l+s_\Delta A.
\end{align}
In practice, we can use an AXY frequency
\begin{align}
  \omega_{DD}=\f13\p{\omega_\l+s_\Delta A}
  \label{w_DD_case1}
\end{align}
and set $f_1=0$.

\subsection*{Case 2: $\omega_\l > s_\Delta A$}
In this case we can possibly have
\begin{align}
  k_m\omega_{DD}=\omega_\l-s_\Delta A,
\end{align}
which we can write as
\begin{align}
  k_m s_{DD}=\f{\omega_\l}{A}-s_\Delta.
\end{align}
We therefore get that
\begin{align}
  s_{DD}=k_m^{-1}\p{\f{\omega_\l}{A}-s_\Delta}
\end{align}
and
\begin{align}
  \f{\omega_\l}{A}=k_m s_{DD}+s_\Delta,
\end{align}
which means that if we want to have a large $k_m$, we have to also
scale up $\omega_\l/A>s_\Delta\gg1$. We can alternately express
\begin{align}
  k_m=s_{DD}^{-1}\p{\f{\omega_\l}{A}-s_\Delta},
\end{align}
which means that if $s_{DD},s_\Delta>s$, then the maximum possible
value of $k_m$ is
\begin{align}
  k_M=\floor{s^{-1}\p{\f{\omega_\l}{A}-s}}
  =\floor{\f{\omega_\l}{sA}-1},
  \label{k_M}
\end{align}
so we set
\begin{align}
  \omega_{DD}=k_m^{-1}\p{\omega_\l-s_\Delta A}
  \label{w_DD_case2}
\end{align}
with
\begin{align}
  k_m=2\floor{\f{k_M}2}=\left\{
    \begin{array}{ll}
      k_M & k_M~\t{even} \\
      k_M-1 & k_M~\t{odd}
    \end{array}\right..
\end{align}
If (\ref{w_DD_case2}) does not satisfy $\omega_{DD}\gg A$, which by
construction is only possible when $k_m=0$, then we revert to using
(\ref{w_DD_case1}) with $f_1=0$.

\newpage

\section*{Coherence of a single qubit}

Any single-qubit density matrix $\rho$ can be decomposed as
\begin{align}
  \rho=\f12\p{I+\v v\c\v\sigma}=\f12\m{1+v_z&v_x-iv_y\\v_x+iv_y&1-v_z}.
\end{align}
for a vector $\v v$ with $\v v\c\v v\le 1$. The components $v^i$ of
$\v v$ can be recovered via the anticommutator
\begin{align}
  v^i=\f12\set{\sigma_i,2\rho-I}.
\end{align}
Question: is $C_p\p\rho=\abs{\v v}$ a proper measure of
coherence?

\subsection*{$l_1$ norm of coherence}

In general,
\begin{align}
  C_{l_1}\p\rho=\sum_{i\ne j}\abs{\rho_{ij}}
  =\f12\p{\abs{v_x-iv_y}+\abs{v_x+iv_y}}=\sqrt{v_x^2+v_y^2}.
\end{align}
Equivalently,
\begin{align}
  C_{l_1}\p\rho=\abs{\v v-\v v\c\v z\uv z}
  =\abs{P\sp{\uv v,\uv x\w\uv y}}=v\sin\theta,
\end{align}
where $\theta\in\sp{0,\pi}$ is the polar angle of $\v v$. For any
given state, therefore, this measure of coherence is thus minimal when
when $\v v\parallel\uv z$ (i.e. $\theta\in\set{0,\pi}$, so
$C_{l_1}\p\rho=0$), and maximal when $\v v\perp\uv z$
(i.e. $\theta=\pi/2$, so $C_{l_1}\p\rho=v$).

It is worthwhile to notice that when $\v v\perp\uv z$,
$C_{l_1}\p\rho=C_p\p\rho$, but that $C_p\p\rho$ is
basis-independent.

\subsection*{Relative entropy of coherence}

The relative entropy of coherence is
\begin{align}
  C_{\t{rel. ent.}}\p\rho=S\p{\rho_{\t{diag}}}-S\p\rho,
\end{align}
The von Neumann entropy is
\begin{align}
  S\p\rho=-\tr\p{\rho\log\rho}.
\end{align}
If $\rho=\sum_j\eta_j\op j$, then $S\p\rho=-\sum_j\eta_j\log\eta_j$. We
can express
\begin{align}
  \rho_{\t{diag}}=\f12\p{I+v^z\sigma_z}
  =\f12\sp{\p{1+v^z}\op{+_z}+\p{1-v^z}\op{-_z}},
\end{align}
and
\begin{align}
  \rho=\f12\p{I+v\sigma_v}
  =\f12\sp{\p{1+v}\op{+_v}+\p{1-v}\op{-_v}}.
\end{align}
Letting $v_\pm\equiv \p{1\pm v}/2$ and $v^z_\pm\equiv\p{1\pm
  v^z}/2=\p{1\pm v\cos\theta}/2$ (where $\theta$ is the polar angle of
$\v v$),
\begin{align}
  \rho_{\t{diag}}=v^z_+\op{+_z}+v^z_-\op{-_z}, &&
  \rho=v_+\op{+_v}+v_-\op{-_v},
\end{align}
which means
\begin{align}
  C_{\t{rel. ent.}}\p\rho
  =-\p{v^z_+\log v^z_++v^z_-\log v^z_-}+\p{v_+\log v_++v_-\log v_-}.
\end{align}
For any given state, this measure of coherence is similarly minimal
when $\v v\parallel\uv z$ (i.e. $\rho_{\t{diag}}=\rho$, so
$C_{\t{rel. ent.}}=0$), and maximal when $\v v\perp\uv z$ (i.e.
$v^z=0$ and $v^z_\pm=1/2$, so $C_{\t{rel. ent.}}\p\rho=\log2-S\p\rho$).

\newpage

\section*{Coherence of many qubits}

Consider a density matrix of the form
\begin{align}
  \rho=\f1{2^N}\p{I
    +\sum_{\substack{i_0,i_1,\cdots,i_{N-1}\\\exists n:i_n\ne0}}
    v^{i_0i_1\cdots i_{N-1}}\bigotimes_{n<N}\sigma_{i_n}},
\end{align}
which identifies the state of $N$ qubits. Here all
$i_n\in\set{0,1,2,3}$,
$\sigma_{i_n}\in\set{I,\sigma_x,\sigma_y,\sigma_z}$, and $n$ indexes
the qubit upon which $\sigma_{i_n}$ acts.

Questions: What restrictions exist on $\rho$? What do these
restrictions imply about $\v v$?

\end{document}

### 2016-02-16 misc/constants_numerical.py

@@ -1,0 +1,66 @@
+#!/usr/bin/env python3
+
+import numpy as np
+import matrix_operations_numerical as mo
+i = complex(0,1)
+
+# identity matrices
+def I(n): return np.eye(n)
+
+# pauli spin operators
+st = I(2)
+sz = np.array([[1,0],[0,-1]])
+sx = np.array([[0,1],[1,0]])
+sy = i*np.array([[0,-1],[1,0]])
+
+# spin-up and spin-down states
+up = np.vstack([1,0])
+dn = np.vstack([0,1])
+
+# two-qubit basis states
+uu = mo.tp(up,up)
+ud = mo.tp(up,dn)
+du = mo.tp(dn,up)
+dd = mo.tp(dn,dn)
+
+# two-qubit singlet/triplet states
+S = (ud-du)/np.sqrt(2)
+T = (ud+du)/np.sqrt(2)
+
+# physical constants in SI
+mu0_SI = 4*np.pi*1e-7 # magnetic constant (tesla meters / amp)
+c_SI = 299792458 # speed of light (meters / second)
+hbar_SI = 6.582119514e-16 # reduced Planck constant (eV / second)
+qe_SI = 1.60217646e-19 # charge of electron (coulombs)
+ge_SI = 1.760859708e11 # gyromagnetic ratio of NV electron (Hz/tesla)
+gc_SI = 67.28284e6 # gyromagnetic ratio of C-13 (Hz/tesla)
+
+# physical constants in natural units (e0 = mu0 = c = hbar = 1); all values in seconds or Hz
+
+D = 2*np.pi*2.87e9 # NV center zero field splitting energy (Hz)
+
+alpha = 1/137.035999074 # fine structure constant
+qe = np.sqrt(4*np.pi*alpha) # unit electric charge
+me = 510998.928/hbar_SI # mass of electron (Hz)
+ge = qe/(2*me) * 2.0023193043617 # gyromagnetic ratio of electron
+gc = gc_SI * ge/ge_SI # gyromagnetic ratio of C-13
+
+# SI values in natural units
+kHz = 1000 # (Hz)
+meter = 1 / c_SI # one meter (s)
+nm = 1e-9*meter # one nanometer (s)
+coulomb = qe / qe_SI # one coulomb
+tesla = ge_SI / ge # one tesla (Hz)
+gauss = tesla*1e-4 # one gauss (Hz)
+volt = 1/(qe*hbar_SI) # one volt (Hz)
+
[…]

### 2016-02-16 misc/constants_symbolic.py

@@ -1,0 +1,50 @@
+#!/usr/bin/env python3
+
+import matrix_operations_symbolic as mo
+import sympy as sym
+i = complex(0,1)
+
+########################################
+# mathematical and physical constants
+########################################
+
+arccos = sym.acos
+
+# identity matrices
+def I(n): return sym.eye(n)
+
+# pauli spin operators
+sz = sym.Matrix([[1,0],[0,-1]])
+sx = sym.Matrix([[0,1],[1,0]])
+sy = i*sym.Matrix([[0,-1],[1,0]])
+
+# spin-up and spin-down states
+up = sym.Matrix([[1],[0]])
+dn = sym.Matrix([[0],[1]])
+
+# two-qubit states
+uu = mo.tp(up,up)
+ud = mo.tp(up,dn)
+du = mo.tp(dn,up)
+dd = mo.tp(dn,dn)
+
+# two-qubit singlet/triplet states
+S = (ud-du)/sym.sqrt(2)
+T = (ud+du)/sym.sqrt(2)
+
+# physical constants
+mu0 = sym.var('\mu_0')
+ge = sym.var('\gamma_e')
+gc = sym.var('\gamma_C')
+D = sym.var('D')
+qe = sym.var('q_e')
+me = sym.var('m_e')
+nm = sym.var('nm')
+
+# excited state to use for two-level NV center
+ms = sym.var('m_s')
+
+# spin matrices of NV center in restricted subspace
+Sz = ms/2*(sz+I(2))
+Sx = sx/sym.sqrt(2)
+Sy = ms*sy/sym.sqrt(2)

### 2016-02-16 misc/matrix_operations_numerical.py

@@ -1,0 +1,89 @@
+#!/usr/bin/env python3
+
+import numpy as np
+
+i = complex(0,1)
+
+# hermitian conjugate
+def herm(M):
+    return np.array(np.matrix(M).H)
+
+# indices of matrix
+def indices(M):
+    try:
+        return [ (m,n) for n in range(M.shape[1]) for m in range(M.shape[0]) ]
+    except:
+        return range(M.shape[0])
+
+# commutator [X,Y]
+def comm(X,Y): return np.dot(X,Y)-np.dot(Y,X)
+
+# tensor product
+def tp(*args):
+    if len(args) == 1 and type(args[0]) is list:
+        args = args[0]
+    out = args[0]
+    for i in range(len(args)-1):
+        out = np.kron(out,args[i+1])
+    return out
+
+# matrix multiplication
+def mm(*args):
+    if len(args) == 1 and type(args[0]) is list:
+        args = args[0]
+    out = args[-1]
+    for i in reversed(range(len(args)-1)):
+        out = np.dot(args[i],out)
+    return out
+
+# remove numerical artifacts from matrix
+def remove_artifacts(M, threshold=1e-12):
+    for ind in indices(M):
+        if abs(np.real(M[ind])) < threshold:
+            M[ind] -= np.real(M[ind])
+        if abs(np.imag(M[ind])) < threshold:
+            M[ind] = np.real(M[ind])
+    if abs(np.imag(M)).max() == 0:
+        M = np.real(M)
+    return M
+
+# get/remove global phase from matrix
+def get_phase(M):
+    phase = 1
+    for ind in indices(M):
+        if abs(M[ind]) != 0:
+            phase = M[ind]/abs(M[ind])
+            break
+    return phase
+
+def remove_phase(M):
+    return M*np.conj(get_phase(M))
+
+# clean up matrix for printing
+def clean(M, threshold=1e-12):
+    out = remove_artifacts(M,threshold)
+    out = remove_phase(out)
+    out = remove_artifacts(out,threshold)
+    if abs(np.imag(out)).max() == 0:
+        out = np.real(out)
+    return out
+
+# generate matrix B to act A on qubits ns (out of N qubits total)
+def act(A,N,*ns):
+    if len(ns) == 1 and type(ns[0]) is list:
+        ns = ns[0]
+    B = i*np.zeros((2**N,2**N))
+    for ind in indices(B):
[…]

### 2016-02-16 misc/matrix_operations_symbolic.py

@@ -1,0 +1,127 @@
+#!/usr/bin/env python3
+
+import numpy as np
+import sympy as sym
+
+i = complex(0,1)
+
+# hermitian conjugate
+def herm(M): return M.H
+
+# matrix inverse
+def inv(M): return M.inv()
+
+# indices of matrix
+def indices(M):
+    return [ (m,n) for n in range(M.shape[1]) for m in range(M.shape[0]) ]
+
+# commutator [X,Y]
+def comm(X,Y): return X*Y-Y*X
+
+# tensor product
+def tp(*args):
+    if len(args) == 1 and type(args[0]) is list:
+        args = args[0]
+    out = np.array(args[0])
+    for i in range(len(args)-1):
+        out = np.kron(out,np.array(args[i+1]))
+    return sym.Matrix(out)
+
+# matrix multiplication
+def mm(*args):
+    if len(args) == 1 and type(args[0]) is list:
+        args = args[0]
+    out = sym.simplify(args[-1])
+    for i in reversed(range(len(args)-1)):
+        out = sym.simplify(args[i]*out)
+    return out
+
+# matrix multiplication with object evaluation
+def emm(*args):
+    if len(args) == 1 and type(args[0]) is list:
+        args = args[0]
+    args = [ arg.evalf() for arg in args ]
+    out = args[-1]
+    for i in reversed(range(len(args)-1)):
+        out = (args[i]*out).evalf()
+    return out
+
+# get/remove global phase from matrix
+def get_phase(M):
+    phase = 1
+    for ind in indices(M):
+        val = sym.simplify(M[ind])
+        if sym.Abs(val) != 0:
+            phase = val/sym.Abs(sym.expand(val))
+            phase = phase.expand(complex=True)
+            break
+    return sym.simplify(phase)
+
+def remove_phase(M):
+    return sym.simplify(sym.expand(M*sym.conjugate(get_phase(M))))
+
+# clean up matrix for printing
+def clean(M):
+    out = M.evalf()
+    out = remove_phase(out)
+    return out
+
+# generate matrix B to act A on qubits ns (out of N qubits total)
+def act(A,N,*ns):
+    if len(ns) == 1 and type(ns[0]) is list:
+        ns = ns[0]
+    B = sym.zeros(2**N)
+    for ind in indices(B):
+        s_out = bin(ind[0])[2:].zfill(N)
+        rest_out = [ s_out[n] for n in range(N) if n not in ns ]
+
[…]

### 2016-02-16 misc/run.py

@@ -1,0 +1,43 @@
+#!/usr/bin/env python3
+
+import sys
+from scipy.linalg import expm,logm,sqrtm
+
+if 'sym' in sys.argv:
+    import pylab as pl
+    from sympy import *
+    from constants_symbolic import *
+    from matrix_operations_symbolic import *
+    from spin_operations_symbolic import *
+    matrix = Matrix
+else:
+    from pylab import *
+    from constants_numerical import *
+    from matrix_operations_numerical import *
+    from spin_operations_numerical import *
+    import numpy as np
+    matrix = array
+
+    np.set_printoptions(linewidth = 95)
+
+
+
+
+phi_over_2pi = float(sys.argv[1])
+U = expm(-i*phi_over_2pi*2*pi*tp(sz,sx))
+print(clean(U))
+
+
+exit()
+
+coupled = True
+
+def pp(psi):
+    psi_NVST = mm(act(couple,3,1,2),psi) if coupled else psi
+    qvec_print(remove_artifacts(psi_NVST))
+    print()
+
+for psi in [tp(up,S),tp(up,T),tp(dn,S),tp(dn,T)]:
+    pp(psi)
+    pp(mm(SWAP_NVST,psi))
+    print()

### 2016-02-16 misc/spin_operations_numerical.py

@@ -1,0 +1,243 @@
+#!/usr/bin/env python3
+
+import numpy as np
+import scipy.linalg as lin
+
+import constants_numerical as const
+import matrix_operations_numerical as mo
+i = complex(0,1)
+
+########################################
+# gate solutions and printing
+########################################
+
+# determine Hamiltonian to generate arbitrary gates (operation time = 1)
+def Hgate(G): return i*lin.logm(G)
+
+# compute propagator for arbitrary time-independent Hamiltonians (operation time = 1)
+def U(tH): return lin.expm(-i*tH)
+
+# ordered list of basis Hamiltonians for a system of N spins
+def vH(N=2,form='matrix'):
+
+    pauli = [np.eye(2),const.sz,const.sx,const.sy]
+    pauli_text = ['I','Z','X','Y']
+
+    vec = []
+    text = []
+    permutation = np.zeros(N,dtype=int)
+    for p in range(4**N):
+        bin = '{0:b}'.format(p).zfill(2*N)
+        for s in range(N):
+            permutation[s] = int(bin[s*2:s*2+2],2)
+        vec.append(mo.tp([ pauli[s] for s in permutation ]))
+        text.append(' '.join([ pauli_text[s] for s in permutation ]))
+
+    if form == 'matrix':
+        return np.column_stack([np.ndarray.flatten(v) for v in vec])
+    elif form == 'list':
+        return vec
+    elif form == 'text':
+        return text
+    else:
+        return None
+
+# decompose Hamiltonian into its basis components
+def H_decompose(H):
+    N = int(np.log(H.shape[0])/np.log(2))
+    hs = lin.solve(vH(N),np.ndarray.flatten(H))
+    return mo.remove_artifacts(hs)
+
+# print Hamiltonian vector in human-readable form
+def H_print(H,factor=1,threshold=1e-10):
+    N = int(np.log(H.shape[0])/np.log(2))
+    hs = mo.remove_artifacts(H_decompose(H),threshold)
+    vHs = vH(N,'text')
+    factor_text = 'prefactor: '
+    if factor == 1:
+        factor_text += 'pi'
+    else:
[…]

### 2016-02-16 misc/spin_operations_symbolic.py

@@ -1,0 +1,180 @@
+#!/usr/bin/env python3
+
+import sympy as sym
+import scipy.linalg as lin
+
+import constants_symbolic as const
+import matrix_operations_symbolic as mo
+i = complex(0,1)
+
+########################################
+# printing
+########################################
+
+# print qubit in human-readable form
+def qvec_print(v):
+    N = len(v)
+    qbits = int(sym.log(N)/sym.log(2))
+    for n in range(N):
+        if v[n] != 0:
+            s = bin(n)[2:].zfill(qbits)
+            s = s.replace('0','u').replace('1','d')
+            print('%s:'%s,v[n])
+
+########################################
+# single qubit gates
+########################################
+
+# spin propagators; Ua corresponds to a Hamiltonian # H = h s_a
+def Uz(ht): return sym.cos(ht)*sym.eye(2)-i*sym.sin(ht)*const.sz
+def Ux(ht): return sym.cos(ht)*sym.eye(2)-i*sym.sin(ht)*const.sx
+def Uy(ht): return sym.cos(ht)*sym.eye(2)-i*sym.sin(ht)*const.sy
+
+# rotation operators
+def Rz(phi): return Uz(phi/2)
+def Rx(phi): return Ux(phi/2)
+def Ry(phi): return Uy(phi/2)
+
+# phase-flip, bit-flip, and Hadamard gates
+Z = sym.Matrix([[1,0],[0,-1]])
+X = sym.Matrix([[0,1],[1,0]])
+HG = sym.Matrix([[1,1],[1,-1]])/sym.sqrt(2)
+
+########################################
+# two qubit gates
+########################################
+
+# propagators coupling two spins; Uab corresponds to a Hamiltonian H = h s_a^1 s_b^2
+def U_spins(ht,axes):
+    spins = []
+    for n in range(2):
+        if axes[n] == 'z':
+            spin = const.sz
+        elif axes[n] == 'x':
+            spin = const.sx
+        elif axes[n] == 'y':
+            spin = const.sy
+        spins.append(spin)
[…]

### 2016-02-16 nv-math.cpp

@@ -592,7 +592,7 @@ MatrixXcd simulate_propagator(const nv_system& nv, const uint cluster,
     } else{ // if(pulse);
       const double t_AXY = t - int(t/t_DD)*t_DD;
       const double dt1 = pulses.at(pulse)*t_DD - t_AXY;
-      const double dt2 = t_AXY + dt - pulses.at(pulse)*t_DD;
+      const double dt2 = dt - dt1;
 
       const Vector3d B1 = nv.static_Bz*zhat + controls.B(t+dt1/2);
       const Vector3d B2 = nv.static_Bz*zhat + controls.B(t+dt1+dt2/2);

### 2016-02-16 nv-math.cpp
slightly simplified integration in simulate_propagator

@@ -545,9 +545,9 @@ MatrixXcd simulate_propagator(const nv_system& nv, const uint cluster,
     return max(largest_control_freq,largest_g*B_cap.norm());
   }();
 
-  // integration step size and number
-  const double dt = 1/(frequency_scale*nv.integration_factor);
-  const uint integration_steps = ceil(simulation_time/dt);
+  // integration step number and size
+  const uint integration_steps = simulation_time*frequency_scale*nv.integration_factor;
+  const double dt = simulation_time/integration_steps;
 
   // static NV+cluster Hamiltonian
   const MatrixXcd H_static = H_int_large_static_Bz(nv,cluster);
@@ -578,21 +578,15 @@ MatrixXcd simulate_propagator(const nv_system& nv, const uint cluster,
 
     // update propagator
     if(!pulse){
-      if(t+dt < end_time){
-        const Vector3d B = nv.static_Bz*zhat + controls.B(t+dt/2);
-        const MatrixXcd H = H_static + H_nZ(nv,cluster,B);
-        U = (exp(-j*dt*H) * U).eval();
+      const Vector3d B = nv.static_Bz*zhat + controls.B(t+dt/2);
+      const MatrixXcd H = H_static + H_nZ(nv,cluster,B);
 
-      } else{ // if t+dt > end_time
-        const double dtf = end_time-t;
-        const Vector3d B = nv.static_Bz*zhat + controls.B(t+dtf/2);
-        const MatrixXcd H = H_static + H_nZ(nv,cluster,B);
-        U = (exp(-j*dtf*H) * U).eval();
-      }
+      U = (exp(-j*dt*H) * U).eval();
+
     } else{ // if(pulse);
-      const double t_AXY = t - int(t/t_DD)*t_DD;
-      const double dt1 = pulses.at(pulse)*t_DD - t_AXY;
-      const double dt2 = dt - dt1;
+      const double t_AXY = t - int(t/t_DD)*t_DD; // time into this AXY sequence
+      const double dt1 = pulses.at(pulse)*t_DD - t_AXY; // time before the pulse
+      const double dt2 = dt - dt1; // time after the pulse
 
       const Vector3d B1 = nv.static_Bz*zhat + controls.B(t+dt1/2);
       const Vector3d B2 = nv.static_Bz*zhat + controls.B(t+dt1+dt2/2);

### 2016-02-16 nv-math.cpp
removed a large-Bz approximation in simulate_propagator

@@ -550,7 +550,7 @@ MatrixXcd simulate_propagator(const nv_system& nv, const uint cluster,
   const double dt = simulation_time/integration_steps;
 
   // static NV+cluster Hamiltonian
-  const MatrixXcd H_static = H_int_large_static_Bz(nv,cluster);
+  const MatrixXcd H_static = H_int(nv,cluster);
 
   // NV center spin flip (pi-)pulse
   const MatrixXcd X = act(sx, {0}, spins);

### 2016-02-16 nv-math.cpp
removed unused method: H_int_large_static_Bz

@@ -348,24 +348,6 @@ MatrixXcd H_int(const nv_system& nv, const uint cluster_index){
   return H;
 }
 
-// spin-spin coupling Hamiltonian for NV center with cluster; assumes large static Bz
-MatrixXcd H_int_large_static_Bz(const nv_system& nv, const uint cluster_index){
-  const vector<uint> cluster = nv.clusters.at(cluster_index);
-  const int spins = cluster.size()+1;
-  MatrixXcd H = MatrixXcd::Zero(pow(2,spins),pow(2,spins));
-  for(uint s = 0; s < cluster.size(); s++){
-    // interaction between NV center and spin s
-    H += act( tp(dot(nv.e.S,zhat), dot(A(nv,cluster.at(s)),nv.nuclei.at(cluster.at(s)).S)),
-              {0,s+1}, spins);
-    for(uint r = 0; r < s; r++){
-      // interaction betwen spin r and spin s
-      H += act(H_ss_large_static_Bz(nv.nuclei.at(cluster.at(r)), nv.nuclei.at(cluster.at(s))),
-               {r+1,s+1}, spins);
-    }
-  }
-  return H;
-}
-
 // nuclear Zeeman Hamiltonian
 MatrixXcd H_nZ(const nv_system& nv, const uint cluster_index, const Vector3d& B){
   const vector<uint> cluster = nv.clusters.at(cluster_index);

### 2016-02-16 nv-math.h

@@ -155,9 +155,6 @@ inline MatrixXcd H_ss_large_static_Bz(const spin& s1, const spin& s2){
 // spin-spin coupling Hamiltonian for NV center with cluster
 MatrixXcd H_int(const nv_system& nv, const uint cluster_index);
 
-// spin-spin coupling Hamiltonian for NV center with cluster; assumes large static Bz
-MatrixXcd H_int_large_static_Bz(const nv_system& nv, const uint cluster_index);
-
 // NV zero-field splitting plus Zeeman Hamiltonian
 inline MatrixXcd H_NV_GS(const nv_system& nv, const Vector3d& B){
   return NV_ZFS*dot(nv.e.S,zhat)*dot(nv.e.S,zhat) - nv.e.g*dot(B,nv.e.S);

### 2016-02-16 nv-math.h
removed unused method: H_ss_large_static_Bz

@@ -147,11 +147,6 @@ int F_AXY(const double x, const vector<double> pulses);
 // Hamiltoninan coupling two spins
 MatrixXcd H_ss(const spin& s1, const spin& s2);
 
-// Hamiltoninan coupling two spins; assumes large static Bz
-inline MatrixXcd H_ss_large_static_Bz(const spin& s1, const spin& s2){
-  return coupling_strength(s1,s2) * (3*tp(dot(s1.S,zhat), dot(s2.S,zhat)) - dot(s1.S,s2.S));
-}
-
 // spin-spin coupling Hamiltonian for NV center with cluster
 MatrixXcd H_int(const nv_system& nv, const uint cluster_index);
 

### 2016-02-16 nv-math.cpp
moved inline method to header file

@@ -362,11 +362,6 @@ MatrixXcd H_nZ(const nv_system& nv, const uint cluster_index, const Vector3d& B)
   return H;
 }
 
-// Zeeman Hamiltonian for NV+cluster system
-inline MatrixXcd H_Z(const nv_system& nv, const uint cluster, const Vector3d& B){
-  return H_nZ(nv,cluster,B) + act(H_NV_GS(nv,B), {0}, nv.clusters.at(cluster).size()+1);
-}
-
 // perform NV coherence measurement with a static magnetic field
 double coherence_measurement(const nv_system& nv, const double w_scan, const double f_DD,
                              const axy_harmonic k_DD, const double scan_time){

### 2016-02-16 nv-math.h

@@ -164,7 +164,9 @@ inline MatrixXcd U_NV_GS(const nv_system& nv, const double time, const uint spin
 MatrixXcd H_nZ(const nv_system& nv, const uint cluster_index, const Vector3d& B);
 
 // Zeeman Hamiltonian for NV center with cluster
-inline MatrixXcd H_Z(const nv_system& nv, const uint cluster_index, const Vector3d& B);
+inline MatrixXcd H_Z(const nv_system& nv, const uint cluster, const Vector3d& B){
+  return H_nZ(nv,cluster,B) + act(H_NV_GS(nv,B), {0}, nv.clusters.at(cluster).size()+1);
+}
 
 // perform NV coherence measurement with a static magnetic field
 double coherence_measurement(const nv_system& nv, const double w_scan, const double f_DD,

### 2016-03-16 nv-gates.h
changed method for computing SWAP_NVST

@@ -5,7 +5,7 @@ using namespace Eigen;
 
 #include "qp-math.h"
 
-struct gates{
+struct nv_gates{
 
   // single qubit gates
   const MatrixXcd Z = sz;
@@ -36,7 +36,6 @@ struct gates{
                        0, 1, 1, 0,
                        0,-1, 1, 0,
                        -1, 0, 0, 1).finished()/sqrt(2);
-  const MatrixXcd uE = E.inverse();
 
   // change between coupled and uncoupled basis for two spins
   const MatrixXcd uncouple = (Matrix4cd() <<
@@ -44,25 +43,26 @@ struct gates{
                               0, 1/sqrt(2), 1/sqrt(2), 0,
                               0,-1/sqrt(2), 1/sqrt(2), 0,
                               0, 0,         0,         1).finished();
-  const MatrixXcd couple = uncouple.inverse();
+  const MatrixXcd couple = uncouple.adjoint();
 
   const VectorXcd S = (ud-du)/sqrt(2);
   const VectorXcd T = (ud+du)/sqrt(2);
 
   // identity on Hilbert space of two qubits mod the ST subspace
-  const MatrixXcd unused_ST_I = uu*uu.transpose() + dd*dd.transpose();
+  const MatrixXcd unused_ST_I = uu*uu.adjoint() + dd*dd.adjoint();
 
   // phase-flip, bit-flip, and Hadamard gates on an ST qubit
-  const MatrixXcd Z_ST = S*S.transpose() - T*T.transpose() + j*unused_ST_I;
-  const MatrixXcd X_ST = S*T.transpose() + T*S.transpose() + j*unused_ST_I;
-  const MatrixXcd H_ST = ((S+T)*S.transpose()+(S-T)*T.transpose())/sqrt(2.) + j*unused_ST_I;
+  const MatrixXcd Z_ST = S*S.adjoint() - T*T.adjoint() + j*unused_ST_I;
+  const MatrixXcd X_ST = S*T.adjoint() + T*S.adjoint() + j*unused_ST_I;
+  const MatrixXcd H_ST = ((S+T)*S.adjoint()+(S-T)*T.adjoint())/sqrt(2.) + j*unused_ST_I;
 
   // operation to store ST state into NV spin
[…]

### 2016-03-16 qp-math.h
remove obsolete dependency

@@ -1,7 +1,5 @@
 #pragma once
 
-using namespace std;
-
 #include <eigen3/Eigen/Dense> // linear algebra library
 #include <eigen3/unsupported/Eigen/KroneckerProduct> // provides tensor product
 #include <eigen3/unsupported/Eigen/MatrixFunctions> // provides matrix functions

### 2016-03-16 misc/notes.tex
implement SWAP_NVST using one 'cheating' operation

@@
   \t{cNOT}^{m,n}=U\sp{\f\pi4\p{\sigma_z^m+\sigma_x^n
-      -\sigma_z^m\sigma_x^n}}
-  =U\sp{\f\pi4\sigma_z^m}U\sp{\f\pi4\sigma_x^n}
+      -\sigma_z^m\sigma_x^n}} =R_z^m\p{\f\pi2} R_x^1\p{\f\pi2}
   U\sp{-\f\pi4\sigma_z^m\sigma_x^n}
@@
 \end{align}
-and therefore
-\begin{multline}
-  \t{SWAP}^{NV,ST}= U\sp{\f\pi4\sigma_z^{NV}}U\sp{\f\pi4\sigma_z^1}
-  U\sp{\f\pi4\sigma_x^{NV}\sigma_x^1}
-  U\sp{\f\pi4\sigma_y^{NV}\sigma_y^1}
-  U\sp{-\f\pi4\sigma_y^{NV}\sigma_x^2} \\
-  U\sp{\f\pi4\sigma_z^{NV}}U\sp{\f\pi4\sigma_x^1}
-  U\sp{-\f\pi4\sigma_z^{NV}\sigma_x^1}
-  U\sp{\f\pi4\sigma_y^{NV}\sigma_x^2} \\
+and therefore, defining
+\begin{align}
+  \mathcal M &={\E^\dag}^{NV,2} i\t{SWAP}^{NV,1}
+  R_z^1\p{-\f\pi2}R_z^{NV}\p{-\f\pi2} \tag*{} \\
+  &=U\sp{\f\pi4\sigma_y^{NV}\sigma_x^2}
   U\sp{-\f\pi4\sigma_y^{NV}\sigma_y^1}
   U\sp{-\f\pi4\sigma_x^{NV}\sigma_x^1}
-  U\sp{-\f\pi4\sigma_z^1}U\sp{-\f\pi4\sigma_z^{NV}}.
-\end{multline}
+  R_z^1\p{-\f\pi2}R_z^{NV}\p{-\f\pi2}
+\end{align}
+we can express
+\begin{align}
+  \t{SWAP}^{NV,ST}=\mathcal M^\dag R_z^{NV}\p{\f\pi2} R_x^1\p{\f\pi2}
+  U\sp{-\f\pi4\sigma_z^{NV}\sigma_x^1} \mathcal M.
+\end{align}
 
@@
 
-Individual nuclear control is a slow operation, whereas operations of
-the form $U\sp{\phi\sum_j\sigma_{\uv n}^j}$ can be performed
-relatively quickly and with high fidelity. We therefore modify the
-above $\t{SWAP}^{NV,ST}$ decomposition as
-\begin{multline}
-  \t{SWAP}^{NV,ST}=
-  U\sp{\f\pi4\sigma_z^{NV}}U\sp{\f\pi4\sum_j\sigma_z^j}
-  U\sp{\f\pi4\sigma_x^{NV}\sigma_x^1}
-  U\sp{\f\pi4\sigma_y^{NV}\sigma_y^1}
-  U\sp{\f\pi4\sigma_y^{NV}\sigma_y^2} \\
-  U\sp{\f\pi4\sigma_z^{NV}}U\sp{\f\pi4\sigma_x^1}
-  U\sp{-\f\pi4\sigma_z^{NV}\sigma_x^1}
-  U\sp{-\f\pi4\sigma_y^{NV}\sigma_y^2} \\
+When addressing larmor pairs with frequency $\omega_\l$, operations of
+the form $\prod_{j\in\set{k:\omega_k=\omega_\l}}R_{\uv n}^j\p\phi$ are
+easier to realize than individual rotations $R_{\uv n}^m\p\phi$. We
+therefore define
+\begin{align}
+  \mathcal M'=U\sp{-\f\pi4\sigma_y^{NV}\sigma_y^2}
   U\sp{-\f\pi4\sigma_y^{NV}\sigma_y^1}
   U\sp{-\f\pi4\sigma_x^{NV}\sigma_x^1}
-  U\sp{-\f\pi4\sum_j\sigma_z^j}U\sp{-\f\pi4\sigma_z^{NV}}.
-\end{multline}
+  \sp{\prod_{j\in\set{k:\omega_k=\omega_\l}}R_z^j\p{-\f\pi2}}
+  R_z^{NV}\p{-\f\pi2}
+\end{align}
+and express $\t{SWAP}^{NV,ST}$ as
+\begin{align}
+  \t{SWAP}^{NV,ST}={\mathcal M'}^\dag R_z^{NV}\p{\f\pi2} R_x^1\p{\f\pi2}
+  U\sp{-\f\pi4\sigma_z^{NV}\sigma_x^1} \mathcal M'.
+\end{align}
 
@@
 
-\section*{Coherence of a single qubit}
-
-Any single-qubit density matrix $\rho$ can be decomposed as
-\begin{align}
-  \rho=\f12\p{I+\v v\c\v\sigma}=\f12\m{1+v_z&v_x-iv_y\\v_x+iv_y&1-v_z}.
-\end{align}
-for a vector $\v v$ with $\v v\c\v v\le 1$. The components $v^i$ of
-$\v v$ can be recovered via the anticommutator
-\begin{align}
-  v^i=\f12\set{\sigma_i,2\rho-I}.
-\end{align}
-Question: is $C_p\p\rho=\abs{\v v}$ a proper measure of
-coherence?
-
-\subsection*{$l_1$ norm of coherence}
-
-In general,
-\begin{align}
-  C_{l_1}\p\rho=\sum_{i\ne j}\abs{\rho_{ij}}
-  =\f12\p{\abs{v_x-iv_y}+\abs{v_x+iv_y}}=\sqrt{v_x^2+v_y^2}.
-\end{align}
-Equivalently,
-\begin{align}
-  C_{l_1}\p\rho=\abs{\v v-\v v\c\v z\uv z}
-  =\abs{P\sp{\uv v,\uv x\w\uv y}}=v\sin\theta,
-\end{align}
-where $\theta\in\sp{0,\pi}$ is the polar angle of $\v v$. For any
-given state, therefore, this measure of coherence is thus minimal when
-when $\v v\parallel\uv z$ (i.e. $\theta\in\set{0,\pi}$, so
-$C_{l_1}\p\rho=0$), and maximal when $\v v\perp\uv z$
-(i.e. $\theta=\pi/2$, so $C_{l_1}\p\rho=v$).
-
-It is worthwhile to notice that when $\v v\perp\uv z$,
-$C_{l_1}\p\rho=C_p\p\rho$, but that $C_p\p\rho$ is
-basis-independent.
-
-\subsection*{Relative entropy of coherence}
-
-The relative entropy of coherence is
-\begin{align}
-  C_{\t{rel. ent.}}\p\rho=S\p{\rho_{\t{diag}}}-S\p\rho,
-\end{align}
-The von Neumann entropy is
-\begin{align}
-  S\p\rho=-\tr\p{\rho\log\rho}.
-\end{align}
-If $\rho=\sum_j\eta_j\op j$, then $S\p\rho=-\sum_j\eta_j\log\eta_j$. We
-can express
-\begin{align}
-  \rho_{\t{diag}}=\f12\p{I+v^z\sigma_z}
-  =\f12\sp{\p{1+v^z}\op{+_z}+\p{1-v^z}\op{-_z}},
-\end{align}
-and
-\begin{align}
-  \rho=\f12\p{I+v\sigma_v}
-  =\f12\sp{\p{1+v}\op{+_v}+\p{1-v}\op{-_v}}.
-\end{align}
-Letting $v_\pm\equiv \p{1\pm v}/2$ and $v^z_\pm\equiv\p{1\pm
-  v^z}/2=\p{1\pm v\cos\theta}/2$ (where $\theta$ is the polar angle of
-$\v v$),
-\begin{align}
-  \rho_{\t{diag}}=v^z_+\op{+_z}+v^z_-\op{-_z}, &&
-  \rho=v_+\op{+_v}+v_-\op{-_v},
-\end{align}
-which means
-\begin{align}
-  C_{\t{rel. ent.}}\p\rho
-  =-\p{v^z_+\log v^z_++v^z_-\log v^z_-}+\p{v_+\log v_++v_-\log v_-}.
-\end{align}
-For any given state, this measure of coherence is similarly minimal
-when $\v v\parallel\uv z$ (i.e. $\rho_{\t{diag}}=\rho$, so
-$C_{\t{rel. ent.}}=0$), and maximal when $\v v\perp\uv z$ (i.e.
-$v^z=0$ and $v^z_\pm=1/2$, so $C_{\t{rel. ent.}}\p\rho=\log2-S\p\rho$).
-
-\newpage
-
-\section*{Coherence of many qubits}
-
-Consider a density matrix of the form
-\begin{align}
-  \rho=\f1{2^N}\p{I
-    +\sum_{\substack{i_0,i_1,\cdots,i_{N-1}\\\exists n:i_n\ne0}}
-    v^{i_0i_1\cdots i_{N-1}}\bigotimes_{n<N}\sigma_{i_n}},
-\end{align}
-which identifies the state of $N$ qubits. Here all
-$i_n\in\set{0,1,2,3}$,
-$\sigma_{i_n}\in\set{I,\sigma_x,\sigma_y,\sigma_z}$, and $n$ indexes
-the qubit upon which $\sigma_{i_n}$ acts.
-
-Questions: What restrictions exist on $\rho$? What do these
-restrictions imply about $\v v$?
+\section*{Addressing larmor pairs}
+
+When applying a static control field $\v B_{\t{ctl}}$, we have the
+effective interaction + control Hamiltonian
+\begin{align}
+  H=\f12m_s\sigma_z\sum_j\v A_j\c\v I_j-\sum_j\gamma_j\v
+  B_{\t{ctl}}\c\v I_j
+\end{align}
 

### 2016-03-16 nv-control.cpp

@@ -7,6 +7,7 @@ using namespace Eigen;
 #include "constants.h"
 #include "qp-math.h"
 #include "nv-math.h"
+#include "nv-gates.h"
 #include "nv-control.h"
 
 //--------------------------------------------------------------------------------------------
@@ -303,18 +304,31 @@ MatrixXcd couple_target(const nv_system& nv, const uint target, const double pha
 MatrixXcd SWAP_NVST(const nv_system& nv, const uint idx1, const uint idx2, const bool exact){
   // assert that both target nuclei are in the same cluster
   const vector<uint> cluster = nv.clusters.at(get_cluster_containing_index(nv,idx1));
+  const uint spins = cluster.size()+1;
   assert(in_vector(idx2,cluster));
 
+  if(exact){
+    const uint idx1_in_cluster = get_index_in_cluster(idx1, cluster);
+    const uint idx2_in_cluster = get_index_in_cluster(idx2, cluster);
+    const MatrixXcd targets_to_natural_basis =
+      act(rotate(natural_basis(nv,idx1), {xhat,yhat,zhat}), {idx1_in_cluster+1}, spins) *
+      act(rotate(natural_basis(nv,idx2), {xhat,yhat,zhat}), {idx2_in_cluster+1}, spins);
+    const nv_gates gates;
+    return (targets_to_natural_basis *
+            act(gates.SWAP_NVST, {0, idx1_in_cluster+1, idx2_in_cluster+1}, spins) *
+            targets_to_natural_basis.adjoint());
+  }
+
   // compute components of SWAP_NVST
-  const MatrixXcd Rz_NV = rotate_NV(nv, pi/2*zhat, cluster.size()+1);
-  const MatrixXcd Rx_1 = rotate_target(nv, idx1, pi/2*xhat, exact);
-  const MatrixXcd Rz_1 = rotate_target(nv, idx1, pi/2*zhat, exact);
-  const MatrixXcd iSWAP_NV_1 = iSWAP(nv, idx1, exact);
-  const MatrixXcd cNOT_NV_1 = (Rz_NV * Rx_1 *
-                               couple_target(nv, idx1, -pi/4, zhat, xhat, exact));
-  const MatrixXcd E_NV_2 = couple_target(nv, idx2, -pi/4, yhat, xhat, exact);
[…]

### 2016-03-16 nv-control.h

@@ -55,10 +55,11 @@ MatrixXcd couple_target(const nv_system& nv, const uint target, const double pha
 //--------------------------------------------------------------------------------------------
 
 // iSWAP operation
-inline MatrixXcd iSWAP(const nv_system& nv, const uint index, const bool exact){
+inline MatrixXcd iSWAP(const nv_system& nv, const uint index, const bool exact = false){
   return (couple_target(nv, index, -pi/4, xhat, xhat, exact) *
           couple_target(nv, index, -pi/4, yhat, yhat, exact));
 };
 
 // SWAP_NVST operation
-MatrixXcd SWAP_NVST(const nv_system& nv, const uint idx1, const uint idx2, const bool exact);
+MatrixXcd SWAP_NVST(const nv_system& nv, const uint idx1, const uint idx2,
+                    const bool exact = false);

### 2016-03-16 simulation.cpp

@@ -15,9 +15,8 @@ namespace po = boost::program_options;
 #include "constants.h"
 #include "qp-math.h"
 #include "nv-math.h"
+#include "nv-gates.h"
 #include "nv-control.h"
-
-#include "gates.h"
 
 int main(const int arg_num, const char *arg_vec[]) {
 
@@ -493,6 +492,29 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint cluster = get_cluster_containing_index(nv, target);
       const uint target_in_cluster = get_index_in_cluster(target, nv.clusters.at(cluster));
+
+
+
+      // rotate into the frame of the nuclei
+      const uint spins = nv.clusters.at(cluster).size()+1;
+      MatrixXcd R = MatrixXcd::Identity(pow(2,spins),pow(2,spins));
+      for(uint index: nv.clusters.at(cluster)){
+        const uint index_in_cluster = get_index_in_cluster(index, nv.clusters.at(cluster));
+        const Matrix2cd R_index = rotate(natural_basis(nv,index), {xhat,yhat,zhat});
+        R = (act(R_index, {index_in_cluster+1},spins) * R).eval();
+      }
+      const MatrixXcd U_e = R.adjoint() * U.at(true) * R;
+      const MatrixXcd U_a = R.adjoint() * U.at(false) * R;
+      const double err = 1e-2;
+      cout << endl;
+      U_print(j*log(U_e)/pi, err);
+      cout << endl << endl;
+      U_print(j*log(U_a)/pi, err);
+      cout << endl;
+
+
+
+
       cout << target << ": " << gate_fidelity(U.at(0), U.at(1), {target_in_cluster}) << endl;
     }
   }
@@ -511,6 +533,28 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint cluster = get_cluster_containing_index(nv, target);
       const uint target_in_cluster = get_index_in_cluster(target, nv.clusters.at(cluster));
+
+
+
+      // rotate into the frame of the nuclei
+      const uint spins = nv.clusters.at(cluster).size()+1;
+      MatrixXcd R = MatrixXcd::Identity(pow(2,spins),pow(2,spins));
+      for(uint index: nv.clusters.at(cluster)){
+        const uint index_in_cluster = get_index_in_cluster(index, nv.clusters.at(cluster));
[…]

### 2016-04-08 misc/notes.tex
updates notes.txt and todo list

@@
   \t{cNOT}^{NV,2}{i\t{SWAP}^\dag}^{NV,1}\t{cNOT}^{NV,2}i\t{SWAP}^{NV,1},
-\end{align}
-and in turn
-\begin{multline}
-  \t{SWAP}^{NV,ST}\cong \\
-  \exp\p{i\f\pi4\sigma_x^{NV}\sigma_x^{ST}}
-  \p{X\t{HG}}^{NV}i\t{SWAP}^{NV,1}\E^{NV,2}
-  \t{cNOT}^{NV,2}{i\t{SWAP}^\dag}^{NV,1}\t{cNOT}^{NV,2}i\t{SWAP}^{NV,1},
-  \label{swap_no_zz}
-\end{multline}
-where
-\begin{align}
-  \sigma_x^{ST}=\op{S}{T}+\op{T}{S}+iI_r
-  \cong\f12\p{\sigma_z^1-\sigma_z^2}.
-\end{align}
-The construction in (\ref{swap_no_zz}) avoids couplings of the form
-$\sigma_z^{NV}\sigma_z^j$.
+  \label{swap_own}
+\end{align}
 
@@
   i\t{SWAP}^{NV,1}R_z^1\p{-\f\pi2}R_z^{NV}\p{-\f\pi2}.
-  \label{swap_no_zz_cnot}
+  \label{swap_cnots}
 \end{multline}
-The constructions in (\ref{swap_no_zz}) and (\ref{swap_no_zz_cnot})
-are theoretically equal (up to global phase), but may have different
+The constructions in (\ref{swap_own}) and (\ref{swap_cnots}) are
+theoretically equal (up to global phase), but may have different
 fidelities in practice.
@@
 
-\newpage
-
-\section*{Addressing larmor pairs}
-
-When applying a static control field $\v B_{\t{ctl}}$, we have the
-effective interaction + control Hamiltonian
-\begin{align}
-  H=\f12m_s\sigma_z\sum_j\v A_j\c\v I_j-\sum_j\gamma_j\v
-  B_{\t{ctl}}\c\v I_j
-\end{align}
-
 \end{document}

### 2016-04-27 nv-control.cpp
enforce 90-character code width

@@ -11,9 +11,9 @@ using namespace Eigen;
 #include "nv-gates.h"
 #include "nv-control.h"
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Coordinate systems
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // return "natural" basis of a nucleus
 vector<Vector3d> natural_basis(const nv_system& nv, const uint index){
@@ -41,9 +41,9 @@ MatrixXcd to_natural_frames(const nv_system& nv, const vector<uint> cluster){
   return rotation;
 }
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // General control methods
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // check whether a nucleus is addressable
 bool can_address(const nv_system& nv, const uint target){
@@ -62,7 +62,7 @@ bool can_address(const nv_system& nv, const uint target){
     const Vector3i s_xy = xy_int_pos(s);
     const Vector3i s_z = z_int_pos(s);
     if(s_z.squaredNorm() == r_z.squaredNorm() && (s_xy == r_xy || s_xy == -r_xy)){
-      // target has a larmor pair with same x-y component of the hyperfine field (up to sign)
+      // target has a larmor pair with a parallel x-y component of the hyperfine field
       return false;
     }
   }
@@ -292,8 +292,9 @@ protocol couple_target(const nv_system& nv, const uint target, const double phas
     const Matrix4cd U =
       exp(-j * phase * tp(dot(s_vec,hat(nv_axis)), dot(s_vec,hat(target_axis))));
 
-    const MatrixXcd G = act(target_to_natural_basis * U * target_to_natural_basis.adjoint(),
-                            {0, target_in_cluster+1}, spins);
+    const MatrixXcd G =
+      act(target_to_natural_basis * U * target_to_natural_basis.adjoint(),
+          {0, target_in_cluster+1}, spins);
     return protocol(G,0);
   }
 
@@ -308,11 +309,12 @@ protocol couple_target(const nv_system& nv, const uint target, const double phas
   return target_to_equator.adjoint() * coupling_xy * target_to_equator;
 }
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Specific operations
[…]

### 2016-04-27 nv-control.h

@@ -5,9 +5,9 @@ using namespace std;
 #include <eigen3/Eigen/Dense> // linear algebra library
 using namespace Eigen;
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Coordinate systems
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // return "natural" basis of a nucleus
 vector<Vector3d> natural_basis(const nv_system& nv, const uint index);
@@ -25,9 +25,9 @@ inline MatrixXcd to_natural_frames(const nv_system& nv, const uint cluster){
   return to_natural_frames(nv, nv.clusters.at(cluster));
 }
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // General control methods
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // check whether a nucleus is addressable
 bool can_address(const nv_system& nv, const uint target);
@@ -62,9 +62,9 @@ protocol couple_target(const nv_system& nv, const uint target, const double phas
                        const Vector3d& nv_axis, const Vector3d& target_axis,
                        const bool exact = false, const bool adjust_AXY = true);
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Specific operations
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // iSWAP operation
 inline protocol iSWAP(const nv_system& nv, const uint index, const bool exact = false){

### 2016-04-27 nv-gates.h

@@ -61,7 +61,8 @@ struct nv_gates{
 
   // operations between NV and ST qubits
   const MatrixXcd cNOT_NVST = act(cZ,{0,1},3);
-  const MatrixXcd cNOT_STNV = act(E,{1,2},3) * act(cNOT,{1,0},3) * act(E.adjoint(),{1,2},3);
+  const MatrixXcd cNOT_STNV =
+    act(E,{1,2},3) * act(cNOT,{1,0},3) * act(E.adjoint(),{1,2},3);
   const MatrixXcd SWAP_NVST = cNOT_NVST * cNOT_STNV * cNOT_NVST;
 
   // spin propagators; Ua corresponds to a Hamiltonian H = h s_a

### 2016-04-27 nv-math.cpp

@@ -9,9 +9,9 @@ using namespace Eigen;
 #include "qp-math.h"
 #include "nv-math.h"
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Spin vectors and structs
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // rotate into one basis from another
 Matrix2cd rotate(const vector<Vector3d>& basis_end, const vector<Vector3d>& basis_start){
@@ -59,9 +59,9 @@ nv_system::nv_system(const int ms, const double static_Bz, const axy_harmonic k_
   scale_factor(scale_factor), integration_factor(integration_factor), no_nn(no_nn)
 {};
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Spin clustering methods
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // determine whether two spins are a larmor pair
 bool is_larmor_pair(const nv_system& nv, const uint idx1, const uint idx2){
@@ -75,7 +75,8 @@ bool is_larmor_pair(const nv_system& nv, const uint idx1, const uint idx2){
 // coupling strength between two spins; assumes strong magnetic field in zhat
 double coupling_strength(const spin& s1, const spin& s2){
   const Vector3d r = s2.pos - s1.pos;
-  return abs(s1.g*s2.g/(8*pi*pow(r.norm()*a0/2,3)) * (1-3*dot(hat(r),zhat)*dot(hat(r),zhat)));
+  return abs(s1.g*s2.g/(8*pi*pow(r.norm()*a0/2,3)) *
+             (1-3*dot(hat(r),zhat)*dot(hat(r),zhat)));
 }
 
 // group nuclei into clusters with intercoupling strengths >= coupling_strength
@@ -101,7 +102,8 @@ vector<vector<uint>> cluster_with_coupling(const nv_system& nv,
       for(uint n_new = 0; n_new < nv.nuclei.size(); n_new++){
         if(in_vector(n_new,clustered)) continue;
 
-        // if n_old and n_new are interacting or are a larmor pair, add n_new to this cluster
+        // if n_old and n_new are interacting or are a larmor pair,
+        //   add n_new to this cluster
         if((coupling_strength(nv,n_old,n_new) > min_coupling_strength) ||
            (cluster_by_larmor_frequency && is_larmor_pair(nv,n_old,n_new))){
           cluster.push_back(n_new);
[…]

### 2016-04-27 nv-math.h

@@ -5,11 +5,11 @@ using namespace std;
 #include <eigen3/Eigen/Dense> // linear algebra library
 using namespace Eigen;
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Diamond lattice parameters
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
-// diamond lattice vectors, scaled to the lattice parameter (i.e. the unit cell side length)
+// diamond lattice vectors in units of the lattice parameter at 300 K
 const Vector3d ao = (Vector3d() << 1,1,1).finished()/2;
 const Vector3d a1 = (Vector3d() << 0,1,1).finished();
 const Vector3d a2 = (Vector3d() << 1,0,1).finished();
@@ -36,9 +36,9 @@ inline Vector3i xy_int_pos(const Vector3d& pos){
   return (Vector3i() << round(p(0)), round(p(1)), round(p(2))).finished();
 }
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Spin vectors and structs
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // spin vector for a spin-1/2 particle
 const mvec s_vec = mvec(sx,xhat) + mvec(sy,yhat) + mvec(sz,zhat);
@@ -54,7 +54,8 @@ inline Matrix2cd rotate(const double angle, const Vector3d& axis){
 
 // rotate into one axis from another
 inline Matrix2cd rotate(const Vector3d& axis_end, const Vector3d& axis_start){
-  return rotate(acos(dot(hat(axis_start),hat(axis_end))), hat(axis_start.cross(axis_end)));
+  return rotate(acos(dot(hat(axis_start),hat(axis_end))),
+                hat(axis_start.cross(axis_end)));
 }
 
 // rotate into one basis from another
@@ -97,9 +98,9 @@ struct nv_system{
             const double scale_factor, const double integration_factor, const bool no_nn);
 };
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Spin clustering methods
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // determine whether two spins are a larmor pair
 bool is_larmor_pair(const nv_system& nv, const uint idx1, const uint idx2);
[…]

### 2016-04-27 qp-math.cpp

@@ -10,9 +10,9 @@ using namespace Eigen;
 #include "constants.h"
 #include "qp-math.h"
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Matrix functions
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // tensor product of many matrices
 MatrixXcd tp(const initializer_list<MatrixXcd>& list){
@@ -48,9 +48,9 @@ complex<double> get_phase(const MatrixXcd& A, const double threshold){
   return 1;
 }
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Operator manipulation
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // generate matrix B to act A on qbits qs_act out of qbits_new
 MatrixXcd act(const MatrixXcd& A, const vector<uint>& qs_act, const uint qbits_new){
@@ -154,9 +154,9 @@ MatrixXcd ptrace(const MatrixXcd& A, const vector<uint>& qs_trace){
   return B;
 }
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Gate decomposition and fidelity
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // returns basis element p for an operator acting on a system with N spins
 MatrixXcd U_basis_element(const uint p, const uint N){
@@ -239,9 +239,9 @@ double gate_fidelity(const MatrixXcd& U, const MatrixXcd& G, const vector<uint>&
   return gate_fidelity(U*exp(j*H_env),G);
 }
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Matrix vectors
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 mvec operator*(const MatrixXcd& G, const mvec& v){
   vector<MatrixXcd> out;
@@ -251,9 +251,9 @@ mvec operator*(const MatrixXcd& G, const mvec& v){
   return mvec(out);
 }
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Printing methods
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // print operator in human-readable form
 void U_print(const MatrixXcd& U, const double threshold){

### 2016-04-27 qp-math.h

@@ -33,9 +33,9 @@ inline Vector3d rotate(const Vector3d& vec, const double angle, const Vector3d& 
           sin(angle) * hat(axis).cross(vec));
 }
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Matrix functions
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 inline complex<double> trace(const MatrixXcd& M){ return M.trace(); }
 inline MatrixXcd log(const MatrixXcd& M){ return M.log(); }
@@ -44,7 +44,9 @@ inline MatrixXcd sqrt(const MatrixXcd& M){ return M.sqrt(); }
 inline MatrixXcd pow(const MatrixXcd& M, const double x){ return M.pow(x); }
 
 // tensor product of two matrices
-inline MatrixXcd tp(const MatrixXcd& A, const MatrixXcd& B){ return kroneckerProduct(A,B); }
+inline MatrixXcd tp(const MatrixXcd& A, const MatrixXcd& B){
+  return kroneckerProduct(A,B);
+}
 
 // tensor product of many matrices
 MatrixXcd tp(const initializer_list<MatrixXcd>& list);
@@ -65,9 +67,9 @@ inline MatrixXcd clean(const MatrixXcd& M, double threshold = 1e-3){
   return remove_artifacts(remove_phase(M,threshold),threshold);
 }
 
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 // Operator manipulation
-//--------------------------------------------------------------------------------------------
+// ---------------------------------------------------------------------------------------
 
 // get the n-th bit of an integer num
 inline bool int_bit(const uint num, const uint n){
@@ -76,7 +78,9 @@ inline bool int_bit(const uint num, const uint n){
 }
 
 // get state of qbit q (of N) from enumerated state s
-inline bool qbit_state(const uint q, const uint N, const uint s){ return int_bit(s,N-1-q); }
+inline bool qbit_state(const uint q, const uint N, const uint s){
+  return int_bit(s,N-1-q);
+}
 
 // get integer corresponding to an 'on' state of bit p (of N)
 inline uint bit_int(const uint q, const int N){ return pow(2,N-1-q); }
[…]

### 2016-04-27 simulation.cpp

@@ -21,9 +21,9 @@ namespace po = boost::program_options;
 
 int main(const int arg_num, const char *arg_vec[]) {
 
-  // -----------------------------------------------------------------------------------------
+  // -------------------------------------------------------------------------------------
   // Parse and process input options
-  // -----------------------------------------------------------------------------------------
+  // -------------------------------------------------------------------------------------
 
   const uint help_text_length = 95;
 
@@ -68,9 +68,11 @@ int main(const int arg_num, const char *arg_vec[]) {
      "search for larmor pairs")
     ("scan", po::value<bool>(&coherence_scan)->default_value(false)->implicit_value(true),
      "perform coherence scan for effective larmor frequencies")
-    ("control", po::value<bool>(&single_control)->default_value(false)->implicit_value(true),
+    ("control",
+     po::value<bool>(&single_control)->default_value(false)->implicit_value(true),
      "control individual nucleus")
-    ("couple", po::value<bool>(&single_coupling)->default_value(false)->implicit_value(true),
+    ("couple",
+     po::value<bool>(&single_coupling)->default_value(false)->implicit_value(true),
      "couple individual nucleus to NV center")
     ("iswap",
      po::value<bool>(&iswap_fidelities)->default_value(false)->implicit_value(true),
@@ -154,7 +156,8 @@ int main(const int arg_num, const char *arg_vec[]) {
   addressing_options.add_options()
     ("targets", po::value<vector<uint>>(&target_nuclei)->multitoken(),
      "indices of nuclei to target")
-    ("phase", po::value<double>(&phase_over_pi)->default_value(0.5,"0.5"), "operation phase")
+    ("phase", po::value<double>(&phase_over_pi)->default_value(0.5,"0.5"),
+     "operation phase")
     ("target_polar", po::value<double>(&target_polar_over_pi)->default_value(0.5,"0.5"),
      "polar angle of target rotation axis")
     ("target_azimuth", po::value<double>(&target_azimuth_over_pi)->default_value(0),
@@ -242,7 +245,8 @@ int main(const int arg_num, const char *arg_vec[]) {
     lattice_path = lattice_file;
 
     if(!set_output_suffix){
-      output_suffix = lattice_path.stem().string() + "-" + output_suffix_with_input_lattice;
+      output_suffix =
+        lattice_path.stem().string() + "-" + output_suffix_with_input_lattice;
     }
 
[…]

### 2016-05-19 pair-compute.py
changed some naming conventions and removed some obsolete lines of code in pair-compute.py

@@ -39,48 +39,44 @@ a3 = np.array([1,1,0])
 norm = np.linalg.norm
 def hat(v): return v/norm(v)
 def A(b,l,m,n):
-    r = b*ao+l*a1+m*a2+n*a3
+    r = b*ao + l*a1 + m*a2 + n*a3
     return norm( ge*gC13/(4*np.pi*(norm(r)*a0/2)**3) *
                  (zhat-3*np.dot(hat(r),zhat)*hat(r)) )
 
+def z_projection_sum(iv): return abs(3*iv[0] + 4*(iv[1]+iv[2]+iv[3]))
+def xy_projection_sum(iv): return 3*(iv[1]**2+iv[2]**2+iv[3]**2) - (iv[1]+iv[2]+iv[3])**2
+
 # maximum allowable magnitude of l, m, or n
-M = int((2*abs(ge*gC13) / (np.pi * a0**3 * hyperfine_cutoff))**(1./3)+1./2)
+max_lmn = int((2*abs(ge*gC13) / (np.pi * a0**3 * hyperfine_cutoff))**(1./3)+1./2)
 
-# list of all equivalence classes of integers (b,l,m,n)
-equivalence_classes = []
+# list of all larmor sets
+larmor_sets = []
 
-# loop over each quarter-integer N <= 3*M (N_4 = 4*N)
-for N_times_4 in range(1,12*M+1):
+# loop over each integer z_sum up to the maximum possible value given the hyperfine cutoff
+# start at 1 to exclude solutions in the x-y plane
+for z_sum in range(1,12*max_lmn+1):
 
-    # vector of integers (b,l,m,n) satisfying abs(l+m+n) == N
-    sum_solutions = [ (b,l,m,n)
-                      for b in [0,1]
-                      for l in range(-M,M+1)
-                      for m in range(-M,M+1)
-                      for n in range(-M,M+1)
-                      if abs(3*b + 4*(l+m+n)) == N_times_4
-                      if A(b,l,m,n) > hyperfine_cutoff ]
+    # vector of integers (b,l,m,n) with this z_sum
+    z_sum_solutions = set([ (b,l,m,n)
+                            for b in [0,1]
+                            for l in range(-max_lmn,max_lmn+1)
+                            for m in range(-max_lmn,max_lmn+1)
+                            for n in range(-max_lmn,max_lmn+1)
+                            if z_projection_sum((b,l,m,n)) == z_sum
[…]

### 2016-05-19 pair-compute.py
minor change to comment

@@ -53,7 +53,7 @@ max_lmn = int((2*abs(ge*gC13) / (np.pi * a0**3 * hyperfine_cutoff))**(1./3)+1./2
 larmor_sets = []
 
 # loop over each integer z_sum up to the maximum possible value given the hyperfine cutoff
-# start at 1 to exclude solutions in the x-y plane
+# start at 1 to exclude nuclei which lie in the x-y plane
 for z_sum in range(1,12*max_lmn+1):
 
     # vector of integers (b,l,m,n) with this z_sum

### 2016-05-19 misc/notes.tex
enforce 90-character code width
added derivation of probability formula in pair-compute.py

@@
 
-If we have a set of $R$ lattice sites indexed by $(b,\l,m,n)$ mutually
-satisfying (\ref{condA0}) and (\ref{condB0}), then the probability of
-filling exactly $r$ of them with $^{13}$C nuclei is
-\begin{align}
-  P_{R,r}=p^r\p{1-p}^{R-r}\m{R\\r}=\f{R!~p^r\p{1-p}^{R-r}}{r!\p{R-r}!},
-\end{align}
-where $p$ is the probability that any particular site with a $^{13}$C
-nucleus, i.e. the relative abundance of $^{13}$C. The probability of
-having at least two $^{13}$C nuclei in these sites is therefore
-\begin{align}
-  P_{R,r\ge2}=\sum_{r=2}^RP_{R,r}=1-\p{P_{R,0}+P_{R,1}}.
-\end{align}
-If we have many such sets of lattice sites, then the total probability
-$\bar P$ of having at least two sites filled within at least one set
-of sites is
-\begin{align}
-  \bar P=1-\prod_R\p{1-P_{R,r\ge2}} =1-\prod_R\p{P_{R,0}+P_{R,1}}
-  =1-\prod_R\p{1-p}^R\p{1+\f{Rp}{1-p}}.
-\end{align}
+Let $p$ denote the isotopic abundance of $^{13}$C, and consider a set
+$R$ of diamond lattice sites mutually satisfying (\ref{condA0}) and
+(\ref{condB0}). If there are $N$ ways of filling exactly 2 out of the
+lattice sites in $R$ with $^{13}$C nuclei in such a way that both
+$^{13}$C nuclear spins are addressable, the probability of doing so is
+\begin{align}
+  P_{R,2}=p^2\p{1-p}^{\abs{R}-2}N.
+\end{align}
+Though there are $\m{\abs{R}\\2}$ ways total of filling the lattice
+sites in $R$ with exactly 2 nuclei, in some of these configurations
+the perpendicular components of the hyperfine fields (i.e.
+$\v A_j^\perp$) for these nuclei are mutually parallel, which makes
+the spins of these nuclei unaddressable. If there is a subset
+$S_R\subset R$ of lattice sites within which the $\v A_j^\perp$ for
+all lattice sites $s_j\in S_R$ are mutually parallel, then there are
+$\m{\abs{S_R}\\2}$ configurations out of the $\m{\abs{R}\\2}$ which
+must be excluded in the counting of $N$; therefore,
+\begin{align}
+  P_{R,2}=p^2\p{1-p}^{\abs{R}-2}
+  \sp{\m{\abs{R}\\2}-\sum_{S_R}\m{\abs{S_R}\\2}}.
+\end{align}
+The total probability $\bar P$ of finding at least one pair of
+addressable $^{13}$C nuclear spins in an NV system with multiple sets
+of larmor equal lattice sites is therefore
+\begin{align}
+  \bar P=1-\prod_R\p{1-P_{R,2}}
+  =1-\prod_R\p{1-p^2\p{1-p}^{\abs{R}-2}
+  \sp{\m{\abs{R}\\2}-\sum_{S_R}\m{\abs{S_R}\\2}}},
+\end{align}
+where the product over $R$ excludes sets of lattice sites at which
+individual nuclei are unaddressable (i.e. lattice sites along the
+natural NV axis $\uv z$, and lattice sites $\v s$ for which
+$\v s\c\uv z=0$).
 

### 2016-06-03 run-jobs.py
changes to run-jobs.py input format

@@ -1,16 +1,30 @@
 #!/usr/bin/env python
-import sys, numpy, subprocess, glob
+import sys, os, numpy, subprocess, glob
 from basename import basename
 
-test_jobs = "test" in sys.argv
-real_jobs = "real" in sys.argv
-assert (test_jobs or real_jobs)
+def input_error():
+    print("usage: " + sys.argv[0] + " sim_type [test] [mkfac.py args]")
+    exit(1)
 
-sim_type = "swap_nvst"
+if len(sys.argv) < 3: input_error()
+
+sim_type = sys.argv[1]
+if sys.argv[2] == "test":
+    test_jobs = True
+    mkfac_args = sys.argv[3:]
+else:
+    test_jobs = False
+    mkfac_args = sys.argv[2:]
+
 c13_natural_percentage = 1.07
 
+project_dir = os.path.dirname(os.path.realpath(__file__))
+run_script = "run-sweep.py"
+
 def cmd_args(sim_args, walltime):
-    return [ "./run-sweep.py" ] + [ str(a) for a in sim_args] + [ walltime, "whide" ]
+    return ([ "{}/{}".format(project_dir,run_script) ]
+            + [ str(a) for a in sim_args]
+            + [ walltime ] + mkfac_args)
 
 for static_Bz in [ 500, 1000, 1500 ]:
     for c13_factor in [ 1, 0.1, 0.01 ]:
@@ -25,7 +39,7 @@ for static_Bz in [ 500, 1000, 1500 ]:
                 if test_jobs:
                     subprocess.call(cmd_args(sim_args,3))
 
-                if real_jobs:
+                else:
                     test_job_name = "./jobs/" + basename(sim_args) + ".o_feedback"
                     fname_candidates = glob.glob(test_job_name)
                     assert (len(fname_candidates) == 1)

### 2016-06-03 fidelity-hist.py
print proportion of samples passing the fidelity cutoff

@@ -1,8 +1,8 @@
 #!/usr/bin/env python
-import sys, os
+import sys, os, re
 
 if len(sys.argv) not in [2,3]:
-    print("usage: {} fidelity_sweep_file [cutoff] [print]".format(sys.argv[0]))
+    print("usage: {} fidelity_data_file [cutoff] [print]".format(sys.argv[0]))
     exit(1)
 
 print_results = True if sys.argv[-1] == "print" else False
@@ -17,6 +17,7 @@ else:
 if not os.path.isfile(fname):
     print("invalid file: {}".format(fname))
     exit(1)
+samples = 10**int(re.split("-|\.",fname)[-2])
 
 results = []
 collect = False
@@ -47,4 +48,6 @@ filtered_results = [ r for r in results if r[0] > cutoff ]
 if print_results:
     for result in filtered_results:
         print(result)
+
 print(len(filtered_results)/len(results))
+print(len(filtered_results)/samples)

### 2016-06-03 swap-nvst-paper/paper.tex
added working draft of swap-nvst paper

\documentclass[twocolumn]{revtex4}

% \usepackage{showframe}

\usepackage{hyperref} % for linking references

%%% math, symbols, etc.
\usepackage{physics,braket,bm,bbm}
\renewcommand{\t}{\text} % text in math mode
\newcommand{\f}[2]{\dfrac{#1}{#2}} % shorthand for fractions
\newcommand{\p}[1]{\left(#1\right)} % square parenthesis
\renewcommand{\sp}[1]{\left[#1\right]} % square parenthesis
\renewcommand{\set}[1]{\left\{#1\right\}} % curly parenthesis
\renewcommand{\v}{\bm} % bold vectors
\newcommand{\uv}[1]{\hat{\v{#1}}} % unit vectors
\renewcommand{\c}{\cdot} % inner product
\newcommand{\bk}{\Braket} % shorthand for braket notation

% shorthand for frequently used commands
\renewcommand{\u}{\uparrow}
\renewcommand{\d}{\downarrow}
\newcommand{\SWAP}{\t{SWAP}}
\newcommand{\cNOT}{\t{cNOT}}
\newcommand{\NV}{\t{NV}}
\newcommand{\AC}{\t{AC}}
\newcommand{\ST}{\t{ST}}
\renewcommand{\S}{\t{S}}
\newcommand{\T}{\t{T}}

%%% figures
\usepackage{graphicx,grffile,float} % floats, etc.
\usepackage{multirow} % multirow entries in tables
\usepackage{footnote} % footnotes in floating objects
\usepackage[font=small,labelfont=bf]{caption} % caption text options

%%% markup
\usepackage{color,soul} % text color and other editing options
% \ul{underline}, \st{strikethrough}, and \hl{highlight}
\usepackage[draft]{fixme} % in text notes
% \fxsetup{layout=footnote}
\newcommand{\nt}{\fxnote}
\newcommand{\re}[1]{{\bf \color{red} #1}}
\newcommand{\bl}[1]{{\bf \color{blue} #1}}

\begin{document}

\title{Noise-Protected Quantum Memory Registers with Nitrogen-Vacancy
  Centers and $^{13}$C Nuclear Spins}

\author{Michael A. Perlin, Zhen-Yu Wang, and Martin B. Plenio}

\affiliation{Institut f\"ur Theoretische Physik, Albert-Einstein-Allee
  11, Universit\"at Ulm, D-89069 Ulm, Germany}

\begin{abstract}
  Here is the abstract.
\end{abstract}

\maketitle

\section{Introduction}

Nitrogen-vacancy (NV) centers in diamond have been recognized in
recent years as a promising platform for quantum sensing and
information technologies. The electronic ground and optically excited
states of NV$^-$ split into spin triplets which can be polarized,
detected, and coherently manipulated with high fidelity with fields
and microwave radiation \cite{dobrovitski2013quantum}. Hyperfine
coupling between the NV center electron and $^{13}$C nuclei in bulk
diamond allows for the coherent control and measurement of individual
nuclear spins, and the realization of universal set of high-fidelity
quantum gates \cite{dobrovitski2013quantum, casanova2016noise}. These
properties have prompted extensive studies of NV centers for quantum
metrology and information processing applications
\cite{mamin2013nanoscale, steinert2010high, wang2015positioning,
  chou2015optimal, childress2006fault, yao2012scalable}. % fixme: the
% first and last sentences of this paragraph are essentially the same

One such application of the NV center is as a memory register to store
quantum information. While typical control operations on the NV
electron spin happen on the scale of nanoseconds, its room-temperature
coherence time is on the scale of microseconds
\cite{dobrovitski2013quantum}.  Dynamic decoupling schemes and the use
of isotopically pure diamond samples can increase the NV electron spin
coherence time by a few orders of magnitude
\cite{ryan2010robust}. Storing quantum information in the NV electron
spin itself, however, reserves a valuable resource, as the center
could otherwise be used to address nuclear spins and other quantum
processing resources. The weaker environmental coupling of $^{13}$C
nuclei present in diamond yields much longer coherence times than that
of the NV electron spin, and by entangling multiple nuclear spins into
the singlet-triplet states $\p{\ket{\u\d}\pm\ket{\d\u}}/\sqrt2$, it is
possible to generate logical qubits which are protected from various
sources of system and environmental dephasing noise. Such techniques
have been used to increase qubit lifetimes in both GaAs and silicon
quantum dots \cite{bluhm2011dephasing, maune2012coherent}, but have
yet to be realized in the NV center system.

In this paper, we propose using the singlet-triplet subspace of two
$^{13}$C nuclear spins with identical effective larmor frequencies as
a logical qubit for storing quantum memory. Here identical effective
larmor frequencies implies that, absent of symmetry-breaking control
fields, the nuclei are indistinguishable from the perspective of the
NV electron. This indistinguishability protects the logical qubit from
dephasing via coupling to the NV electron spin, potentially increasing
its coherence time by a few orders of magnitude. % fixme: elaborate
We investigate the efficacy of this quantum memory register when
realized via the recently developed dynamical decoupling protocol
dubbed adaptive XY-$n$ (AXY-$n$) \cite{casanova2015robust}.

\section{Theory}

\subsection{Basic system model}

The Hamiltonian of the NV center system in the presence of a strong,
static magnetic field $\v B$ can be decomposed as
\begin{align}
  H_\t{sys} = H_\t{NV}^\t{GS} + H_\t{hf} + H_\t{nZ}  + H_\t{nn},
\end{align}
where
\begin{align}
  H_\t{NV}^\t{GS} = D\p{\v S\c\uv z}^2 - \gamma_e\v B\c\v S
\end{align}
is the ground-state NV electron spin Hamiltonian with zero-field
splitting $D$, spin-1 operator $\v S$, natural NV axis $\uv z$, and
electron gyromagnetic ratio $\gamma_e$;
\begin{align}
  H_\t{hf} = \sum_j\f{\gamma_e\gamma_j}{4\pi r_j^3}
  \p{\v S\c\v I_j-3\sp{\v S\c\uv r_j}\sp{\v I_j\c\uv r_j}}
\end{align}
is the hyperfine coupling between the NV electron spin (located at the
origin) and nuclei indexed by $j$ located at $\v r_j$;
\begin{align}
  H_\t{nZ} = -\sum_j\gamma_j\v B\c\v I_j
\end{align}
is the Zeeman Hamiltonian for nuclei indexed by $j$ with gyromagnetic
ratio $\gamma_j$ and spin operators $\v I_j$; and
\begin{align}
  H_\t{nn} = \sum_{j<k}\f{\gamma_j\gamma_k}{4\pi r_{jk}^3}
  \p{\v I_j\c\v I_k-3\sp{\v I_j\c\uv r_{jk}}\sp{\v I_k\c\uv r_{jk}}}
\end{align}
is the internuclear coupling with $\v r_{jk}\equiv\v r_j-\v r_k$. We
will hereafter neglect internuclear coupling in all analytical work,
though we will keep $H_\t{nn}$ in any numerical results.

Changing into the rotating frame of $H_\t{NV}^\t{GS}$ affects only the
hyperfine Hamiltonian, which becomes
\begin{align}
  \tilde H_\t{hf} = S_z\sum_j \v A_j\c\v I_j,
\end{align}
where we define the hyperfine field
\begin{align}
  \v A_j = \f{\gamma_e\gamma_j}{4\pi r_j^3}\p{\uv z - 3\sp{\uv
  r_j\c\uv z}\uv r_j}.
\end{align}
The system Hamiltonian is thus
\begin{align}
  \tilde H_\t{sys} = S_z\sum_j \v A_j\c\v I_j
  -\sum_j\gamma_j\v B\c\v I_j.
\end{align}

When restricted to the subspace of $\set{\ket0,\ket{m_s}}$ for the NV
electron spin, with $m_s\in\set{1,-1}$, we can say that
\begin{align}
  S_z = \f{m_s}2\p{\sigma_z^{NV}+\mathbbm1},
\end{align}
where $\sigma_z^{NV}\equiv\op{m_s}-\op{0}$ and
$\mathbbm1\equiv\op{m_s}+\op{0}$ is the identity. Defining the
interaction Hamiltonian
\begin{align}
  H_\t{int} = \f{m_s}2\sigma_z^{NV}\sum_j\v A_j\c\v I_j
\end{align}
the effective larmor frequency
\begin{align}
  \v\omega_j = \gamma_j\v B - \f{m_s}2\v A_j,
\end{align}
and the effective Zeeman Hamiltonian
\begin{align}
  H_\t{nZ}^\t{eff} = -\sum_j\p{\gamma_j\v B - \f{m_s}2\v A_j}\c\v I_j
  \equiv -\sum_j\v\omega_j\c\v I_j,
\end{align}
we can say that
\begin{align}
  \tilde H_\t{sys} = H_\t{int} + H_\t{nZ}^\t{eff}.
  \label{H_sys_int_nZ}
\end{align}

Moving into the rotating frame of $H_\t{nZ}^\t{eff}$, the entire
system is described the the Hamiltonian
\begin{align}
  \tilde H_\t{int} = \f{m_s}2\sigma_z^{NV}
  \sum_j\tilde{\v A_j}\p{t}\c\v I_j,
  \label{H_int_no_DD}
\end{align}
where $\tilde{\v A_j}\p{t}$ is the vector $\v A_j$ rotated about
$\uv\omega_j$ by an angle $\omega_jt$. Written explicitly,
\begin{align}
  \tilde{\v A_j}\p{t} = \v A_j^\parallel + \v A_j^\perp\cos\p{\omega_jt}
  + \v A_j^{\perp\perp}\sin\p{\omega_jt},
  \label{A_rot}
\end{align}
where $\v A_j^\parallel\equiv\p{\v A_j\c\uv\omega_j}\uv\omega_j$ is
the projection of $\v A_j$ along $\v \omega_j$,
$\v A_j^\perp\equiv\v A_j-\v A_j^\parallel$ is the projection of
$\v A_j$ onto the plane orthogonal to $\v\omega_j$, and
$\v A_j^{\perp\perp}\equiv\uv\omega_j\times\v A_j^\perp$ is the vector
$\v A_j^\perp$ rotated about $\uv\omega_j$ by $\pi/2$.

\subsection{Dynamic decoupling and nuclear spin addressing}

Dynamic decoupling schemes effectively prepend a modulation function
\begin{align}
  F\p{t}=\sum_kf_k\cos\p{k\omega_{DD}t-\phi_{DD}}
\end{align}
with fundamental frequency $\omega_{DD}$, phase $\phi_{DD}$, and range
$\set{1,-1}$ to $\sigma_z^{NV}$, so that the system Hamiltonian reads
\begin{align}
  \tilde H_\t{int} =
  F\p{t}\f{m_s}2\sigma_z^{NV}\sum_j\tilde{\v A_j}\p{t}\c\v I_j.
\end{align}
At a resonance $k_{DD}\omega_{DD}\equiv\omega_r\gg A_j$, the secular
approximation allows one to neglect $\v A_j^\parallel$ and express
\begin{align}
  \tilde H_\t{int} = f_{k_{DD}}\f{m_s}4\sigma_z^{NV}
  \sum_{j:\omega_j=\omega_r} A_j^\perp\v I_j\c\uv n_j,
  \label{H_int_resonance}
\end{align}
where $\uv n_j$ is the direction of $\v A_j^\perp$ rotated about
$\uv\omega_j$ by $\phi_{DD}$, i.e.
\begin{align}
  \uv n_j = \uv A_j^\perp\cos\phi_{DD} +
  \uv A_j^{\perp\perp}\sin\phi_{DD}.
\end{align}
One can concisely write (\ref{H_int_resonance}) with
$h_j^\t{int}\equiv f_{k_{DD}}m_sA_j^\perp/8$ and the Pauli spin-1/2
vector $\v\sigma^j$ (as we consider only spin-1/2 nuclei) as
\begin{align}
  \tilde H_\t{int} = \sum_{j:\omega_j=\omega_r}
  h_j^\t{int}\sigma_z^{NV}\v\sigma^j\c\uv n_j.
  \label{H_int}
\end{align}

When the harmonics of $F\p{t}$ are off resonance with all $\omega_j$
and $\omega_{DD}\gg A_j$ for all $j$, the secular approximation allows
one to neglect $H_\t{int}$ entirely. In this case, one can apply an
auxiliary magnetic field
$\v B_\t{ctl}^{\p\omega}\p{t}=\v
B_\t{ctl}\cos\p{\omega_\t{ctl}t-\phi_\t{ctl}}$ and shift into the
rotating frame of $H_\t{nZ}^\t{eff}$, much like the frame shift
between (\ref{H_sys_int_nZ}) and (\ref{H_int_no_DD}), to realize the
Hamiltonian
\begin{align}
  \tilde H_\t{sys}^\t{ctl} =
  -\sum_j\gamma_j\tilde{\v B}_{\t{ctl},j}\p{t}
  \cos\p{\omega_\t{ctl}t-\phi_\t{ctl}}\c\v I_j,
\end{align}
with $\tilde{\v B}_{\t{ctl},j}\p{t}$ defined using $\v B_\t{ctl}$ and
$\v\omega_j$ the same way that $\tilde{\v A_j}\p{t}$ was defined using
$\v A_j$ and $\v\omega_j$ in (\ref{A_rot}), i.e. as $\v B_\t{ctl}$
rotated about $\uv\omega_j$ by an angle $\omega_jt$:
\begin{align}
  \tilde{\v B}_{\t{ctl},j}\p{t} = \v B_{\t{ctl},j}^\parallel
  + \v B_{\t{ctl},j}^\perp\cos\p{\omega_jt}
  + \v B_{\t{ctl},j}^{\perp\perp}\sin\p{\omega_jt},
\end{align}
where
$\v B_{\t{ctl},j}^\parallel\equiv\p{\v B_\t{ctl}
  \c\uv\omega_j}\uv\omega_j$,
$\v B_{\t{ctl},j}^\perp\equiv\v B_\t{ctl} - \v
B_{\t{ctl},j}^\parallel$, and
$\v B_{\t{ctl},j}^{\perp\perp}\equiv\uv\omega_j\times\v
B_\t{ctl}^\perp$.

When $\omega_\t{ctl}\gg\gamma_jB_\t{ctl}$, the secular approximation
allows one to neglect $\v B_{\t{ctl},j}^\parallel$ and express
\begin{align}
  \tilde H_\t{ctl} = -\f12\sum_{j:\omega_j=\omega_\t{ctl}}
  \gamma_jB_{\t{ctl},j}^\perp \v I_j\c\uv m_j,
  \label{H_ctl_resonance}
\end{align}
where $\uv m_j$ is the direction of $\v B_{\t{ctl},j}^\perp$ rotated
about $\uv\omega_j$ by $\phi_\t{ctl}$, i.e.
\begin{align}
  \uv m_j = \uv B_{\t{ctl},j}^\perp\cos\phi_\t{ctl} +
  \uv B_{\t{ctl},j}^{\perp\perp}\sin\phi_\t{ctl}.
\end{align}
One can concisely write (\ref{H_ctl_resonance}) with
$h_j^\t{ctl}\equiv-\gamma_jB_{\t{ctl},j}^\perp/4$ and the Pauli
spin-1/2 vector $\v\sigma^j$ as
\begin{align}
  \tilde H_\t{ctl} = \sum_{j:\omega_j=\omega_\t{ctl}}
  h_j^\t{ctl}\v\sigma^j\c\uv m_j.
  \label{H_ctl}
\end{align}

In both (\ref{H_int}) and (\ref{H_ctl}), one can choose $\phi_{DD}$
and $\phi_\t{ctl}$ such that $\uv n_j\p\phi$ and
$\uv m_j\p{\phi_\t{ctl}}$ lie anywhere in the plane perpendicular to
$\uv\omega_j$. One can also tune $h_j^\t{int}$ and $h_j^\t{ctl}$
respectively via free parameters in the AXY-$n$ sequence and
$\v B_\t{ctl}$. These controls, together with rotations of the NV
electron spin, in principle allow one to realize a universal set of
quantum gates. An exception to this statement is when two or more
nuclei have the same effective larmor frequency $\omega_j$, in which
case they are addressed simultaneously in (\ref{H_int}) and
(\ref{H_ctl}).

\subsection{Addressing larmor pairs}

We call two spins indexed by $j$ and $k$ elements of a \emph{larmor
  set} if their effective larmor frequencies are equal,
i.e. $\omega_j=\omega_k$, and refer to a larmor set with exactly two
spins as a \emph{larmor pair}. The problem with individually
addressing elements of a larmor set is manifest in (\ref{H_int}) and
(\ref{H_ctl}), wherein the previously developed procedure for nuclear
spin addressing does not single out any nuclei. Nonetheless, under
certain conditions it is possible to individually address elements of
a larmor set by applying additional control fields.

When employing a dynamic decoupling protocol on resonance with an
effective larmor frequency $\omega_r$, one can apply an additional
magnetic decoupling field
$\v B_\t{dec}^{\p\omega}\p{t}=\v B_\t{dec}\cos\p{\omega_r
  t-\phi_\t{dec}}$ and realize, with a rotating wave approximation in
the frame of $H_\t{nZ}^\t{eff}$, the Hamiltonian
\begin{align}
  \tilde H_\t{int}^\t{dec} = \sum_{j:\omega_j=\omega_r}
  \tilde h_j^\t{int}\sigma_z^{NV}\v\sigma^j\c\tilde{\v n}_j,
  \label{H_int_dec}
\end{align}
where
\begin{align}
  \tilde h_j^\t{int}
  = h_j^\t{int}\p{\uv A_j^\perp\c\uv B_{\t{dec},j}^\perp}
  = h_j^\t{int}A_{j,\t{dec}}^\perp/A_j^\perp
\end{align}
and
\begin{align}
  \tilde{\v n}_j
  &= \uv A_{j,\t{dec}}^\perp\cos\phi_{DD}
    + \uv A_{j,\t{dec}}^{\perp\perp}\sin\phi_{DD}
\end{align}
with
\begin{align}
  \v A_{j,\t{dec}}^\perp
  &= \p{\v A_j^{\perp}\c\uv B_{\t{dec},j}^\perp}\uv B_{\t{dec},j}^\perp, \\
  \v A_{j,\t{dec}}^{\perp\perp}
  &= \uv\omega_j\times\v A_{j,\t{dec}}^\perp, \\
  \v B_{\t{dec},j}^\perp
  &= \v B_\t{dec} - \p{\v B_\t{dec}\c\uv\omega_j}\uv\omega_j.
\end{align} % fixme: provide derivation of these results?
In words: the decoupling field $\v B_\t{dec}^{\p\omega}$ effectively
suppresses the components of $\v A_j^\perp$ perpendicular to
$\uv B_\t{dec}^\perp$. These results to not depend on $\phi_\t{dec}$,
but do require that $A_j\ll\gamma_jB_{\t{dec},j}^\perp\ll\gamma_jB$.

The utility of the decoupling field lies in the fact that when
$\uv B_\t{dec}^\perp$ is orthogonal to $\v A_j^\perp$, the interaction
with spin $j$ is suppressed as $\tilde h_j^\t{int}=0$. Considering a
single larmor pair, one can therefore apply a decoupling field to
eliminate one of the two terms in (\ref{H_int_dec}) and realize an
effective Hamiltonian which couples the NV electron spin to only one
nuclear spin. This scheme fails for larmor pairs with mutually
parallel $\v A_j^\perp$.

The tools developed in this paper do not allow for single-spin
operations on elements of a larmor pair. Such operations must
therefore be either forgone, or else realized via composite operations
making use of (\ref{H_ctl}) and (\ref{H_int_dec}). The same is true of
spin-spin coupling between the NV electron spin and a single element
of a larmor set with more than two nuclei.

\subsection{Coherent SWAP with a singlet-triplet qubit}

For the following analysis, we will consider a single addressable
larmor pair, i.e. a pair of nuclei indexed by 1 and 2 with effective
larmor frequencies $\omega$ and for which $\v A_j^\perp$ are not
mutually parallel. We will use the basis
$\set{\ket\u\equiv\ket 0, \ket\d\equiv\ket{m_s}}$ for the spin states
of the NV electron, and the standard basis
$\set{\ket{\u\u}, \ket{\u\d}, \ket{\d\u}, \ket{\d\d}}$ for the spin
states of the nuclei. We will refer to the logical qubit consisting of
the basis states $\set{\ket{\u\d},\ket{\d\u}}$ as the anti-correlated
(AC) qubit, and the logical qubit consisting of the basis states
$\set{\ket\S,\ket\T}$ as the singlet-triplet (ST) qubit, where
\begin{align}
  \ket\S &\equiv \f1{\sqrt2}\p{\ket{\u\d}-\ket{\d\u}}, \\
  \ket\T &\equiv \f1{\sqrt2}\p{\ket{\u\d}+\ket{\d\u}}.
\end{align}

A SWAP operation between two qubits indexed by 1 and 2 can be realized
via the composite operation
\begin{align}
  \SWAP^{1,2} = \cNOT^{2\to1}\cNOT^{1\to2}\cNOT^{2\to1},
\end{align}
where $\cNOT^{j\to k}$ is the controlled-NOT gate, which flips the
state of qubit $k$ conditionally on the state of qubit $j$. The
$\cNOT^{j\to k}$ gate is realized via
\begin{multline}
  \cNOT^{j\to k} \\
  = \exp\p{-j\f\pi4\sigma_z^j} \exp\p{-j\f\pi4\sigma_x^k}
  \exp\p{j\f\pi4\sigma_z^j\sigma_x^k}.
\end{multline}

If we wish to perform a SWAP operation between the NV electron spin
and an ST qubit, it is easier to first realize the operation
\begin{multline}
  \SWAP^{\NV,\AC} \\
  = {\cNOT^{\AC\to\NV}}^\dagger\cNOT^{\NV\to\AC}\cNOT^{\AC\to\NV},
  \label{SWAP_NVAC_sketch}
\end{multline}
where
\begin{align}
  \cNOT^{\AC\to\NV} = \cNOT^{1\to\NV}
\end{align}
and
\begin{align}
  \cNOT^{\NV\to\AC} = \cNOT^{\NV\to2}\cNOT^{\NV\to1}.
\end{align}
For later convenience, (\ref{SWAP_NVAC_sketch}) makes use of the fact
that ${\cNOT^{j\to k}}^\dagger=\cNOT^{j\to k}$. Therefore,
\begin{multline}
  \SWAP^{\NV,\AC} = \\
  \exp\p{-j\f\pi4\sigma_x^\NV} \exp\p{j\f\pi4\sigma_{z'}^1}
  \exp\p{-j\f\pi4\sigma_x^\NV\sigma_{z'}^1}
  \times \\
  \exp\p{-j\f\pi4\sigma_z^\NV} \exp\p{-j\f\pi4\sigma_{x'}^1}
  \exp\p{j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
  \times \\
  \exp\p{-j\f\pi4\sigma_z^\NV} \exp\p{-j\f\pi4\sigma_{x''}^2}
  \exp\p{j\f\pi4\sigma_z^\NV\sigma_{x''}^2}
  \times \\
  \exp\p{-j\f\pi4\sigma_x^\NV} \exp\p{-j\f\pi4\sigma_{z'}^1}
  \exp\p{j\f\pi4\sigma_x^\NV\sigma_{z'}^1},
  \label{SWAP_NVAC_full}
\end{multline}
where we make explicit the fact that the the spin of nuclei 1 and 2
may be given in their own respective bases
$\set{\uv x',\uv y',\uv z'}$ and $\set{\uv x'',\uv y'',\uv z''}$. We
can evaluate the first and last rotations of spin 1 in
(\ref{SWAP_NVAC_full}) and combine factors to get
\begin{multline}
  \SWAP^{\NV,\AC} = \exp\p{j\f\pi4\sigma_x^\NV}
  \exp\p{-j\f\pi4\sigma_x^\NV\sigma_{z'}^1}
  \times \\
  \exp\p{-j\f\pi2\sigma_z^\NV}
  \exp\p{j\f\pi4\sp{\sigma_{y'}^1-\sigma_{x''}^2}}
  \times \\
  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^1}
  \exp\p{j\f\pi4\sigma_z^\NV\sigma_{x''}^2}
  \times \\
  \exp\p{j\f\pi4\sigma_x^\NV\sigma_{z'}^1}
  \exp\p{-j\f\pi4\sigma_x^\NV}.
\end{multline}
Letting
\begin{align}
  \uv x' = \uv y'' &= \uv A_1^\perp, \\
  \uv y' = -\uv x'' &= \uv A_1^{\perp\perp}, \\
  \uv z' = \uv z'' &= \uv\omega_1\approx\uv z, \label{w=z}
\end{align}
where the approximation in (\ref{w=z}) holds for $\gamma_1B\gg A_1/2$,
we can say that
\begin{multline}
  \SWAP^{\NV,\AC} = \exp\p{j\f\pi4\sigma_x^\NV}
  \exp\p{-j\f\pi4\sigma_x^\NV\sigma_z^1}
  \times \\
  \exp\p{-j\f\pi2\sigma_z^\NV} \exp\p{j\f\pi4\sum_j\sigma_{y'}^j}
  \times \\
  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^1}
  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^2}
  \times \\
  \exp\p{j\f\pi4\sigma_x^\NV\sigma_z^1} \exp\p{-j\f\pi4\sigma_x^\NV}.
  \label{SWAP_NVAC_sxsz}
\end{multline}
As we cannot directly realize the coupling $\sigma_x^\NV\sigma_z^1$,
we must perform rotations as
\begin{multline}
  \exp\p{-j\f\pi4\sigma_x^\NV\sigma_z^1} =
  \exp\p{-j\f\pi4\sigma_y^\NV} \exp\p{j\f\pi4\sigma_{y'}^1}
  \times \\
  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
  \times \\
  \exp\p{-j\f\pi4\sigma_{y'}^1} \exp\p{j\f\pi4\sigma_y^\NV}.
\end{multline}
Substituting this identity into (\ref{SWAP_NVAC_sxsz}) yields
\begin{multline}
  \SWAP^{\NV,\AC} = \exp\p{j\f\pi4\sigma_x^\NV}
  \exp\p{-j\f\pi4\sigma_y^\NV}
  \times \\
  \exp\p{j\f\pi4\sum_j\sigma_{y'}^j}
  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
  \exp\p{j\f\pi4\sigma_y^\NV}
  \times \\
  \exp\p{-j\f\pi2\sigma_z^\NV} \exp\p{j\f\pi4\sum_j\sigma_{y'}^j}
  \times \\
  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^1}
  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^2}
  \times \\
  \exp\p{-j\f\pi4\sigma_y^\NV}
  \exp\p{j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
  \exp\p{-j\f\pi4\sum_j\sigma_{y'}^j}
  \times \\
  \exp\p{j\f\pi4\sigma_y^\NV} \exp\p{-j\f\pi4\sigma_x^\NV},
  \label{SWAP_NVAC}
\end{multline}
where we have canceled out two rotations of the form
$\exp\p{\pm j\pi/4~\sigma_{y'}^1}$ and inserted two rotations of the
form $\exp\p{\pm j\pi/4~\sigma_{y'}^2}$ with no net effect.

The $\SWAP^{\NV,\ST}$ can be realized using the $\SWAP^{\NV,\AC}$ gate
via
\begin{align}
  \SWAP^{\NV,\ST} = R_\NV^\dagger \SWAP^{\NV,\AC} R_\NV,
\end{align}
where the rotation $R_\NV$ takes $\ket\u\to\p{\ket\u-\ket\d}/\sqrt2$
and $\ket\d\to\p{\ket\u+\ket\d}/\sqrt2$. Written explicitly,
\begin{align}
  R_\NV = \exp\p{j\f\pi4\sigma_y^\NV}.
\end{align}
We therefore have that
\begin{multline}
  \SWAP^{\NV,\ST} = \exp\p{j\f\pi2\v\sigma^\NV\c\uv a}
  \times \\
  \exp\p{j\f\pi4\sum_j\sigma_{n'}^j}
  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
  \exp\p{j\f\pi4\sigma_y^\NV}
  \times \\
  \exp\p{-j\f\pi2\sigma_z^\NV} \exp\p{j\f\pi4\sum_j\sigma_{y'}^j}
  \times \\
  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^1}
  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^2}
  \times \\
  \exp\p{-j\f\pi4\sigma_y^\NV}
  \exp\p{j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
  \exp\p{-j\f\pi4\sum_j\sigma_{y'}^j}
  \times \\
  \exp\p{-j\f\pi2\v\sigma^\NV\c\uv a},
  \label{SWAP_NVST}
\end{multline}
where $\v a = \uv x - \uv y$ and we have used the fact that
\begin{multline}
  \exp\p{j\f\pi4\sigma_y} \exp\p{-j\f\pi4\sigma_x}
  \exp\p{j\f\pi4\sigma_y} \\
  = \exp\p{-j\f\pi2\v\sigma\c\uv a}.
\end{multline}

In the subspace of interest, we have thus
constructed the non-entangling SWAP operation
\begin{multline}
  \SWAP^{\NV,\ST} \\
  = \op{\u\S}{\S\u} + \op{\u\T}{\d\S} + \op{\d\S}{\u\T} +
  \op{\d\T}{\d\T}.
\end{multline}
If $\gamma_1=\gamma_2$, i.e. if nuclei 1 and 2 are of the same
species, all factors in (\ref{SWAP_NVST}) can be realized directly via
the protocols for (\ref{H_ctl}), (\ref{H_int_dec}), and rotations of
the NV electron spin.

Realizing $\SWAP^{\NV,\AC}$ by switching the cNOT operations in
(\ref{SWAP_NVAC_sketch}) is seemingly impossible, as doing so requires
rotating one spin in the larmor pair without rotating the other. It is
possible to realize $\SWAP^{\NV,\ST}$ via cNOT operations between the
NV and ST qubits directly, but this method requires performing many
more individual spin addressing operations, and therefore has a
substantially lower fidelity.

\subsection{Robustness against noise}

Talk about the robustness of the ST qubit against dephasing via the NV
center, as well as its robustness against slowly varying (frequencies
$\nu\ll\gamma_jB$) external magnetic noise.

\section{Simulations and Results}

\subsection{Abundance of larmor pairs}

For any given hyperfine cutoff $A_\t{min}$ and an isotopic abundance
$n$ of $^{13}$C, we can compute exactly the probability
$P\p{A_\t{min},n}$ of finding an addressable larmor pair for which
$A_j\ge A_\t{min}$. The simulations developed for this paper can also
be used to test the computation of $P\p{A_\t{min},n}$ via the Monte
Carlo method of simply generating many NV systems and counting the
proportion of them which contain an addressable larmor pair.

\subsection{SWAP fidelities via AXY-$n$}

Discuss simulations and any relevant nuances therein. Present
histograms of $\SWAP^{\NV,\ST}$ fidelities and net operation times.

Note: the same simulations can also be used to generate similar
histograms (as well as other info) about other operations,
e.g. single-spin $\SWAP$ or $i\SWAP$ operations. Furthermore, the
simulations can, without any modification, reproduce results such as
Figure 2 in \cite{wang2015positioning} (``Positioning Nuclear Spins in
Interacting Clusters for Quantum Technologies and
Bio-imaging''). Minor additions to the codes might make them useful
for comparing the efficacy of different spin-addressing protocols. Is
there any interest in doing any of these things (for this paper or
elsewhere)?

\section{Conclusions}

\section{Acknowledgments}

\footnotesize \bibliography{\jobname}

\end{document}

### 2016-06-03 misc/constants_numerical.py
remove misc directory and files

@@ -1,66 +1,0 @@
-#!/usr/bin/env python3
-
-import numpy as np
-import matrix_operations_numerical as mo
-i = complex(0,1)
-
-# identity matrices
-def I(n): return np.eye(n)
-
-# pauli spin operators
-st = I(2)
-sz = np.array([[1,0],[0,-1]])
-sx = np.array([[0,1],[1,0]])
-sy = i*np.array([[0,-1],[1,0]])
-
-# spin-up and spin-down states
-up = np.vstack([1,0])
-dn = np.vstack([0,1])
-
-# two-qubit basis states
-uu = mo.tp(up,up)
-ud = mo.tp(up,dn)
-du = mo.tp(dn,up)
-dd = mo.tp(dn,dn)
-
-# two-qubit singlet/triplet states
-S = (ud-du)/np.sqrt(2)
-T = (ud+du)/np.sqrt(2)
-
-# physical constants in SI
-mu0_SI = 4*np.pi*1e-7 # magnetic constant (tesla meters / amp)
-c_SI = 299792458 # speed of light (meters / second)
-hbar_SI = 6.582119514e-16 # reduced Planck constant (eV / second)
-qe_SI = 1.60217646e-19 # charge of electron (coulombs)
-ge_SI = 1.760859708e11 # gyromagnetic ratio of NV electron (Hz/tesla)
-gc_SI = 67.28284e6 # gyromagnetic ratio of C-13 (Hz/tesla)
-
-# physical constants in natural units (e0 = mu0 = c = hbar = 1); all values in seconds or Hz
-
-D = 2*np.pi*2.87e9 # NV center zero field splitting energy (Hz)
-
-alpha = 1/137.035999074 # fine structure constant
-qe = np.sqrt(4*np.pi*alpha) # unit electric charge
-me = 510998.928/hbar_SI # mass of electron (Hz)
-ge = qe/(2*me) * 2.0023193043617 # gyromagnetic ratio of electron
-gc = gc_SI * ge/ge_SI # gyromagnetic ratio of C-13
-
-# SI values in natural units
-kHz = 1000 # (Hz)
-meter = 1 / c_SI # one meter (s)
-nm = 1e-9*meter # one nanometer (s)
-coulomb = qe / qe_SI # one coulomb
-tesla = ge_SI / ge # one tesla (Hz)
-gauss = tesla*1e-4 # one gauss (Hz)
-volt = 1/(qe*hbar_SI) # one volt (Hz)
-
[…]

### 2016-06-03 misc/constants_symbolic.py

@@ -1,50 +1,0 @@
-#!/usr/bin/env python3
-
-import matrix_operations_symbolic as mo
-import sympy as sym
-i = complex(0,1)
-
-########################################
-# mathematical and physical constants
-########################################
-
-arccos = sym.acos
-
-# identity matrices
-def I(n): return sym.eye(n)
-
-# pauli spin operators
-sz = sym.Matrix([[1,0],[0,-1]])
-sx = sym.Matrix([[0,1],[1,0]])
-sy = i*sym.Matrix([[0,-1],[1,0]])
-
-# spin-up and spin-down states
-up = sym.Matrix([[1],[0]])
-dn = sym.Matrix([[0],[1]])
-
-# two-qubit states
-uu = mo.tp(up,up)
-ud = mo.tp(up,dn)
-du = mo.tp(dn,up)
-dd = mo.tp(dn,dn)
-
-# two-qubit singlet/triplet states
-S = (ud-du)/sym.sqrt(2)
-T = (ud+du)/sym.sqrt(2)
-
-# physical constants
-mu0 = sym.var('\mu_0')
-ge = sym.var('\gamma_e')
-gc = sym.var('\gamma_C')
-D = sym.var('D')
-qe = sym.var('q_e')
-me = sym.var('m_e')
-nm = sym.var('nm')
-
-# excited state to use for two-level NV center
-ms = sym.var('m_s')
-
-# spin matrices of NV center in restricted subspace
-Sz = ms/2*(sz+I(2))
-Sx = sx/sym.sqrt(2)
-Sy = ms*sy/sym.sqrt(2)

### 2016-06-03 misc/matrix_operations_numerical.py

@@ -1,89 +1,0 @@
-#!/usr/bin/env python3
-
-import numpy as np
-
-i = complex(0,1)
-
-# hermitian conjugate
-def herm(M):
-    return np.array(np.matrix(M).H)
-
-# indices of matrix
-def indices(M):
-    try:
-        return [ (m,n) for n in range(M.shape[1]) for m in range(M.shape[0]) ]
-    except:
-        return range(M.shape[0])
-
-# commutator [X,Y]
-def comm(X,Y): return np.dot(X,Y)-np.dot(Y,X)
-
-# tensor product
-def tp(*args):
-    if len(args) == 1 and type(args[0]) is list:
-        args = args[0]
-    out = args[0]
-    for i in range(len(args)-1):
-        out = np.kron(out,args[i+1])
-    return out
-
-# matrix multiplication
-def mm(*args):
-    if len(args) == 1 and type(args[0]) is list:
-        args = args[0]
-    out = args[-1]
-    for i in reversed(range(len(args)-1)):
-        out = np.dot(args[i],out)
-    return out
-
-# remove numerical artifacts from matrix
-def remove_artifacts(M, threshold=1e-12):
-    for ind in indices(M):
-        if abs(np.real(M[ind])) < threshold:
-            M[ind] -= np.real(M[ind])
-        if abs(np.imag(M[ind])) < threshold:
-            M[ind] = np.real(M[ind])
-    if abs(np.imag(M)).max() == 0:
-        M = np.real(M)
-    return M
-
-# get/remove global phase from matrix
-def get_phase(M):
-    phase = 1
-    for ind in indices(M):
-        if abs(M[ind]) != 0:
-            phase = M[ind]/abs(M[ind])
-            break
-    return phase
-
-def remove_phase(M):
-    return M*np.conj(get_phase(M))
-
-# clean up matrix for printing
-def clean(M, threshold=1e-12):
-    out = remove_artifacts(M,threshold)
-    out = remove_phase(out)
-    out = remove_artifacts(out,threshold)
-    if abs(np.imag(out)).max() == 0:
-        out = np.real(out)
-    return out
-
-# generate matrix B to act A on qubits ns (out of N qubits total)
-def act(A,N,*ns):
-    if len(ns) == 1 and type(ns[0]) is list:
-        ns = ns[0]
-    B = i*np.zeros((2**N,2**N))
-    for ind in indices(B):
[…]

### 2016-06-03 misc/matrix_operations_symbolic.py

@@ -1,127 +1,0 @@
-#!/usr/bin/env python3
-
-import numpy as np
-import sympy as sym
-
-i = complex(0,1)
-
-# hermitian conjugate
-def herm(M): return M.H
-
-# matrix inverse
-def inv(M): return M.inv()
-
-# indices of matrix
-def indices(M):
-    return [ (m,n) for n in range(M.shape[1]) for m in range(M.shape[0]) ]
-
-# commutator [X,Y]
-def comm(X,Y): return X*Y-Y*X
-
-# tensor product
-def tp(*args):
-    if len(args) == 1 and type(args[0]) is list:
-        args = args[0]
-    out = np.array(args[0])
-    for i in range(len(args)-1):
-        out = np.kron(out,np.array(args[i+1]))
-    return sym.Matrix(out)
-
-# matrix multiplication
-def mm(*args):
-    if len(args) == 1 and type(args[0]) is list:
-        args = args[0]
-    out = sym.simplify(args[-1])
-    for i in reversed(range(len(args)-1)):
-        out = sym.simplify(args[i]*out)
-    return out
-
-# matrix multiplication with object evaluation
-def emm(*args):
-    if len(args) == 1 and type(args[0]) is list:
-        args = args[0]
-    args = [ arg.evalf() for arg in args ]
-    out = args[-1]
-    for i in reversed(range(len(args)-1)):
-        out = (args[i]*out).evalf()
-    return out
-
-# get/remove global phase from matrix
-def get_phase(M):
-    phase = 1
-    for ind in indices(M):
-        val = sym.simplify(M[ind])
-        if sym.Abs(val) != 0:
-            phase = val/sym.Abs(sym.expand(val))
-            phase = phase.expand(complex=True)
-            break
-    return sym.simplify(phase)
-
-def remove_phase(M):
-    return sym.simplify(sym.expand(M*sym.conjugate(get_phase(M))))
-
-# clean up matrix for printing
-def clean(M):
-    out = M.evalf()
-    out = remove_phase(out)
-    return out
-
-# generate matrix B to act A on qubits ns (out of N qubits total)
-def act(A,N,*ns):
-    if len(ns) == 1 and type(ns[0]) is list:
-        ns = ns[0]
-    B = sym.zeros(2**N)
-    for ind in indices(B):
-        s_out = bin(ind[0])[2:].zfill(N)
-        rest_out = [ s_out[n] for n in range(N) if n not in ns ]
-
[…]

### 2016-06-03 misc/run.py

@@ -1,43 +1,0 @@
-#!/usr/bin/env python3
-
-import sys
-from scipy.linalg import expm,logm,sqrtm
-
-if 'sym' in sys.argv:
-    import pylab as pl
-    from sympy import *
-    from constants_symbolic import *
-    from matrix_operations_symbolic import *
-    from spin_operations_symbolic import *
-    matrix = Matrix
-else:
-    from pylab import *
-    from constants_numerical import *
-    from matrix_operations_numerical import *
-    from spin_operations_numerical import *
-    import numpy as np
-    matrix = array
-
-    np.set_printoptions(linewidth = 95)
-
-
-
-
-phi_over_2pi = float(sys.argv[1])
-U = expm(-i*phi_over_2pi*2*pi*tp(sz,sx))
-print(clean(U))
-
-
-exit()
-
-coupled = True
-
-def pp(psi):
-    psi_NVST = mm(act(couple,3,1,2),psi) if coupled else psi
-    qvec_print(remove_artifacts(psi_NVST))
-    print()
-
-for psi in [tp(up,S),tp(up,T),tp(dn,S),tp(dn,T)]:
-    pp(psi)
-    pp(mm(SWAP_NVST,psi))
-    print()

### 2016-06-03 misc/spin_operations_numerical.py

@@ -1,243 +1,0 @@
-#!/usr/bin/env python3
-
-import numpy as np
-import scipy.linalg as lin
-
-import constants_numerical as const
-import matrix_operations_numerical as mo
-i = complex(0,1)
-
-########################################
-# gate solutions and printing
-########################################
-
-# determine Hamiltonian to generate arbitrary gates (operation time = 1)
-def Hgate(G): return i*lin.logm(G)
-
-# compute propagator for arbitrary time-independent Hamiltonians (operation time = 1)
-def U(tH): return lin.expm(-i*tH)
-
-# ordered list of basis Hamiltonians for a system of N spins
-def vH(N=2,form='matrix'):
-
-    pauli = [np.eye(2),const.sz,const.sx,const.sy]
-    pauli_text = ['I','Z','X','Y']
-
-    vec = []
-    text = []
-    permutation = np.zeros(N,dtype=int)
-    for p in range(4**N):
-        bin = '{0:b}'.format(p).zfill(2*N)
-        for s in range(N):
-            permutation[s] = int(bin[s*2:s*2+2],2)
-        vec.append(mo.tp([ pauli[s] for s in permutation ]))
-        text.append(' '.join([ pauli_text[s] for s in permutation ]))
-
-    if form == 'matrix':
-        return np.column_stack([np.ndarray.flatten(v) for v in vec])
-    elif form == 'list':
-        return vec
-    elif form == 'text':
-        return text
-    else:
-        return None
-
-# decompose Hamiltonian into its basis components
-def H_decompose(H):
-    N = int(np.log(H.shape[0])/np.log(2))
-    hs = lin.solve(vH(N),np.ndarray.flatten(H))
-    return mo.remove_artifacts(hs)
-
-# print Hamiltonian vector in human-readable form
-def H_print(H,factor=1,threshold=1e-10):
-    N = int(np.log(H.shape[0])/np.log(2))
-    hs = mo.remove_artifacts(H_decompose(H),threshold)
-    vHs = vH(N,'text')
-    factor_text = 'prefactor: '
-    if factor == 1:
-        factor_text += 'pi'
-    else:
[…]

### 2016-06-03 misc/spin_operations_symbolic.py

@@ -1,180 +1,0 @@
-#!/usr/bin/env python3
-
-import sympy as sym
-import scipy.linalg as lin
-
-import constants_symbolic as const
-import matrix_operations_symbolic as mo
-i = complex(0,1)
-
-########################################
-# printing
-########################################
-
-# print qubit in human-readable form
-def qvec_print(v):
-    N = len(v)
-    qbits = int(sym.log(N)/sym.log(2))
-    for n in range(N):
-        if v[n] != 0:
-            s = bin(n)[2:].zfill(qbits)
-            s = s.replace('0','u').replace('1','d')
-            print('%s:'%s,v[n])
-
-########################################
-# single qubit gates
-########################################
-
-# spin propagators; Ua corresponds to a Hamiltonian # H = h s_a
-def Uz(ht): return sym.cos(ht)*sym.eye(2)-i*sym.sin(ht)*const.sz
-def Ux(ht): return sym.cos(ht)*sym.eye(2)-i*sym.sin(ht)*const.sx
-def Uy(ht): return sym.cos(ht)*sym.eye(2)-i*sym.sin(ht)*const.sy
-
-# rotation operators
-def Rz(phi): return Uz(phi/2)
-def Rx(phi): return Ux(phi/2)
-def Ry(phi): return Uy(phi/2)
-
-# phase-flip, bit-flip, and Hadamard gates
-Z = sym.Matrix([[1,0],[0,-1]])
-X = sym.Matrix([[0,1],[1,0]])
-HG = sym.Matrix([[1,1],[1,-1]])/sym.sqrt(2)
-
-########################################
-# two qubit gates
-########################################
-
-# propagators coupling two spins; Uab corresponds to a Hamiltonian H = h s_a^1 s_b^2
-def U_spins(ht,axes):
-    spins = []
-    for n in range(2):
-        if axes[n] == 'z':
-            spin = const.sz
-        elif axes[n] == 'x':
-            spin = const.sx
-        elif axes[n] == 'y':
-            spin = const.sy
-        spins.append(spin)
[…]

### 2016-06-04 swap-nvst-paper/paper.tex
add note about reading out the state of the ST qubit
added \fixme command to paper

@@
 % \ul{underline}, \st{strikethrough}, and \hl{highlight}
-\usepackage[draft]{fixme} % in text notes
-% \fxsetup{layout=footnote}
-\newcommand{\nt}{\fxnote}
-\newcommand{\re}[1]{{\bf \color{red} #1}}
-\newcommand{\bl}[1]{{\bf \color{blue} #1}}
+\newcommand{\fixme}[1]{{\bf \color{red} fixme: #1}}
 
@@
 \cite{mamin2013nanoscale, steinert2010high, wang2015positioning,
-  chou2015optimal, childress2006fault, yao2012scalable}. % fixme: the
-% first and last sentences of this paragraph are essentially the same
+  chou2015optimal, childress2006fault, yao2012scalable}. \fixme{the
+  first and last sentences of this paragraph are essentially the same}
 
@@
 dephasing via coupling to the NV electron spin, potentially increasing
-its coherence time by a few orders of magnitude. % fixme: elaborate
-We investigate the efficacy of this quantum memory register when
-realized via the recently developed dynamical decoupling protocol
-dubbed adaptive XY-$n$ (AXY-$n$) \cite{casanova2015robust}.
+its coherence time by a few orders of magnitude. \fixme{elaborate} We
+investigate the efficacy of this quantum memory register when realized
+via the recently developed dynamical decoupling protocol dubbed
+adaptive XY-$n$ (AXY-$n$) \cite{casanova2015robust}.
 
@@
   &= \v B_\t{dec} - \p{\v B_\t{dec}\c\uv\omega_j}\uv\omega_j.
-\end{align} % fixme: provide derivation of these results?
+\end{align} \fixme{derive these results explicitly?}
 In words: the decoupling field $\v B_\t{dec}^{\p\omega}$ effectively
@@
 
+\fixme{when we wish to read out the ST qubit, it is possible to do so
+  without performing the full coherent SWAP operation so long as we no
+  longer need the larmor pair as a resource for the time being. Talk
+  about this.}
+
 \subsection{Robustness against noise}

### 2016-06-21 nv-control.cpp
in act_target: compute both polar and equatorial rotations and use the one which is faster

@@ -190,11 +190,7 @@ protocol act_target(const nv_system& nv, const uint target, const Matrix2cd& U,
   const double azimuth = atan2(ry,rx);
   const double pitch = asin(rz/angle);
 
-  const double net_pole_rotation = pi - 2*abs(pitch);
-  const double net_equatorial_rotation =
-    2*abs(pitch) + (angle < pi ? angle : 2*pi - angle);
-
-  if (net_pole_rotation < net_equatorial_rotation) {
+  const protocol pole_rotation = [&]() -> protocol {
     const int pole = pitch > 0 ? 1 : -1; // "north" vs "south" pole
     const double angle_to_pole = pi/2 - abs(pitch);
 
@@ -203,16 +199,22 @@ protocol act_target(const nv_system& nv, const uint target, const Matrix2cd& U,
       else return U_ctl(nv, target, pole*angle_to_pole, azimuth-pi/2, adjust_AXY);
     }();
     const protocol rotate_z = U_ctl(nv, target, 0, 0, adjust_AXY, pole*angle);
-    return to_pole.adjoint() * rotate_z * to_pole;
 
-  } else {
+    return to_pole.adjoint() * rotate_z * to_pole;
+  }();
+
+  const protocol equatorial_rotation = [&]() -> protocol {
     const protocol to_equator = [&]() -> protocol {
       if (abs(pitch) < numerical_error) return protocol::Identity(D);
       else return U_ctl(nv, target, pitch, azimuth+pi/2, adjust_AXY);
     }();
     const protocol rotate_xy = U_ctl(nv, target, angle, azimuth, adjust_AXY);
+
     return to_equator.adjoint() * rotate_xy * to_equator;
-  }
+  }();
+
+  if (pole_rotation.t < equatorial_rotation.t) return pole_rotation;
+  else return equatorial_rotation;
 }
 
 // propagator U = exp(-i * phase * I_{NV}^{n_1}*I_{target}^{n_2})
@@ -270,7 +272,6 @@ protocol U_int(const nv_system& nv, const uint target, const double phase,
 
   // time for which to interact
   double interaction_time = mod(phase/w_phase, t_phase);
-  cout << "interaction_time/t_phase: " << interaction_time/t_phase << endl;
   if (interaction_time > t_phase/2) {
     f_DD *= -1;
     interaction_time = t_phase - interaction_time;
@@ -278,16 +279,16 @@ protocol U_int(const nv_system& nv, const uint target, const double phase,
 
[…]

### 2016-06-21 nv-math.cpp
minor changes in nv-math.cpp

@@ -521,7 +521,7 @@ MatrixXcd simulate_AXY(const nv_system& nv, const uint cluster,
   }
 
   // propagator for AXY sequence remainder
-  const double remaining_time = simulation_time - int(simulation_time/t_DD)*t_DD;
+  const double remaining_time = mod(simulation_time, t_DD);
   for (uint i = 1; i < advanced_pulses.size(); i++) {
     const double t = advanced_pulses.at(i-1)*t_DD;
     const double dt = advanced_pulses.at(i)*t_DD - t;
@@ -551,7 +551,8 @@ MatrixXcd simulate_AXY(const nv_system& nv, const uint cluster,
                         simulation_time, advance, controls.gB());
   }
   const uint spins = nv.clusters.at(cluster).size()+1;
-  if (simulation_time == 0) return MatrixXcd::Identity(pow(2,spins),pow(2,spins));
+  const uint D = pow(2,spins);
+  if (simulation_time == 0) return MatrixXcd::Identity(D,D);
 
   // AXY sequence parameters
   const double t_DD = 2*pi/w_DD;
@@ -576,7 +577,7 @@ MatrixXcd simulate_AXY(const nv_system& nv, const uint cluster,
 
   const MatrixXcd H_0 = H_sys(nv, cluster); // full system Hamiltonian
   const MatrixXcd X = act_NV(nv, sx, spins); // NV center spin flip (pi-)pulse
-  MatrixXcd U = MatrixXcd::Identity(H_0.rows(),H_0.cols()); // system propagator
+  MatrixXcd U = MatrixXcd::Identity(D,D); // system propagator
   Matrix2cd U_NV = I2; // NV-only propagator
 
   // if we need to start with a flipped NV center, flip it

### 2016-06-21 swap-nvst-paper/paper.tex
update paper

@@
 \newcommand{\T}{\t{T}}
+\newcommand{\R}{\mathcal R}
 
@@
 \begin{align}
-  H_\t{sys} = H_\t{NV}^\t{GS} + H_\t{hf} + H_\t{nZ}  + H_\t{nn},
+  H_\t{sys} = H_\NV^\t{GS} + H_\t{hf} + H_\t{nZ}  + H_\t{nn},
 \end{align}
@@
 \begin{align}
-  H_\t{NV}^\t{GS} = D\p{\v S\c\uv z}^2 - \gamma_e\v B\c\v S
+  H_\NV^\t{GS} = D\p{\v S\c\uv z}^2 - \gamma_e\v B\c\v S
 \end{align}
@@
 
-Changing into the rotating frame of $H_\t{NV}^\t{GS}$ affects only the
+Changing into the rotating frame of $H_\NV^\t{GS}$ affects only the
 hyperfine Hamiltonian, which becomes
@@
 
-When restricted to the subspace of $\set{\ket0,\ket{m_s}}$ for the NV
-electron spin, with $m_s\in\set{1,-1}$, we can say that
+When restricted to the subspace of $\set{\ket0,\ket{m_s}}$ with with
+$m_s\in\set{1,-1}$ for the NV electron spin,
 \begin{align}
-  S_z = \f{m_s}2\p{\sigma_z^{NV}+\mathbbm1},
+  S_z = \f{m_s}2\p{I_\NV^z+\mathbbm1},
 \end{align}
-where $\sigma_z^{NV}\equiv\op{m_s}-\op{0}$ and
-$\mathbbm1\equiv\op{m_s}+\op{0}$ is the identity. Defining the
-interaction Hamiltonian
+where $I_\NV^z\equiv\p{\op{m_s}-\op{0}}/2$ and
+$\mathbbm1\equiv\op{m_s}+\op{0}$. Defining the interaction Hamiltonian
 \begin{align}
-  H_\t{int} = \f{m_s}2\sigma_z^{NV}\sum_j\v A_j\c\v I_j
+  H_\t{int} = m_sI_\NV^z\sum_j\v A_j\c\v I_j
 \end{align}
@@
   H_\t{nZ}^\t{eff} = -\sum_j\p{\gamma_j\v B - \f{m_s}2\v A_j}\c\v I_j
-  \equiv -\sum_j\v\omega_j\c\v I_j,
+  = -\sum_j\v\omega_j\c\v I_j,
 \end{align}
-we can say that
+the system Hamiltonian can be written as
 \begin{align}
@@
 Moving into the rotating frame of $H_\t{nZ}^\t{eff}$, the entire
-system is described the the Hamiltonian
+system is described by the Hamiltonian
 \begin{align}
-  \tilde H_\t{int} = \f{m_s}2\sigma_z^{NV}
+  \tilde H_\t{int} = m_sI_\NV^z
   \sum_j\tilde{\v A_j}\p{t}\c\v I_j,
@@
 \end{align}
-where $\v A_j^\parallel\equiv\p{\v A_j\c\uv\omega_j}\uv\omega_j$ is
-the projection of $\v A_j$ along $\v \omega_j$,
-$\v A_j^\perp\equiv\v A_j-\v A_j^\parallel$ is the projection of
-$\v A_j$ onto the plane orthogonal to $\v\omega_j$, and
-$\v A_j^{\perp\perp}\equiv\uv\omega_j\times\v A_j^\perp$ is the vector
-$\v A_j^\perp$ rotated about $\uv\omega_j$ by $\pi/2$.
+where
+\begin{align}
+  \v A_j^\parallel\equiv\p{\v A_j\c\uv\omega_j}\uv\omega_j
+\end{align}
+is the projection of $\v A_j$ along $\v \omega_j$,
+\begin{align}
+\v A_j^\perp\equiv\v A_j-\v A_j^\parallel
+\end{align}
+is the projection of $\v A_j$ onto the plane orthogonal to
+$\v\omega_j$, and
+\begin{align}
+\v A_j^{\perp\perp}\equiv\uv\omega_j\times\v A_j^\perp
+\end{align}
+is the vector $\v A_j^\perp$ rotated about $\uv\omega_j$ by $\pi/2$.
 
@@
 with fundamental frequency $\omega_{DD}$, phase $\phi_{DD}$, and range
-$\set{1,-1}$ to $\sigma_z^{NV}$, so that the system Hamiltonian reads
+$\set{1,-1}$ to $\sigma_z^\NV$, so that the system Hamiltonian reads
 \begin{align}
   \tilde H_\t{int} =
-  F\p{t}\f{m_s}2\sigma_z^{NV}\sum_j\tilde{\v A_j}\p{t}\c\v I_j.
+  F\p{t}m_sI_\NV^z\sum_j\tilde{\v A_j}\p{t}\c\v I_j.
 \end{align}
@@
 \begin{align}
-  \tilde H_\t{int} = f_{k_{DD}}\f{m_s}4\sigma_z^{NV}
+  \tilde H_\t{int} = \f12 f_{k_{DD}} m_sI_\NV^z
   \sum_{j:\omega_j=\omega_r} A_j^\perp\v I_j\c\uv n_j,
@@
 One can concisely write (\ref{H_int_resonance}) with
-$h_j^\t{int}\equiv f_{k_{DD}}m_sA_j^\perp/8$ and the Pauli spin-1/2
+$h_j^\t{int}\equiv f_{k_{DD}}m_sA_j^\perp/2$ and the Pauli spin-1/2
 vector $\v\sigma^j$ (as we consider only spin-1/2 nuclei) as
@@
   \tilde H_\t{int} = \sum_{j:\omega_j=\omega_r}
-  h_j^\t{int}\sigma_z^{NV}\v\sigma^j\c\uv n_j.
+  h_j^\t{int}I_\NV^z\v I_j\c\uv n_j.
   \label{H_int}
@@
 and $\omega_{DD}\gg A_j$ for all $j$, the secular approximation allows
-one to neglect $H_\t{int}$ entirely. In this case, one can apply an
-auxiliary magnetic field
+one to neglect $\tilde H_\t{int}$ entirely. In this case, one can
+apply an auxiliary magnetic field
 $\v B_\t{ctl}^{\p\omega}\p{t}=\v
@@
 where
-$\v B_{\t{ctl},j}^\parallel\equiv\p{\v B_\t{ctl}
-  \c\uv\omega_j}\uv\omega_j$,
-$\v B_{\t{ctl},j}^\perp\equiv\v B_\t{ctl} - \v
-B_{\t{ctl},j}^\parallel$, and
-$\v B_{\t{ctl},j}^{\perp\perp}\equiv\uv\omega_j\times\v
-B_\t{ctl}^\perp$.
+\begin{align}
+  \v B_{\t{ctl},j}^\parallel
+  &\equiv \p{\v B_\t{ctl} \c\uv\omega_j}\uv\omega_j \\
+  \v B_{\t{ctl},j}^\perp
+  &\equiv \v B_\t{ctl} - \v B_{\t{ctl},j}^\parallel \\
+  \v B_{\t{ctl},j}^{\perp\perp}
+  &\equiv \uv\omega_j\times\v B_\t{ctl}^\perp.
+\end{align}
 
@@
 One can concisely write (\ref{H_ctl_resonance}) with
-$h_j^\t{ctl}\equiv-\gamma_jB_{\t{ctl},j}^\perp/4$ and the Pauli
-spin-1/2 vector $\v\sigma^j$ as
+$h_j^\t{ctl}\equiv-\gamma_jB_{\t{ctl},j}^\perp/2$ as
 \begin{align}
   \tilde H_\t{ctl} = \sum_{j:\omega_j=\omega_\t{ctl}}
-  h_j^\t{ctl}\v\sigma^j\c\uv m_j.
+  h_j^\t{ctl}\v I_j\c\uv m_j.
   \label{H_ctl}
@@
 $\v B_\t{dec}^{\p\omega}\p{t}=\v B_\t{dec}\cos\p{\omega_r
-  t-\phi_\t{dec}}$ and realize, with a rotating wave approximation in
-the frame of $H_\t{nZ}^\t{eff}$, the Hamiltonian
+  t-\phi_\t{dec}}$ and realize, in the frame of $H_\NV^\t{GS}$, the
+system Hamiltonian
+\begin{align}
+  \tilde H_\t{sys}^\t{dec} = H_\t{int} + H_\t{nZ}^\t{eff} + H_\t{dec},
+\end{align}
+where
+\begin{align}
+  H_\t{dec} = -\sum_j\gamma_j\v B_\t{dec}\c\v I_j
+  \cos\p{\omega_rt-\phi_\t{dec}}.
+\end{align}
+
+In the frame of $H_\t{nZ}^\t{eff}=-\sum_j\v\omega_j\c\v I_j$, the
+decoupling Hamiltonian becomes
+\begin{align}
+  \tilde H_\t{dec} = -\sum_j\gamma_j\tilde{\v B}_{\t{dec},j}
+  \c\v I_j \cos\p{\omega_rt-\phi_\t{dec}}
+  \label{H_dec_eff_full}
+\end{align}
+with
+\begin{align}
+  \tilde{\v B}_{\t{dec},j} = \v B_{\t{dec},j}^\parallel
+  + \v B_{\t{dec},j}^\perp\cos\p{\omega_j t}
+  + \v B_{\t{dec},j}^{\perp\perp}\sin\p{\omega_j t}
+\end{align}
+and
+\begin{align}
+  \v B_{\t{dec},j}^\parallel
+  &\equiv \p{\v B_\t{dec} \c\uv\omega_j}\uv\omega_j, \\
+  \v B_{\t{dec},j}^\perp
+  &\equiv \v B_\t{dec} - \v B_{\t{dec},j}^\parallel, \\
+  \v B_{\t{dec},j}^{\perp\perp}
+  &\equiv \uv\omega_j\times\v B_\t{dec}^\perp.
+\end{align}
+If $\omega_r,\omega_j\gg \gamma_jB_\t{dec}$, then we can neglect
+$\v B_{\t{dec},j}^\parallel$ in (\ref{H_dec_eff_full}) by the secular
+approximation, and by the rotating approximation express
+\begin{multline}
+  \tilde H_\t{dec} \\
+  = -\sum_{j:\omega_j=\omega_r}
+  \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_\t{dec}
+  + \v B_{\t{dec},j}^{\perp\perp}\sin\phi_\t{dec}}\c\v I_j.
+\end{multline}
+Defining
+\begin{align}
+  \v\nu_j = \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_\t{dec}
+  + \v B_{\t{dec},j}^{\perp\perp}\sin\phi_\t{dec}},
+\end{align}
+we can express
+\begin{align}
+  \tilde H_\t{dec} = -\sum_{j:\omega_j=\omega_r}\v\nu_j\c\v I_j.
+\end{align}
+The system Hamiltonian in the frame of $H_\t{nZ}^\t{eff}$ thus takes
+the form
+\begin{align}
+  \tilde H_\t{sys}^\t{dec} = \tilde H_\t{int} + \tilde H_\t{dec}
+  = \sum_{j:\omega_j=\omega_r}
+  \p{h_j^\t{int}I_\NV^z\v I_j\c\uv n_j - \v\nu_j\c\v I_j}.
+\end{align}
+
+In the frame of $\tilde H_\t{dec}$, the entire system is governed by
+the Hamiltonian
 \begin{align}
   \tilde H_\t{int}^\t{dec} = \sum_{j:\omega_j=\omega_r}
-  \tilde h_j^\t{int}\sigma_z^{NV}\v\sigma^j\c\tilde{\v n}_j,
+  h_j^\t{int}I_\NV^z\v I_j\c\tilde{\v n}_j\p{t},
+  \label{H_int_dec_full}
+\end{align}
+where $\tilde{\v n}_j\p{t}$ is the unit vector $\uv n_j$ rotated
+about $\uv\nu_j$ by $\nu_jt$, i.e.
+\begin{align}
+  \tilde{\v n}_j\p{t} = \v n_j^\parallel +
+  \v n_j^\perp\cos\p{\nu_jt} + \v n_j^{\perp\perp}\sin\p{\nu_jt},
+\end{align}
+where
+\begin{align}
+  \v n_j^\parallel &\equiv \p{\uv n_j\c\uv\nu_j}\uv\nu_j, \\
+  \v n_j^\perp &\equiv \uv n_j - \uv n_j^\parallel, \\
+  \v n_j^{\perp\perp} &\equiv \uv\nu_j\times\uv n_j.
+\end{align}
+If $\omega_j\gg\nu_j\gg h_j^\t{int}$, the secular approximation allows
+us to neglect $\v n_j^\perp$ and $\v n_j^{\perp\perp}$ in
+(\ref{H_int_dec_full}), leaving
+\begin{align}
+  \tilde H_\t{int}^\t{dec}
+  = \sum_{j:\omega_j=\omega_r}
+  \tilde h_j^\t{int}I_\NV^z\v I_j\c\uv\nu_j,
   \label{H_int_dec}
@@
 \begin{align}
-  \tilde h_j^\t{int}
-  = h_j^\t{int}\p{\uv A_j^\perp\c\uv B_{\t{dec},j}^\perp}
-  = h_j^\t{int}A_{j,\t{dec}}^\perp/A_j^\perp
+  \tilde h_j^\t{int} = h_j\uv n_j\c\uv\nu_j.
 \end{align}
-and
-\begin{align}
-  \tilde{\v n}_j
-  &= \uv A_{j,\t{dec}}^\perp\cos\phi_{DD}
-    + \uv A_{j,\t{dec}}^{\perp\perp}\sin\phi_{DD}
-\end{align}
-with
-\begin{align}
-  \v A_{j,\t{dec}}^\perp
-  &= \p{\v A_j^{\perp}\c\uv B_{\t{dec},j}^\perp}\uv B_{\t{dec},j}^\perp, \\
-  \v A_{j,\t{dec}}^{\perp\perp}
-  &= \uv\omega_j\times\v A_{j,\t{dec}}^\perp, \\
-  \v B_{\t{dec},j}^\perp
-  &= \v B_\t{dec} - \p{\v B_\t{dec}\c\uv\omega_j}\uv\omega_j.
-\end{align} \fixme{derive these results explicitly?}
-In words: the decoupling field $\v B_\t{dec}^{\p\omega}$ effectively
-suppresses the components of $\v A_j^\perp$ perpendicular to
-$\uv B_\t{dec}^\perp$. These results to not depend on $\phi_\t{dec}$,
-but do require that $A_j\ll\gamma_jB_{\t{dec},j}^\perp\ll\gamma_jB$.
 
 The utility of the decoupling field lies in the fact that when
-$\uv B_\t{dec}^\perp$ is orthogonal to $\v A_j^\perp$, the interaction
-with spin $j$ is suppressed as $\tilde h_j^\t{int}=0$. Considering a
-single larmor pair, one can therefore apply a decoupling field to
-eliminate one of the two terms in (\ref{H_int_dec}) and realize an
-effective Hamiltonian which couples the NV electron spin to only one
-nuclear spin. This scheme fails for larmor pairs with mutually
-parallel $\v A_j^\perp$.
+$\uv n_j$ and $\uv\nu_j$ are orthogonal, the interaction with spin $j$
+is suppressed as $\tilde h_j^\t{int}=0$. Considering a single larmor
+pair, one can therefore apply a decoupling field to eliminate one of
+the two terms in (\ref{H_int_dec}) and realize an effective
+Hamiltonian which couples the NV electron spin to only one nuclear
+spin. This scheme fails for larmor pairs with mutually parallel
+$\v A_j^\perp$.
 
@@
   \cNOT^{j\to k} \\
-  = \exp\p{-j\f\pi4\sigma_z^j} \exp\p{-j\f\pi4\sigma_x^k}
-  \exp\p{j\f\pi4\sigma_z^j\sigma_x^k}.
+  = \exp\p{-j\f\pi2I_j^z} \exp\p{-j\f\pi2I_k^x}
+  \exp\p{j\pi I_j^z I_k^x}.
 \end{multline}
@@
   \SWAP^{\NV,\AC} = \\
-  \exp\p{-j\f\pi4\sigma_x^\NV} \exp\p{j\f\pi4\sigma_{z'}^1}
-  \exp\p{-j\f\pi4\sigma_x^\NV\sigma_{z'}^1}
+  \exp\p{-j\f\pi2 I_\NV^x} \exp\p{j\f\pi2 I_1^{z'}}
+  \exp\p{-j\pi I_\NV^x I_1^{z'}}
   \times \\
-  \exp\p{-j\f\pi4\sigma_z^\NV} \exp\p{-j\f\pi4\sigma_{x'}^1}
-  \exp\p{j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
+  \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_1^{x'}}
+  \exp\p{j\pi I_\NV^z I_1^{x'}}
   \times \\
-  \exp\p{-j\f\pi4\sigma_z^\NV} \exp\p{-j\f\pi4\sigma_{x''}^2}
-  \exp\p{j\f\pi4\sigma_z^\NV\sigma_{x''}^2}
+  \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_2^{x''}}
+  \exp\p{j\pi I_\NV^zI_2^{x''}}
   \times \\
-  \exp\p{-j\f\pi4\sigma_x^\NV} \exp\p{-j\f\pi4\sigma_{z'}^1}
-  \exp\p{j\f\pi4\sigma_x^\NV\sigma_{z'}^1},
+  \exp\p{-j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_1^{z'}}
+  \exp\p{j\pi I_\NV^x I_1^{z'}},
   \label{SWAP_NVAC_full}
@@
 \begin{multline}
-  \SWAP^{\NV,\AC} = \exp\p{j\f\pi4\sigma_x^\NV}
-  \exp\p{-j\f\pi4\sigma_x^\NV\sigma_{z'}^1}
+  \SWAP^{\NV,\AC} = \exp\p{j\f\pi2 I_\NV^x}
+  \exp\p{-j\pi I_\NV^x I_1^{z'}}
   \times \\
-  \exp\p{-j\f\pi2\sigma_z^\NV}
-  \exp\p{j\f\pi4\sp{\sigma_{y'}^1-\sigma_{x''}^2}}
+  \exp\p{-j\pi I_\NV^z}
+  \exp\p{j\f\pi2\sp{I_1^{y'}-I_2^{x''}}}
   \times \\
-  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^1}
-  \exp\p{j\f\pi4\sigma_z^\NV\sigma_{x''}^2}
+  \exp\p{-j\pi I_\NV^z I_1^{y'}}
+  \exp\p{j\pi I_\NV^z I_2^{x''}}
   \times \\
-  \exp\p{j\f\pi4\sigma_x^\NV\sigma_{z'}^1}
-  \exp\p{-j\f\pi4\sigma_x^\NV}.
+  \exp\p{j\pi I_\NV^x I_1^{z'}}
+  \exp\p{-j\f\pi2 I_\NV^x}.
 \end{multline}
@@
 where the approximation in (\ref{w=z}) holds for $\gamma_1B\gg A_1/2$,
-we can say that
 \begin{multline}
-  \SWAP^{\NV,\AC} = \exp\p{j\f\pi4\sigma_x^\NV}
-  \exp\p{-j\f\pi4\sigma_x^\NV\sigma_z^1}
+  \SWAP^{\NV,\AC} = \exp\p{j\f\pi2 I_\NV^x}
+  \exp\p{-j\pi I_\NV^x I_1^z}
   \times \\
-  \exp\p{-j\f\pi2\sigma_z^\NV} \exp\p{j\f\pi4\sum_j\sigma_{y'}^j}
+  \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
   \times \\
-  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^1}
-  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^2}
+  \exp\p{-j\pi I_\NV^z I_1^{y'}}
+  \exp\p{-j\pi I_\NV^z I_2{y'}}
   \times \\
-  \exp\p{j\f\pi4\sigma_x^\NV\sigma_z^1} \exp\p{-j\f\pi4\sigma_x^\NV}.
+  \exp\p{j\pi I_\NV^x I_1^z} \exp\p{-j\f\pi2 I_\NV^x}.
   \label{SWAP_NVAC_sxsz}
@@
 \begin{multline}
-  \exp\p{-j\f\pi4\sigma_x^\NV\sigma_z^1} =
-  \exp\p{-j\f\pi4\sigma_y^\NV} \exp\p{j\f\pi4\sigma_{y'}^1}
+  \exp\p{-j\pi I_\NV^x I_1^z} =
+  \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\f\pi2 I_1^{y'}}
   \times \\
-  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
-  \times \\
-  \exp\p{-j\f\pi4\sigma_{y'}^1} \exp\p{j\f\pi4\sigma_y^\NV}.
+  \exp\p{-j\pi I_\NV^z I_1^{x'}}
+  \times \exp\p{-j\f\pi2 I_1^{y'}} \exp\p{j\f\pi2 I_\NV^y}.
 \end{multline}
@@
 \begin{multline}
-  \SWAP^{\NV,\AC} = \exp\p{j\f\pi4\sigma_x^\NV}
-  \exp\p{-j\f\pi4\sigma_y^\NV}
+  \SWAP^{\NV,\AC} = \exp\p{j\f\pi2 I_\NV^x}
+  \exp\p{-j\f\pi2 I_\NV^y}
   \times \\
-  \exp\p{j\f\pi4\sum_j\sigma_{y'}^j}
-  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
-  \exp\p{j\f\pi4\sigma_y^\NV}
+  \exp\p{j\f\pi2\sum_jI_j^{y'}}
+  \exp\p{-j\pi I_\NV^z I_1^{x'}}
+  \exp\p{j\f\pi2 I_\NV^y}
   \times \\
-  \exp\p{-j\f\pi2\sigma_z^\NV} \exp\p{j\f\pi4\sum_j\sigma_{y'}^j}
+  \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
   \times \\
-  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^1}
-  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^2}
+  \exp\p{-j\pi I_\NV^z I_1^{y'}}
+  \exp\p{-j\pi I_\NV^z I_2^{y'}}
   \times \\
-  \exp\p{-j\f\pi4\sigma_y^\NV}
-  \exp\p{j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
-  \exp\p{-j\f\pi4\sum_j\sigma_{y'}^j}
+  \exp\p{-j\f\pi2 I_\NV^y}
+  \exp\p{j\pi I_\NV^z I_1^{x'}}
+  \exp\p{-j\f\pi2\sum_jI_j^{y'}}
   \times \\
-  \exp\p{j\f\pi4\sigma_y^\NV} \exp\p{-j\f\pi4\sigma_x^\NV},
+  \exp\p{j\f\pi2 I_\NV^y} \exp\p{-j\f\pi2 I_\NV^x},
   \label{SWAP_NVAC}
@@
 where we have canceled out two rotations of the form
-$\exp\p{\pm j\pi/4~\sigma_{y'}^1}$ and inserted two rotations of the
-form $\exp\p{\pm j\pi/4~\sigma_{y'}^2}$ with no net effect.
+$\exp\p{\pm j\pi/2~I_1^{y'}}$ and inserted two rotations of the
+form $\exp\p{\pm j\pi/2~I_2^{y'}}$ with no net effect.
 
@@
 \begin{align}
-  R_\NV = \exp\p{j\f\pi4\sigma_y^\NV}.
+  R_\NV = \exp\p{j\f\pi2 I_\NV^y}.
 \end{align}
@@
 \begin{multline}
-  \SWAP^{\NV,\ST} = \exp\p{j\f\pi2\v\sigma^\NV\c\uv a}
+  \SWAP^{\NV,\ST} = \exp\p{j\pi\v I_\NV\c\uv a}
   \times \\
-  \exp\p{j\f\pi4\sum_j\sigma_{n'}^j}
-  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
-  \exp\p{j\f\pi4\sigma_y^\NV}
+  \exp\p{j\f\pi2\sum_jI_j^{y'}}
+  \exp\p{-j\pi I_\NV^z I_1^{x'}}
+  \exp\p{j\f\pi2 I_\NV^y}
   \times \\
-  \exp\p{-j\f\pi2\sigma_z^\NV} \exp\p{j\f\pi4\sum_j\sigma_{y'}^j}
+  \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
   \times \\
-  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^1}
-  \exp\p{-j\f\pi4\sigma_z^\NV\sigma_{y'}^2}
+  \exp\p{-j\pi I_\NV^z I_1^{y'}}
+  \exp\p{-j\pi I_\NV^z I_2^{y'}}
   \times \\
-  \exp\p{-j\f\pi4\sigma_y^\NV}
-  \exp\p{j\f\pi4\sigma_z^\NV\sigma_{x'}^1}
-  \exp\p{-j\f\pi4\sum_j\sigma_{y'}^j}
+  \exp\p{-j\f\pi2 I_\NV^y}
+  \exp\p{j\pi I_\NV^z I_1^{x'}}
+  \exp\p{-j\f\pi2\sum_jI_j^{y'}}
   \times \\
-  \exp\p{-j\f\pi2\v\sigma^\NV\c\uv a},
+  \exp\p{-j\pi\v I_\NV\c\uv a},
   \label{SWAP_NVST}
@@
 \begin{multline}
-  \exp\p{j\f\pi4\sigma_y} \exp\p{-j\f\pi4\sigma_x}
-  \exp\p{j\f\pi4\sigma_y} \\
-  = \exp\p{-j\f\pi2\v\sigma\c\uv a}.
+  \exp\p{j\f\pi2 I^y} \exp\p{-j\f\pi2 I^x}
+  \exp\p{j\f\pi2 I^y} \\
+  = \exp\p{-j\pi\v I\c\uv a}.
 \end{multline}

### 2016-06-23 nv-control.cpp
made the constructions of protocols in SWAP_NVST a bit clearer

@@ -428,17 +428,17 @@ protocol SWAP_NVST(const nv_system& nv, const uint idx1, const uint idx2,
     const protocol hXmY_NV = protocol(act_NV(nv, rotate(pi,xhat-yhat), spins));
 
     const protocol cNOT_AC_NV_adapted =
-      (qY_NV *
-       couple_target(nv, idx1, -pi, zhat, xhat, exact) *
-       rotate_target(nv, idx1, pi/2, yhat, exact) *
-       hXmY_NV);
+      qY_NV *
+      couple_target(nv, idx1, -pi, zhat, xhat) *
+      rotate_target(nv, idx1, pi/2, yhat) *
+      hXmY_NV;
 
     const Vector3d y1_in_idx2_basis = to_basis(nv, idx2) * from_basis(nv, idx1) * yhat;
     const protocol cNOT_NV_AC_adapted =
-      (hZ_NV *
-       rotate_target(nv, idx1, -pi/2, yhat, exact) *
-       couple_target(nv, idx1, pi, zhat, yhat, exact) *
-       couple_target(nv, idx2, pi, zhat, y1_in_idx2_basis, exact));
+      hZ_NV *
+      rotate_target(nv, idx1, -pi/2, yhat) *
+      couple_target(nv, idx1, pi, zhat, yhat) *
+      couple_target(nv, idx2, pi, zhat, y1_in_idx2_basis);
 
     return (cNOT_AC_NV_adapted.adjoint() *
             cNOT_NV_AC_adapted *

### 2016-06-23 constants.h
added comment explaining max_gB_ctl

@@ -40,4 +40,4 @@ const double NV_ZFS = 2*pi*2.87e9; // NV center zero field splitting energy (Hz)
 const double a0 = 0.35668 * nm; // diamond lattice parameter at 300 K
 
 // experimental considerations
-const double max_gB_ctl = 5e4;
+const double max_gB_ctl = 5e4; // maximum strength of control field (times g_C13) (Hz)

### 2016-06-23 run-fidelity-jobs.py
changed default parameters in run-fidelity-jobs.py

@@ -18,10 +18,10 @@ else:
 
 c13_natural_percentage = 1.07
 
-static_Bzs = [ 500, 1000, 1500 ]
-c13_factors = [ 1, 0.1, 0.01 ]
-max_cluster_sizes = [ 4 ]
-scale_factors = [ 5, 10, 20 ]
+static_Bzs = [ 50, 100, 500, 1000 ]
+c13_factors = [ 0.1, 0.01 ]
+max_cluster_sizes = [ 5 ]
+scale_factors = [ 5, 10, 15 ]
 
 project_dir = os.path.dirname(os.path.realpath(__file__))
 run_script = "fidelity-sweep-job.py"

### 2016-06-23 swap-nvst-paper/paper.tex
added text with an intuitive summary of H_int_dec

@@
 \end{align}
-where $\uv n_j$ is the direction of $\v A_j^\perp$ rotated about
-$\uv\omega_j$ by $\phi_{DD}$, i.e.
+where $\uv n_j$ is a unit vector in the direction of $\v A_j^\perp$
+rotated about $\uv\omega_j$ by $\phi_{DD}$, i.e.
 \begin{align}
@@
 One can concisely write (\ref{H_int_resonance}) with
-$h_j^\t{int}\equiv f_{k_{DD}}m_sA_j^\perp/2$ and the Pauli spin-1/2
-vector $\v\sigma^j$ (as we consider only spin-1/2 nuclei) as
+\begin{align}
+h_j^\t{int}\equiv f_{k_{DD}}m_sA_j^\perp/2
+\end{align}
+as
 \begin{align}
@@
 One can concisely write (\ref{H_ctl_resonance}) with
-$h_j^\t{ctl}\equiv-\gamma_jB_{\t{ctl},j}^\perp/2$ as
+\begin{align}
+h_j^\t{ctl}\equiv-\gamma_jB_{\t{ctl},j}^\perp/2
+\end{align}
+as
 \begin{align}
@@
 $\v B_\t{ctl}$. These controls, together with rotations of the NV
-electron spin, in principle allow one to realize a universal set of
-quantum gates. An exception to this statement is when two or more
-nuclei have the same effective larmor frequency $\omega_j$, in which
-case they are addressed simultaneously in (\ref{H_int}) and
-(\ref{H_ctl}).
+electron spin, allow one to realize a universal set of quantum
+gates. An exception to this statement is when two or more nuclei have
+the same effective larmor frequency $\omega_j$, in which case they are
+addressed simultaneously in (\ref{H_int}) and (\ref{H_ctl}).
 
@@
 \end{align}
-where
+with
 \begin{align}
@@
   = \sum_{j:\omega_j=\omega_r}
+  h_j^\t{int}I_\NV^z\v I_j\c\v n_j^\parallel
+  = \sum_{j:\omega_j=\omega_r}
   \tilde h_j^\t{int}I_\NV^z\v I_j\c\uv\nu_j,
@@
 
-The utility of the decoupling field lies in the fact that when
-$\uv n_j$ and $\uv\nu_j$ are orthogonal, the interaction with spin $j$
-is suppressed as $\tilde h_j^\t{int}=0$. Considering a single larmor
-pair, one can therefore apply a decoupling field to eliminate one of
-the two terms in (\ref{H_int_dec}) and realize an effective
-Hamiltonian which couples the NV electron spin to only one nuclear
-spin. This scheme fails for larmor pairs with mutually parallel
-$\v A_j^\perp$.
+In words, the decoupling field $\v B_\t{dec}^{\p\omega}\p{t}$ modifies
+$\tilde H_\t{int}$ in (\ref{H_int}) by suppressing the components of
+$\uv n_j$ (i.e. $\uv A_j^\perp$ rotated about $\uv\omega_j$ by
+$\phi_{DD}$) which are perpendicular to the respective $\uv\nu_j$
+(i.e.  $\uv B_{\t{dec},j}^\perp$ rotated about $\uv\omega_j$ by
+$\phi_\t{dec}$). The utility of this decoupling field lies in the fact
+that when $\uv n_j$ and $\uv\nu_j$ are orthogonal, the interaction
+with spin $j$ is suppressed as $\tilde h_j^\t{int}=0$. Considering a
+single larmor pair, one can therefore apply a decoupling field to
+eliminate one of the two terms in (\ref{H_int_dec}) and realize an
+effective Hamiltonian which couples the NV electron spin to only one
+nuclear spin. This scheme fails for larmor pairs with mutually
+parallel $\v A_j^\perp$.
 

### 2016-06-23 nv-control.cpp
removed explicit 'false' arguments in a call of act_target

@@ -311,7 +311,7 @@ protocol U_int(const nv_system& nv, const uint target, const double phase,
   const double xy_angle = mod(interaction_time*w_ctl, 2*pi);
   const Vector3d xy_axis = rotate(xhat, target_azimuth, zhat);
   const protocol flush_target =
-    act_target(nv, target, rotate(xy_angle,xy_axis)*rotate(z_angle,zhat), false, false);
+    act_target(nv, target, rotate(xy_angle,xy_axis)*rotate(z_angle,zhat));
 
   return flush_target * protocol(U_coupling, interaction_time);
 }

### 2016-06-23 nv-control.cpp
made decoupling methods used in U_int consistent with those in the paper; fixed some methods and bugs in simulate_AXY

@@ -225,57 +225,68 @@ protocol U_int(const nv_system& nv, const uint target, const double phase,
   const uint cluster = get_cluster_containing_target(nv,target);
   const uint spins = nv.clusters.at(cluster).size()+1;
 
-  // larmor frequency, resolution, perpendicular component of hyperfine field,
+  // effective larmor frequency and rotation axis,
+  //   perpendicular component of hyperfine field,
   //   and maximum possible value of f_DD
   const double w_larmor = effective_larmor(nv,target).norm();
-  const double dw_min = larmor_resolution(nv,target);
+  const Vector3d w_hat = hat(effective_larmor(nv,target));
   const Vector3d A_perp = hyperfine_perp(nv,target);
   const double f_DD_max = axy_f_max(nv.k_DD);
 
-  // control field
+  // control fields, AXY sequence phase, and effective hyperfine coupling strength
   control_fields controls;
-  if (decouple) {
-    for (uint index: nv.clusters.at(cluster)) {
-      if (index == target) continue;
-      if (is_larmor_pair(nv,index,target)) {
-        const Vector3d A_perp_alt = hyperfine_perp(nv,index);
-        const double gB_ctl =
-          min({ exp( (log(2*w_larmor) + log(f_DD_max*A_perp.norm())) / 2),
-                2*w_larmor / nv.scale_factor,
-                max_gB_ctl});
-        const Vector3d axis_ctl =
-          hat(A_perp - dot(A_perp,hat(A_perp_alt))*hat(A_perp_alt));
-        controls.add(gB_ctl*axis_ctl, w_larmor);
-      }
-    }
-  }
-  assert(controls.num() <= 1);
+  double phi_DD;
+  double A_int;
 
-  // "interaction vector": A_perp without the component suppressed by the control field
-  const Vector3d A_int = [&]() -> Vector3d {
-    if (controls.num() == 0) return A_perp;
+  const int decouple_index = [&]() -> int {
+    if (!decouple) return -1;
     else {
-      const Vector3d ctl_dir = hat(controls.gB());
-      return dot(A_perp,ctl_dir)*ctl_dir;
+      for (uint index: nv.clusters.at(cluster)) {
+        if (index == target) continue;
+        if (is_larmor_pair(nv,index,target)) {
+          return index;
+        }
+      }
+      return -1;
     }
   }();
 
[…]

### 2016-06-23 nv-math.cpp

@@ -325,8 +325,8 @@ vector<double> axy_pulse_times(const double f, const axy_harmonic k) {
   return pulse_times;
 }
 
-vector<double> advanced_pulse_times(const vector<double> pulse_times,
-                                    const double advance) {
+vector<double> advanced_pulse_times(const vector<double> pulse_times, double advance) {
+  advance = mod(advance);
   if (advance == 0) return pulse_times;
 
   // number of pulses
@@ -346,11 +346,11 @@ vector<double> advanced_pulse_times(const vector<double> pulse_times,
 }
 
 // evaluate F(x) (i.e. sign in front of sigma_z^{NV}) for given AXY pulses
-int F_AXY(const double x, const vector<double> pulses) {
-  const double normed_x = mod(x);
+int F_AXY(double x, const vector<double> pulses) {
+  x = mod(x);
   uint pulse_count = 0;
   for (uint i = 1; i < pulses.size()-1; i++) {
-    if (pulses.at(i) < normed_x) pulse_count++;
+    if (pulses.at(i) < x) pulse_count++;
     else break;
   }
   return (pulse_count % 2 == 0 ? 1 : -1);
@@ -488,8 +488,8 @@ MatrixXcd simulate_AXY(const nv_system& nv, const uint cluster,
   // AXY sequence parameters
   const double t_DD = 2*pi/w_DD;
   const double advance = advance_time/t_DD;
-  const vector<double> pulses = axy_pulse_times(f_DD,k_DD);
-  const vector<double> advanced_pulses = advanced_pulse_times(pulses, advance);
+  const vector<double> axy_pulses = axy_pulse_times(f_DD,k_DD);
+  const vector<double> pulses = advanced_pulse_times(axy_pulses, advance);
 
   const MatrixXcd H = H_sys(nv, cluster) + H_ctl(nv, cluster, gB_ctl); // full Hamiltonian
   const MatrixXcd X = act_NV(nv, sx, spins); // NV center spin flip (pi-)pulse
@@ -497,7 +497,7 @@ MatrixXcd simulate_AXY(const nv_system& nv, const uint cluster,
   Matrix2cd U_NV = I2; // NV-only propagator
 
   // if we need to start with a flipped NV center, flip it
-  if (F_AXY(advance, pulses) == -1) {
+  if (F_AXY(advance, axy_pulses) == -1) {
     U = (X * U).eval();
[…]

### 2016-06-23 nv-math.h

@@ -191,11 +191,10 @@ inline double axy_f_max(const axy_harmonic k) {
 vector<double> axy_pulse_times(const double f, const axy_harmonic k);
 
 // advance pulses by a given (normalized) time
-vector<double> advanced_pulse_times(const vector<double> pulse_times,
-                                    const double advance);
+vector<double> advanced_pulse_times(const vector<double> pulse_times, double advance);
 
 // evaluate F(x) (i.e. sign in front of sigma_z^{NV}) for given AXY pulses
-int F_AXY(const double x, const vector<double> pulses);
+int F_AXY(double x, const vector<double> pulses);
 
 // Hamiltoninan coupling two spins
 MatrixXcd H_ss(const Vector3d& p1, const double g1, const mvec& S1,
@@ -319,14 +318,14 @@ MatrixXcd act_NV(const nv_system& nv, const Matrix2cd& U, const uint spins);
 // simulate propagator with static control fields
 MatrixXcd simulate_AXY(const nv_system& nv, const uint cluster,
                        const double w_DD, const double f_DD, const axy_harmonic k_DD,
-                       const double simulation_time, const double advance = 0,
+                       const double simulation_time, const double advance_time = 0,
                        const Vector3d B_ctl = Vector3d::Zero());
 
 // simulate propagator with dynamic control fields
 MatrixXcd simulate_AXY(const nv_system& nv, const uint cluster,
                        const double w_DD, const double f_DD, const axy_harmonic k_DD,
                        const control_fields& controls, const double simulation_time,
-                       const double advance = 0);
+                       const double advance_time = 0, const double phi_DD = 0);
 
 // ---------------------------------------------------------------------------------------
 // Protocol object

### 2016-06-29 nv-control.cpp
added get_index_in_subsystem() method and fixed indexing errors

@@ -40,7 +40,7 @@ MatrixXcd to_natural_frames(const nv_system& nv, const vector<uint> cluster,
   const uint spins = cluster.size()+1;
   MatrixXcd rotation = MatrixXcd::Identity(pow(2,spins),pow(2,spins));
   for (uint index: cluster) {
-    const uint index_in_cluster = get_index_in_cluster(index, cluster);
+    const uint subsystem_index = get_index_in_subsystem(nv, index);
     const Matrix2cd index_rotation = [&]() -> Matrix2cd {
       if (can_address(nv,index)) {
         if (target == (uint)(-1)) {
@@ -52,7 +52,7 @@ MatrixXcd to_natural_frames(const nv_system& nv, const vector<uint> cluster,
         return I2;
       }
     }();
-    rotation = (act(index_rotation, {index_in_cluster+1}, spins) * rotation).eval();
+    rotation = (act(index_rotation, {subsystem_index}, spins) * rotation).eval();
   }
   return rotation;
 }
@@ -154,7 +154,7 @@ protocol act_target(const nv_system& nv, const uint target, const Matrix2cd& U,
   assert(exact || !decouple);
 
   const uint cluster = get_cluster_containing_target(nv,target);
-  const uint target_in_cluster = get_index_in_cluster(nv,target);
+  const uint subsystem_target = get_index_in_subsystem(nv,target);
   const uint spins = nv.clusters.at(cluster).size()+1;
   const uint D = pow(2,spins);
 
@@ -165,7 +165,7 @@ protocol act_target(const nv_system& nv, const uint target, const Matrix2cd& U,
 
     if (decouple) {
       // rotate only target nucleus
-      return protocol(act(rotation, {target_in_cluster+1}, spins));
+      return protocol(act(rotation, {subsystem_target}, spins));
     } else {
       // rotate all nuclei with the same effective larmor frequency as the target
       MatrixXcd G = MatrixXcd::Identity(D,D);
@@ -336,14 +336,14 @@ protocol couple_target(const nv_system& nv, const uint target, const double phas
   if (exact) {
     // identify cluster of target nucleus
     const uint cluster = get_cluster_containing_target(nv,target);
-    const uint target_in_cluster = get_index_in_cluster(nv,target);
+    const uint subsystem_target = get_index_in_subsystem(nv,target);
[…]

### 2016-06-29 nv-math.h

@@ -155,6 +155,9 @@ inline uint get_index_in_cluster(const nv_system& nv, const uint index) {
   const uint cluster = get_cluster_containing_target(nv,index);
   return get_index_in_cluster(index, nv.clusters.at(cluster));
 }
+inline uint get_index_in_subsystem(const nv_system& nv, const uint index) {
+  return get_index_in_cluster(nv, index) + 1;
+}
 
 // ---------------------------------------------------------------------------------------
 // AXY scanning methods

### 2016-06-29 simulation.cpp

@@ -521,9 +521,9 @@ int main(const int arg_num, const char *arg_vec[]) {
       for (bool exact : {true,false}) {
         P.at(exact) = rotate_target(nv, target, phase, target_axis, exact);
       }
-      const uint target_in_cluster = get_index_in_cluster(nv, target);
+      const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P.at(0), P.at(1), {0, target_in_cluster}) << " "
+           << gate_fidelity(P.at(0), P.at(1), {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -542,9 +542,9 @@ int main(const int arg_num, const char *arg_vec[]) {
       for (bool exact : {true,false}) {
         P.at(exact) = couple_target(nv, target, phase, nv_axis, target_axis, exact);
       }
-      const uint target_in_cluster = get_index_in_cluster(nv, target);
+      const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P.at(0), P.at(1), {0, target_in_cluster}) << " "
+           << gate_fidelity(P.at(0), P.at(1), {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -561,9 +561,9 @@ int main(const int arg_num, const char *arg_vec[]) {
       for (bool exact : {true,false}) {
         P.at(exact) = iSWAP(nv, target, exact);
       }
-      const uint target_in_cluster = get_index_in_cluster(nv, target);
+      const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P.at(0), P.at(1), {0, target_in_cluster}) << " "
+           << gate_fidelity(P.at(0), P.at(1), {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -580,9 +580,9 @@ int main(const int arg_num, const char *arg_vec[]) {
       for (bool exact : {true,false}) {
         P.at(exact) = SWAP(nv, target, exact);
       }
-      const uint target_in_cluster = get_index_in_cluster(nv, target);
+      const uint subsystem_target = get_index_in_subsystem(nv, target);
[…]

### 2016-06-29 nv-math.cpp
changed some conventions involving H_nZ

@@ -377,8 +377,9 @@ MatrixXcd H_int(const nv_system& nv, const uint cluster_index) {
   return H;
 }
 
-// nuclear Zeeman Hamiltonian
-MatrixXcd H_nZ(const nv_system& nv, const uint cluster_index, const Vector3d& gB) {
+// nuclear Zeeman Hamiltonian; default gB to the static control field
+MatrixXcd H_nZ(const nv_system& nv, const uint cluster_index, Vector3d gB) {
+  if (gB == Vector3d::Zero()) gB = nv.static_gBz*zhat;
   const vector<uint> cluster = nv.clusters.at(cluster_index);
   const int spins = cluster.size()+1;
   // zero-field splitting and interaction of NV center with magnetic field

### 2016-06-29 nv-math.h

@@ -222,8 +222,9 @@ inline MatrixXcd H_nn(const Vector3d& p1, const Vector3d& p2) {
 // spin-spin coupling Hamiltonian for the entire system
 MatrixXcd H_int(const nv_system& nv, const uint cluster_index);
 
-// nuclear Zeeman Hamiltonian
-MatrixXcd H_nZ(const nv_system& nv, const uint cluster_index, const Vector3d& gB);
+// nuclear Zeeman Hamiltonian; default gB to the static control field
+MatrixXcd H_nZ(const nv_system& nv, const uint cluster_index,
+               Vector3d gB = Vector3d::Zero());
 
 // NV Zeeman Hamiltonian
 inline MatrixXcd H_NV_Z(const nv_system& nv, const Vector3d& gB) {
@@ -242,14 +243,15 @@ inline MatrixXcd H_NV(const nv_system& nv, const Vector3d& gB) {
 
 // total internal system Hamiltonian
 inline MatrixXcd H_sys(const nv_system& nv, const uint cluster) {
-  return (H_int(nv,cluster) + H_nZ(nv,cluster,nv.static_gBz*zhat) +
+  return (H_int(nv,cluster) +
+          H_nZ(nv,cluster) +
           act(H_NV_GS(nv), {0}, nv.clusters.at(cluster).size()+1));
 }
 
 // total control Hamiltonian for the entire system
-inline MatrixXcd H_ctl(const nv_system& nv, const uint cluster, const Vector3d& B_ctl) {
-  return H_nZ(nv,cluster,B_ctl) + act(H_NV_Z(nv,B_ctl), {0},
-                                      nv.clusters.at(cluster).size()+1);
+inline MatrixXcd H_ctl(const nv_system& nv, const uint cluster, const Vector3d& gB_ctl) {
+  return (H_nZ(nv,cluster,gB_ctl) +
+          act(H_NV_Z(nv,gB_ctl), {0}, nv.clusters.at(cluster).size()+1));
 }
 
 // perform NV coherence measurement with a static magnetic field
@@ -384,7 +386,7 @@ protocol act_NV(const nv_system& nv, const Matrix2cd& U, const uint spins);
 protocol simulate_AXY(const nv_system& nv, const uint cluster,
                       const double w_DD, const double f_DD, const axy_harmonic k_DD,
                       const double simulation_time, const double advance_time = 0,
-                      const Vector3d B_ctl = Vector3d::Zero());
[…]

### 2016-06-29 nv-control.h
removed polarize method

@@ -48,11 +48,6 @@ inline MatrixXcd to_natural_frames(const nv_system& nv, const uint spin_in_clust
 // General control methods
 // ---------------------------------------------------------------------------------------
 
-// polarize an arbitrary state into the pure state psi; warning: not a unitary operation
-inline MatrixXcd polarize(const VectorXcd psi) {
-  return psi*VectorXcd::Ones(psi.size()).adjoint();
-}
-
 // propagator U = exp(-i * angle * I_{target}^{axis})
 protocol U_ctl(const nv_system& nv, const uint target, const double phase,
                const double target_azimuth, const bool adjust_AXY = true,

### 2016-06-29 nv-control.cpp
added identity fidelity method

@@ -457,3 +457,20 @@ protocol SWAP_NVST(const nv_system& nv, const uint idx1, const uint idx2,
             cNOT_AC_NV_adapted);
   }
 }
+
+// identity operation on the cluster containing a target nucleus
+//   assumes that the NV center is polarized to the |0> state
+protocol identity(const nv_system& nv, const uint target, const double time,
+                  const bool exact) {
+  const uint cluster = get_cluster_containing_target(nv,target);
+  const uint cluster_spins = nv.clusters.at(cluster).size();
+
+  if (exact) return protocol::Identity(pow(2,cluster_spins));
+
+  const MatrixXcd H = H_sys(nv,cluster) - H_nZ(nv,cluster);
+  const MatrixXcd proj_0 = act(dn*dn.adjoint(),{0},cluster_spins+1); // |0><0|
+  const MatrixXcd H_0 = ptrace(H*proj_0, {0}); // <0|H|0>
+
+  const MatrixXcd U = exp(-j*time*H_0);
+  return protocol(U);
+}

### 2016-06-29 nv-control.h

@@ -91,3 +91,8 @@ protocol SWAP(const nv_system& nv, const uint target, const bool exact = false);
 //   where {x1,y1,z1} is the natural basis of spin 1
 protocol SWAP_NVST(const nv_system& nv, const uint idx1, const uint idx2,
                    const bool exact = false);
+
+// identity operation on the cluster containing a target nucleus
+//   assumes that the NV center is polarized to the |0> state
+protocol identity(const nv_system& nv, const uint target, const double time,
+                  const bool exact = false);

### 2016-06-29 simulation.cpp

@@ -44,6 +44,7 @@ int main(const int arg_num, const char *arg_vec[]) {
   bool iswap_fidelities;
   bool swap_fidelities;
   bool swap_nvst_fidelity;
+  bool identity_fidelity;
   bool testing;
 
   po::options_description simulations("Available simulations",help_text_length);
@@ -67,6 +68,9 @@ int main(const int arg_num, const char *arg_vec[]) {
     ("swap_nvst",
      po::value<bool>(&swap_nvst_fidelity)->default_value(false)->implicit_value(true),
      "compute expected SWAP_NVST fidelity")
+    ("identity",
+     po::value<bool>(&identity_fidelity)->default_value(false)->implicit_value(true),
+     "compute expected fidelity of an identity operation")
     ("test" ,po::value<bool>(&testing)->default_value(false)->implicit_value(true),
      "enable testing mode")
     ;
@@ -81,6 +85,7 @@ int main(const int arg_num, const char *arg_vec[]) {
   uint k_DD_int;
   axy_harmonic k_DD;
   double static_Bz_in_gauss;
+  double identity_time;
   double scale_factor;
   double integration_factor;
   bool no_nn;
@@ -99,6 +104,8 @@ int main(const int arg_num, const char *arg_vec[]) {
      "resonance harmonic used in spin addressing (1 or 3)")
     ("static_Bz", po::value<double>(&static_Bz_in_gauss)->default_value(140.1,"140.1"),
      "strength of static magnetic field along the NV axis (gauss)")
+    ("identity_time", po::value<double>(&identity_time)->default_value(1),
+     "time of identity operation (s)")
     ("scale_factor", po::value<double>(&scale_factor)->default_value(10),
      "factor used to define different scales (i.e. if a << b, then a = b/scale_factor)")
     ("integration_factor", po::value<double>(&integration_factor)->default_value(10),
@@ -203,6 +210,7 @@ int main(const int arg_num, const char *arg_vec[]) {
                    + int(iswap_fidelities)
                    + int(swap_fidelities)
                    + int(swap_nvst_fidelity)
+                   + int(identity_fidelity)
                    != 1)) {
     cout << "Please choose one simulation to perform\n";
     return -1;
@@ -611,6 +619,29 @@ int main(const int arg_num, const char *arg_vec[]) {
            << gate_fidelity(P.at(0), P.at(1), {0, ss_idx1, ss_idx2}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
+    }
+  }
+
[…]

### 2016-06-29 fidelity-summary.py
updated fidelity-summary.py to reflect the addition of a pulse count to simulation data

@@ -34,14 +34,14 @@ with open(fname,'r') as f:
             continue
         if collect:
             line = line.split()
-            if len(line) == 3:
-                targets = int(line[0])
-            elif len(line) == 4:
+            if len(line) == 4:
+                targets = [int(line[0])]
+            elif len(line) == 5:
                 targets = [int(line[0]),int(line[1])]
             else:
                 print("invalid data")
                 exit(1)
-            results += [(float(line[-2]),float(line[-1]),seed,targets)]
+            results += [(float(line[-3]),float(line[-2]),int(line[-1]),seed,targets)]
 
 if len(results) == 0:
     print("no simulation data in file: {}".format(fname))
@@ -53,9 +53,7 @@ cutoff_results.sort(key = lambda x: -x[0])
 with open(out_file,"w") as f:
     f.write("# samples: {}\n".format(samples))
     f.write("# total results: {}\n".format(len(results)))
-    f.write("# fidelity time seed target(s)\n")
+    f.write("# fidelity time pulses seed target(s)\n")
     for result in cutoff_results:
-        f.write("{} {} {}".format(result[0],result[1],result[2]))
-        for target in result[3]:
-            f.write(" {}".format(target))
+        f.write(" ".join([ str(r) for r in results[:-1] + results[-1] ]))
         f.write("\n")

### 2016-06-29 simulation.cpp
removed debugging artifact

@@ -636,12 +636,6 @@ int main(const int arg_num, const char *arg_vec[]) {
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
            << gate_fidelity(P.at(0), P.at(1), {subsystem_target}) << endl;
-
-      cout << endl
-           << clean(P.at(false).U, 1e-2) << endl
-           << endl;
-
-      U_print(j*log(P.at(false).U)/pi);
     }
   }
 

### 2016-06-29 fidelity-summary.py
updated fidelity-summary.py to accomodate output data of different formats

@@ -24,36 +24,30 @@ results = []
 collect = False
 with open(fname,'r') as f:
     for line in f:
-        if "--seed" in line:
-            seed = int(line.split()[-1])
-        if " fidelity time\n" in line:
-            collect = True
-            continue
-        if line == "\n":
-            collect = False
-            continue
-        if collect:
-            line = line.split()
-            if len(line) == 4:
-                targets = [int(line[0])]
-            elif len(line) == 5:
-                targets = [int(line[0]),int(line[1])]
-            else:
-                print("invalid data")
-                exit(1)
-            results += [(float(line[-3]),float(line[-2]),int(line[-1]),seed,targets)]
+        if not collect:
+            if "--seed" in line:
+                seed = int(line.split()[line.split().index("--seed")+1])
+            elif " fidelity" in line:
+                description = line.replace("\n"," seed")
+                collect = True
+        else:
+            if line == "\n":
+                collect = False
+                continue
+            results += [ "{} {}".format(line.replace("\n",""),seed) ]
 
 if len(results) == 0:
     print("no simulation data in file: {}".format(fname))
     exit(1)
 
-cutoff_results = [ result for result in results if result[0] > fidelity_cutoff ]
-cutoff_results.sort(key = lambda x: -x[0])
+fidelity_column = description.split().index("fidelity")
+cutoff_results = [ result for result in results
+                   if float(result.split()[fidelity_column]) > fidelity_cutoff ]
+cutoff_results.sort(key = lambda r: -float(r.split()[fidelity_column]))
 
 with open(out_file,"w") as f:
     f.write("# samples: {}\n".format(samples))
     f.write("# total results: {}\n".format(len(results)))
-    f.write("# fidelity time pulses seed target(s)\n")
+    f.write("# {}\n".format(description))
     for result in cutoff_results:
-        f.write(" ".join([ str(r) for r in results[:-1] + results[-1] ]))
-        f.write("\n")
+        f.write(result+"\n")

### 2016-07-13 nv-control.cpp
remove 'decouple' option from U_ctl

@@ -148,13 +148,9 @@ protocol U_ctl(const nv_system& nv, const uint target, const double angle,
 
 // determine and simulate operations necessary to act U on target nucleus
 protocol act_target(const nv_system& nv, const uint target, const Matrix2cd& U,
-                    const bool exact, const bool decouple, const bool adjust_AXY) {
-  // when performing this operation on larmor sets, we cannot "decouple",
-  //   i.e. act on only one spin
-  assert(exact || !decouple);
+                    const bool exact, const bool adjust_AXY) {
 
   const uint cluster = get_cluster_containing_target(nv,target);
-  const uint subsystem_target = get_index_in_subsystem(nv,target);
   const uint spins = nv.clusters.at(cluster).size()+1;
   const uint D = pow(2,spins);
 
@@ -163,19 +159,14 @@ protocol act_target(const nv_system& nv, const uint target, const Matrix2cd& U,
     const Matrix2cd to_target_basis = rotate(natural_basis(nv,target), {xhat,yhat,zhat});
     const Matrix2cd rotation = to_target_basis * U * to_target_basis.adjoint();
 
-    if (decouple) {
-      // rotate only target nucleus
-      return protocol(act(rotation, {subsystem_target}, spins));
-    } else {
-      // rotate all nuclei with the same effective larmor frequency as the target
-      MatrixXcd G = MatrixXcd::Identity(D,D);
-      for (uint s = 0; s < nv.clusters.at(cluster).size(); s++) {
-        if (is_larmor_pair(nv,target,nv.clusters.at(cluster).at(s))) {
-          G *= act(rotation, {s+1}, spins);
-        }
+    // rotate all nuclei with the same effective larmor frequency as the target
+    MatrixXcd G = MatrixXcd::Identity(D,D);
+    for (uint s = 0; s < nv.clusters.at(cluster).size(); s++) {
+      if (is_larmor_pair(nv,target,nv.clusters.at(cluster).at(s))) {
+        G *= act(rotation, {s+1}, spins);
       }
-      return protocol(G);
     }
+    return protocol(G);
   }
 
   const Vector4cd H_vec = U_decompose(j*log(U)*2);

### 2016-07-13 nv-control.h

@@ -55,14 +55,13 @@ protocol U_ctl(const nv_system& nv, const uint target, const double phase,
 
 // compute and perform operationc necessary to act U on target nucleus
 protocol act_target(const nv_system& nv, const uint target, const Matrix2cd& U,
-                    const bool exact = false, const bool decouple = false,
-                    const bool adjust_AXY = true);
+                    const bool exact = false, const bool adjust_AXY = true);
 
 // perform given rotation on a target nucleus
 inline protocol rotate_target(const nv_system& nv, const uint target, const double angle,
                               const Vector3d& axis, const bool exact = false,
-                              const bool decouple = false, const bool adjust_AXY = true) {
-  return act_target(nv, target, rotate(angle, axis), exact, decouple, adjust_AXY);
+                              const bool adjust_AXY = true) {
+  return act_target(nv, target, rotate(angle, axis), exact, adjust_AXY);
 }
 
 // propagator U = exp(-i * phase * I_{NV}^{n_1}*I_{target}^{n_2})

### 2016-07-13 swap-nvst-paper/paper.tex
fixed missing label on a variable
fixed minor error
adjusted paper to focus on larmor control instead of a DFS SWAP

@@
 %%% math, symbols, etc.
-\usepackage{physics,braket,bm,bbm}
+\usepackage{physics,braket,bm}
 \renewcommand{\t}{\text} % text in math mode
@@
 
-\title{Noise-Protected Quantum Memory Registers with Nitrogen-Vacancy
-  Centers and $^{13}$C Nuclear Spins}
+\title{Realization of a Decoherence-Free Subspaces with
+  Nitrogen-Vacancy Centers and $^{13}$C Nuclear Spins}
 
@@
 nuclei present in diamond yields much longer coherence times than that
-of the NV electron spin, and by entangling multiple nuclear spins into
-the singlet-triplet states $\p{\ket{\u\d}\pm\ket{\d\u}}/\sqrt2$, it is
-possible to generate logical qubits which are protected from various
-sources of system and environmental dephasing noise. Such techniques
-have been used to increase qubit lifetimes in both GaAs and silicon
-quantum dots \cite{bluhm2011dephasing, maune2012coherent}, but have
-yet to be realized in the NV center system.
+of the NV electron spin, and by entangling multiple nuclear spins,
+e.g. into the singlet-triplet states
+$\p{\ket{\u\d}\pm\ket{\d\u}}/\sqrt2$, it is possible to generate
+logical qubits which are protected from various sources of system and
+environmental dephasing noise.
 
-In this paper, we propose using the singlet-triplet subspace of two
-$^{13}$C nuclear spins with identical effective larmor frequencies as
-a logical qubit for storing quantum memory. Here identical effective
-larmor frequencies implies that, absent of symmetry-breaking control
-fields, the nuclei are indistinguishable from the perspective of the
-NV electron. This indistinguishability protects the logical qubit from
-dephasing via coupling to the NV electron spin, potentially increasing
-its coherence time by a few orders of magnitude. \fixme{elaborate} We
-investigate the efficacy of this quantum memory register when realized
-via the recently developed dynamical decoupling protocol dubbed
-adaptive XY-$n$ (AXY-$n$) \cite{casanova2015robust}.
+In this letter, we present a means to address individual $^{13}$C
+nuclear spins which are normally indistinguishable due to symmetric
+coupling to the NV center. We use this addressing scheme to initialize
+qubits in a decoherence-free subspace (DFS) of nuclear spins, and
+propose a means for realizing a coherent SWAP operation between the NV
+center electron spin state and the DFS qubit.
+
+\section{Addressing symmetric $^{13}$C nuclear spins}
+
+Restricting the NV electron spin states to the subspace spanned by
+$\set{\ket0,\ket{m_s}}$ ($m_s=\pm1$), the AXY-$n$ pulse sequence
+developed in by Casanova et al. in \cite{casanova2015robust} and
+control scheme developed by Wang et al. in \cite{wang2015positioning}
+allows addressing individual $^{13}$C nuclear spins via Hamiltonians
+of the form
+\begin{align}
+  H_\t{int} = h_\t{int} I_\NV^z\v I_j\c\uv n_j,
+  \label{H_int}
+\end{align}
+for a tunable coupling strength $h_\t{int}$ and direction $\uv n_j$,
+where $I_\NV^z\equiv\p{\op{m_s}-\op{0}}/2$ and $\v I_j$ is the spin
+operator for nuclear spin $j$. The protocol for realizing this
+effective Hamiltonian, however, is conditional on a sufficiently
+unique larmor frequency $\omega_j$, i.e. that for all $n\ne j$
+\begin{align}
+  \abs{\omega_n-\omega_j} \gg \abs{f_{k_{DD}}\v A_j^\perp},
+\end{align}
+where $f_{k_{DD}}$ is the fourier component of the AXY-$n$ protocol on
+resonance with $\omega_j$ and $\v A_j^\perp$ is the component of the
+hyperfine vector $\v A_j$ perpendicular to the effective larmor
+precession axis $\v\omega_j$.
+
+It is possible, however, for two nuclear spins (indexed by 1 and 2) to
+have identical larmor frequencies $\omega_1=\omega_2\equiv\omega$,
+which occurs when they couple symmetrically to the NV center with
+$A_1=A_2$. The state space of two such spins, which we call {\it
+  larmor pairs}, contains a decoherence-free subspace (DFS) with
+respect to spin-spin coupling to the NV center. This DFS is spanned by
+the singlet-triplet states $\p{\ket{\u\d}\pm\ket{\d\u}}/\sqrt2$, or
+equivalently by $\set{\ket{\u\d},\ket{\d\u}}$.
+
+When trying to address one spin in a larmor pair, the protocols for
+(\ref{H_int}) will simultaneously couple $I_\NV^z$ to both
+$\v I_1\c\uv n_1$ and $\v I_2\c\uv n_2$ with identical coupling
+strength ($h_\t{int}$). So long as $\uv n_1$ and $\uv n_2$
+(equivalently, $\v A_1^\perp$ and $\v A_2^\perp$) are not parallel,
+however, it is possible to address only one of these spins at a time
+by applying additional control fields. In particular, the application
+of a magnetic decoupling field
+$\v B_\t{dec}^{\p\omega}\p{t}=\v B_\t{dec}\cos\p{\omega
+  t-\phi_\t{dec}}$ during the AXY-$n$ addressing protocol suppresses
+components of $\uv n_j$ which are perpendicular to the vector
+$\v B_\t{dec}$ projected onto the plane perpendicular to precession
+axis $\v\omega_j$ and rotated about this axis by $\phi_\t{dec}$. One
+can therefore choose a direction $\v B_\t{dec}$ which completely
+suppresses NV electron spin coupling to spin 1 (2), leaving only
+coupling to spin 2 (1).
+
+\fixme{Comment on how likely are we to find larmor pairs?}
+
+\section{Qubit initialization in a decoherence-free subspace}
+
+\bibliography{\jobname}
+
+\pagebreak
+\clearpage
+\widetext
+\begin{center}
+  \textbf{\large Supplementary Information for ``Delayed entanglement
+    echo for individual control of a large number of nuclear spins''}
+\end{center}
+\setcounter{equation}{0} \setcounter{figure}{0} \setcounter{table}{0}
+\setcounter{page}{1} \makeatletter
+\renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\bibnumfmt}[1]{[S#1]}
+\renewcommand{\citenumfont}[1]{S#1}
+
+\tableofcontents{}
 
@@
 \begin{align}
-  S_z = \f{m_s}2\p{I_\NV^z+\mathbbm1},
+  S_z = \f{m_s}2\p{I_\NV^z+\mathbf1},
 \end{align}
 where $I_\NV^z\equiv\p{\op{m_s}-\op{0}}/2$ and
-$\mathbbm1\equiv\op{m_s}+\op{0}$. Defining the interaction Hamiltonian
+$\mathbf1\equiv\op{m_s}+\op{0}$. Defining the interaction Hamiltonian
 \begin{align}
@@
   \tilde H_\t{sys} = H_\t{int} + H_\t{nZ}^\t{eff}.
-  \label{H_sys_int_nZ}
+  \label{S_H_sys_int_nZ}
 \end{align}
@@
   \sum_j\tilde{\v A_j}\p{t}\c\v I_j,
-  \label{H_int_no_DD}
+  \label{S_H_int_no_DD}
 \end{align}
@@
   + \v A_j^{\perp\perp}\sin\p{\omega_jt},
-  \label{A_rot}
+  \label{S_A_rot}
 \end{align}
@@
 with fundamental frequency $\omega_{DD}$, phase $\phi_{DD}$, and range
-$\set{1,-1}$ to $\sigma_z^\NV$, so that the system Hamiltonian reads
+$\set{1,-1}$ to $I_\NV^z$, so that the system Hamiltonian reads
 \begin{align}
@@
   \sum_{j:\omega_j=\omega_r} A_j^\perp\v I_j\c\uv n_j,
-  \label{H_int_resonance}
+  \label{S_H_int_resonance}
 \end{align}
@@
 \end{align}
-One can concisely write (\ref{H_int_resonance}) with
+One can concisely write (\ref{S_H_int_resonance}) with
 \begin{align}
@@
   h_j^\t{int}I_\NV^z\v I_j\c\uv n_j.
-  \label{H_int}
+  \label{S_H_int}
 \end{align}
@@
 rotating frame of $H_\t{nZ}^\t{eff}$, much like the frame shift
-between (\ref{H_sys_int_nZ}) and (\ref{H_int_no_DD}), to realize the
-Hamiltonian
+between (\ref{S_H_sys_int_nZ}) and (\ref{S_H_int_no_DD}), to realize
+the Hamiltonian
 \begin{align}
@@
 $\v\omega_j$ the same way that $\tilde{\v A_j}\p{t}$ was defined using
-$\v A_j$ and $\v\omega_j$ in (\ref{A_rot}), i.e. as $\v B_\t{ctl}$
+$\v A_j$ and $\v\omega_j$ in (\ref{S_A_rot}), i.e. as $\v B_\t{ctl}$
 rotated about $\uv\omega_j$ by an angle $\omega_jt$:
@@
   \gamma_jB_{\t{ctl},j}^\perp \v I_j\c\uv m_j,
-  \label{H_ctl_resonance}
+  \label{S_H_ctl_resonance}
 \end{align}
@@
 \end{align}
-One can concisely write (\ref{H_ctl_resonance}) with
+One can concisely write (\ref{S_H_ctl_resonance}) with
 \begin{align}
@@
   h_j^\t{ctl}\v I_j\c\uv m_j.
-  \label{H_ctl}
+  \label{S_H_ctl}
 \end{align}
 
-In both (\ref{H_int}) and (\ref{H_ctl}), one can choose $\phi_{DD}$
-and $\phi_\t{ctl}$ such that $\uv n_j\p\phi$ and
+In both (\ref{S_H_int}) and (\ref{S_H_ctl}), one can choose
+$\phi_{DD}$ and $\phi_\t{ctl}$ such that $\uv n_j\p\phi$ and
 $\uv m_j\p{\phi_\t{ctl}}$ lie anywhere in the plane perpendicular to
@@
 the same effective larmor frequency $\omega_j$, in which case they are
-addressed simultaneously in (\ref{H_int}) and (\ref{H_ctl}).
+addressed simultaneously in (\ref{S_H_int}) and (\ref{S_H_ctl}).
 
@@
 spins as a \emph{larmor pair}. The problem with individually
-addressing elements of a larmor set is manifest in (\ref{H_int}) and
-(\ref{H_ctl}), wherein the previously developed procedure for nuclear
-spin addressing does not single out any nuclei. Nonetheless, under
-certain conditions it is possible to individually address elements of
-a larmor set by applying additional control fields.
+addressing elements of a larmor set is manifest in (\ref{S_H_int}) and
+(\ref{S_H_ctl}), wherein the previously developed procedure for
+nuclear spin addressing does not single out any nuclei. Nonetheless,
+under certain conditions it is possible to individually address
+elements of a larmor set by applying additional control fields.
 
@@
   \c\v I_j \cos\p{\omega_rt-\phi_\t{dec}}
-  \label{H_dec_eff_full}
+  \label{S_H_dec_eff_full}
 \end{align}
@@
 If $\omega_r,\omega_j\gg \gamma_jB_\t{dec}$, then we can neglect
-$\v B_{\t{dec},j}^\parallel$ in (\ref{H_dec_eff_full}) by the secular
-approximation, and by the rotating approximation express
-\begin{multline}
-  \tilde H_\t{dec} \\
-  = -\sum_{j:\omega_j=\omega_r}
-  \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_\t{dec}
-  + \v B_{\t{dec},j}^{\perp\perp}\sin\phi_\t{dec}}\c\v I_j.
-\end{multline}
+$\v B_{\t{dec},j}^\parallel$ in (\ref{S_H_dec_eff_full}) by the
+secular approximation, and by the rotating approximation express
+\begin{align}
+  \tilde H_\t{dec} = -\sum_{j:\omega_j=\omega_r}
+  \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_\t{dec} +
+  \v B_{\t{dec},j}^{\perp\perp}\sin\phi_\t{dec}}\c\v I_j.
+\end{align}
 Defining
@@
   h_j^\t{int}I_\NV^z\v I_j\c\tilde{\v n}_j\p{t},
-  \label{H_int_dec_full}
+  \label{S_H_int_dec_full}
 \end{align}
-where $\tilde{\v n}_j\p{t}$ is the unit vector $\uv n_j$ rotated
-about $\uv\nu_j$ by $\nu_jt$, i.e.
+where $\tilde{\v n}_j\p{t}$ is the unit vector $\uv n_j$ rotated about
+$\uv\nu_j$ by $\nu_jt$, i.e.
 \begin{align}
@@
 us to neglect $\v n_j^\perp$ and $\v n_j^{\perp\perp}$ in
-(\ref{H_int_dec_full}), leaving
+(\ref{S_H_int_dec_full}), leaving
 \begin{align}
@@
   = \sum_{j:\omega_j=\omega_r}
-  h_j^\t{int}I_\NV^z\v I_j\c\v n_j^\parallel
-  = \sum_{j:\omega_j=\omega_r}
   \tilde h_j^\t{int}I_\NV^z\v I_j\c\uv\nu_j,
-  \label{H_int_dec}
+  \label{S_H_int_dec}
 \end{align}
@@
 \begin{align}
-  \tilde h_j^\t{int} = h_j\uv n_j\c\uv\nu_j.
+  \tilde h_j^\t{int} = h_j^\t{int}\uv n_j\c\uv\nu_j.
 \end{align}
@@
 In words, the decoupling field $\v B_\t{dec}^{\p\omega}\p{t}$ modifies
-$\tilde H_\t{int}$ in (\ref{H_int}) by suppressing the components of
+$\tilde H_\t{int}$ in (\ref{S_H_int}) by suppressing the components of
 $\uv n_j$ (i.e. $\uv A_j^\perp$ rotated about $\uv\omega_j$ by
@@
 single larmor pair, one can therefore apply a decoupling field to
-eliminate one of the two terms in (\ref{H_int_dec}) and realize an
+eliminate one of the two terms in (\ref{S_H_int_dec}) and realize an
 effective Hamiltonian which couples the NV electron spin to only one
@@
 therefore be either forgone, or else realized via composite operations
-making use of (\ref{H_ctl}) and (\ref{H_int_dec}). The same is true of
-spin-spin coupling between the NV electron spin and a single element
-of a larmor set with more than two nuclei.
+making use of (\ref{S_H_ctl}) and (\ref{S_H_int_dec}). The same is
+true of spin-spin coupling between the NV electron spin and a single
+element of a larmor set with more than two nuclei.
 
@@
 $\cNOT^{j\to k}$ gate is realized via
-\begin{multline}
-  \cNOT^{j\to k} \\
-  = \exp\p{-j\f\pi2I_j^z} \exp\p{-j\f\pi2I_k^x}
+\begin{align}
+  \cNOT^{j\to k} = \exp\p{-j\f\pi2I_j^z} \exp\p{-j\f\pi2I_k^x}
   \exp\p{j\pi I_j^z I_k^x}.
-\end{multline}
+\end{align}
 
@@
 and an ST qubit, it is easier to first realize the operation
-\begin{multline}
-  \SWAP^{\NV,\AC} \\
+\begin{align}
+  \SWAP^{\NV,\AC}
   = {\cNOT^{\AC\to\NV}}^\dagger\cNOT^{\NV\to\AC}\cNOT^{\AC\to\NV},
-  \label{SWAP_NVAC_sketch}
-\end{multline}
+  \label{S_SWAP_NVAC_sketch}
+\end{align}
 where
@@
 \end{align}
-For later convenience, (\ref{SWAP_NVAC_sketch}) makes use of the fact
-that ${\cNOT^{j\to k}}^\dagger=\cNOT^{j\to k}$. Therefore,
-\begin{multline}
-  \SWAP^{\NV,\AC} = \\
-  \exp\p{-j\f\pi2 I_\NV^x} \exp\p{j\f\pi2 I_1^{z'}}
-  \exp\p{-j\pi I_\NV^x I_1^{z'}}
-  \times \\
-  \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_1^{x'}}
-  \exp\p{j\pi I_\NV^z I_1^{x'}}
-  \times \\
-  \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_2^{x''}}
-  \exp\p{j\pi I_\NV^zI_2^{x''}}
-  \times \\
-  \exp\p{-j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_1^{z'}}
-  \exp\p{j\pi I_\NV^x I_1^{z'}},
-  \label{SWAP_NVAC_full}
-\end{multline}
+For later convenience, (\ref{S_SWAP_NVAC_sketch}) makes use of the
+fact that ${\cNOT^{j\to k}}^\dagger=\cNOT^{j\to k}$. Therefore,
+\begin{align}
+  \SWAP^{\NV,\AC}
+  =& \exp\p{-j\f\pi2 I_\NV^x} \exp\p{j\f\pi2 I_1^{z'}} \exp\p{-j\pi
+     I_\NV^x I_1^{z'}}
+     \times \tag*{} \\
+   & \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_1^{x'}} \exp\p{j\pi
+     I_\NV^z I_1^{x'}}
+     \times \tag*{} \\
+   & \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_2^{x''}} \exp\p{j\pi
+     I_\NV^zI_2^{x''}}
+     \times \tag*{} \\
+   & \exp\p{-j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_1^{z'}} \exp\p{j\pi
+     I_\NV^x I_1^{z'}},
+  \label{S_SWAP_NVAC_full}
+\end{align}
 where we make explicit the fact that the the spin of nuclei 1 and 2
@@
 can evaluate the first and last rotations of spin 1 in
-(\ref{SWAP_NVAC_full}) and combine factors to get
-\begin{multline}
-  \SWAP^{\NV,\AC} = \exp\p{j\f\pi2 I_\NV^x}
-  \exp\p{-j\pi I_\NV^x I_1^{z'}}
-  \times \\
-  \exp\p{-j\pi I_\NV^z}
-  \exp\p{j\f\pi2\sp{I_1^{y'}-I_2^{x''}}}
-  \times \\
-  \exp\p{-j\pi I_\NV^z I_1^{y'}}
-  \exp\p{j\pi I_\NV^z I_2^{x''}}
-  \times \\
-  \exp\p{j\pi I_\NV^x I_1^{z'}}
-  \exp\p{-j\f\pi2 I_\NV^x}.
-\end{multline}
+(\ref{S_SWAP_NVAC_full}) and combine factors to get
+\begin{align}
+  \SWAP^{\NV,\AC}
+  =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\pi I_\NV^x I_1^{z'}}
+     \times \tag*{} \\
+   & \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sp{I_1^{y'}-I_2^{x''}}}
+     \times \tag*{} \\
+   & \exp\p{-j\pi I_\NV^z I_1^{y'}} \exp\p{j\pi I_\NV^z I_2^{x''}}
+     \times \tag*{} \\
+   & \exp\p{j\pi I_\NV^x I_1^{z'}} \exp\p{-j\f\pi2 I_\NV^x}.
+\end{align}
 Letting
@@
   \uv y' = -\uv x'' &= \uv A_1^{\perp\perp}, \\
-  \uv z' = \uv z'' &= \uv\omega_1\approx\uv z, \label{w=z}
+  \uv z' = \uv z'' &= \uv\omega_1\approx\uv z, \label{S_w=z}
 \end{align}
-where the approximation in (\ref{w=z}) holds for $\gamma_1B\gg A_1/2$,
-\begin{multline}
-  \SWAP^{\NV,\AC} = \exp\p{j\f\pi2 I_\NV^x}
-  \exp\p{-j\pi I_\NV^x I_1^z}
-  \times \\
-  \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
-  \times \\
-  \exp\p{-j\pi I_\NV^z I_1^{y'}}
-  \exp\p{-j\pi I_\NV^z I_2{y'}}
-  \times \\
-  \exp\p{j\pi I_\NV^x I_1^z} \exp\p{-j\f\pi2 I_\NV^x}.
-  \label{SWAP_NVAC_sxsz}
-\end{multline}
+where the approximation in (\ref{S_w=z}) holds for
+$\gamma_1B\gg A_1/2$,
+\begin{align}
+  \SWAP^{\NV,\AC}
+  =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\pi I_\NV^x I_1^z}
+     \times \tag*{} \\
+   & \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
+     \times \tag*{} \\
+   & \exp\p{-j\pi I_\NV^z I_1^{y'}} \exp\p{-j\pi I_\NV^z I_2{y'}}
+     \times \tag*{} \\
+   & \exp\p{j\pi I_\NV^x I_1^z} \exp\p{-j\f\pi2 I_\NV^x}.
+  \label{S_SWAP_NVAC_sxsz}
+\end{align}
 As we cannot directly realize the coupling $\sigma_x^\NV\sigma_z^1$,
 we must perform rotations as
-\begin{multline}
-  \exp\p{-j\pi I_\NV^x I_1^z} =
-  \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\f\pi2 I_1^{y'}}
-  \times \\
-  \exp\p{-j\pi I_\NV^z I_1^{x'}}
-  \times \exp\p{-j\f\pi2 I_1^{y'}} \exp\p{j\f\pi2 I_\NV^y}.
-\end{multline}
-Substituting this identity into (\ref{SWAP_NVAC_sxsz}) yields
-\begin{multline}
-  \SWAP^{\NV,\AC} = \exp\p{j\f\pi2 I_\NV^x}
-  \exp\p{-j\f\pi2 I_\NV^y}
-  \times \\
-  \exp\p{j\f\pi2\sum_jI_j^{y'}}
-  \exp\p{-j\pi I_\NV^z I_1^{x'}}
+\begin{align}
+  \exp\p{-j\pi I_\NV^x I_1^z}
+  =& \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\f\pi2 I_1^{y'}}
+     \times \tag*{} \\
+   & \exp\p{-j\pi I_\NV^z I_1^{x'}} \times \exp\p{-j\f\pi2 I_1^{y'}}
+     \exp\p{j\f\pi2 I_\NV^y}.
+\end{align}
+Substituting this identity into (\ref{S_SWAP_NVAC_sxsz}) yields
+\begin{align}
+  \SWAP^{\NV,\AC} =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_\NV^y}
+  \times \tag*{} \\
+  & \exp\p{j\f\pi2\sum_jI_j^{y'}} \exp\p{-j\pi I_\NV^z I_1^{x'}}
   \exp\p{j\f\pi2 I_\NV^y}
-  \times \\
-  \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
-  \times \\
-  \exp\p{-j\pi I_\NV^z I_1^{y'}}
-  \exp\p{-j\pi I_\NV^z I_2^{y'}}
-  \times \\
-  \exp\p{-j\f\pi2 I_\NV^y}
-  \exp\p{j\pi I_\NV^z I_1^{x'}}
+  \times \tag*{} \\
+  & \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
+  \times \tag*{} \\
+  & \exp\p{-j\pi I_\NV^z I_1^{y'}} \exp\p{-j\pi I_\NV^z I_2^{y'}}
+  \times \tag*{} \\
+  & \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\pi I_\NV^z I_1^{x'}}
   \exp\p{-j\f\pi2\sum_jI_j^{y'}}
-  \times \\
-  \exp\p{j\f\pi2 I_\NV^y} \exp\p{-j\f\pi2 I_\NV^x},
-  \label{SWAP_NVAC}
-\end{multline}
+  \times \tag*{} \\
+  & \exp\p{j\f\pi2 I_\NV^y} \exp\p{-j\f\pi2 I_\NV^x},
+  \label{S_SWAP_NVAC}
+\end{align}
 where we have canceled out two rotations of the form
-$\exp\p{\pm j\pi/2~I_1^{y'}}$ and inserted two rotations of the
-form $\exp\p{\pm j\pi/2~I_2^{y'}}$ with no net effect.
+$\exp\p{\pm j\pi/2~I_1^{y'}}$ and inserted two rotations of the form
+$\exp\p{\pm j\pi/2~I_2^{y'}}$ with no net effect.
 
@@
 We therefore have that
-\begin{multline}
-  \SWAP^{\NV,\ST} = \exp\p{j\pi\v I_\NV\c\uv a}
-  \times \\
-  \exp\p{j\f\pi2\sum_jI_j^{y'}}
-  \exp\p{-j\pi I_\NV^z I_1^{x'}}
-  \exp\p{j\f\pi2 I_\NV^y}
-  \times \\
-  \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
-  \times \\
-  \exp\p{-j\pi I_\NV^z I_1^{y'}}
-  \exp\p{-j\pi I_\NV^z I_2^{y'}}
-  \times \\
-  \exp\p{-j\f\pi2 I_\NV^y}
-  \exp\p{j\pi I_\NV^z I_1^{x'}}
-  \exp\p{-j\f\pi2\sum_jI_j^{y'}}
-  \times \\
-  \exp\p{-j\pi\v I_\NV\c\uv a},
-  \label{SWAP_NVST}
-\end{multline}
+\begin{align}
+  \SWAP^{\NV,\ST}
+  =& \exp\p{j\pi\v I_\NV\c\uv a} \times \tag*{} \\
+   & \exp\p{j\f\pi2\sum_jI_j^{y'}} \exp\p{-j\pi I_\NV^z I_1^{x'}}
+     \exp\p{j\f\pi2 I_\NV^y} \times \tag*{} \\
+   & \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
+     \times \tag*{} \\
+   & \exp\p{-j\pi I_\NV^z I_1^{y'}} \exp\p{-j\pi I_\NV^z I_2^{y'}}
+     \times \tag*{} \\
+   & \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\pi I_\NV^z I_1^{x'}}
+     \exp\p{-j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
+   & \exp\p{-j\pi\v I_\NV\c\uv a},
+  \label{S_SWAP_NVST}
+\end{align}
 where $\v a = \uv x - \uv y$ and we have used the fact that
-\begin{multline}
+\begin{align}
   \exp\p{j\f\pi2 I^y} \exp\p{-j\f\pi2 I^x}
-  \exp\p{j\f\pi2 I^y} \\
+  \exp\p{j\f\pi2 I^y}
   = \exp\p{-j\pi\v I\c\uv a}.
-\end{multline}
+\end{align}
 
-In the subspace of interest, we have thus
-constructed the non-entangling SWAP operation
-\begin{multline}
-  \SWAP^{\NV,\ST} \\
-  = \op{\u\S}{\S\u} + \op{\u\T}{\d\S} + \op{\d\S}{\u\T} +
-  \op{\d\T}{\d\T}.
-\end{multline}
+In the subspace of interest, we have thus constructed the
+non-entangling SWAP operation
+\begin{align}
+  \SWAP^{\NV,\ST} = \op{\u\S}{\S\u} + \op{\u\T}{\d\S}
+  + \op{\d\S}{\u\T} + \op{\d\T}{\d\T}.
+\end{align}
 If $\gamma_1=\gamma_2$, i.e. if nuclei 1 and 2 are of the same
-species, all factors in (\ref{SWAP_NVST}) can be realized directly via
-the protocols for (\ref{H_ctl}), (\ref{H_int_dec}), and rotations of
-the NV electron spin.
+species, all factors in (\ref{S_SWAP_NVST}) can be realized directly
+via the protocols for (\ref{S_H_ctl}), (\ref{S_H_int_dec}), and
+rotations of the NV electron spin.
 
 Realizing $\SWAP^{\NV,\AC}$ by switching the cNOT operations in
-(\ref{SWAP_NVAC_sketch}) is seemingly impossible, as doing so requires
-rotating one spin in the larmor pair without rotating the other. It is
-possible to realize $\SWAP^{\NV,\ST}$ via cNOT operations between the
-NV and ST qubits directly, but this method requires performing many
-more individual spin addressing operations, and therefore has a
-substantially lower fidelity.
+(\ref{S_SWAP_NVAC_sketch}) is seemingly impossible, as doing so
+requires rotating one spin in the larmor pair without rotating the
+other. It is possible to realize $\SWAP^{\NV,\ST}$ via cNOT operations
+between the NV and ST qubits directly, but this method requires
+performing many more individual spin addressing operations, and
+therefore has a substantially lower fidelity.
 
@@
 
-\footnotesize \bibliography{\jobname}
+\bibliography{\jobname}
 

### 2016-07-13 qp-math.cpp
normalize output of ptrace

@@ -153,7 +153,7 @@ MatrixXcd ptrace(const MatrixXcd& A, const vector<uint>& qs_trace) {
       }
     }
   }
-  return B;
+  return B  / sqrt(real(trace(B.adjoint()*B)) / B.rows());
 }
 
 // extract sub-matrix which acts only on the given qbits

### 2016-07-15 swap-nvst-paper/paper.tex
changed conventions on specifying angle in a coupling operation

@@
 \begin{align}
-  H_\t{int} = h_\t{int} I_\NV^z\v I_j\c\uv n_j,
+  H_\t{int} = h_j^\t{int}\sigma_\NV^z\v I_j\c\uv n_j,
   \label{H_int}
@@
 for a tunable coupling strength $h_\t{int}$ and direction $\uv n_j$,
-where $I_\NV^z\equiv\p{\op{m_s}-\op{0}}/2$ and $\v I_j$ is the spin
+where $\sigma_\NV^z\equiv\op{m_s}-\op{0}$ and $\v I_j$ is the spin
 operator for nuclear spin $j$. The protocol for realizing this
@@
 When trying to address one spin in a larmor pair, the protocols for
-(\ref{H_int}) will simultaneously couple $I_\NV^z$ to both
+(\ref{H_int}) will simultaneously couple $\sigma_\NV^z$ to both
 $\v I_1\c\uv n_1$ and $\v I_2\c\uv n_2$ with identical coupling
@@
 \begin{align}
-  S_z = \f{m_s}2\p{I_\NV^z+\mathbf1},
+  S_z = \f{m_s}2\p{\sigma_\NV^z+\mathbf1},
 \end{align}
-where $I_\NV^z\equiv\p{\op{m_s}-\op{0}}/2$ and
+where $\sigma_\NV^z\equiv\op{m_s}-\op{0}$ and
 $\mathbf1\equiv\op{m_s}+\op{0}$. Defining the interaction Hamiltonian
 \begin{align}
-  H_\t{int} = m_sI_\NV^z\sum_j\v A_j\c\v I_j
+  H_\t{int} = \f12m_s\sigma_\NV^z\sum_j\v A_j\c\v I_j
 \end{align}
@@
 \begin{align}
-  \tilde H_\t{int} = m_sI_\NV^z
+  \tilde H_\t{int} = \f12m_s\sigma_\NV^z
   \sum_j\tilde{\v A_j}\p{t}\c\v I_j,
@@
 with fundamental frequency $\omega_{DD}$, phase $\phi_{DD}$, and range
-$\set{1,-1}$ to $I_\NV^z$, so that the system Hamiltonian reads
+$\set{1,-1}$ to $\sigma_\NV^z$, so that the system Hamiltonian reads
 \begin{align}
   \tilde H_\t{int} =
-  F\p{t}m_sI_\NV^z\sum_j\tilde{\v A_j}\p{t}\c\v I_j.
+  \f12m_sF\p{t}\sigma_\NV^z\sum_j\tilde{\v A_j}\p{t}\c\v I_j.
 \end{align}
@@
 \begin{align}
-  \tilde H_\t{int} = \f12 f_{k_{DD}} m_sI_\NV^z
+  \tilde H_\t{int} = \f14 f_{k_{DD}} m_s\sigma_\NV^z
   \sum_{j:\omega_j=\omega_r} A_j^\perp\v I_j\c\uv n_j,
@@
 \begin{align}
-  h_j^\t{int}\equiv f_{k_{DD}}m_sA_j^\perp/2
+  h_j^\t{int}\equiv f_{k_{DD}}m_sA_j^\perp/4
 \end{align}
@@
   \tilde H_\t{int} = \sum_{j:\omega_j=\omega_r}
-  h_j^\t{int}I_\NV^z\v I_j\c\uv n_j.
+  h_j^\t{int}\sigma_\NV^z\v I_j\c\uv n_j.
   \label{S_H_int}
@@
   = \sum_{j:\omega_j=\omega_r}
-  \p{h_j^\t{int}I_\NV^z\v I_j\c\uv n_j - \v\nu_j\c\v I_j}.
+  \p{h_j^\t{int}\sigma_\NV^z\v I_j\c\uv n_j - \v\nu_j\c\v I_j}.
 \end{align}
@@
   \tilde H_\t{int}^\t{dec} = \sum_{j:\omega_j=\omega_r}
-  h_j^\t{int}I_\NV^z\v I_j\c\tilde{\v n}_j\p{t},
+  h_j^\t{int}\sigma_\NV^z\v I_j\c\tilde{\v n}_j\p{t},
   \label{S_H_int_dec_full}
@@
   = \sum_{j:\omega_j=\omega_r}
-  \tilde h_j^\t{int}I_\NV^z\v I_j\c\uv\nu_j,
+  \tilde h_j^\t{int}\sigma_\NV^z\v I_j\c\uv\nu_j,
   \label{S_H_int_dec}
@@
 For later convenience, (\ref{S_SWAP_NVAC_sketch}) makes use of the
-fact that ${\cNOT^{j\to k}}^\dagger=\cNOT^{j\to k}$. Therefore,
+fact that ${\cNOT^{j\to k}}^\dagger=\cNOT^{j\to k}$. Therefore (with
+$\v I_\NV=\v\sigma_\NV/2$),
 \begin{align}
   \SWAP^{\NV,\AC}
-  =& \exp\p{-j\f\pi2 I_\NV^x} \exp\p{j\f\pi2 I_1^{z'}} \exp\p{-j\pi
-     I_\NV^x I_1^{z'}}
-     \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_1^{x'}} \exp\p{j\pi
-     I_\NV^z I_1^{x'}}
-     \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_2^{x''}} \exp\p{j\pi
-     I_\NV^zI_2^{x''}}
-     \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_1^{z'}} \exp\p{j\pi
-     I_\NV^x I_1^{z'}},
+  =& \exp\p{-j\f\pi2 I_\NV^x} \exp\p{j\f\pi2 I_1^{z'}}
+     \exp\p{-j\f\pi2 \sigma_\NV^x I_1^{z'}} \times \tag*{} \\
+   & \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_1^{x'}}
+     \exp\p{j\f\pi2 \sigma_\NV^z I_1^{x'}} \times \tag*{} \\
+   & \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_2^{x''}}
+     \exp\p{j\f\pi2 \sigma_\NV^z I_2^{x''}} \times \tag*{} \\
+   & \exp\p{-j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_1^{z'}}
+     \exp\p{j\f\pi2 \sigma_\NV^x I_1^{z'}},
   \label{S_SWAP_NVAC_full}
@@
   \SWAP^{\NV,\AC}
-  =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\pi I_\NV^x I_1^{z'}}
+  =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 \sigma_\NV^x I_1^{z'}}
      \times \tag*{} \\
@@
      \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z I_1^{y'}} \exp\p{j\pi I_\NV^z I_2^{x''}}
-     \times \tag*{} \\
-   & \exp\p{j\pi I_\NV^x I_1^{z'}} \exp\p{-j\f\pi2 I_\NV^x}.
+   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
+     \exp\p{j\f\pi2 \sigma_\NV^z I_2^{x''}} \times \tag*{} \\
+   & \exp\p{j\f\pi2 \sigma_\NV^x I_1^{z'}} \exp\p{-j\f\pi2 I_\NV^x}.
 \end{align}
@@
   \SWAP^{\NV,\AC}
-  =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\pi I_\NV^x I_1^z}
-     \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
-     \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z I_1^{y'}} \exp\p{-j\pi I_\NV^z I_2{y'}}
-     \times \tag*{} \\
-   & \exp\p{j\pi I_\NV^x I_1^z} \exp\p{-j\f\pi2 I_\NV^x}.
+  =& \exp\p{j\f\pi2 I_\NV^x}
+     \exp\p{-j\f\pi2 \sigma_\NV^x I_1^z} \times \tag*{} \\
+   & \exp\p{-j\pi I_\NV^z}
+     \exp\p{j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
+   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
+     \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \times \tag*{} \\
+   & \exp\p{j\f\pi2 \sigma_\NV^x I_1^z} \exp\p{-j\f\pi2 I_\NV^x}.
   \label{S_SWAP_NVAC_sxsz}
 \end{align}
-As we cannot directly realize the coupling $\sigma_x^\NV\sigma_z^1$,
+As we cannot directly realize the coupling $\sigma_x^\NV I_z^1$,
 we must perform rotations as
 \begin{align}
-  \exp\p{-j\pi I_\NV^x I_1^z}
+  \exp\p{-j\f\pi2 \sigma_\NV^x I_1^z}
   =& \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\f\pi2 I_1^{y'}}
-     \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z I_1^{x'}} \times \exp\p{-j\f\pi2 I_1^{y'}}
-     \exp\p{j\f\pi2 I_\NV^y}.
+     \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{x'}}
+     \exp\p{-j\f\pi2 I_1^{y'}} \exp\p{j\f\pi2 I_\NV^y}.
 \end{align}
@@
 \begin{align}
-  \SWAP^{\NV,\AC} =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_\NV^y}
-  \times \tag*{} \\
-  & \exp\p{j\f\pi2\sum_jI_j^{y'}} \exp\p{-j\pi I_\NV^z I_1^{x'}}
-  \exp\p{j\f\pi2 I_\NV^y}
-  \times \tag*{} \\
-  & \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
-  \times \tag*{} \\
-  & \exp\p{-j\pi I_\NV^z I_1^{y'}} \exp\p{-j\pi I_\NV^z I_2^{y'}}
-  \times \tag*{} \\
-  & \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\pi I_\NV^z I_1^{x'}}
-  \exp\p{-j\f\pi2\sum_jI_j^{y'}}
-  \times \tag*{} \\
+  \SWAP^{\NV,\AC}
+  =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_\NV^y} \times \tag*{} \\
+   & \exp\p{j\f\pi2\sum_jI_j^{y'}}
+     \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{x'}}
+     \exp\p{j\f\pi2 I_\NV^y} \times \tag*{} \\
+   & \exp\p{-j\pi I_\NV^z}
+     \exp\p{j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
+   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
+     \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \times \tag*{} \\
+   & \exp\p{-j\f\pi2 I_\NV^y}
+     \exp\p{j\f\pi2 \sigma_\NV^z I_1^{x'}}
+     \exp\p{-j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
    & \exp\p{j\f\pi2 I_\NV^y} \exp\p{-j\f\pi2 I_\NV^x},
@@
   =& \exp\p{j\pi\v I_\NV\c\uv a} \times \tag*{} \\
-   & \exp\p{j\f\pi2\sum_jI_j^{y'}} \exp\p{-j\pi I_\NV^z I_1^{x'}}
+   & \exp\p{j\f\pi2\sum_jI_j^{y'}}
+     \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{x'}}
      \exp\p{j\f\pi2 I_\NV^y} \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sum_jI_j^{y'}}
-     \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z I_1^{y'}} \exp\p{-j\pi I_\NV^z I_2^{y'}}
-     \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\pi I_\NV^z I_1^{x'}}
+   & \exp\p{-j\pi I_\NV^z}
+     \exp\p{j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
+   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
+     \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \times \tag*{} \\
+   & \exp\p{-j\f\pi2 I_\NV^y}
+     \exp\p{j\f\pi2 \sigma_\NV^z I_1^{x'}}
      \exp\p{-j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\

### 2016-07-15 nv-control.cpp

@@ -210,8 +210,8 @@ protocol act_target(const nv_system& nv, const uint target, const Matrix2cd& U,
   else return equatorial_rotation;
 }
 
-// propagator U = exp(-i * phase * I_{NV}^{n_1}*I_{target}^{n_2})
-protocol U_int(const nv_system& nv, const uint target, const double phase,
+// propagator U = exp(-i * angle * sigma_{NV}^{n_1}*I_{target}^{n_2})
+protocol U_int(const nv_system& nv, const uint target, const double angle,
                const Vector3d& nv_axis, const double target_azimuth,
                const bool decouple) {
   // identify cluster of target nucleus
@@ -281,11 +281,11 @@ protocol U_int(const nv_system& nv, const uint target, const double phase,
   }
 
   // coupling strength and rotation period
-  double h_int = f_DD*nv.ms*A_int/2;
-  const double t_rot = abs(4*pi/h_int);
+  double h_int = f_DD*nv.ms*A_int/4;
+  const double t_rot = abs(2*pi/h_int);
 
   // time for which to interact
-  double interaction_time = mod(phase/h_int, t_rot);
+  double interaction_time = mod(angle/h_int, t_rot);
   if (interaction_time > t_rot/2) {
     f_DD *= -1;
     h_int *= -1;
@@ -323,7 +323,7 @@ protocol U_int(const nv_system& nv, const uint target, const double phase,
 }
 
 // perform given NV coupling operation on a target nucleus
-protocol couple_target(const nv_system& nv, const uint target, const double phase,
+protocol couple_target(const nv_system& nv, const uint target, const double angle,
                        const Vector3d& nv_axis, const Vector3d& target_axis,
                        const bool exact, const bool decouple, const bool adjust_AXY) {
   if (exact) {
@@ -332,7 +332,7 @@ protocol couple_target(const nv_system& nv, const uint target, const double phas
     const uint subsystem_target = get_index_in_subsystem(nv,target);
     const uint spins = nv.clusters.at(cluster).size()+1;
 
-    const Matrix4cd U = exp(-j * phase * tp(dot(I_vec,hat(nv_axis)),
+    const Matrix4cd U = exp(-j * angle * tp(dot(s_vec,hat(nv_axis)),
[…]

### 2016-07-15 nv-control.h

@@ -64,13 +64,13 @@ inline protocol rotate_target(const nv_system& nv, const uint target, const doub
   return act_target(nv, target, rotate(angle, axis), exact, adjust_AXY);
 }
 
-// propagator U = exp(-i * phase * I_{NV}^{n_1}*I_{target}^{n_2})
-protocol U_int(const nv_system& nv, const uint target, const double phase,
+// propagator U = exp(-i * angle * sigma_{NV}^{n_1}*I_{target}^{n_2})
+protocol U_int(const nv_system& nv, const uint target, const double angle,
                const Vector3d& nv_axis, const double target_azimuth,
                const bool decouple = true);
 
 // perform given NV coupling operation on a target nucleus
-protocol couple_target(const nv_system& nv, const uint target, const double phase,
+protocol couple_target(const nv_system& nv, const uint target, const double angle,
                        const Vector3d& nv_axis, const Vector3d& target_axis,
                        const bool exact = false, const bool decouple = true,
                        const bool adjust_AXY = true);

### 2016-07-15 simulation.cpp

@@ -122,8 +122,8 @@ int main(const int arg_num, const char *arg_vec[]) {
 
   vector<uint> target_nuclei;
   bool target_pairs;
-  double phase;
-  double phase_over_pi;
+  double angle;
+  double angle_over_pi;
   double target_polar;
   double target_pitch_over_pi;
   double target_azimuth;
@@ -142,8 +142,8 @@ int main(const int arg_num, const char *arg_vec[]) {
     ("target_pairs",
      po::value<bool>(&target_pairs)->default_value(false)->implicit_value(true),
      "target only one nucleus in each larmor pair")
-    ("phase", po::value<double>(&phase_over_pi)->default_value(1),
-     "phase of operation to perform")
+    ("angle", po::value<double>(&angle_over_pi)->default_value(1),
+     "angle of operation to perform")
     ("target_pitch", po::value<double>(&target_pitch_over_pi)->default_value(0),
      "pitch (angle above x-y plane) of target rotation axis")
     ("target_azimuth", po::value<double>(&target_azimuth_over_pi)->default_value(0),
@@ -247,7 +247,7 @@ int main(const int arg_num, const char *arg_vec[]) {
   k_DD = (k_DD_int == 1 ? first : third);
   scan_time = scan_time_in_ms*1e-3;
 
-  phase = phase_over_pi*pi;
+  angle = angle_over_pi*pi;
   target_polar = pi/2 - target_pitch_over_pi*pi;
   target_azimuth = target_azimuth_over_pi*pi;
   nv_polar = pi/2 - nv_pitch_over_pi*pi;
@@ -507,7 +507,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       const Vector3d target_axis = axis(target_polar,target_azimuth);
       vector<protocol> P(2);
       for (bool exact : {true,false}) {
-        P.at(exact) = rotate_target(nv, target, phase, target_axis, exact);
+        P.at(exact) = rotate_target(nv, target, angle, target_axis, exact);
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
@@ -528,7 +528,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       const Vector3d target_axis = axis(target_polar, target_azimuth);
       vector<protocol> P(2);
       for (bool exact : {true,false}) {
-        P.at(exact) = couple_target(nv, target, phase, nv_axis, target_axis, exact);
[…]

### 2016-07-15 nv-control.cpp
fixed incorrect limits on f_DD in U_int

@@ -226,6 +226,12 @@ protocol U_int(const nv_system& nv, const uint target, const double angle,
   const Vector3d A_perp = hyperfine_perp(nv,target);
   const double f_DD_max = axy_f_max(nv.k_DD);
 
+  // AXY sequence parameters
+  const double w_DD = w_larmor/nv.k_DD; // AXY protocol angular frequency
+  const double t_DD = 2*pi/w_DD; // AXY protocol period
+  const double dw_min = larmor_resolution(nv,target);
+  double f_DD = min(dw_min/(A_perp.norm()*nv.scale_factor), f_DD_max);
+
   // control fields, AXY sequence phase, and effective hyperfine coupling strength
   control_fields controls;
   double phi_DD;
@@ -266,18 +272,12 @@ protocol U_int(const nv_system& nv, const uint target, const double angle,
     const Vector3d A_perp_rot = rotate(A_perp, phi_DD, w_hat);
     A_int = dot(A_perp_rot, axis_ctl);
 
+    // enforce additional limit on allowed values of f_DD
+    f_DD = min(f_DD, gB_ctl/(A_perp.norm()*nv.scale_factor));
+
   } else { // there is nothing to decouple
     phi_DD = target_azimuth;
     A_int = A_perp.norm();
-  }
-
-  // AXY sequence parameters
-  const double w_DD = w_larmor/nv.k_DD; // AXY protocol angular frequency
-  const double t_DD = 2*pi/w_DD; // AXY protocol period
-  double f_DD = min(larmor_resolution(nv,target)/(abs(A_int)*nv.scale_factor), f_DD_max);
-  if (decouple_index >= 0 &&
-      controls.gB().norm() / (f_DD*abs(A_int)) < nv.scale_factor) {
-    f_DD = controls.gB().norm() / (nv.scale_factor*abs(A_int));
   }
 
   // coupling strength and rotation period

### 2016-07-15 fidelity-sweep.py
generate summary of data (in fidelity-sweep.py) before copying everything back to the project directory

@@ -41,6 +41,7 @@ job_dir = os.environ["TMPDIR"] + "/" + os.environ["USER"] + "/" + "".join(sys.ar
 # move into job directory
 os.makedirs(job_dir)
 shutil.copy2(project_dir+"/"+sim_file, job_dir+"/"+sim_file)
+shutil.copy2(project_dir+"/"+summary_script, job_dir+"/"+summary_script)
 os.chdir(job_dir)
 os.mkdir(data_dir)
 
@@ -86,10 +87,8 @@ for s in range(samples):
 while threading.active_count() > 1:
     time.sleep(1)
 
-# copy final results into the project directory
-copy_results()
-
 # generate fidelity summary file
-os.chdir(project_dir)
 subprocess.call(["./"+summary_script,out_file])
 
+# copy final results into the project directory
+copy_results()

### 2016-07-15 simulation.cpp
changed simulation behavior with printing options

@@ -37,8 +37,6 @@ int main(const int arg_num, const char *arg_vec[]) {
      "seed for random number generator")
     ;
 
-  bool print_lattice;
-  bool print_pairs;
   bool coherence_scan;
   bool rotation;
   bool coupling;
@@ -46,17 +44,10 @@ int main(const int arg_num, const char *arg_vec[]) {
   bool swap_fidelities;
   bool swap_nvst_fidelity;
   bool identity_fidelity;
-  bool target_info;
   bool testing;
 
   po::options_description simulations("Available simulations",help_text_length);
   simulations.add_options()
-    ("print_lattice",
-     po::value<bool>(&print_lattice)->default_value(false)->implicit_value(true),
-     "print C-13 lattice to a file")
-    ("print_pairs",
-     po::value<bool>(&print_pairs)->default_value(false)->implicit_value(true),
-     "search for larmor pairs")
     ("scan", po::value<bool>(&coherence_scan)->default_value(false)->implicit_value(true),
      "perform coherence scan for effective larmor frequencies")
     ("rotate", po::value<bool>(&rotation)->default_value(false)->implicit_value(true),
@@ -75,9 +66,6 @@ int main(const int arg_num, const char *arg_vec[]) {
     ("identity",
      po::value<bool>(&identity_fidelity)->default_value(false)->implicit_value(true),
      "compute expected fidelity of an identity operation")
-    ("target_info",
-     po::value<bool>(&target_info)->default_value(false)->implicit_value(true),
-     "print information about target nuclei")
     ("test" ,po::value<bool>(&testing)->default_value(false)->implicit_value(true),
      "enable testing mode")
     ;
@@ -177,6 +165,23 @@ int main(const int arg_num, const char *arg_vec[]) {
      "input file defining system configuration")
     ;
 
+  bool print_lattice;
+  bool print_pairs;
+  bool target_info;
+
+  po::options_description print_options("Available printing options",help_text_length);
+  print_options.add_options()
+    ("print_lattice",
+     po::value<bool>(&print_lattice)->default_value(false)->implicit_value(true),
+     "print C-13 lattice to a file")
+    ("print_pairs",
+     po::value<bool>(&print_pairs)->default_value(false)->implicit_value(true),
+     "print larmor pairs")
+    ("target_info",
+     po::value<bool>(&target_info)->default_value(false)->implicit_value(true),
+     "print information about target nuclei")
+    ;
+
[…]

### 2016-07-15 nv-control.cpp
set w_ctl safely in U_int and assign default values to phi_DD and A_int

@@ -218,7 +218,7 @@ protocol U_int(const nv_system& nv, const uint target, const double angle,
   const uint cluster = get_cluster_containing_target(nv,target);
   const uint spins = nv.clusters.at(cluster).size()+1;
 
-  // effective larmor frequency and rotation axis,
+  // effective larmor frequency and precession axis,
   //   perpendicular component of hyperfine field,
   //   and maximum possible value of f_DD
   const double w_larmor = effective_larmor(nv,target).norm();
@@ -232,10 +232,13 @@ protocol U_int(const nv_system& nv, const uint target, const double angle,
   const double dw_min = larmor_resolution(nv,target);
   double f_DD = min(dw_min/(A_perp.norm()*nv.scale_factor), f_DD_max);
 
-  // control fields, AXY sequence phase, and effective hyperfine coupling strength
+  // control field and frequency of precession about its axis
   control_fields controls;
-  double phi_DD;
-  double A_int;
+  double w_ctl = 0;
+
+  // default values for AXY sequence phase and effective hyperfine coupling strength
+  double phi_DD = target_azimuth;
+  double A_int = A_perp.norm();
 
   // identify index of nucleus to decouple with a control field
   const int decouple_index = [&]() -> int {
@@ -253,13 +256,14 @@ protocol U_int(const nv_system& nv, const uint target, const double angle,
 
   // if we have identified a nucleus to decouple
   if (decouple_index >= 0) {
-    // set control field
+    // set control field and precession frequency
     const double gB_ctl =
       min({ exp( (log(2*w_larmor) + log(f_DD_max*A_perp.norm())) / 2),
             2*w_larmor / nv.scale_factor,
             max_gB_ctl});
     const Vector3d axis_ctl = hat(rotate(A_perp, target_azimuth, w_hat));
     controls.add(gB_ctl*axis_ctl, w_larmor);
+    w_ctl = gB_ctl/2;
 
     // set AXY sequence phase
     const Vector3d axis_ctl_rot = rotate(axis_ctl, pi/2, w_hat);
@@ -274,10 +278,6 @@ protocol U_int(const nv_system& nv, const uint target, const double angle,
 
     // enforce additional limit on allowed values of f_DD
     f_DD = min(f_DD, gB_ctl/(A_perp.norm()*nv.scale_factor));
-
-  } else { // there is nothing to decouple
-    phi_DD = target_azimuth;
-    A_int = A_perp.norm();
   }
 
[…]

### 2016-07-15 nv-control.cpp
renamed some variables, rearranged some code, and added comments for future methods

@@ -452,8 +452,8 @@ protocol SWAP_NVST(const nv_system& nv, const uint idx1, const uint idx2,
 
 // identity operation on the cluster containing a target nucleus
 //   assumes that the NV center is polarized to the |0> state
-protocol identity(const nv_system& nv, const uint target, const double time,
-                  const bool exact) {
+protocol target_identity(const nv_system& nv, const uint target, const double time,
+                         const bool exact) {
   const uint cluster = get_cluster_containing_target(nv,target);
   const uint cluster_spins = nv.clusters.at(cluster).size();
 

### 2016-07-15 nv-control.h

@@ -93,5 +93,5 @@ protocol SWAP_NVST(const nv_system& nv, const uint idx1, const uint idx2,
 
 // identity operation on the cluster containing a target nucleus
 //   assumes that the NV center is polarized to the |0> state
-protocol identity(const nv_system& nv, const uint target, const double time,
-                  const bool exact = false);
+protocol target_identity(const nv_system& nv, const uint target, const double time,
+                         const bool exact = false);

### 2016-07-15 simulation.cpp

@@ -40,11 +40,11 @@ int main(const int arg_num, const char *arg_vec[]) {
   bool coherence_scan;
   bool rotation;
   bool coupling;
-  bool iswap_fidelities;
-  bool swap_fidelities;
-  bool swap_nvst_fidelity;
-  bool identity_fidelity;
-  bool testing;
+  bool iswap;
+  bool swap;
+  bool swap_nvst;
+  bool identity;
+  bool testing_mode;
 
   po::options_description simulations("Available simulations",help_text_length);
   simulations.add_options()
@@ -54,19 +54,15 @@ int main(const int arg_num, const char *arg_vec[]) {
      "rotate an individual nucleus")
     ("couple", po::value<bool>(&coupling)->default_value(false)->implicit_value(true),
      "couple an individual nucleus to NV center")
-    ("iswap",
-     po::value<bool>(&iswap_fidelities)->default_value(false)->implicit_value(true),
+    ("iswap", po::value<bool>(&iswap)->default_value(false)->implicit_value(true),
      "compute expected iSWAP fidelities")
-    ("swap",
-     po::value<bool>(&swap_fidelities)->default_value(false)->implicit_value(true),
+    ("swap", po::value<bool>(&swap)->default_value(false)->implicit_value(true),
      "compute expected SWAP fidelities")
-    ("swap_nvst",
-     po::value<bool>(&swap_nvst_fidelity)->default_value(false)->implicit_value(true),
+    ("swap_nvst", po::value<bool>(&swap_nvst)->default_value(false)->implicit_value(true),
      "compute expected SWAP_NVST fidelity")
-    ("identity",
-     po::value<bool>(&identity_fidelity)->default_value(false)->implicit_value(true),
+    ("identity", po::value<bool>(&identity)->default_value(false)->implicit_value(true),
      "compute expected fidelity of an identity operation")
-    ("test" ,po::value<bool>(&testing)->default_value(false)->implicit_value(true),
+    ("test" ,po::value<bool>(&testing_mode)->default_value(false)->implicit_value(true),
      "enable testing mode")
     ;
 
@@ -209,16 +205,16 @@ int main(const int arg_num, const char *arg_vec[]) {
   bool set_target_nuclei = inputs.count("target");
 
   // run a sanity check on inputs
-  if (!testing) {
+  if (!testing_mode) {
     const bool printing = print_lattice || print_pairs || target_info;
     if (!printing) {
       if (int(coherence_scan)
[…]

### 2016-07-19 nv-control.cpp
added methods to initialize nuclear spins

@@ -463,3 +463,22 @@ protocol target_identity(const nv_system& nv, const uint target, const double ti
   const MatrixXcd U = exp(-j*time*H);
   return protocol(U, time);
 }
+
+// operation to deterministically initialize a thermalized nucleus into |u> or |d>
+protocol initialize_spin_Z(const nv_system& nv, const uint target, const bool exact) {
+  const uint cluster = get_cluster_containing_target(nv,target);
+  const uint spins = nv.clusters.at(cluster).size()+1;
+  return (couple_target(nv, target, pi/2, zhat, yhat, exact) *
+          rotate_NV(nv, pi/2, xhat, spins) *
+          couple_target(nv, target, pi/2, zhat, xhat, exact) *
+          rotate_NV(nv, pi/2, yhat, spins));
+}
+
+// operation to probabalistically initialize a thermalized nucleus into |u> +/- |d>
+protocol initialize_spin_X(const nv_system& nv, const uint target, const bool exact) {
+  const uint cluster = get_cluster_containing_target(nv,target);
+  const uint spins = nv.clusters.at(cluster).size()+1;
+  return (rotate_NV(nv, pi/2, xhat, spins) *
+          couple_target(nv, target, pi/2, zhat, xhat, exact) *
+          rotate_NV(nv, pi/2, yhat, spins));
+}

### 2016-07-19 nv-control.h

@@ -95,3 +95,11 @@ protocol SWAP_NVST(const nv_system& nv, const uint idx1, const uint idx2,
 //   assumes that the NV center is polarized to the |0> state
 protocol target_identity(const nv_system& nv, const uint target, const double time,
                          const bool exact = false);
+
+// operation to deterministically initialize a thermalized nucleus into |u> or |d>
+protocol initialize_spin_Z(const nv_system& nv, const uint target,
+                           const bool exact = false);
+
+// operation to probabalistically initialize a thermalized nucleus into |u> +/- |d>
+protocol initialize_spin_X(const nv_system& nv, const uint target,
+                           const bool exact = false);

### 2016-07-19 simulation.cpp

@@ -45,6 +45,8 @@ int main(const int arg_num, const char *arg_vec[]) {
   bool identity;
   bool swap_nvst;
   bool larmor_identity;
+  bool initialize_z;
+  bool initialize_x;
   bool testing_mode;
 
   po::options_description simulations("Available simulations",help_text_length);
@@ -66,6 +68,14 @@ int main(const int arg_num, const char *arg_vec[]) {
     ("larmor_identity",
      po::value<bool>(&larmor_identity)->default_value(false)->implicit_value(true),
      "compute expected fidelity of an identity operation on a larmor qubit")
+    ("initialize_z",
+     po::value<bool>(&initialize_z)->default_value(false)->implicit_value(true),
+     "compute expected fidelity of a deterministic initialization of"
+     " a thermalized nucleus into |u> or |d>")
+    ("initialize_x",
+     po::value<bool>(&initialize_x)->default_value(false)->implicit_value(true),
+     "compute expected fidelity of a probabalistic initialization of"
+     " a thermalized nucleus into |u> +/- |d>")
     ("test" ,po::value<bool>(&testing_mode)->default_value(false)->implicit_value(true),
      "enable testing mode")
     ;
@@ -220,6 +230,8 @@ int main(const int arg_num, const char *arg_vec[]) {
           + int(identity)
           + int(swap_nvst)
           + int(larmor_identity)
+          + int(initialize_z)
+          + int(initialize_x)
           != 1) {
         cout << "Please choose one simulation to perform\n";
         return -1;
@@ -694,12 +706,42 @@ int main(const int arg_num, const char *arg_vec[]) {
   }
 
   // -------------------------------------------------------------------------------------
-  // Fidelity of initializing a thermalized nucleus into |d>
+  // Fidelity of deterministically initializing a thermalized nucleus into |u> or |d>
   // -------------------------------------------------------------------------------------
+
+  if (initialize_z) {
+    cout << "target fidelity time pulses\n";
+    for (uint target: target_nuclei) {
+      vector<protocol> P(2);
+      for (bool exact : {true,false}) {
+        P.at(exact) = initialize_spin_Z(nv, target, exact);
+      }
+      const uint subsystem_target = get_index_in_subsystem(nv, target);
+      cout << target << " "
+           << gate_fidelity(P.at(0), P.at(1), {0, subsystem_target}) << " "
+           << P.at(false).time << " "
+           << P.at(false).pulses << endl;
+    }
+  }
 
[…]

### 2016-07-19 simulation.cpp
minor change to help text

@@ -58,23 +58,23 @@ int main(const int arg_num, const char *arg_vec[]) {
     ("couple", po::value<bool>(&coupling)->default_value(false)->implicit_value(true),
      "couple an individual nucleus to NV center")
     ("iswap", po::value<bool>(&iswap)->default_value(false)->implicit_value(true),
-     "compute expected iSWAP fidelities")
+     "compute iSWAP fidelities")
     ("swap", po::value<bool>(&swap)->default_value(false)->implicit_value(true),
-     "compute expected SWAP fidelities")
+     "compute SWAP fidelities")
     ("identity", po::value<bool>(&identity)->default_value(false)->implicit_value(true),
-     "compute expected fidelity of an identity operation on a single spin")
+     "compute fidelity of an identity operation on a single spin")
     ("swap_nvst", po::value<bool>(&swap_nvst)->default_value(false)->implicit_value(true),
-     "compute expected SWAP_NVST fidelity")
+     "compute SWAP_NVST fidelity")
     ("larmor_identity",
      po::value<bool>(&larmor_identity)->default_value(false)->implicit_value(true),
-     "compute expected fidelity of an identity operation on a larmor qubit")
+     "compute fidelity of an identity operation on a larmor qubit")
     ("initialize_z",
      po::value<bool>(&initialize_z)->default_value(false)->implicit_value(true),
-     "compute expected fidelity of a deterministic initialization of"
+     "compute fidelity of a deterministic initialization of"
      " a thermalized nucleus into |u> or |d>")
     ("initialize_x",
      po::value<bool>(&initialize_x)->default_value(false)->implicit_value(true),
-     "compute expected fidelity of a probabalistic initialization of"
+     "compute fidelity of a probabalistic initialization of"
      " a thermalized nucleus into |u> +/- |d>")
     ("test" ,po::value<bool>(&testing_mode)->default_value(false)->implicit_value(true),
      "enable testing mode")

### 2016-07-19 simulation.cpp
changed comments in simulation.cpp

@@ -23,7 +23,7 @@ namespace po = boost::program_options;
 int main(const int arg_num, const char *arg_vec[]) {
 
   // -------------------------------------------------------------------------------------
-  // Parse and process input options
+  // Set input options
   // -------------------------------------------------------------------------------------
 
   const uint help_text_length = 90;
@@ -206,11 +206,17 @@ int main(const int arg_num, const char *arg_vec[]) {
   po::store(parse_command_line(arg_num, arg_vec, all), inputs);
   po::notify(inputs);
 
+
   // if requested, print help text
   if (inputs.count("help")) {
     cout << all;
     return 0;
   }
+
+
+  // -------------------------------------------------------------------------------------
+  // Run a sanity check on inputs
+  // -------------------------------------------------------------------------------------
 
   // determine whether certain options were used
   bool using_input_lattice = inputs.count("lattice_file");
@@ -218,7 +224,7 @@ int main(const int arg_num, const char *arg_vec[]) {
   bool set_c13_factor = !inputs["c13_factor"].defaulted();
   bool set_target_nuclei = inputs.count("target");
 
-  // run a sanity check on inputs
+  // make sure we are either printing something, or performing a simulation
   if (!testing_mode) {
     const bool printing = print_lattice || print_pairs || target_info;
     if (!printing) {

### 2016-07-19 nv-control.cpp
added method to initialize a larmor qubit

@@ -482,3 +482,17 @@ protocol initialize_spin_X(const nv_system& nv, const uint target, const bool ex
           couple_target(nv, target, pi/2, zhat, xhat, exact) *
           rotate_NV(nv, pi/2, yhat, spins));
 }
+
+// operation to probabalistically initialize a larmor pair from |dd> into |ud> +/- |du>
+protocol initialize_larmor_qubit(const nv_system& nv, const uint idx1, const uint idx2,
+                                 const bool exact) {
+  assert(is_larmor_pair(nv,idx1,idx2));
+  const uint cluster = get_cluster_containing_target(nv,idx1);
+  const uint spins = nv.clusters.at(cluster).size()+1;
+  assert(in_vector(idx2,nv.clusters.at(cluster)));
+
+  const bool decouple_spins = false;
+  return (rotate_NV(nv, pi/2, yhat, spins) *
+          couple_target(nv, idx1, pi/2, zhat, yhat, exact, decouple_spins) *
+          rotate_NV(nv, pi/2, yhat, spins));
+}

### 2016-07-19 nv-control.h

@@ -103,3 +103,7 @@ protocol initialize_spin_Z(const nv_system& nv, const uint target,
 // operation to probabalistically initialize a thermalized nucleus into |u> +/- |d>
 protocol initialize_spin_X(const nv_system& nv, const uint target,
                            const bool exact = false);
+
+// operation to probabalistically initialize a larmor pair from |dd> into |S> or |T>
+protocol initialize_larmor_qubit(const nv_system& nv, const uint idx1, const uint idx2,
+                                 const bool exact = false);

### 2016-07-19 simulation.cpp

@@ -47,6 +47,7 @@ int main(const int arg_num, const char *arg_vec[]) {
   bool larmor_identity;
   bool initialize_z;
   bool initialize_x;
+  bool initialize_larmor;
   bool testing_mode;
 
   po::options_description simulations("Available simulations",help_text_length);
@@ -70,12 +71,16 @@ int main(const int arg_num, const char *arg_vec[]) {
      "compute fidelity of an identity operation on a larmor qubit")
     ("initialize_z",
      po::value<bool>(&initialize_z)->default_value(false)->implicit_value(true),
-     "compute fidelity of a deterministic initialization of"
-     " a thermalized nucleus into |u> or |d>")
+     "compute fidelity of a deterministic initialization of a thermalized nucleus"
+     " into |u> or |d>")
     ("initialize_x",
      po::value<bool>(&initialize_x)->default_value(false)->implicit_value(true),
-     "compute fidelity of a probabalistic initialization of"
-     " a thermalized nucleus into |u> +/- |d>")
+     "compute fidelity of a probabalistic initialization of a thermalized nucleus"
+     " into |u> +/- |d>")
+    ("initialize_larmor",
+     po::value<bool>(&initialize_larmor)->default_value(false)->implicit_value(true),
+     "compute fidelity of a probabalistic initialization of a larmor pair"
+     " from |dd> into |ud> +/- |du>")
     ("test" ,po::value<bool>(&testing_mode)->default_value(false)->implicit_value(true),
      "enable testing mode")
     ;
@@ -238,6 +243,7 @@ int main(const int arg_num, const char *arg_vec[]) {
           + int(larmor_identity)
           + int(initialize_z)
           + int(initialize_x)
+          + int(initialize_larmor)
           != 1) {
         cout << "Please choose one simulation to perform\n";
         return -1;
@@ -750,7 +756,25 @@ int main(const int arg_num, const char *arg_vec[]) {
   }
 
   // -------------------------------------------------------------------------------------
-  // Fidelity of probabalistically initializing a |dd> larmor pair into |ud> + |du>
+  // Fidelity of probabalistically initializing a larmor pair from |dd> into |ud> +/- |du>
   // -------------------------------------------------------------------------------------
+
+  if (initialize_larmor) {
+    cout << "idx1 idx2 fidelity time pulses\n";
[…]

### 2016-07-19 fidelity-sweep.py
add copy baseanme module to tmpdir in fidelity-sweep.py

@@ -30,6 +30,7 @@ project_dir = os.path.dirname(os.path.realpath(__file__))
 data_dir = "data"
 sim_file = "simulate.exe"
 summary_script = "fidelity-summary.py"
+basename_module = "basename.py"
 out_file = "{}/{}.txt".format(data_dir,basename(sim_args))
 base_cmd = ["./"+sim_file] + cmd_args
 
@@ -40,8 +41,8 @@ job_dir = os.environ["TMPDIR"] + "/" + os.environ["USER"] + "/" + "".join(sys.ar
 
 # move into job directory
 os.makedirs(job_dir)
-shutil.copy2(project_dir+"/"+sim_file, job_dir+"/"+sim_file)
-shutil.copy2(project_dir+"/"+summary_script, job_dir+"/"+summary_script)
+for fname in [ sim_file, summary_script, basename_module ]:
+    shutil.copy2(project_dir+"/"+fname, job_dir+"/"+fname)
 os.chdir(job_dir)
 os.mkdir(data_dir)
 

### 2016-07-19 nv-control.cpp
renamed some methods

@@ -465,7 +465,7 @@ protocol target_identity(const nv_system& nv, const uint target, const double ti
 }
 
 // operation to deterministically initialize a thermalized nucleus into |u> or |d>
-protocol initialize_spin_Z(const nv_system& nv, const uint target, const bool exact) {
+protocol initialize_spin(const nv_system& nv, const uint target, const bool exact) {
   const uint cluster = get_cluster_containing_target(nv,target);
   const uint spins = nv.clusters.at(cluster).size()+1;
   return (couple_target(nv, target, pi/2, zhat, yhat, exact) *

### 2016-07-19 nv-control.h

@@ -97,8 +97,8 @@ protocol target_identity(const nv_system& nv, const uint target, const double ti
                          const bool exact = false);
 
 // operation to deterministically initialize a thermalized nucleus into |u> or |d>
-protocol initialize_spin_Z(const nv_system& nv, const uint target,
-                           const bool exact = false);
+protocol initialize_spin(const nv_system& nv, const uint target,
+                         const bool exact = false);
 
 // operation to probabalistically initialize a thermalized nucleus into |u> +/- |d>
 protocol initialize_spin_X(const nv_system& nv, const uint target,

### 2016-07-19 simulation.cpp

@@ -45,7 +45,7 @@ int main(const int arg_num, const char *arg_vec[]) {
   bool identity;
   bool swap_nvst;
   bool larmor_identity;
-  bool initialize_z;
+  bool initialize;
   bool initialize_x;
   bool initialize_larmor;
   bool testing_mode;
@@ -69,8 +69,8 @@ int main(const int arg_num, const char *arg_vec[]) {
     ("larmor_identity",
      po::value<bool>(&larmor_identity)->default_value(false)->implicit_value(true),
      "compute fidelity of an identity operation on a larmor qubit")
-    ("initialize_z",
-     po::value<bool>(&initialize_z)->default_value(false)->implicit_value(true),
+    ("initialize",
+     po::value<bool>(&initialize)->default_value(false)->implicit_value(true),
      "compute fidelity of a deterministic initialization of a thermalized nucleus"
      " into |u> or |d>")
     ("initialize_x",
@@ -241,7 +241,7 @@ int main(const int arg_num, const char *arg_vec[]) {
           + int(identity)
           + int(swap_nvst)
           + int(larmor_identity)
-          + int(initialize_z)
+          + int(initialize)
           + int(initialize_x)
           + int(initialize_larmor)
           != 1) {
@@ -721,12 +721,12 @@ int main(const int arg_num, const char *arg_vec[]) {
   // Fidelity of deterministically initializing a thermalized nucleus into |u> or |d>
   // -------------------------------------------------------------------------------------
 
-  if (initialize_z) {
+  if (initialize) {
     cout << "target fidelity time pulses\n";
     for (uint target: target_nuclei) {
       vector<protocol> P(2);
       for (bool exact : {true,false}) {
-        P.at(exact) = initialize_spin_Z(nv, target, exact);
+        P.at(exact) = initialize_spin(nv, target, exact);
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "

### 2016-07-19 nv-control.cpp
changed argument format for gate_fidelity methods, and fixed minor bug in target_fidelity; note: target_identity still gives the wrong answer

@@ -455,11 +455,10 @@ protocol SWAP_NVST(const nv_system& nv, const uint idx1, const uint idx2,
 protocol target_identity(const nv_system& nv, const uint target, const double time,
                          const bool exact) {
   const uint cluster = get_cluster_containing_target(nv,target);
-  const uint cluster_spins = nv.clusters.at(cluster).size();
 
-  if (exact) return protocol::Identity(pow(2,cluster_spins));
+  MatrixXcd H = H_nZ(nv, cluster, nv.static_gBz*zhat);
+  if (!exact && !nv.no_nn) H += H_nn(nv, cluster);
 
-  const MatrixXcd H = H_nn(nv, cluster) + H_nZ(nv, cluster, nv.static_gBz*zhat);
   const MatrixXcd U = exp(-j*time*H);
   return protocol(U, time);
 }

### 2016-07-19 nv-math.h

@@ -356,12 +356,9 @@ struct protocol {
 inline protocol pow(const protocol& U, const uint n) { return U.pow(n); }
 inline protocol pow(const protocol& U, const long unsigned int n) { return U.pow(n); }
 
-inline double gate_fidelity(const protocol& U, const protocol& G) {
-  return gate_fidelity(U.U, G.U);
-}
-inline double gate_fidelity(const protocol& U, const protocol& G,
-                            const vector<uint>& nuclei) {
-  return gate_fidelity(U.U, G.U, nuclei);
+inline double gate_fidelity(const vector<protocol>& P, const vector<uint> nuclei = {}) {
+  assert(P.size() == 2);
+  return gate_fidelity(P.at(0).U, P.at(1).U, nuclei);
 }
 
 // ---------------------------------------------------------------------------------------

### 2016-07-19 qp-math.cpp

@@ -198,15 +198,7 @@ VectorXcd U_decompose(const MatrixXcd& U, const bool fast) {
   else return U_basis_matrix(N).fullPivHouseholderQr().solve(flatten(U));
 }
 
-// compute mean fidelity of gate U with respect to G, i.e. how well U approximates G
-double gate_fidelity(const MatrixXcd&  U, const MatrixXcd& G) {
-  assert(U.size() == G.size());
-  const uint D = U.rows();
-  const MatrixXcd M = G.adjoint() * U;
-  return real( trace(M.adjoint()*M) + trace(M)*conj(trace(M)) ) / (D*(D+1));
-}
-
-// compute mean fidelity of propagator acting on given qbits
+// compute mean fidelity of gate U with respect to G within a given subsystem
 double gate_fidelity(const MatrixXcd& U, const MatrixXcd& G,
                      const vector<uint>& system_qbits) {
   assert(U.size() == G.size());
@@ -219,8 +211,9 @@ double gate_fidelity(const MatrixXcd& U, const MatrixXcd& G,
     }
   }
 
+  const uint D = pow(2,system_qbits.size());
   const MatrixXcd M = ptrace(G * U.adjoint(), environment_qbits);
-  return gate_fidelity(M, MatrixXcd::Identity(M.rows(),M.cols()));
+  return real( trace(M.adjoint()*M) + trace(M)*conj(trace(M)) ) / (D*(D+1));
 }
 
 // ---------------------------------------------------------------------------------------

### 2016-07-19 qp-math.h

@@ -116,12 +116,9 @@ MatrixXcd U_basis_matrix(const uint N);
 // decompose Hamiltonian into its basis elements
 VectorXcd U_decompose(const MatrixXcd& U, const bool fast = false);
 
-// compute mean fidelity of gate U with respect to G, i.e. how well U approximates G
-double gate_fidelity(const MatrixXcd&  U, const MatrixXcd& G);
-
-// compute mean fidelity of propagator acting on given qbits
+// compute mean fidelity of gate U with respect to G within a given subsystem
 double gate_fidelity(const MatrixXcd& U, const MatrixXcd& G,
-                     const vector<uint>& system_qbits);
+                     const vector<uint>& system_qbits = {});
 
 // compute fidelity of state rho with respect to state sigma
 inline double state_fidelity(const MatrixXcd& rho, const MatrixXcd& sigma) {

### 2016-07-19 simulation.cpp

@@ -583,7 +583,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P.at(0), P.at(1), {0, subsystem_target}) << " "
+           << gate_fidelity(P, {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -604,7 +604,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P.at(0), P.at(1), {0, subsystem_target}) << " "
+           << gate_fidelity(P, {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -623,7 +623,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P.at(0), P.at(1), {0, subsystem_target}) << " "
+           << gate_fidelity(P, {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -642,7 +642,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P.at(0), P.at(1), {0, subsystem_target}) << " "
+           << gate_fidelity(P, {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -659,9 +659,9 @@ int main(const int arg_num, const char *arg_vec[]) {
       for (bool exact : {true,false}) {
         P.at(exact) = target_identity(nv, target, identity_time, exact);
       }
-      const uint subsystem_target = get_index_in_subsystem(nv, target);
+      const uint cluster_target = get_index_in_cluster(nv, target);
       cout << target << " "
-           << gate_fidelity(P.at(0), P.at(1), {subsystem_target}) << endl;
[…]

### 2016-07-19 swap-nvst-paper/paper.tex
changed revtex4 to revtex4-1
minor changes + new text under DFS qubit initialization section

@@
-\documentclass[twocolumn]{revtex4}
+\documentclass[twocolumn]{revtex4-1}
 
@@
 
-\title{Realization of a Decoherence-Free Subspaces with
+\title{Qubit Storage in a Decoherence-Free Subspace with
   Nitrogen-Vacancy Centers and $^{13}$C Nuclear Spins}
@@
 metrology and information processing applications
-\cite{mamin2013nanoscale, steinert2010high, wang2015positioning,
+\cite{mamin2013nanoscale, steinert2010high, wang2016positioning,
   chou2015optimal, childress2006fault, yao2012scalable}. \fixme{the
@@
 In this letter, we present a means to address individual $^{13}$C
-nuclear spins which are normally indistinguishable due to symmetric
-coupling to the NV center. We use this addressing scheme to initialize
-qubits in a decoherence-free subspace (DFS) of nuclear spins, and
-propose a means for realizing a coherent SWAP operation between the NV
-center electron spin state and the DFS qubit.
+nuclear spins which are normally indistinguishable due to their
+symmetric coupling to the NV center. We use this addressing scheme to
+initialize qubits in a decoherence-free subspace (DFS) of nuclear
+spins, and propose a means for realizing a coherent SWAP operation
+between the NV center electron spin state and the DFS qubit.
 
@@
 developed in by Casanova et al. in \cite{casanova2015robust} and
-control scheme developed by Wang et al. in \cite{wang2015positioning}
+control scheme developed by Wang et al. in \cite{wang2016positioning}
 allows addressing individual $^{13}$C nuclear spins via Hamiltonians
@@
 $A_1=A_2$. The state space of two such spins, which we call {\it
-  larmor pairs}, contains a decoherence-free subspace (DFS) with
-respect to spin-spin coupling to the NV center. This DFS is spanned by
-the singlet-triplet states $\p{\ket{\u\d}\pm\ket{\d\u}}/\sqrt2$, or
-equivalently by $\set{\ket{\u\d},\ket{\d\u}}$.
+  larmor pairs}, contains a subspace free of decoherence via spin
+coupling to the NV center electron, i.e. a decoherence-free subspace
+(DFS). This DFS is spanned by the singlet-triplet states
+$\p{\ket{\u\d}\pm\ket{\d\u}}/\sqrt2$, or equivalently by
+$\set{\ket{\u\d},\ket{\d\u}}$. \fixme{show that this subspace is
+  decoherence-free (in the supplementary material)}
 
@@
 components of $\uv n_j$ which are perpendicular to the vector
-$\v B_\t{dec}$ projected onto the plane perpendicular to precession
-axis $\v\omega_j$ and rotated about this axis by $\phi_\t{dec}$. One
-can therefore choose a direction $\v B_\t{dec}$ which completely
-suppresses NV electron spin coupling to spin 1 (2), leaving only
-coupling to spin 2 (1).
-
-\fixme{Comment on how likely are we to find larmor pairs?}
+$\v B_\t{dec}$ projected onto the plane perpendicular to $\v\omega_j$
+and rotated in this plane by $\phi_\t{dec}$. One can therefore choose
+a direction $\v B_\t{dec}$ which completely suppresses NV electron
+spin coupling to spin 1 (2), leaving only coupling to spin 2 (1).
 
 \section{Qubit initialization in a decoherence-free subspace}
+
+The protocols for addressing an individual nucleus in a larmor pair
+can be used to initialize a qubit in the DFS of a larmor pair. In
+particular, one can use the gate sequences in
+\cite{reiserer2016robust} to deterministically initialize the larmor
+pair into $\ket{\d\d}$, then probabilistically convert this state into
+$\p{\ket{\u\d}+e^{i\phi}\ket{\d\u}}/\sqrt2$ for some phase $\phi$
+determined by the choice of bases for the nuclear spins. While the
+sequences to initialize into $\ket{\d\d}$ require individually
+addressing each nuclear spin, the conversion
+$\ket{\d\d}\to\p{\ket{\u\d}+e^{i\phi}\ket{\d\u}}/\sqrt2$ can be
+performed with simultaneous coupling to both larmor pairs,
+i.e. without the magnetic decoupling field.
 
@@
 \widetext
+\makeatletter
 \begin{center}
-  \textbf{\large Supplementary Information for ``Delayed entanglement
-    echo for individual control of a large number of nuclear spins''}
+  \large \bf Supplementary Information for ``\@title''
 \end{center}
-\setcounter{equation}{0} \setcounter{figure}{0} \setcounter{table}{0}
-\setcounter{page}{1} \makeatletter
+\setcounter{equation}{0}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\setcounter{page}{1}
 \renewcommand{\theequation}{S\arabic{equation}}
@@
 simulations can, without any modification, reproduce results such as
-Figure 2 in \cite{wang2015positioning} (``Positioning Nuclear Spins in
+Figure 2 in \cite{wang2016positioning} (``Positioning Nuclear Spins in
 Interacting Clusters for Quantum Technologies and

### 2016-07-19 qp-math.cpp
some renaming; fixed error in gate_fidelity method

@@ -200,19 +200,21 @@ VectorXcd U_decompose(const MatrixXcd& U, const bool fast) {
 
 // compute mean fidelity of gate U with respect to G within a given subsystem
 double gate_fidelity(const MatrixXcd& U, const MatrixXcd& G,
-                     const vector<uint>& system_qbits) {
+                     const vector<uint>& system) {
   assert(U.size() == G.size());
 
   const uint spins = log2(G.rows());
-  vector<uint> environment_qbits = {};
-  for (uint n = 0; n < spins; n++) {
-    if (!in_vector(n,system_qbits)) {
-      environment_qbits.push_back(n);
+  vector<uint> environment = {};
+  if (system.size() > 0) {
+    for (uint n = 0; n < spins; n++) {
+      if (!in_vector(n,system)) {
+        environment.push_back(n);
+      }
     }
   }
 
-  const uint D = pow(2,system_qbits.size());
-  const MatrixXcd M = ptrace(G * U.adjoint(), environment_qbits);
+  const uint D = pow(2,system.size());
+  const MatrixXcd M = ptrace(G * U.adjoint(), environment);
   return real( trace(M.adjoint()*M) + trace(M)*conj(trace(M)) ) / (D*(D+1));
 }
 

### 2016-07-19 qp-math.h

@@ -118,7 +118,7 @@ VectorXcd U_decompose(const MatrixXcd& U, const bool fast = false);
 
 // compute mean fidelity of gate U with respect to G within a given subsystem
 double gate_fidelity(const MatrixXcd& U, const MatrixXcd& G,
-                     const vector<uint>& system_qbits = {});
+                     const vector<uint>& system = {});
 
 // compute fidelity of state rho with respect to state sigma
 inline double state_fidelity(const MatrixXcd& rho, const MatrixXcd& sigma) {

### 2016-07-19 simulation.cpp

@@ -703,12 +703,12 @@ int main(const int arg_num, const char *arg_vec[]) {
 
       const uint cluster = get_cluster_containing_target(nv,idx1);
       const uint cluster_size = nv.clusters.at(cluster).size();
-      vector<uint> environment_qbits = {}; // in cluster system
+      vector<uint> environment = {}; // in cluster system
       for(uint i = 0; i < cluster_size; i++) {
-        if (i != idx1 && i != idx2) environment_qbits.push_back(i);
+        if (i != idx1 && i != idx2) environment.push_back(i);
       }
       const Matrix2cd larmor_operation =
-        ptrace(gates::SWAP_NVST * tp(I2, ptrace(P.at(false).U,environment_qbits)), {1,2});
+        ptrace(gates::SWAP_NVST * tp(I2, ptrace(P.at(false).U,environment)), {1,2});
 
       cout << idx1 << " " << idx2 << " " << gate_fidelity(larmor_operation, I2) << endl;
     }

### 2016-07-19 qp-math.cpp
fixed potential bug with gate_fidelity when no subsystem is specified

@@ -213,8 +213,8 @@ double gate_fidelity(const MatrixXcd& U, const MatrixXcd& G,
     }
   }
 
-  const uint D = pow(2,system.size());
   const MatrixXcd M = ptrace(G * U.adjoint(), environment);
+  const uint D = M.rows();
   return real( trace(M.adjoint()*M) + trace(M)*conj(trace(M)) ) / (D*(D+1));
 }
 

### 2016-07-19 nv-math.h
renamed gate_fidelity to protocol_fidelity when it accepts protocols

@@ -356,9 +356,10 @@ struct protocol {
 inline protocol pow(const protocol& U, const uint n) { return U.pow(n); }
 inline protocol pow(const protocol& U, const long unsigned int n) { return U.pow(n); }
 
-inline double gate_fidelity(const vector<protocol>& P, const vector<uint> nuclei = {}) {
+inline double protocol_fidelity(const vector<protocol>& P,
+                                const vector<uint> nuclei = {}) {
   assert(P.size() == 2);
-  return gate_fidelity(P.at(0).U, P.at(1).U, nuclei);
+  return gate_fidelity(P.at(false).U, P.at(true).U, nuclei);
 }
 
 // ---------------------------------------------------------------------------------------

### 2016-07-19 simulation.cpp

@@ -583,7 +583,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P, {0, subsystem_target}) << " "
+           << protocol_fidelity(P, {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -604,7 +604,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P, {0, subsystem_target}) << " "
+           << protocol_fidelity(P, {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -623,7 +623,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P, {0, subsystem_target}) << " "
+           << protocol_fidelity(P, {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -642,7 +642,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << gate_fidelity(P, {0, subsystem_target}) << " "
+           << protocol_fidelity(P, {0, subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }
@@ -661,7 +661,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint cluster_target = get_index_in_cluster(nv, target);
       cout << target << " "
-           << gate_fidelity(P, {cluster_target}) << endl;
+           << protocol_fidelity(P, {cluster_target}) << endl;
     }
   }
 
@@ -681,7 +681,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       const uint ss_idx1 = get_index_in_subsystem(nv,idx1);
       const uint ss_idx2 = get_index_in_subsystem(nv,idx2);
       cout << idx1 << " " << idx2 << " "
[…]

### 2016-07-20 simulation.cpp
minor change to subsystem definition in rotation fidelity

@@ -583,7 +583,7 @@ int main(const int arg_num, const char *arg_vec[]) {
       }
       const uint subsystem_target = get_index_in_subsystem(nv, target);
       cout << target << " "
-           << protocol_fidelity(P, {0, subsystem_target}) << " "
+           << protocol_fidelity(P, {subsystem_target}) << " "
            << P.at(false).time << " "
            << P.at(false).pulses << endl;
     }

### 2016-07-20 swap-nvst-paper/paper.tex
slight reorganization of paper

@@
 
+\fixme{Write about NV centers, C-13 nuclei, introduction to larmor
+  pairs and DFS, quantum memory/networks, etc.}
+
 Nitrogen-vacancy (NV) centers in diamond have been recognized in
@@
 
-\section{Addressing symmetric $^{13}$C nuclear spins}
+\section{Identifying symmetrically coupled $^{13}$C nuclear spins}
+
+\fixme{How do we identify and locate larmor pairs?}
+
+\section{Individually addressing larmor pairs}
+
+\fixme{How do we individually address larmor pairs?}
 
@@
 
+\fixme{Implement PRX\cite{reiserer2016robust} methods for initializing
+  a qubit in $\ket{\u\d}\pm\ket{\d\u}$}
+
 The protocols for addressing an individual nucleus in a larmor pair
@@
 i.e. without the magnetic decoupling field.
+
+\section{Coherent SWAP operation with DFS qubit}
 

### 2016-08-20 swap-nvst-paper/paper.tex
added material to paper, and did some reorganization

@@
 
-\title{Qubit Storage in a Decoherence-Free Subspace with
+\title{Realization of a Decoherence-Free Subspace with
   Nitrogen-Vacancy Centers and $^{13}$C Nuclear Spins}
 
-\author{Michael A. Perlin, Zhen-Yu Wang, and Martin B. Plenio}
+\author{Michael A. Perlin, Zhen-Yu Wang, Jorge Casanova, and Martin B. Plenio}
 
@@
 Nitrogen-vacancy (NV) centers in diamond have been recognized in
-recent years as a promising platform for quantum sensing and
-information technologies. The electronic ground and optically excited
-states of NV$^-$ split into spin triplets which can be polarized,
-detected, and coherently manipulated with high fidelity with fields
-and microwave radiation \cite{dobrovitski2013quantum}. Hyperfine
-coupling between the NV center electron and $^{13}$C nuclei in bulk
-diamond allows for the coherent control and measurement of individual
-nuclear spins, and the realization of universal set of high-fidelity
-quantum gates \cite{dobrovitski2013quantum, casanova2016noise}. These
-properties have prompted extensive studies of NV centers for quantum
-metrology and information processing applications
-\cite{mamin2013nanoscale, steinert2010high, wang2016positioning,
-  chou2015optimal, childress2006fault, yao2012scalable}. \fixme{the
-  first and last sentences of this paragraph are essentially the same}
+recent years as a promising platform for quantum sensing and quantum
+information technologies\cite{mamin2013nanoscale, steinert2010high,
+  wang2016positioning, chou2015optimal, childress2006fault,
+  yao2012scalable}. The electronic ground and optically excited states
+of NV$^-$ split into spin triplets which can be polarized, detected,
+and coherently manipulated with high fidelity with fields and
+microwave radiation \cite{dobrovitski2013quantum}. Hyperfine coupling
+between the NV center electron and $^{13}$C nuclei in bulk diamond
+allows for the coherent control and measurement of individual nuclear
+spins, and the realization of universal set of high-fidelity quantum
+gates \cite{dobrovitski2013quantum, casanova2016noise}.
 
-One such application of the NV center is as a memory register to store
-quantum information. While typical control operations on the NV
-electron spin happen on the scale of nanoseconds, its room-temperature
-coherence time is on the scale of microseconds
+One promising application of the NV center is as a memory register for
+storing quantum information. While typical control operations on the
+NV electron spin happen on the scale of nanoseconds, its
+room-temperature coherence time is on the scale of microseconds
 \cite{dobrovitski2013quantum}. Dynamic decoupling schemes and the use
@@
 In this letter, we present a means to address individual $^{13}$C
-nuclear spins which are normally indistinguishable due to their
-symmetric coupling to the NV center. We use this addressing scheme to
+nuclear spins which are normally indistinguishable due to a symmetry
+in their coupling to the NV center. We use this addressing scheme to
 initialize qubits in a decoherence-free subspace (DFS) of nuclear
@@
 \section{Identifying symmetrically coupled $^{13}$C nuclear spins}
-
-\fixme{How do we identify and locate larmor pairs?}
-
-\section{Individually addressing larmor pairs}
-
-\fixme{How do we individually address larmor pairs?}
 
@@
 effective Hamiltonian, however, is conditional on a sufficiently
-unique larmor frequency $\omega_j$, i.e. that for all $n\ne j$
+unique effective larmor frequency $\omega_j$, i.e. that for all
+$n\ne j$
 \begin{align}
@@
 where $f_{k_{DD}}$ is the fourier component of the AXY-$n$ protocol on
-resonance with $\omega_j$ and $\v A_j^\perp$ is the component of the
-hyperfine vector $\v A_j$ perpendicular to the effective larmor
-precession axis $\v\omega_j$.
+resonance with $\omega_j$ and $\v A_j^\perp$ ($\v A_j^\parallel$) is
+the component of the hyperfine vector $\v A_j$ perpendicular
+(parallel) to the effective larmor precession axis $\uv\omega_j$.
 
@@
 have identical larmor frequencies $\omega_1=\omega_2\equiv\omega$,
-which occurs when they couple symmetrically to the NV center with
-$A_1=A_2$. The state space of two such spins, which we call {\it
-  larmor pairs}, contains a subspace free of decoherence via spin
-coupling to the NV center electron, i.e. a decoherence-free subspace
-(DFS). This DFS is spanned by the singlet-triplet states
-$\p{\ket{\u\d}\pm\ket{\d\u}}/\sqrt2$, or equivalently by
-$\set{\ket{\u\d},\ket{\d\u}}$. \fixme{show that this subspace is
-  decoherence-free (in the supplementary material)}
+which occurs when both nuclei lie along the edges of a cylinder
+centered on the NV center and oriented along the natural NV axis. We
+call such nuclei {\it larmor pairs}, and their geometry results in
+$A_1^\perp=A_2^\perp\equiv A^\perp$ and
+$A_1^\parallel=A_2^\parallel\equiv A^\parallel$ (see Supplementary
+Information) \fixme{prove in the SI}.
+
+\fixme{Reference \cite{wang2016positioning} for identifying and
+  location nuclei with unique larmor frequencies}
+
+\fixme{Provide derivation for NV coherence when on resonance with the
+  larmor frequency of a larmor pair}
+
+\fixme{Provide derivation for NV coherence when on resonance with a
+  larmor frequency when applying a control field for both the one- and
+  two-nucleus case}
+
+\fixme{Walk through protocol to identify and locate larmor pairs}
+
+\section{Individually addressing nuclei in larmor pairs}
 
@@
 $\v B_\t{dec}$ projected onto the plane perpendicular to $\v\omega_j$
-and rotated in this plane by $\phi_\t{dec}$. One can therefore choose
-a direction $\v B_\t{dec}$ which completely suppresses NV electron
-spin coupling to spin 1 (2), leaving only coupling to spin 2 (1).
+and rotated about the axis $\uv\omega_j$ by the angle
+$\phi_\t{dec}$. One can therefore choose a direction $\v B_\t{dec}$
+which completely suppresses NV electron spin coupling to spin 1 (2),
+leaving only coupling to spin 2 (1).
+
+\fixme{Give more information or details about this protocol? Reference
+  SI}
 
@@
 
-The protocols for addressing an individual nucleus in a larmor pair
-can be used to initialize a qubit in the DFS of a larmor pair. In
-particular, one can use the gate sequences in
+The state space of larmor pairs contains a subspace free of
+decoherence via spin coupling to the NV center electron, i.e. a
+decoherence-free subspace (DFS). This DFS is spanned by the
+singlet-triplet states $\p{\ket{\u\d}\pm\ket{\d\u}}/\sqrt2$, or
+equivalently by $\ket{\u\d}$ and $\ket{\d\u}$. \fixme{prove that this
+  subspace is decoherence-free in the SI} The protocols for addressing
+an individual nucleus in a larmor pair can be used to initialize a
+qubit in this DFS. In particular, one can use the gate sequences in
 \cite{reiserer2016robust} to deterministically initialize the larmor
@@
 \end{document}
+
+notes:
+
+prove DFS
+
+how to locate spins?
+- identify larmor frequencies for C-13 nuclei
+- identify a frequency with two spins
+- locate two spins
+
+perform elementary gate on one spin
+implement PRX gates

### 2016-08-30 plot-coherence-signal.py
fixes to plot-coherence-signal.py script

@@ -23,11 +23,11 @@ def nums_in(line):
     return n
 
 def figname(targets):
-    return fname.replace(".txt","-{}.pdf".format("-".join(targets)))
+    return fname.replace(".txt","-{}.png".format("-".join(targets)))
 
 def line_plot(targets,k_DD,f_DD,coherence):
 
-    plot = plt.plot(f_DD,coherence,'k-',linewidth=2)
+    plot = plt.plot(f_DD,coherence,"k-",linewidth=2)
 
     plt.xlim(0,f_DD[-1])
     plt.ylim(-1,1)
@@ -49,10 +49,10 @@ def color_plot(targets,k_DD,f_DD,coherence,azimuths):
     plt.pcolor(angles_over_pi,f_DD_boundaries,coherence)
     if show_azimuths:
         for azimuth in azimuths:
-            pi_phi = azimuth
+            pi_phi = 1 - azimuth
             while pi_phi < 0: pi_phi +=1
-            while pi_phi >= 1: ip_phi -= 1
-            plt.axvline(pi_phi,color='k')
+            while pi_phi >= 1: pi_phi -= 1
+            plt.axvline(pi_phi,color="k",linewidth=2)
 
     plt.xlim(0,1)
     plt.ylim(0,f_DD_boundaries[-1])
@@ -74,6 +74,8 @@ def make_plot(targets,k_DD,f_DD,coherence,azimuths):
     coherence = np.array(coherence)
 
     if coherence.shape[0] == 0: return None
+
+    plt.figure()
     if coherence.shape[1] == 1:
         line_plot(targets,k_DD,f_DD,coherence)
     else:

### 2016-09-22 plot-coherence-signal.py
add change output filename when running plot-coherence-signals.py with azimuths option

@@ -23,7 +23,9 @@ def nums_in(line):
     return n
 
 def figname(targets):
-    return fname.replace(".txt","-{}.png".format("-".join(targets)))
+    suffix = "-{}".format("-".join(targets))
+    if show_azimuths: suffix += "-azimuths"
+    return fname.replace(".txt",suffix+".png")
 
 def line_plot(targets,k_DD,f_DD,coherence):
 
@@ -40,6 +42,11 @@ def line_plot(targets,k_DD,f_DD,coherence):
 
     if show: plt.show()
 
+def mod(x,m=1):
+    while x < 0: x += m
+    while x >= m: x -= m
+    return x
+
 def color_plot(targets,k_DD,f_DD,coherence,azimuths):
 
     f_DD_boundaries = ( f_DD - (f_DD[1]-f_DD[0])/2 )
@@ -49,9 +56,7 @@ def color_plot(targets,k_DD,f_DD,coherence,azimuths):
     plt.pcolor(angles_over_pi,f_DD_boundaries,coherence)
     if show_azimuths:
         for azimuth in azimuths:
-            pi_phi = 1 - azimuth
-            while pi_phi < 0: pi_phi +=1
-            while pi_phi >= 1: pi_phi -= 1
+            pi_phi = mod(1 - azimuth)
             plt.axvline(pi_phi,color="k",linewidth=2)
 
     plt.xlim(0,1)

### 2016-09-22 swap-nvst-paper/paper.tex
removed obsolete fixme from paper
added more content to paper pertaining to identifying and locating larmor pairs

@@
 \newcommand{\R}{\mathcal R}
+\newcommand{\A}{\mathcal A}
+\newcommand{\B}{\mathcal B}
 
@@
 
-\author{Michael A. Perlin, Zhen-Yu Wang, Jorge Casanova, and Martin B. Plenio}
+\author{Michael A. Perlin, Zhen-Yu Wang, Jorge Casanova, and Martin
+  B. Plenio}
 
@@
 
-Restricting the NV electron spin states to the subspace spanned by
+Restricting the NV electron spin states to the span of
 $\set{\ket0,\ket{m_s}}$ ($m_s=\pm1$), the AXY-$n$ pulse sequence
@@
 \begin{align}
-  H_\t{int} = h_j^\t{int}\sigma_\NV^z\v I_j\c\uv n_j,
-  \label{H_int}
+  H_{\t{int}} = h_j^{\t{int}}\sigma_\NV^z\v I_j\c\uv n_j,
+  \label{eq:H_int}
 \end{align}
-for a tunable coupling strength $h_\t{int}$ and direction $\uv n_j$,
-where $\sigma_\NV^z\equiv\op{m_s}-\op{0}$ and $\v I_j$ is the spin
-operator for nuclear spin $j$. The protocol for realizing this
-effective Hamiltonian, however, is conditional on a sufficiently
-unique effective larmor frequency $\omega_j$, i.e. that for all
-$n\ne j$
+for a tunable coupling strength $h_j^{\t{int}}$ and direction
+$\uv n_j$, where $\sigma_\NV^z\equiv\op{m_s}-\op{0}$ and $\v I_j$ is
+the spin operator for nuclear spin $j$. The protocol for realizing
+this effective Hamiltonian is conditional on a sufficiently unique
+effective larmor frequency $\omega_j$, i.e. that for all $n\ne j$
 \begin{align}
@@
 centered on the NV center and oriented along the natural NV axis. We
-call such nuclei {\it larmor pairs}, and their geometry results in
+call such nuclei {\it larmor pairs}, and their geometry implies
 $A_1^\perp=A_2^\perp\equiv A^\perp$ and
 $A_1^\parallel=A_2^\parallel\equiv A^\parallel$ (see Supplementary
-Information) \fixme{prove in the SI}.
+Information) \fixme{prove in the SI}. We wish to identify larmor
+pairs and individually address the nuclei making up the pair.
 
-\fixme{Reference \cite{wang2016positioning} for identifying and
-  location nuclei with unique larmor frequencies}
+The AXY-$n$ sequence and the Hamiltonian in Eq. (\ref{eq:H_int})
+allows for measurement of distinct frequencies $\omega_j$, hyperfine
+couplings $A_j^\perp$, and ultimately the positions of $^{13}$C nuclei
+via a coupling protocol ending in an NV coherence measurement,
+outlined in \cite{wang2016positioning}. When on resonance with several
+frequencies $\set{\omega_j}$ which the protocol cannot resolve, the NV
+coherence after a time $t$ reads
+\begin{align}
+  \label{eq:L}
+  L\p{t} = \prod_j\cos\p{\f14 f_{k_{DD}}A_j^\perp t}.
+\end{align}
+After selecting an effective larmor frequency $\omega$ of interest via
+the scanning protocol in \cite{wang2016positioning}, coherence
+measurements as per Eq. (\ref{eq:L}) for different fourier components
+$f_{k_{DD}}$ (or times $t$) are sufficient to determine the number of
+nuclei with effective larmor frequency $\omega$. The protocol for
+measuring $L$ can thus be used to identify a larmor pair.
 
-\fixme{Provide derivation for NV coherence when on resonance with the
-  larmor frequency of a larmor pair}
+After identifying a larmor pair, in order to locate the individual
+nuclei in the pair we introduce an auxiliary magnetic decoupling field
+$\tilde{\v B}_{\t{dec}}\p{t} = \v
+B_{\t{dec}}\cos\p{\omega_{\t{dec}}t-\phi_{\t{dec}}}$. When
+$\omega_{\t{dec}}$ is on resonance with the effective larmor frequency
+$\omega$, the coherence in Eq. (\ref{eq:L}) is modified as
+\begin{align}
+  \label{eq:L_dec}
+  \tilde L\p{t}
+  = \prod_j\cos\p{\f14 f_{k_{DD}}A_j^\perp t\cos\eta_j},
+\end{align}
+where the angle $\eta_j$ is determined by the directions
+$\uv A_j^\perp$ and $\uv B_{\t{dec}}$, as well as the phases
+$\phi_{DD}$ and $\phi_{\t{dec}}$ (see Supplementary Info
+\ref{sec:addressing_pairs}). Measurements of the coherence $\tilde L$
+as a function of fourier components $f_{k_{DD}}$ (or times $t$) and
+phases $\phi_{DD}$ thus provides information about the directions
+$\uv A_j^\perp$.
 
-\fixme{Provide derivation for NV coherence when on resonance with a
-  larmor frequency when applying a control field for both the one- and
-  two-nucleus case}
-
-\fixme{Walk through protocol to identify and locate larmor pairs}
+\fixme{How do we locate larmor pairs using Eq. (\ref{eq:L_dec})?}
 
@@
 When trying to address one spin in a larmor pair, the protocols for
-(\ref{H_int}) will simultaneously couple $\sigma_\NV^z$ to both
+Eq. (\ref{eq:H_int}) will simultaneously couple $\sigma_\NV^z$ to both
 $\v I_1\c\uv n_1$ and $\v I_2\c\uv n_2$ with identical coupling
-strength ($h_\t{int}$). So long as $\uv n_1$ and $\uv n_2$
+strength ($h_j^{\t{int}}$). So long as $\uv n_1$ and $\uv n_2$
 (equivalently, $\v A_1^\perp$ and $\v A_2^\perp$) are not parallel,
@@
 of a magnetic decoupling field
-$\v B_\t{dec}^{\p\omega}\p{t}=\v B_\t{dec}\cos\p{\omega
-  t-\phi_\t{dec}}$ during the AXY-$n$ addressing protocol suppresses
+$\tilde{\v B}_{\t{dec}}\p{t}=\v B_{\t{dec}}\cos\p{\omega
+  t-\phi_{\t{dec}}}$ during the AXY-$n$ addressing protocol suppresses
 components of $\uv n_j$ which are perpendicular to the vector
-$\v B_\t{dec}$ projected onto the plane perpendicular to $\v\omega_j$
-and rotated about the axis $\uv\omega_j$ by the angle
-$\phi_\t{dec}$. One can therefore choose a direction $\v B_\t{dec}$
-which completely suppresses NV electron spin coupling to spin 1 (2),
-leaving only coupling to spin 2 (1).
+$\v B_{\t{dec}}$ projected onto the plane perpendicular to
+$\v\omega_j$ and rotated about the axis $\uv\omega_j$ by the angle
+$\phi_{\t{dec}}$. One can therefore choose a direction
+$\v B_{\t{dec}}$ which completely suppresses NV electron spin coupling
+to spin 1 (2), leaving only coupling to spin 2 (1).
 
@@
 \section{Qubit initialization in a decoherence-free subspace}
-
-\fixme{Implement PRX\cite{reiserer2016robust} methods for initializing
-  a qubit in $\ket{\u\d}\pm\ket{\d\u}$}
 
@@
 
+\fixme{Provide result for initialization fidelities.}
+
 \section{Coherent SWAP operation with DFS qubit}
+
+The protocols developed for addressing larmor pairs can be used to
+perform a coherent SWAP operation between the NV center spin and the
+DFS qubit. In principle, such a coherent SWAP allows using larmor
+pairs as quantum memory registers.
+
+\fixme{Expand.}
 
@@
 \clearpage
-\widetext
-\makeatletter
+\widetext \makeatletter
 \begin{center}
@@
 \end{center}
-\setcounter{equation}{0}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\setcounter{page}{1}
-\renewcommand{\theequation}{S\arabic{equation}}
+\setcounter{equation}{0} \setcounter{figure}{0} \setcounter{table}{0}
+\setcounter{page}{1} \renewcommand{\theequation}{S\arabic{equation}}
 \renewcommand{\thefigure}{S\arabic{figure}}
@@
 \begin{align}
-  H_\t{sys} = H_\NV^\t{GS} + H_\t{hf} + H_\t{nZ}  + H_\t{nn},
+  H_{\t{sys}} = H_\NV^{\t{GS}} + H_{\t{hf}} + H_{\t{nZ}}  + H_{\t{nn}},
 \end{align}
@@
 \begin{align}
-  H_\NV^\t{GS} = D\p{\v S\c\uv z}^2 - \gamma_e\v B\c\v S
+  H_\NV^{\t{GS}} = D\p{\v S\c\uv z}^2 - \gamma_e\v B\c\v S
 \end{align}
@@
 \begin{align}
-  H_\t{hf} = \sum_j\f{\gamma_e\gamma_j}{4\pi r_j^3}
+  H_{\t{hf}} = \sum_j\f{\gamma_e\gamma_j}{4\pi r_j^3}
   \p{\v S\c\v I_j-3\sp{\v S\c\uv r_j}\sp{\v I_j\c\uv r_j}}
@@
 \begin{align}
-  H_\t{nZ} = -\sum_j\gamma_j\v B\c\v I_j
+  H_{\t{nZ}} = -\sum_j\gamma_j\v B\c\v I_j
 \end{align}
@@
 \begin{align}
-  H_\t{nn} = \sum_{j<k}\f{\gamma_j\gamma_k}{4\pi r_{jk}^3}
+  H_{\t{nn}} = \sum_{j<k}\f{\gamma_j\gamma_k}{4\pi r_{jk}^3}
   \p{\v I_j\c\v I_k-3\sp{\v I_j\c\uv r_{jk}}\sp{\v I_k\c\uv r_{jk}}}
@@
 will hereafter neglect internuclear coupling in all analytical work,
-though we will keep $H_\t{nn}$ in any numerical results.
+though we will keep $H_{\t{nn}}$ in any numerical results.
 
-Changing into the rotating frame of $H_\NV^\t{GS}$ affects only the
+Changing into the rotating frame of $H_\NV^{\t{GS}}$ affects only the
 hyperfine Hamiltonian, which becomes
 \begin{align}
-  \tilde H_\t{hf} = S_z\sum_j \v A_j\c\v I_j,
+  \tilde H_{\t{hf}} = S_z\sum_j \v A_j\c\v I_j,
 \end{align}
@@
 \begin{align}
-  \tilde H_\t{sys} = S_z\sum_j \v A_j\c\v I_j
+  \tilde H_{\t{sys}} = S_z\sum_j \v A_j\c\v I_j
   -\sum_j\gamma_j\v B\c\v I_j.
@@
 
-When restricted to the subspace of $\set{\ket0,\ket{m_s}}$ with with
-$m_s\in\set{1,-1}$ for the NV electron spin,
+When NV electron spin is restricted to the span of
+$\set{\ket0,\ket{m_s}}$ with $m_s\in\set{1,-1}$,
 \begin{align}
@@
 \begin{align}
-  H_\t{int} = \f12m_s\sigma_\NV^z\sum_j\v A_j\c\v I_j
+  H_{\t{int}} = \f12m_s\sigma_\NV^z\sum_j\v A_j\c\v I_j
 \end{align}
@@
 \begin{align}
-  H_\t{nZ}^\t{eff} = -\sum_j\p{\gamma_j\v B - \f{m_s}2\v A_j}\c\v I_j
+  H_{\t{nZ}}^{\t{eff}} = -\sum_j\p{\gamma_j\v B - \f{m_s}2\v A_j}\c\v I_j
   = -\sum_j\v\omega_j\c\v I_j,
@@
 \begin{align}
-  \tilde H_\t{sys} = H_\t{int} + H_\t{nZ}^\t{eff}.
-  \label{S_H_sys_int_nZ}
+  \tilde H_{\t{sys}} = H_{\t{int}} + H_{\t{nZ}}^{\t{eff}}.
+  \label{eq:S_H_sys_int_nZ}
 \end{align}
 
-Moving into the rotating frame of $H_\t{nZ}^\t{eff}$, the entire
+Moving into the rotating frame of $H_{\t{nZ}}^{\t{eff}}$, the entire
 system is described by the Hamiltonian
 \begin{align}
-  \tilde H_\t{int} = \f12m_s\sigma_\NV^z
-  \sum_j\tilde{\v A_j}\p{t}\c\v I_j,
-  \label{S_H_int_no_DD}
+  \tilde H_{\t{int}} = \f12m_s\sigma_\NV^z
+  \sum_j\v\A_j\p{t}\c\v I_j,
+  \label{eq:S_H_int_no_DD}
 \end{align}
-where $\tilde{\v A_j}\p{t}$ is the vector $\v A_j$ rotated about
-$\uv\omega_j$ by an angle $\omega_jt$. Written explicitly,
+where $\v\A_j\p{t}$ is the vector $\v A_j$ rotated about $\uv\omega_j$
+by an angle $\omega_jt$. Written explicitly,
 \begin{align}
-  \tilde{\v A_j}\p{t} = \v A_j^\parallel + \v A_j^\perp\cos\p{\omega_jt}
+  \v\A_j\p{t} = \v A_j^\parallel + \v A_j^\perp\cos\p{\omega_jt}
   + \v A_j^{\perp\perp}\sin\p{\omega_jt},
-  \label{S_A_rot}
+  \label{eq:S_A_rot}
 \end{align}
@@
 \subsection{Dynamic decoupling and nuclear spin addressing}
+\label{sec:dynamic_decoupling}
 
@@
 \begin{align}
-  \tilde H_\t{int} =
-  \f12m_sF\p{t}\sigma_\NV^z\sum_j\tilde{\v A_j}\p{t}\c\v I_j.
+  \tilde H_{\t{int}} =
+  \f12m_sF\p{t}\sigma_\NV^z\sum_j\v\A_j\p{t}\c\v I_j.
 \end{align}
@@
 \begin{align}
-  \tilde H_\t{int} = \f14 f_{k_{DD}} m_s\sigma_\NV^z
+  \tilde H_{\t{int}} = \f14 f_{k_{DD}} m_s\sigma_\NV^z
   \sum_{j:\omega_j=\omega_r} A_j^\perp\v I_j\c\uv n_j,
-  \label{S_H_int_resonance}
+  \label{eq:S_H_int_resonance}
 \end{align}
@@
 \end{align}
-One can concisely write (\ref{S_H_int_resonance}) with
+One can concisely write Eq. (\ref{eq:S_H_int_resonance}) with
 \begin{align}
-  h_j^\t{int}\equiv f_{k_{DD}}m_sA_j^\perp/4
+  h_j^{\t{int}}\equiv f_{k_{DD}}m_sA_j^\perp/4
 \end{align}
@@
 \begin{align}
-  \tilde H_\t{int} = \sum_{j:\omega_j=\omega_r}
-  h_j^\t{int}\sigma_\NV^z\v I_j\c\uv n_j.
-  \label{S_H_int}
+  \tilde H_{\t{int}} = \sum_{j:\omega_j=\omega_r}
+  h_j^{\t{int}}\sigma_\NV^z\v I_j\c\uv n_j.
+  \label{eq:S_H_int}
 \end{align}
@@
 and $\omega_{DD}\gg A_j$ for all $j$, the secular approximation allows
-one to neglect $\tilde H_\t{int}$ entirely. In this case, one can
+one to neglect $\tilde H_{\t{int}}$ entirely. In this case, one can
 apply an auxiliary magnetic field
-$\v B_\t{ctl}^{\p\omega}\p{t}=\v
-B_\t{ctl}\cos\p{\omega_\t{ctl}t-\phi_\t{ctl}}$ and shift into the
-rotating frame of $H_\t{nZ}^\t{eff}$, much like the frame shift
-between (\ref{S_H_sys_int_nZ}) and (\ref{S_H_int_no_DD}), to realize
-the Hamiltonian
+$\tilde{\v B}_{\t{ctl}}\p{t}=\v
+B_{\t{ctl}}\cos\p{\omega_{\t{ctl}}t-\phi_{\t{ctl}}}$ and shift into
+the rotating frame of $H_{\t{nZ}}^{\t{eff}}$, much like the frame
+shift between Eqs. (\ref{eq:S_H_sys_int_nZ}) and
+(\ref{eq:S_H_int_no_DD}), to realize the Hamiltonian
 \begin{align}
-  \tilde H_\t{sys}^\t{ctl} =
-  -\sum_j\gamma_j\tilde{\v B}_{\t{ctl},j}\p{t}
-  \cos\p{\omega_\t{ctl}t-\phi_\t{ctl}}\c\v I_j,
+  \tilde H_{\t{sys}}^{\t{ctl}} =
+  -\sum_j\gamma_j\v\B_{\t{ctl},j}\p{t}
+  \cos\p{\omega_{\t{ctl}}t-\phi_{\t{ctl}}}\c\v I_j,
 \end{align}
-with $\tilde{\v B}_{\t{ctl},j}\p{t}$ defined using $\v B_\t{ctl}$ and
-$\v\omega_j$ the same way that $\tilde{\v A_j}\p{t}$ was defined using
-$\v A_j$ and $\v\omega_j$ in (\ref{S_A_rot}), i.e. as $\v B_\t{ctl}$
-rotated about $\uv\omega_j$ by an angle $\omega_jt$:
+with $\v\B_{\t{ctl},j}\p{t}$ defined using $\v B_{\t{ctl}}$ and
+$\v\omega_j$ the same way that $\v\A_j\p{t}$ was defined using
+$\v A_j$ and $\v\omega_j$ in Eq. (\ref{eq:S_A_rot}), i.e. as
+$\v B_{\t{ctl}}$ rotated about $\uv\omega_j$ by an angle $\omega_jt$:
 \begin{align}
-  \tilde{\v B}_{\t{ctl},j}\p{t} = \v B_{\t{ctl},j}^\parallel
+  \v\B_{\t{ctl},j}\p{t} = \v B_{\t{ctl},j}^\parallel
   + \v B_{\t{ctl},j}^\perp\cos\p{\omega_jt}
@@
   \v B_{\t{ctl},j}^\parallel
-  &\equiv \p{\v B_\t{ctl} \c\uv\omega_j}\uv\omega_j \\
+  &\equiv \p{\v B_{\t{ctl}} \c\uv\omega_j}\uv\omega_j \\
   \v B_{\t{ctl},j}^\perp
-  &\equiv \v B_\t{ctl} - \v B_{\t{ctl},j}^\parallel \\
+  &\equiv \v B_{\t{ctl}} - \v B_{\t{ctl},j}^\parallel \\
   \v B_{\t{ctl},j}^{\perp\perp}
-  &\equiv \uv\omega_j\times\v B_\t{ctl}^\perp.
+  &\equiv \uv\omega_j\times\v B_{\t{ctl}}^\perp.
 \end{align}
 
-When $\omega_\t{ctl}\gg\gamma_jB_\t{ctl}$, the secular approximation
-allows one to neglect $\v B_{\t{ctl},j}^\parallel$ and express
+When $\omega_{\t{ctl}}\gg\gamma_jB_{\t{ctl}}$, the secular
+approximation allows one to neglect $\v B_{\t{ctl},j}^\parallel$ and
+express
 \begin{align}
-  \tilde H_\t{ctl} = -\f12\sum_{j:\omega_j=\omega_\t{ctl}}
+  \tilde H_{\t{ctl}} = -\f12\sum_{j:\omega_j=\omega_{\t{ctl}}}
   \gamma_jB_{\t{ctl},j}^\perp \v I_j\c\uv m_j,
-  \label{S_H_ctl_resonance}
+  \label{eq:S_H_ctl_resonance}
 \end{align}
 where $\uv m_j$ is the direction of $\v B_{\t{ctl},j}^\perp$ rotated
-about $\uv\omega_j$ by $\phi_\t{ctl}$, i.e.
+about $\uv\omega_j$ by $\phi_{\t{ctl}}$, i.e.
 \begin{align}
-  \uv m_j = \uv B_{\t{ctl},j}^\perp\cos\phi_\t{ctl} +
-  \uv B_{\t{ctl},j}^{\perp\perp}\sin\phi_\t{ctl}.
+  \uv m_j = \uv B_{\t{ctl},j}^\perp\cos\phi_{\t{ctl}} +
+  \uv B_{\t{ctl},j}^{\perp\perp}\sin\phi_{\t{ctl}}.
 \end{align}
-One can concisely write (\ref{S_H_ctl_resonance}) with
+One can concisely write Eq. (\ref{eq:S_H_ctl_resonance}) with
 \begin{align}
-  h_j^\t{ctl}\equiv-\gamma_jB_{\t{ctl},j}^\perp/2
+  h_j^{\t{ctl}}\equiv-\gamma_jB_{\t{ctl},j}^\perp/2
 \end{align}
@@
 \begin{align}
-  \tilde H_\t{ctl} = \sum_{j:\omega_j=\omega_\t{ctl}}
-  h_j^\t{ctl}\v I_j\c\uv m_j.
-  \label{S_H_ctl}
+  \tilde H_{\t{ctl}} = \sum_{j:\omega_j=\omega_{\t{ctl}}}
+  h_j^{\t{ctl}}\v I_j\c\uv m_j.
+  \label{eq:S_H_ctl}
 \end{align}
 
-In both (\ref{S_H_int}) and (\ref{S_H_ctl}), one can choose
-$\phi_{DD}$ and $\phi_\t{ctl}$ such that $\uv n_j\p\phi$ and
-$\uv m_j\p{\phi_\t{ctl}}$ lie anywhere in the plane perpendicular to
-$\uv\omega_j$. One can also tune $h_j^\t{int}$ and $h_j^\t{ctl}$
+In both Eqs. (\ref{eq:S_H_int}) and (\ref{eq:S_H_ctl}), one can choose
+$\phi_{DD}$ and $\phi_{\t{ctl}}$ such that $\uv n_j\p\phi$ and
+$\uv m_j\p{\phi_{\t{ctl}}}$ lie anywhere in the plane perpendicular to
+$\uv\omega_j$. One can also tune $h_j^{\t{int}}$ and $h_j^{\t{ctl}}$
 respectively via free parameters in the AXY-$n$ sequence and
-$\v B_\t{ctl}$. These controls, together with rotations of the NV
+$\v B_{\t{ctl}}$. These controls, together with rotations of the NV
 electron spin, allow one to realize a universal set of quantum
@@
 the same effective larmor frequency $\omega_j$, in which case they are
-addressed simultaneously in (\ref{S_H_int}) and (\ref{S_H_ctl}).
+addressed simultaneously in Eqs. (\ref{eq:S_H_int}) and
+(\ref{eq:S_H_ctl}).
 
 \subsection{Addressing larmor pairs}
+\label{sec:addressing_pairs}
 
@@
 spins as a \emph{larmor pair}. The problem with individually
-addressing elements of a larmor set is manifest in (\ref{S_H_int}) and
-(\ref{S_H_ctl}), wherein the previously developed procedure for
-nuclear spin addressing does not single out any nuclei. Nonetheless,
-under certain conditions it is possible to individually address
-elements of a larmor set by applying additional control fields.
+addressing elements of a larmor set is manifest in
+Eqs. (\ref{eq:S_H_int}) and (\ref{eq:S_H_ctl}), wherein the previously
+developed procedure for nuclear spin addressing does not single out
+any nuclei. Nonetheless, under certain conditions it is possible to
+individually address elements of a larmor set by applying additional
+control fields.
 
@@
 magnetic decoupling field
-$\v B_\t{dec}^{\p\omega}\p{t}=\v B_\t{dec}\cos\p{\omega_r
-  t-\phi_\t{dec}}$ and realize, in the frame of $H_\NV^\t{GS}$, the
-system Hamiltonian
+$\tilde{\v B}_{\t{dec}}\p{t}=\v B_{\t{dec}}\cos\p{\omega_r
+  t-\phi_{\t{dec}}}$ and realize, in the frame of $H_\NV^{\t{GS}}$,
+the system Hamiltonian
 \begin{align}
-  \tilde H_\t{sys}^\t{dec} = H_\t{int} + H_\t{nZ}^\t{eff} + H_\t{dec},
+  \tilde H_{\t{sys}}^{\t{dec}}
+  = H_{\t{int}} + H_{\t{nZ}}^{\t{eff}} + H_{\t{dec}},
 \end{align}
@@
 \begin{align}
-  H_\t{dec} = -\sum_j\gamma_j\v B_\t{dec}\c\v I_j
-  \cos\p{\omega_rt-\phi_\t{dec}}.
+  H_{\t{dec}} = -\sum_j\gamma_j\v B_{\t{dec}}\c\v I_j
+  \cos\p{\omega_rt-\phi_{\t{dec}}}.
 \end{align}
 
-In the frame of $H_\t{nZ}^\t{eff}=-\sum_j\v\omega_j\c\v I_j$, the
+In the frame of $H_{\t{nZ}}^{\t{eff}}=-\sum_j\v\omega_j\c\v I_j$, the
 decoupling Hamiltonian becomes
 \begin{align}
-  \tilde H_\t{dec} = -\sum_j\gamma_j\tilde{\v B}_{\t{dec},j}
-  \c\v I_j \cos\p{\omega_rt-\phi_\t{dec}}
-  \label{S_H_dec_eff_full}
+  \tilde H_{\t{dec}} = -\sum_j\gamma_j\v\B_{\t{dec},j}
+  \c\v I_j \cos\p{\omega_rt-\phi_{\t{dec}}}
+  \label{eq:S_H_dec_eff_full}
 \end{align}
@@
 \begin{align}
-  \tilde{\v B}_{\t{dec},j} = \v B_{\t{dec},j}^\parallel
+  \v\B_{\t{dec},j} = \v B_{\t{dec},j}^\parallel
   + \v B_{\t{dec},j}^\perp\cos\p{\omega_j t}
@@
   \v B_{\t{dec},j}^\parallel
-  &\equiv \p{\v B_\t{dec} \c\uv\omega_j}\uv\omega_j, \\
+  &\equiv \p{\v B_{\t{dec}}\c\uv\omega_j}\uv\omega_j, \\
   \v B_{\t{dec},j}^\perp
-  &\equiv \v B_\t{dec} - \v B_{\t{dec},j}^\parallel, \\
+  &\equiv \v B_{\t{dec}} - \v B_{\t{dec},j}^\parallel, \\
   \v B_{\t{dec},j}^{\perp\perp}
-  &\equiv \uv\omega_j\times\v B_\t{dec}^\perp.
+  &\equiv \uv\omega_j\times\v B_{\t{dec}}^\perp.
 \end{align}
-If $\omega_r,\omega_j\gg \gamma_jB_\t{dec}$, then we can neglect
-$\v B_{\t{dec},j}^\parallel$ in (\ref{S_H_dec_eff_full}) by the
+If $\omega_r,\omega_j\gg \gamma_jB_{\t{dec}}$, then we can neglect
+$\v B_{\t{dec},j}^\parallel$ in Eq. (\ref{eq:S_H_dec_eff_full}) by the
 secular approximation, and by the rotating approximation express
 \begin{align}
-  \tilde H_\t{dec} = -\sum_{j:\omega_j=\omega_r}
-  \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_\t{dec} +
-  \v B_{\t{dec},j}^{\perp\perp}\sin\phi_\t{dec}}\c\v I_j.
+  \tilde H_{\t{dec}} = -\sum_{j:\omega_j=\omega_r}
+  \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_{\t{dec}} +
+  \v B_{\t{dec},j}^{\perp\perp}\sin\phi_{\t{dec}}}\c\v I_j.
 \end{align}
@@
 \begin{align}
-  \v\nu_j = \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_\t{dec}
-  + \v B_{\t{dec},j}^{\perp\perp}\sin\phi_\t{dec}},
+  \v\nu_j = \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_{\t{dec}}
+  + \v B_{\t{dec},j}^{\perp\perp}\sin\phi_{\t{dec}}},
 \end{align}
@@
 \begin{align}
-  \tilde H_\t{dec} = -\sum_{j:\omega_j=\omega_r}\v\nu_j\c\v I_j.
+  \tilde H_{\t{dec}} = -\sum_{j:\omega_j=\omega_r}\v\nu_j\c\v I_j.
 \end{align}
-The system Hamiltonian in the frame of $H_\t{nZ}^\t{eff}$ thus takes
-the form
+The system Hamiltonian in the frame of $H_{\t{nZ}}^{\t{eff}}$ thus
+takes the form
 \begin{align}
-  \tilde H_\t{sys}^\t{dec} = \tilde H_\t{int} + \tilde H_\t{dec}
+  \tilde H_{\t{sys}}^{\t{dec}} = \tilde H_{\t{int}} + \tilde H_{\t{dec}}
   = \sum_{j:\omega_j=\omega_r}
-  \p{h_j^\t{int}\sigma_\NV^z\v I_j\c\uv n_j - \v\nu_j\c\v I_j}.
+  \p{h_j^{\t{int}}\sigma_\NV^z\v I_j\c\uv n_j - \v\nu_j\c\v I_j}.
 \end{align}
 
-In the frame of $\tilde H_\t{dec}$, the entire system is governed by
+In the frame of $\tilde H_{\t{dec}}$, the entire system is governed by
 the Hamiltonian
 \begin{align}
-  \tilde H_\t{int}^\t{dec} = \sum_{j:\omega_j=\omega_r}
-  h_j^\t{int}\sigma_\NV^z\v I_j\c\tilde{\v n}_j\p{t},
-  \label{S_H_int_dec_full}
+  \tilde H_{\t{int}}^{\t{dec}} = \sum_{j:\omega_j=\omega_r}
+  h_j^{\t{int}}\sigma_\NV^z\v I_j\c\tilde{\v n}_j\p{t},
+  \label{eq:S_H_int_dec_full}
 \end{align}
@@
 \end{align}
-If $\omega_j\gg\nu_j\gg h_j^\t{int}$, the secular approximation allows
-us to neglect $\v n_j^\perp$ and $\v n_j^{\perp\perp}$ in
-(\ref{S_H_int_dec_full}), leaving
+If $\omega_j\gg\nu_j\gg h_j^{\t{int}}$, the secular approximation
+allows us to neglect $\v n_j^\perp$ and $\v n_j^{\perp\perp}$ in
+Eq. (\ref{eq:S_H_int_dec_full}), leaving
 \begin{align}
-  \tilde H_\t{int}^\t{dec}
+  \tilde H_{\t{int}}^{\t{dec}}
   = \sum_{j:\omega_j=\omega_r}
-  \tilde h_j^\t{int}\sigma_\NV^z\v I_j\c\uv\nu_j,
-  \label{S_H_int_dec}
+  \tilde h_j^{\t{int}}\sigma_\NV^z\v I_j\c\uv\nu_j,
+  \label{eq:S_H_int_dec}
 \end{align}
@@
 \begin{align}
-  \tilde h_j^\t{int} = h_j^\t{int}\uv n_j\c\uv\nu_j.
+  \tilde h_j^{\t{int}}
+  = h_j^{\t{int}}\uv n_j\c\uv\nu_j.
 \end{align}
+Letting $\theta_j$ and $\theta_{\t{dec}}$ respectively be the angular
+positions of $\uv A_j^\perp$ and $\uv B_{\t{dec}}^\perp$ in the plane
+perpendicular to $\uv\omega_j$, we can say that
+\begin{align}
+  \tilde h_j^{\t{int}} = h_j^{\t{int}}\cos\eta_j,
+\end{align}
+where $\eta_j=\theta_j+\phi_{DD}-\p{\theta_{\t{dec}}+\phi_{\t{dec}}}$.
 
-In words, the decoupling field $\v B_\t{dec}^{\p\omega}\p{t}$ modifies
-$\tilde H_\t{int}$ in (\ref{S_H_int}) by suppressing the components of
-$\uv n_j$ (i.e. $\uv A_j^\perp$ rotated about $\uv\omega_j$ by
-$\phi_{DD}$) which are perpendicular to the respective $\uv\nu_j$
-(i.e.  $\uv B_{\t{dec},j}^\perp$ rotated about $\uv\omega_j$ by
-$\phi_\t{dec}$). The utility of this decoupling field lies in the fact
-that when $\uv n_j$ and $\uv\nu_j$ are orthogonal, the interaction
-with spin $j$ is suppressed as $\tilde h_j^\t{int}=0$. Considering a
-single larmor pair, one can therefore apply a decoupling field to
-eliminate one of the two terms in (\ref{S_H_int_dec}) and realize an
-effective Hamiltonian which couples the NV electron spin to only one
-nuclear spin. This scheme fails for larmor pairs with mutually
-parallel $\v A_j^\perp$.
+In words, the decoupling field $\tilde{\v B}_{\t{dec}}\p{t}$ modifies
+$\tilde H_{\t{int}}$ in Eq. (\ref{eq:S_H_int}) by suppressing the
+components of $\uv n_j$ (i.e. $\uv A_j^\perp$ rotated about
+$\uv\omega_j$ by $\phi_{DD}$) which are perpendicular to the
+respective $\uv\nu_j$ (i.e.  $\uv B_{\t{dec},j}^\perp$ rotated about
+$\uv\omega_j$ by $\phi_{\t{dec}}$). The utility of this decoupling
+field lies in the fact that when $\uv n_j$ and $\uv\nu_j$ are
+orthogonal, the interaction with spin $j$ is suppressed as
+$\tilde h_j^{\t{int}}=0$. Considering a single larmor pair, one can
+therefore apply a decoupling field to eliminate one of the two terms
+in Eq. (\ref{eq:S_H_int_dec}) and realize an effective Hamiltonian
+which couples the NV electron spin to only one nuclear spin. This
+scheme fails for larmor pairs with mutually parallel $\v A_j^\perp$.
 
@@
 therefore be either forgone, or else realized via composite operations
-making use of (\ref{S_H_ctl}) and (\ref{S_H_int_dec}). The same is
-true of spin-spin coupling between the NV electron spin and a single
-element of a larmor set with more than two nuclei.
+making use of Eqs. (\ref{eq:S_H_ctl}) and (\ref{eq:S_H_int_dec}). The
+same is true of spin-spin coupling between the NV electron spin and a
+single element of a larmor set with more than two nuclei.
 
@@
 
-For the following analysis, we will consider a single addressable
-larmor pair, i.e. a pair of nuclei indexed by 1 and 2 with effective
-larmor frequencies $\omega$ and for which $\v A_j^\perp$ are not
-mutually parallel. We will use the basis
+In the following section, we will consider an addressable larmor pair
+with effective larmor frequencies $\omega$. We will use the basis
 $\set{\ket\u\equiv\ket 0, \ket\d\equiv\ket{m_s}}$ for the spin states
@@
   = {\cNOT^{\AC\to\NV}}^\dagger\cNOT^{\NV\to\AC}\cNOT^{\AC\to\NV},
-  \label{S_SWAP_NVAC_sketch}
+  \label{eq:S_SWAP_NVAC_sketch}
 \end{align}
@@
 \end{align}
-For later convenience, (\ref{S_SWAP_NVAC_sketch}) makes use of the
-fact that ${\cNOT^{j\to k}}^\dagger=\cNOT^{j\to k}$. Therefore (with
-$\v I_\NV=\v\sigma_\NV/2$),
+For later convenience, Eq. (\ref{eq:S_SWAP_NVAC_sketch}) makes use of
+the fact that ${\cNOT^{j\to k}}^\dagger=\cNOT^{j\to k}$. Therefore
+(with $\v I_\NV=\v\sigma_\NV/2$),
 \begin{align}
   \SWAP^{\NV,\AC}
-  =& \exp\p{-j\f\pi2 I_\NV^x} \exp\p{j\f\pi2 I_1^{z'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^x I_1^{z'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_1^{x'}}
-     \exp\p{j\f\pi2 \sigma_\NV^z I_1^{x'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_2^{x''}}
-     \exp\p{j\f\pi2 \sigma_\NV^z I_2^{x''}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_1^{z'}}
+  &= \exp\p{-j\f\pi2 I_\NV^x} \exp\p{j\f\pi2 I_1^{z'}}
+    \exp\p{-j\f\pi2 \sigma_\NV^x I_1^{z'}} \tag*{} \\
+  &~~\times \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_1^{x'}}
+    \exp\p{j\f\pi2 \sigma_\NV^z I_1^{x'}} \tag*{} \\
+  &~~\times \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_2^{x''}}
+    \exp\p{j\f\pi2 \sigma_\NV^z I_2^{x''}} \tag*{} \\
+  &~~\times \exp\p{-j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_1^{z'}}
     \exp\p{j\f\pi2 \sigma_\NV^x I_1^{z'}},
-  \label{S_SWAP_NVAC_full}
+    \label{eq:S_SWAP_NVAC_full}
 \end{align}
@@
 can evaluate the first and last rotations of spin 1 in
-(\ref{S_SWAP_NVAC_full}) and combine factors to get
+Eq. (\ref{eq:S_SWAP_NVAC_full}) and combine factors to get
 \begin{align}
   \SWAP^{\NV,\AC}
-  =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 \sigma_\NV^x I_1^{z'}}
-     \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sp{I_1^{y'}-I_2^{x''}}}
-     \times \tag*{} \\
-   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
-     \exp\p{j\f\pi2 \sigma_\NV^z I_2^{x''}} \times \tag*{} \\
-   & \exp\p{j\f\pi2 \sigma_\NV^x I_1^{z'}} \exp\p{-j\f\pi2 I_\NV^x}.
+  &= \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 \sigma_\NV^x I_1^{z'}}
+    \tag*{} \\
+  &~~\times \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sp{I_1^{y'}-I_2^{x''}}}
+    \tag*{} \\
+  &~~\times \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
+    \exp\p{j\f\pi2 \sigma_\NV^z I_2^{x''}} \tag*{} \\
+  &~~\times \exp\p{j\f\pi2 \sigma_\NV^x I_1^{z'}}
+    \exp\p{-j\f\pi2 I_\NV^x}.
 \end{align}
@@
   \uv y' = -\uv x'' &= \uv A_1^{\perp\perp}, \\
-  \uv z' = \uv z'' &= \uv\omega_1\approx\uv z, \label{S_w=z}
+  \uv z' = \uv z'' &= \uv\omega_1\approx\uv z, \label{eq:S_w=z}
 \end{align}
-where the approximation in (\ref{S_w=z}) holds for
+where the approximation in Eq. (\ref{eq:S_w=z}) holds for
 $\gamma_1B\gg A_1/2$,
@@
   \SWAP^{\NV,\AC}
-  =& \exp\p{j\f\pi2 I_\NV^x}
-     \exp\p{-j\f\pi2 \sigma_\NV^x I_1^z} \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z}
-     \exp\p{j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \times \tag*{} \\
-   & \exp\p{j\f\pi2 \sigma_\NV^x I_1^z} \exp\p{-j\f\pi2 I_\NV^x}.
-  \label{S_SWAP_NVAC_sxsz}
+  &= \exp\p{j\f\pi2 I_\NV^x}
+    \exp\p{-j\f\pi2 \sigma_\NV^x I_1^z} \tag*{} \\
+  &~~\times \exp\p{-j\pi I_\NV^z}
+    \exp\p{j\f\pi2\sum_jI_j^{y'}} \tag*{} \\
+  &~~\times \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
+    \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \tag*{} \\
+  &~~\times \exp\p{j\f\pi2 \sigma_\NV^x I_1^z} \exp\p{-j\f\pi2 I_\NV^x}.
+    \label{eq:S_SWAP_NVAC_sxsz}
 \end{align}
-As we cannot directly realize the coupling $\sigma_x^\NV I_z^1$,
-we must perform rotations as
+As we cannot directly realize the coupling $\sigma_x^\NV I_z^1$, we
+must perform rotations as
 \begin{align}
   \exp\p{-j\f\pi2 \sigma_\NV^x I_1^z}
-  =& \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\f\pi2 I_1^{y'}}
+  = \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\f\pi2 I_1^{y'}}
   \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{x'}}
@@
 \end{align}
-Substituting this identity into (\ref{S_SWAP_NVAC_sxsz}) yields
+Substituting this identity into Eq. (\ref{eq:S_SWAP_NVAC_sxsz}) yields
 \begin{align}
   \SWAP^{\NV,\AC}
-  =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_\NV^y} \times \tag*{} \\
-   & \exp\p{j\f\pi2\sum_jI_j^{y'}}
+  &= \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_\NV^y} \tag*{} \\
+  &~~\times \exp\p{j\f\pi2\sum_jI_j^{y'}}
     \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{x'}}
-     \exp\p{j\f\pi2 I_\NV^y} \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z}
-     \exp\p{j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^y}
+    \exp\p{j\f\pi2 I_\NV^y} \tag*{} \\
+  &~~\times \exp\p{-j\pi I_\NV^z}
+    \exp\p{j\f\pi2\sum_jI_j^{y'}} \tag*{} \\
+  &~~\times \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
+    \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \tag*{} \\
+  &~~\times \exp\p{-j\f\pi2 I_\NV^y}
     \exp\p{j\f\pi2 \sigma_\NV^z I_1^{x'}}
-     \exp\p{-j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
-   & \exp\p{j\f\pi2 I_\NV^y} \exp\p{-j\f\pi2 I_\NV^x},
-  \label{S_SWAP_NVAC}
+    \exp\p{-j\f\pi2\sum_jI_j^{y'}} \tag*{} \\
+  &~~\times \exp\p{j\f\pi2 I_\NV^y} \exp\p{-j\f\pi2 I_\NV^x},
+    \label{eq:S_SWAP_NVAC}
 \end{align}
@@
   \SWAP^{\NV,\ST}
-  =& \exp\p{j\pi\v I_\NV\c\uv a} \times \tag*{} \\
-   & \exp\p{j\f\pi2\sum_jI_j^{y'}}
+  &= \exp\p{j\pi\v I_\NV\c\uv a} \tag*{} \\
+  &~~\times \exp\p{j\f\pi2\sum_jI_j^{y'}}
     \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{x'}}
-     \exp\p{j\f\pi2 I_\NV^y} \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z}
-     \exp\p{j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^y}
+    \exp\p{j\f\pi2 I_\NV^y} \tag*{} \\
+  &~~\times \exp\p{-j\pi I_\NV^z}
+    \exp\p{j\f\pi2\sum_jI_j^{y'}} \tag*{} \\
+  &~~\times \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
+    \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \tag*{} \\
+  &~~\times \exp\p{-j\f\pi2 I_\NV^y}
     \exp\p{j\f\pi2 \sigma_\NV^z I_1^{x'}}
-     \exp\p{-j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
-   & \exp\p{-j\pi\v I_\NV\c\uv a},
-  \label{S_SWAP_NVST}
+    \exp\p{-j\f\pi2\sum_jI_j^{y'}} \tag*{} \\
+  &~~\times \exp\p{-j\pi\v I_\NV\c\uv a},
+    \label{eq:S_SWAP_NVST}
 \end{align}
@@
 If $\gamma_1=\gamma_2$, i.e. if nuclei 1 and 2 are of the same
-species, all factors in (\ref{S_SWAP_NVST}) can be realized directly
-via the protocols for (\ref{S_H_ctl}), (\ref{S_H_int_dec}), and
-rotations of the NV electron spin.
+species, all factors in Eq. (\ref{eq:S_SWAP_NVST}) can be realized
+directly via the protocols for Eq. (\ref{eq:S_H_ctl}) and
+Eq. (\ref{eq:S_H_int_dec}), as well as rotations of the NV electron
+spin.
 
-Realizing $\SWAP^{\NV,\AC}$ by switching the cNOT operations in
-(\ref{S_SWAP_NVAC_sketch}) is seemingly impossible, as doing so
-requires rotating one spin in the larmor pair without rotating the
-other. It is possible to realize $\SWAP^{\NV,\ST}$ via cNOT operations
-between the NV and ST qubits directly, but this method requires
-performing many more individual spin addressing operations, and
-therefore has a substantially lower fidelity.
+As a last note, it is possible to realize $\SWAP^{\NV,\ST}$ via cNOT
+operations between the NV and ST qubits directly, i.e. without
+performing $\SWAP^{\NV,\AC}$, but doing so requires performing many
+more individual spin addressing operations, which results in a
+substantially lower fidelity.
 
 \fixme{when we wish to read out the ST qubit, it is possible to do so
-  without performing the full coherent SWAP operation so long as we no
-  longer need the larmor pair as a resource for the time being. Talk
+  without performing the full coherent SWAP operation so long as we
+  are willing to discard the initial state of the NV center. Talk
   about this.}
@@
 
-Talk about the robustness of the ST qubit against dephasing via the NV
-center, as well as its robustness against slowly varying (frequencies
-$\nu\ll\gamma_jB$) external magnetic noise.
+\fixme{Talk about the robustness of the ST qubit against dephasing via
+  the NV center, as well as its robustness against slowly varying
+  (frequencies $\nu\ll\gamma_jB$) external magnetic noise.}
 
@@
 
-For any given hyperfine cutoff $A_\t{min}$ and an isotopic abundance
+For any given hyperfine cutoff $A_{\t{min}}$ and an isotopic abundance
 $n$ of $^{13}$C, we can compute exactly the probability
-$P\p{A_\t{min},n}$ of finding an addressable larmor pair for which
-$A_j\ge A_\t{min}$. The simulations developed for this paper can also
-be used to test the computation of $P\p{A_\t{min},n}$ via the Monte
-Carlo method of simply generating many NV systems and counting the
-proportion of them which contain an addressable larmor pair.
+$P\p{A_{\t{min}},n}$ of finding an addressable larmor pair for which
+$A_j\ge A_{\t{min}}$. The simulations developed for this paper can
+also be used to test the computation of $P\p{A_{\t{min}},n}$ via the
+Monte Carlo method of simply generating many NV systems and counting
+the proportion of them which contain an addressable larmor pair.
 

### 2016-10-01 simulation.cpp
fix phi_dec and change phi_DD in coherence signal measurement; use control fields at a given angle for single-axis coherence signal measurement

@@ -614,26 +614,36 @@ int main(const int arg_num, const char *arg_vec[]) {
         cout << endl;
       }
 
+      // determine control field to use during coherence signal measurement
       const double w_signal = effective_larmor(nv,target).norm();
+      const double phi_dec = [&]() -> double {
+        if (!angular_coherence_signal) return angle;
+        else return 0;
+      }();
+      const control_fields controls(nv.static_gBz/signal_gB_factor*xhat,
+                                    w_signal, phi_dec);
+      cout << "# phi_dec/pi: " << phi_dec/pi << endl;
+
+      // fix coherence signal measurement time
       const double measurement_time = 4*pi / (axy_f_max(nv.k_DD) * max_f_factor
                                               * hyperfine_perp(nv,target).norm() / 4);
-      cout << "# measurement_time (s): " << measurement_time << endl;
+      cout << "# measurement_time (ms): " << measurement_time * 1e3 << endl;
+
       for (uint ii = 0; ii < coherence_bins; ii++) {
         const double f_DD = (ii+0.5)/coherence_bins * axy_f_max(nv.k_DD) * max_f_factor;
 
         if (!angular_coherence_signal) {
           const double coherence =
-            coherence_measurement(nv, w_signal, f_DD, measurement_time);
+            coherence_measurement(nv, w_signal, f_DD, measurement_time, controls);
           cout << f_DD << " " << coherence << endl;
 
         } else {
           cout << f_DD;
           for (uint jj = 0; jj < angular_resolution; jj++) {
-            const double phi_dec = -(jj+0.5)/angular_resolution * pi;
-            const control_fields controls(nv.static_gBz/signal_gB_factor*xhat,
-                                          w_signal, phi_dec);
+            const double phi_DD = (jj+0.5)/angular_resolution * pi;
             const double coherence =
-              coherence_measurement(nv, w_signal, f_DD, measurement_time, controls);
+              coherence_measurement(nv, w_signal, f_DD, measurement_time,
+                                    controls, phi_DD);
             cout << " " << coherence;
           }
           cout << endl;

### 2016-10-01 swap-nvst-paper/paper.tex
add derivation of nuclear positions from coherence data

@@
 %%% math, symbols, etc.
-\usepackage{physics,braket,bm}
+\usepackage{physics,braket,bm,amssymb}
 \renewcommand{\t}{\text} % text in math mode
@@
   \label{eq:L}
-  L\p{t} = \prod_j\cos\p{\f14 f_{k_{DD}}A_j^\perp t}.
+  L = \prod_j\cos\p{\f14 f_{k_{DD}}A_j^\perp t}.
 \end{align}
@@
 the scanning protocol in \cite{wang2016positioning}, coherence
-measurements as per Eq. (\ref{eq:L}) for different fourier components
-$f_{k_{DD}}$ (or times $t$) are sufficient to determine the number of
-nuclei with effective larmor frequency $\omega$. The protocol for
-measuring $L$ can thus be used to identify a larmor pair.
+measurements as per Eq. (\ref{eq:L}) for different AXY-$n$ fourier
+components $f_{k_{DD}}$ (or times $t$) are sufficient to determine the
+number of nuclei with effective larmor frequency $\omega$. The
+protocol for measuring NV coherence can thus be used to identify a
+larmor pair.
 
@@
 $\omega_{\t{dec}}$ is on resonance with the effective larmor frequency
-$\omega$, the coherence in Eq. (\ref{eq:L}) is modified as
+$\omega$ of a larmor pair (and some simple conditions on
+$\v B_{\t{dec}}$ are satisfied), the coherence in Eq. (\ref{eq:L}) can
+be written as
 \begin{align}
   \label{eq:L_dec}
-  \tilde L\p{t}
-  = \prod_j\cos\p{\f14 f_{k_{DD}}A_j^\perp t\cos\eta_j},
+  L = \f12\p{\cos\sp{2\xi\cos\alpha_+\cos\alpha_-}
+  + \cos\sp{2\xi\sin\alpha_+\sin\alpha_-}}.
 \end{align}
-where the angle $\eta_j$ is determined by the directions
-$\uv A_j^\perp$ and $\uv B_{\t{dec}}$, as well as the phases
-$\phi_{DD}$ and $\phi_{\t{dec}}$ (see Supplementary Info
-\ref{sec:addressing_pairs}). Measurements of the coherence $\tilde L$
-as a function of fourier components $f_{k_{DD}}$ (or times $t$) and
-phases $\phi_{DD}$ thus provides information about the directions
-$\uv A_j^\perp$.
-
-\fixme{How do we locate larmor pairs using Eq. (\ref{eq:L_dec})?}
+Here $\xi$ is a constant phase determined by $f_{k_{DD}}$, $A^\perp$,
+and interaction time $t$; the angle $\alpha_-$ is determined by the
+directions $\uv A_j^\perp$; and $\alpha_+$ is determined by the
+directions $\uv A_j^\perp$ as well as $\phi_{DD}$, $\phi_{\t{dec}}$,
+and $\uv B_{\t{dec}}$. Measurement of e.g.  $L\p{\xi,\phi_{DD}}$ thus
+provides sufficient information to deduce the directions
+$\uv A_j^\perp$, knowing which is necessary for individual nuclear
+addressing protocols (see Supplementary Info section
+\ref{sec:S_locating_pairs}).
 
@@
 
+\section{Conclusions}
+
+\section{Acknowledgments}
+
 \bibliography{\jobname}
@@
 \end{center}
-\setcounter{equation}{0} \setcounter{figure}{0} \setcounter{table}{0}
-\setcounter{page}{1} \renewcommand{\theequation}{S\arabic{equation}}
+\setcounter{equation}{0}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\renewcommand{\theequation}{S\arabic{equation}}
 \renewcommand{\thefigure}{S\arabic{figure}}
@@
 
+\setcounter{section}{0}
+\renewcommand{\thesection}{S.I. \Roman{section}}
+
 \tableofcontents{}
 
-\section{Theory}
-
-\subsection{Basic system model}
+\section{Basic system model}
 
@@
 
-\subsection{Dynamic decoupling and nuclear spin addressing}
-\label{sec:dynamic_decoupling}
+\section{Dynamic decoupling and nuclear spin addressing}
+\label{sec:S_dynamic_decoupling}
 
@@
   \v B_{\t{ctl},j}^\parallel
-  &\equiv \p{\v B_{\t{ctl}} \c\uv\omega_j}\uv\omega_j \\
-  \v B_{\t{ctl},j}^\perp
-  &\equiv \v B_{\t{ctl}} - \v B_{\t{ctl},j}^\parallel \\
-  \v B_{\t{ctl},j}^{\perp\perp}
-  &\equiv \uv\omega_j\times\v B_{\t{ctl}}^\perp.
+  \equiv \p{\v B_{\t{ctl}} \c\uv\omega_j}\uv\omega_j,
+  && \v B_{\t{ctl},j}^\perp
+  \equiv \v B_{\t{ctl}} - \v B_{\t{ctl},j}^\parallel,
+  && \v B_{\t{ctl},j}^{\perp\perp}
+  \equiv \uv\omega_j\times\v B_{\t{ctl}}^\perp.
 \end{align}
@@
 
-\subsection{Addressing larmor pairs}
-\label{sec:addressing_pairs}
+\section{Addressing larmor pairs}
+\label{sec:S_addressing_pairs}
 
@@
   \v B_{\t{dec},j}^\parallel
-  &\equiv \p{\v B_{\t{dec}}\c\uv\omega_j}\uv\omega_j, \\
-  \v B_{\t{dec},j}^\perp
-  &\equiv \v B_{\t{dec}} - \v B_{\t{dec},j}^\parallel, \\
-  \v B_{\t{dec},j}^{\perp\perp}
-  &\equiv \uv\omega_j\times\v B_{\t{dec}}^\perp.
+  \equiv \p{\v B_{\t{dec}}\c\uv\omega_j}\uv\omega_j,
+  && \v B_{\t{dec},j}^\perp
+  \equiv \v B_{\t{dec}} - \v B_{\t{dec},j}^\parallel,
+  && \v B_{\t{dec},j}^{\perp\perp}
+  \equiv \uv\omega_j\times\v B_{\t{dec}}^\perp.
 \end{align}
@@
 \begin{align}
-  \tilde h_j^{\t{int}} = h_j^{\t{int}}\cos\eta_j,
+  \tilde h_j^{\t{int}} = h_j^{\t{int}}\cos\p{\theta_j-\eta},
 \end{align}
-where $\eta_j=\theta_j+\phi_{DD}-\p{\theta_{\t{dec}}+\phi_{\t{dec}}}$.
+where $\eta=-\phi_{DD}+\theta_{\t{dec}}+\phi_{\t{dec}}$.
 
@@
 
-\subsection{Coherent SWAP with a singlet-triplet qubit}
+\section{Identifying and locating larmor pairs}
+\label{sec:S_locating_pairs}
+
+Larmor pairs can be identified and located via NV coherence
+measurements as in \cite{wang2016positioning}. When the AXY-$n$
+sequence is on resonance with a larmor pair, the NV coherence reads
+\begin{align}
+  L = \cos^2\xi,
+\end{align}
+where the phase $\xi = h^{\t{int}}t = f_{k_{DD}}m_sA_j^\perp t/4$.
+Applying a decoupling field as in section \ref{sec:S_addressing_pairs}
+modifies $h_j^{\t{int}}\to h_j^{\t{int}}\cos\p{\theta_j-\eta}$, which
+makes the NV coherence
+($\eta=-\phi_{DD}+\theta_{\t{dec}}+\phi_{\t{dec}}$)
+\begin{align}
+  L
+  = \cos\p{\xi\cos\sp{\theta_1-\eta}}\cos\p{\xi\cos\sp{\theta_2-\eta}}.
+\end{align}
+Defining
+\begin{align}
+  \alpha_- = \f12\p{\sp{\theta_1-\eta}-\sp{\theta_2-\eta}}
+  = \f12\p{\theta_1-\theta_2},
+  && \alpha_+ = \f12\p{\sp{\theta_1-\eta}+\sp{\theta_2-\eta}}
+     = \f12\p{\theta_1+\theta_2} - \eta,
+\end{align}
+we can expand
+\begin{align}
+  L
+  = \f12\p{\cos\sp{2\xi\cos\alpha_+\cos\alpha_-}
+  + \cos\sp{2\xi\sin\alpha_+\sin\alpha_-}}.
+\end{align}
+When $\alpha_+$ is an integer multiple of $\pi/2$, this coherence
+simplifies to ($n\in\mathbb Z$)
+\begin{align}
+  \label{eq:S_L_simplified}
+  L\p{\alpha_+=n\pi} = \f12\p{1 + \cos\sp{2\xi\cos\alpha_-}},
+  && L\p{\alpha_+=n\pi+\f\pi2}
+     = \f12\p{1 + \cos\sp{2\xi\sin\alpha_-}}.
+\end{align}
+By collecting data on $L\p{\xi,\eta}$, one can identify fixed angles
+$\bar\eta$ at which $L_{\bar\eta}\p\xi\equiv L\p{\xi,\bar\eta}$ takes
+the form above. Knowing $L_{\bar\eta}\p\xi$ is then sufficient to
+deduce the values of $\theta_1$ and $\theta_2$ up to a degeneracy
+which does not affect nuclear spin addressing protocols. To find the
+angles $\set{\theta_j}$ and understand this degeneracy, we first note
+that changing these angles by $\pi$ as $\theta_j\to\theta_j+\pi$ does
+not affect any protocols, so we can safely enforce all
+$\theta_j\in\sp{0,\pi}$ and in turn $\alpha_\pm\in\sp{0,\pi}$. The
+coherence $L\p{\xi,\eta}$ then takes the forms in
+(\ref{eq:S_L_simplified}) when $\alpha_+\in\set{0,\pi/2}$, in which
+case a fourier transform of $L_{\bar\eta}\p\xi$ can be used to
+identify the coherence modes
+\begin{align}
+  \omega_L\p{\alpha_+=0}=2\xi\cos\alpha_-,
+  && \omega_L\p{\alpha_+=\pi/2}=2\xi\sin\alpha_-,
+\end{align}
+and in turn the angles
+\begin{align}
+  \alpha_-\p{\alpha_+=0} = \acos\p{\f1{2\xi}\omega_L\p{\alpha_+=0}},
+  && \alpha_-\p{\alpha_+=\f\pi2}
+     = \asin\p{\f1{2\xi}\omega_L\p{\alpha_+=\f\pi2}}.
+\end{align}
+When $\alpha_+=0$, the angles $\theta_1$ and $\theta_2$ are then
+\begin{align}
+  \label{eq:S_nuclear_angles}
+  \theta_1 = \bar\eta\p{\alpha_+=0} + \alpha_-\p{\alpha_+=0},
+  && \theta_2 = \bar\eta\p{\alpha_+=0} - \alpha_-\p{\alpha_+=0},
+\end{align}
+The obvious problem with this recipe for $\set{\theta_j}$ is the fact
+that measuring $L_{\bar\eta}\p\xi$ does not allow one to distinguish
+the case of $\alpha_+=0$ from $\alpha_+=\pi/2$, as the form of
+$L_{\bar\eta}\p\xi$ is identical in both cases. As it turns out, in
+finding $\theta_1$ and $\theta_2$ via the prescription above, one is
+free to simply assume without consequence that $\alpha_+=0$ whenever
+the coherence $L_{\bar\eta}\p\xi$ takes the form in
+(\ref{eq:S_L_simplified}). Incorrectly identifying the value of
+$\alpha_+'=\pi/2-\alpha_+$ instead of $\alpha_+$ will result in the
+deduction of $\alpha_-'=\pi/2-\alpha_-$ instead of $\alpha_-$. The
+prescriptions in (\ref{eq:S_nuclear_angles}) then yield
+\begin{align}
+  \bar\eta\p{\alpha_+'=0} + \alpha_-'\p{\alpha_+'=0}
+  = \sp{\bar\eta\p{\alpha_+=0} - \f\pi2}
+  + \sp{\f\pi2 - \alpha_-\p{\alpha_+=0}}
+  = \bar\eta\p{\alpha_+=0} - \alpha_-\p{\alpha_+=0} = \theta_2
+\end{align}
+and similarly
+\begin{align}
+  \bar\eta\p{\alpha_+'=0} - \alpha_-'\p{\alpha_+'=0} = \theta_1.
+\end{align}
+Using $\alpha_\pm'$ instead of $\alpha_\pm$ to find $\set{\theta_j}$
+thus amounts to merely relabeling nuclei, which has no physical
+consequence.
+
+\section{Coherent SWAP with a singlet-triplet qubit}
 
@@
 \begin{align}
-  \ket\S &\equiv \f1{\sqrt2}\p{\ket{\u\d}-\ket{\d\u}}, \\
-  \ket\T &\equiv \f1{\sqrt2}\p{\ket{\u\d}+\ket{\d\u}}.
+  \ket\S \equiv \f1{\sqrt2}\p{\ket{\u\d}-\ket{\d\u}},
+  &&  \ket\T \equiv \f1{\sqrt2}\p{\ket{\u\d}+\ket{\d\u}}.
 \end{align}
@@
 \begin{align}
-  \cNOT^{\AC\to\NV} = \cNOT^{1\to\NV}
-\end{align}
-and
-\begin{align}
-  \cNOT^{\NV\to\AC} = \cNOT^{\NV\to2}\cNOT^{\NV\to1}.
+  \cNOT^{\AC\to\NV} = \cNOT^{1\to\NV},
+  && \cNOT^{\NV\to\AC} = \cNOT^{\NV\to2}\cNOT^{\NV\to1}.
 \end{align}
@@
 
-\subsection{Robustness against noise}
+\section{Robustness against noise}
 
@@
 
-\section{Simulations and Results}
-
-\subsection{Abundance of larmor pairs}
+\section{Abundance of larmor pairs}
 
@@
 
-\subsection{SWAP fidelities via AXY-$n$}
+\section{SWAP fidelities via AXY-$n$}
 
-Discuss simulations and any relevant nuances therein. Present
-histograms of $\SWAP^{\NV,\ST}$ fidelities and net operation times.
-
-Note: the same simulations can also be used to generate similar
-histograms (as well as other info) about other operations,
-e.g. single-spin $\SWAP$ or $i\SWAP$ operations. Furthermore, the
-simulations can, without any modification, reproduce results such as
-Figure 2 in \cite{wang2016positioning} (``Positioning Nuclear Spins in
-Interacting Clusters for Quantum Technologies and
-Bio-imaging''). Minor additions to the codes might make them useful
-for comparing the efficacy of different spin-addressing protocols. Is
-there any interest in doing any of these things (for this paper or
-elsewhere)?
-
-\section{Conclusions}
-
-\section{Acknowledgments}
+\fixme{Discuss simulations and any relevant nuances therein. Present
+  histograms of $\SWAP^{\NV,\ST}$ fidelities and net operation times.}
 
@@
 \end{document}
-
-notes:
-
-prove DFS
-
-how to locate spins?
-- identify larmor frequencies for C-13 nuclei
-- identify a frequency with two spins
-- locate two spins
-
-perform elementary gate on one spin
-implement PRX gates

### 2017-08-11 swap-nvst-paper/paper.tex
added actual paper

--- 2016-08-20 swap-nvst-paper/paper.tex
@@
-\documentclass[twocolumn]{revtex4-1}
+%% LyX 2.0.6 created this file. For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
+\documentclass[twocolumn,prl,aps,twocolumn]{revtex4-1}
+\setcounter{secnumdepth}{3}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\usepackage{esint}
+\usepackage[unicode=true,pdfusetitle,
+ bookmarks=false,
+ breaklinks=false,pdfborder={0 0 1},backref=false,colorlinks=false]
+ {hyperref}
+\hypersetup{
+ bookmarksnumbered=false,bookmarksopen=false}
 
-% \usepackage{showframe}
+\makeatletter
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
+\@ifundefined{textcolor}{}
+{%
+ \definecolor{BLACK}{gray}{0}
+ \definecolor{WHITE}{gray}{1}
+ \definecolor{RED}{rgb}{1,0,0}
+ \definecolor{GREEN}{rgb}{0,1,0}
+ \definecolor{BLUE}{rgb}{0,0,1}
+ \definecolor{CYAN}{cmyk}{1,0,0,0}
+ \definecolor{MAGENTA}{cmyk}{0,1,0,0}
+ \definecolor{YELLOW}{cmyk}{0,0,1,0}
+}
 
-\usepackage{hyperref} % for linking references
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+\usepackage{color}
+\usepackage{soul}
+\newcommand{\note}[1]{\textcolor{blue}{(#1)}}
+\newcommand{\MP}[1]{\textcolor{magenta}{#1}}
+\newcommand{\wzy}[1]{\textcolor{red}{#1}}
 
-%%% math, symbols, etc.
-\usepackage{physics,braket,bm}
-\renewcommand{\t}{\text} % text in math mode
-\newcommand{\f}[2]{\dfrac{#1}{#2}} % shorthand for fractions
-\newcommand{\p}[1]{\left(#1\right)} % square parenthesis
-\renewcommand{\sp}[1]{\left[#1\right]} % square parenthesis
-\renewcommand{\set}[1]{\left\{#1\right\}} % curly parenthesis
-\renewcommand{\v}{\bm} % bold vectors
-\newcommand{\uv}[1]{\hat{\v{#1}}} % unit vectors
-\renewcommand{\c}{\cdot} % inner product
-\newcommand{\bk}{\Braket} % shorthand for braket notation
+\newcommand{\CNV}{$^{13}$C }
 
-% shorthand for frequently used commands
-\renewcommand{\u}{\uparrow}
-\renewcommand{\d}{\downarrow}
-\newcommand{\SWAP}{\t{SWAP}}
-\newcommand{\cNOT}{\t{cNOT}}
-\newcommand{\NV}{\t{NV}}
-\newcommand{\AC}{\t{AC}}
-\newcommand{\ST}{\t{ST}}
-\renewcommand{\S}{\t{S}}
-\newcommand{\T}{\t{T}}
-\newcommand{\R}{\mathcal R}
-
-%%% figures
-\usepackage{graphicx,grffile,float} % floats, etc.
-\usepackage{multirow} % multirow entries in tables
-\usepackage{footnote} % footnotes in floating objects
-\usepackage[font=small,labelfont=bf]{caption} % caption text options
-
-%%% markup
-\usepackage{color,soul} % text color and other editing options
-% \ul{underline}, \st{strikethrough}, and \hl{highlight}
-\newcommand{\fixme}[1]{{\bf \color{red} fixme: #1}}
+\makeatother
 
@@
 
-\title{Realization of a Decoherence-Free Subspace with
-  Nitrogen-Vacancy Centers and $^{13}$C Nuclear Spins}
+\title{Controlling Spectrally-indistinguishable Nuclear Spins \\ for a
+  Decoherence-Free Subspace}
 
-\author{Michael A. Perlin, Zhen-Yu Wang, Jorge Casanova, and Martin B. Plenio}
+\author{Michael A. Perlin}
+\affiliation{Institut f\"ur Theoretische Physik and IQST, Albert-Einstein-Allee
+11, Universit\"at Ulm, D-89069 Ulm, Germany}
 
-\affiliation{Institut f\"ur Theoretische Physik, Albert-Einstein-Allee
+\author{Zhen-Yu Wang}
+\email{zhenyu3cn@gmail.com}
+\affiliation{Institut f\"ur Theoretische Physik and IQST, Albert-Einstein-Allee
+11, Universit\"at Ulm, D-89069 Ulm, Germany}
+
+\author{Jorge Casanova}
+\affiliation{Institut f\"ur Theoretische Physik and IQST, Albert-Einstein-Allee
+11, Universit\"at Ulm, D-89069 Ulm, Germany}
+
+\author{Martin. B. Plenio}
+\affiliation{Institut f\"ur Theoretische Physik and IQST, Albert-Einstein-Allee
 11, Universit\"at Ulm, D-89069 Ulm, Germany}
@@
 \begin{abstract}
-  Here is the abstract.
+  Close nuclear spins with identical precession frequencies have the
+  remarkable property of feeling the same magnetic noise, which makes
+  them exceptional candidates for constructing a decoherence-free
+  subspace (DFS). However, selective control of such nuclei is not
+  possible with existing methods based on spectroscopic
+  discrimination. We overcome this obstacle and present a protocol for
+  storage and retrieval of quantum information from a DFS. We
+  demonstrate the efficacy of our protocol with detailed numerical
+  simulations of a nitrogen-vacancy (NV) center with nearby \CNV
+  nuclei, and show that the resulting DFS is immune to NV magnetic
+  noise and external magnetic field drifts.
 \end{abstract}
-
 \maketitle
 
-\section{Introduction}
+\emph{Introduction.}~-- Quantum spins in a solid-state platform are
+natural and reliable quantum resources for performing tasks such as
+information processing, simulations, and nano-scale
+sensing~\cite{Zhong2015Optically, Doherty2013Nitrogen,
+  Dobrovitski2013Quantum, Schirhagl2014Nitrogen}. A particularly
+promising platform containing such resources is the nitrogen-vacancy
+(NV) center in diamond~\cite{Doherty2013Nitrogen,
+  Dobrovitski2013Quantum, Schirhagl2014Nitrogen}. \MP{At room
+  temperature, the electron spin of an NV center has a $T_1$-limited
+  lifetime on the order of milliseconds, as $T_2$ decoherence
+  processes can be suppressed via dynamical decoupling
+  techniques~\cite{Jarmola12, vanderSar12}. During this time, the
+  electron spin can be polarized, detected, and coherently manipulated
+  with high fidelity via optical fields and microwave
+  radiation~\cite{Taminiau14}. By working at lower temperatures and
+  high purity diamond samples, the electron spin lifetime can be
+  extended upwards to seconds~\cite{Gill13}.}
+% old text here: At room temperature, the electron spins of NV centers
+% have coherence times on the order of milliseconds, and can be
+% polarized, detected, and coherently manipulated with high fidelity
+% via optical fields and microwave radiation~\cite{Jarmola12,
+% vanderSar12, Taminiau14}. By working at lower temperatures and
+% employing dynamical decoupling techniques, these coherence times can
+% be extended upwards to seconds~\cite{Gill13}.
+Furthermore, the NV electron spin can be selectively coupled to nearby
+\CNV nuclear spins by appropriately controlling individual
+electron-nuclear hyperfine interactions. In this manner, nuclear spins
+can be individually addressed and manipulated via the NV center when
+they have distinct precession frequencies $\omega_{j}$, with $j$
+indexing a particular nucleus. These distinctions are a consequence of
+the energy shifts produced by the components $A_{j}^{\parallel}$ of
+the hyperfine field parallel to the NV symmetry axis at the location
+of the each nucleus~\cite{Kolkowitz2012Sensing,Taminiau2012Detection,
+  Zhao2012Sensing}. Individual addressing allows for the realization
+of noise-resilient quantum gates~\cite{Liu2013Noise}, quantum error
+correcting codes~\cite{Taminiau2014Universal, Waldherr2014Quantum},
+quantum computing~\cite{Casanova2016Noise}, and quantum simulation
+protocols~\cite{Cai2013Large} in the hybrid system of a NV center and
+its surrounding nuclei. In addition, the NV electron spin provides an
+optical interface to entangle spins with
+photons~\cite{Togan2010Quantum}, which together with the available
+nuclear memory establishes a key prerequisite for scalable quantum
+architectures~\cite{Nemoto2014Photonic}. To this end, recent
+remarkable experiments have established photon-mediated entanglement
+between distant NV quantum-network
+nodes~\cite{Bernien2013Entanglement,
+  Pfaff2014Unconditional,Hensen2015Loophole}, as well as entanglement
+distillation on entangled spin qubits~\cite{Kalb2016Entanglement}.
 
-\fixme{Write about NV centers, C-13 nuclei, introduction to larmor
-  pairs and DFS, quantum memory/networks, etc.}
+% todo: insert citations 24, 31, and 32 into first paragraph
 
-Nitrogen-vacancy (NV) centers in diamond have been recognized in
-recent years as a promising platform for quantum sensing and quantum
-information technologies\cite{mamin2013nanoscale, steinert2010high,
-  wang2016positioning, chou2015optimal, childress2006fault,
-  yao2012scalable}. The electronic ground and optically excited states
-of NV$^-$ split into spin triplets which can be polarized, detected,
-and coherently manipulated with high fidelity with fields and
-microwave radiation \cite{dobrovitski2013quantum}. Hyperfine coupling
-between the NV center electron and $^{13}$C nuclei in bulk diamond
-allows for the coherent control and measurement of individual nuclear
-spins, and the realization of universal set of high-fidelity quantum
-gates \cite{dobrovitski2013quantum, casanova2016noise}.
+\begin{figure}[t!]
+  \includegraphics[width=0.95\columnwidth]{FigDrawing}
+  \caption{(Color online) (a) Energy splittings of bare, DPS, and DFS
+    qubit states. (b) A pair of \CNV nuclear spins located in a
+    symmetric configuration about the NV center have the same parallel
+    and perpendicular components of the hyperfine field. (c)
+    Perpendicular hyperfine components of the spin pair in (b) and the
+    effective direction of a RF field. (d) Polar plot of the NV
+    transition signal (red solid line) with respect to the RF phase
+    $\phi_{{\rm RF}}$. Dashed lines show the polar plots of single
+    spin signals, and the gray solid circle is the single spin signal
+    without RF control.}
+\label{fig:Drawing}
+\end{figure}
 
-One promising application of the NV center is as a memory register for
-storing quantum information. While typical control operations on the
-NV electron spin happen on the scale of nanoseconds, its
-room-temperature coherence time is on the scale of microseconds
-\cite{dobrovitski2013quantum}. Dynamic decoupling schemes and the use
-of isotopically pure diamond samples can increase the NV electron spin
-coherence time by a few orders of magnitude
-\cite{ryan2010robust}. Storing quantum information in the NV electron
-spin itself, however, reserves a valuable resource, as the center
-could otherwise be used to address nuclear spins and other quantum
-processing resources. The weaker environmental coupling of $^{13}$C
-nuclei present in diamond yields much longer coherence times than that
-of the NV electron spin, and by entangling multiple nuclear spins,
-e.g. into the singlet-triplet states
-$\p{\ket{\u\d}\pm\ket{\d\u}}/\sqrt2$, it is possible to generate
-logical qubits which are protected from various sources of system and
-environmental dephasing noise.
+Although strong electron-nuclear hyperfine interactions are generally
+desirable for fast and reliable nuclear spin control via the NV
+center, these strong interactions can also dephase the nuclear
+spins~\cite{Maurer2012Room} % removed citation for Wang2017Delayed
+due to, for example, electron spin relaxation. More specifically, the
+electron undergoes stochastic spin flips ($T_1$ processes), thereby
+acting as a source of magnetic noise for the nuclear spins. This noise
+is most severe during the optical initialization and readout of NV
+electrons, as well as during the reset for establishing
+electron-photon entanglement~\cite{Reiserer2016Robust}\MP{, and cannot
+  be suppressed with dynamical decoupling techniques}.
+% Because these NV electron spin flips are much faster than external
+% radio frequency control over nuclei, noise suppression techniques
+% such as dynamical decoupling~\cite{Yang2011Preserving} are incapable
+% of prolonging nuclear spin coherence times.
+Electron spin noise thus limits the use of individual nuclear spins as
+a quantum resource. While nuclear spins with weaker hyperfine coupling
+to the NV center are less sensitive to electron spin flip noise, weak
+coupling also unavoidably implies poor nuclear spin controllability,
+which again limits their utility for quantum memory registers.
 
-In this letter, we present a means to address individual $^{13}$C
-nuclear spins which are normally indistinguishable due to a symmetry
-in their coupling to the NV center. We use this addressing scheme to
-initialize qubits in a decoherence-free subspace (DFS) of nuclear
-spins, and propose a means for realizing a coherent SWAP operation
-between the NV center electron spin state and the DFS qubit.
+By pairing nuclear spins, one can reduce the magnitude of NV electron
+spin noise on individual qubits by constructing decoherence-protected
+subspaces (DPS)~\cite{Reiserer2016Robust} {[}see
+Fig.~\ref{fig:Drawing}(a){]}.  Similar to standard techniques in
+nuclear magnetic resonance (NMR)~\cite{Mehring1983Principle} or
+electron-nuclear double resonance
+(ENDOR)~\cite{Schweiger2001Principles}, current protocols for
+realizing a DPS rely on the distinct nuclear precession frequencies
+$\omega_{j}$ for addressing and control~\cite{Kolkowitz2012Sensing,
+  Taminiau2012Detection, Zhao2012Sensing, Liu2013Noise,
+  London2013Detecting, Taminiau2014Universal, Casanova2015Robust,
+  Wang2016Positioning, Wang2017Delayed}. The logical qubits in a DPS
+are therefore still sensitive to electron spin
+noise~\cite{Reiserer2016Robust}.
 
-\section{Identifying symmetrically coupled $^{13}$C nuclear spins}
+In this work, we address the problem of selectively manipulating
+nuclear spins with identical precession frequencies $\omega_{j}$ by
+combining dynamical decoupling techniques with radio-frequency (RF)
+nuclear spin control. As a result, we are able to construct an
+accessible decoherence-free subspace (DFS) in a solid-state platform,
+and thereby realize robust quantum memory registers which are
+resilient to dephasing processes such as NV initialisation and
+readout. Among the possible applications of this work, we highlight
+storage of the electron spin state into the DFS, leaving the NV center
+free to perform other tasks such as forming entangled quantum
+networks.
 
-Restricting the NV electron spin states to the subspace spanned by
-$\set{\ket0,\ket{m_s}}$ ($m_s=\pm1$), the AXY-$n$ pulse sequence
-developed in by Casanova et al. in \cite{casanova2015robust} and
-control scheme developed by Wang et al. in \cite{wang2016positioning}
-allows addressing individual $^{13}$C nuclear spins via Hamiltonians
-of the form
-\begin{align}
-  H_\t{int} = h_j^\t{int}\sigma_\NV^z\v I_j\c\uv n_j,
-  \label{H_int}
-\end{align}
-for a tunable coupling strength $h_\t{int}$ and direction $\uv n_j$,
-where $\sigma_\NV^z\equiv\op{m_s}-\op{0}$ and $\v I_j$ is the spin
-operator for nuclear spin $j$. The protocol for realizing this
-effective Hamiltonian, however, is conditional on a sufficiently
-unique effective larmor frequency $\omega_j$, i.e. that for all
-$n\ne j$
-\begin{align}
-  \abs{\omega_n-\omega_j} \gg \abs{f_{k_{DD}}\v A_j^\perp},
-\end{align}
-where $f_{k_{DD}}$ is the fourier component of the AXY-$n$ protocol on
-resonance with $\omega_j$ and $\v A_j^\perp$ ($\v A_j^\parallel$) is
-the component of the hyperfine vector $\v A_j$ perpendicular
-(parallel) to the effective larmor precession axis $\uv\omega_j$.
+\emph{Electron-nuclear coupling.}~-- In the typical situation with the
+electron-nuclear flip-flop terms suppressed by a large energy
+mismatch, on the order of GHz in the case of an NV center and nearby
+\CNV nuclei, the hyperfine interactions between the electron and
+nuclear spins reads
+$H_{{\rm hf}}=S_{z}\sum_{j}\vec{A}_{j}\cdot\vec{I}_{j}$, where $S_{z}$
+and $\vec{I}_{j}$ are respectively electron and nuclear spin
+operators. Denoting by $\hat{z}$ a unit vector along the NV symmetry
+axis, the hyperfine fields $\vec{A}_{j}$ can be decomposed into
+parallel and perpendicular components
+$A_{j}^{\parallel}=\vec{A}_{j}\cdot\hat{z}$ and
+$\vec{A}_{j}^{\perp}=\vec{A}_{j}-A_{j}^{\parallel}\hat{z}$. In the
+presence of a static magnetic field $B_{z}\hat{z}$ with strength
+$B_z\gg A_{j}^{\perp}/\gamma_{\rm n}$, where $\gamma_{\rm n}$ is the
+nuclear \CNV gyromagnetic ratio, the perpendicular components
+$\vec{A}_{j}^{\perp}\cdot\vec{I}_{j}=A_{j}^{\perp}I_{j}^{x}$ in
+$H_{{\rm hf}}$ are suppressed, resulting in the coupling (see for
+example~\cite{Maurer2012Room})
+\begin{equation}
+  H_{{\rm hf}} = S_{z}\sum_{j}A_{j}^{\parallel}I_{j}^{z},
+  \label{eq:SzIz}
+\end{equation}
+where $I_{j}^{z}=\vec{I}_{j}\cdot\hat{z}$. While nuclear spins are
+excellent candidates for a quantum memory, uncontrolled electron spin
+flips generate random noise with the strengths $A_{j}^{\parallel}$ on
+the nuclei through the coupling in Eq.~\eqref{eq:SzIz}.
 
-It is possible, however, for two nuclear spins (indexed by 1 and 2) to
-have identical larmor frequencies $\omega_1=\omega_2\equiv\omega$,
-which occurs when both nuclei lie along the edges of a cylinder
-centered on the NV center and oriented along the natural NV axis. We
-call such nuclei {\it larmor pairs}, and their geometry results in
-$A_1^\perp=A_2^\perp\equiv A^\perp$ and
-$A_1^\parallel=A_2^\parallel\equiv A^\parallel$ (see Supplementary
-Information) \fixme{prove in the SI}.
+By pairing nuclear spins, the strength of dephasing noise can be
+diminished to $\delta_{1,2}=A_{1}^{\parallel}-A_{2}^{\parallel}$ in a
+DPS~\cite{Reiserer2016Robust}. Existing protocols for selective spin
+manipulation, however, have gate times on the scale of
+$1/\delta_{1,2}$, which are furthermore bounded from above by the NV
+electron spin coherence time. This restriction is prohibitive for the
+realization of an accessible DFS, which requires $\delta_{1,2}=0$
+{[}see Fig.~\ref{fig:Drawing}(a){]}.
 
-\fixme{Reference \cite{wang2016positioning} for identifying and
-  location nuclei with unique larmor frequencies}
+\emph{Larmor pairs.}~-- Due to symmetries of the diamond lattice, it
+is possible for multiple \CNV nuclear spins to share the same
+hyperfine components $A_{j}^{\parallel}=A^{\parallel}$ and
+$A_{j}^{\perp}=A^{\perp}$. Such nuclei manifestly satisfy the
+necessary conditions for containing a DFS. We refer to exactly two
+\CNV nuclei in such a symmetric configuration {[}see
+Fig.~\ref{fig:Drawing}(b){]} as a \emph{Larmor pair}, and observe
+their relatively large probability of occurrence in an NV system with
+natural \CNV abundance {[}see Fig.~\ref{fig:FigChance}{]}. Because
+$A^{\parallel}$ for the Larmor pair is different from the parallel
+hyperfine field $A_{j}^{\parallel}$ of other spins, we can use our
+recently developed dynamical decoupling
+sequence~\cite{Casanova2015Robust} to selectively couple the NV
+electron to only the Larmor pair, realizing the effective interaction
+Hamiltonian
+\begin{equation}
+  H_{{\rm int}}
+  = \frac{1}{4}f_{k_{{\rm DD}}}A^{\perp}\sigma_{z}(I_{1}^{x}+I_{2}^{x}),
+  \label{eq:Hint}
+\end{equation}
+where $f_{k_{{\rm DD}}}$ is a tunable parameter of the dynamical
+decoupling sequence~\cite{Casanova2015Robust} and $\sigma_{z}$ is an
+electron spin Pauli operator. The Hamiltonian in Eq.~\eqref{eq:Hint}
+generates the entangling gate
+\begin{equation}
+  U_{{\rm int}}(\theta)
+  = \exp\left[-i\theta\sigma_{z}(I_{1}^{x}+I_{2}^{x})\right]
+  \label{eq:Uint}
+\end{equation}
+with an interaction time $4\theta/(f_{k_{{\rm DD}}}A^{\perp})$.
 
-\fixme{Provide derivation for NV coherence when on resonance with the
-  larmor frequency of a larmor pair}
+To find a Larmor pair, we use the recently developed delayed
+entanglement echo (DEE) in \cite{Wang2017Delayed} to find spectrally
+resolvable resonances, and identify the number of nuclear spins within
+them. Having found a Larmor pair, we can measure the corresponding
+hyperfine fields $\vec{A}_{j}^{\perp}$ via our recently developed
+nuclear positioning method in \cite{Wang2016Positioning}. Therein, we
+turn on an external RF magnetic field on resonance with the nuclear
+spin precession frequency. In the rotating frame of the nuclear spin
+precession, the phase of this RF field corresponds to an effective
+static magnetic field direction $\phi_{\rm{RF}}$ in the $x$-$y$ plane
+{[}see Fig.~ \ref{fig:Drawing}(c) and (d){]}. When the effective field
+direction is parallel to $\vec{A}_{j}^{\perp}$, the electron-nuclear
+spin coupling vanishes for spin $j$; an effective field direction not
+parallel to $\vec{A}_{j}^{\perp}$ will simply reduce the magnitude of
+this coupling. By varying the phase of the RF field, one can thus
+measure the positions of both nuclei in the Larmor pair. This
+measurement can be simplified by taking symmetries of the diamond
+lattice into account {[}see Fig.~\ref{fig:Drawing}(d) for the NV
+transition signal in a strong magnetic field{]}. The ambiguity of
+$180^{\circ}$ in Fig.~\ref{fig:Drawing}(d) can be eliminated by
+checking the NV transition signal in the presence of a weak magnetic
+field ($B_{z}\sim A_{j}^{\perp}/\gamma_{{\rm n}}$)
+\cite{Wang2016Positioning}. As we will see, however, resolving this
+ambiguity is not necessary for our protocol.
 
-\fixme{Provide derivation for NV coherence when on resonance with a
-  larmor frequency when applying a control field for both the one- and
-  two-nucleus case}
+\begin{figure}[t!]
+  \includegraphics[width=0.95\columnwidth]{FigChance}
+  \caption{(Color online) Probability to find at least one Larmor pair
+    near the NV electron spin for a natural \CNV abundance of
+    1.1\%. Different markers denote different minimum values of the
+    $A^\perp$, which couples the nuclei to the NV electron spin, and
+    $\Delta_{{\rm min}}^{\parallel}$ is the minimum difference between
+    $A^\parallel$ and the parallel hyperfine field for any other \CNV
+    nucleus in the NV system. Each of spin in the Larmor pair is
+    coupled to other nuclear spins with a strength smaller than
+    $2\pi\times50$ Hz, and the directions of hyperfine fields satisfy
+    the constrain Eq.~\eqref{eq:AngleRange}.  Each data point is
+    obtained via Monte Carlo sampling with $4\times10^{5}$ randomly
+    generated NV systems.}
+\label{fig:FigChance}
+\end{figure}
 
-\fixme{Walk through protocol to identify and locate larmor pairs}
+\emph{Controlling spectrally indistinguishable nuclear spins}. -- The
+symmetry between nuclear spins in Eq.~\eqref{eq:Hint} can be broken by
+a RF control field, allowing for individual control of each nucleus in
+a Larmor pair. Using the technique outlined in
+\cite{Wang2016Positioning}, we can decouple all electron-nuclear
+interactions, and introduce RF control fields targeting the desired
+Larmor pair in a coherence-protected manner to realize the Hamiltonian
+\begin{equation}
+  H_{{\rm RF}}
+  = \vec{\Omega}(\phi_{{\rm RF}})\cdot(\vec{I}_{1}+\vec{I}_{2})
+  = \Omega(I_{1}^{\phi_{{\rm RF}}-\phi_{1}}+I_{2}^{\phi_{{\rm RF}}-\phi_{2}}),
+  \label{eq:Hrf}
+\end{equation}
+where $\phi_{j}$ are the azimuthal angles of the perpendicular
+components of the local hyperfine fields {[}see Fig.~\ref{fig:Drawing}
+(c){]}; $I_{j}^{\phi}=I_{j}^{x}\cos\phi+I_{j}^{y}\sin\phi$; and
+$\Omega$, $\phi_{{\rm RF}}$ are respectively the Rabi frequency and
+phase of the RF drive. Note that the spin operators $I_{j}^{x}$ are
+quantized along the azimuthal directions of their respective local
+hyperfine fields $\vec{A}_{j}^{\perp}$. By combining the non-selective
+control of $H_{{\rm RF}}$ and $H_{{\rm int}}$, we can selectively
+address only one of the two nuclei in the Larmor pair. Without loss of
+the generality, we let the index $j=1$ for the target nucleus.
 
-\section{Individually addressing nuclei in larmor pairs}
+The control in Eq.~\eqref{eq:Hrf} allows us to apply $\pi$ pulses on
+both nuclei simultaneously by applying the RF drive for a time
+$\pi/\Omega$. Using $\phi_{{\rm RF}}=\phi_{2}+\pi/2$ and defining
+$\alpha=\phi_{2}-\phi_{1}+\frac{\pi}{2}$, we can thus generate the
+gate
+\begin{equation}
+  U_{\pi} = \exp(i\pi I_{2}^{y})\exp(i\pi I_{1}^{\alpha}).
+  \label{eq:Upi}
+\end{equation}
+One can then show that the sequence
+\begin{equation}
+  U_{{\rm DEE}}
+  = U_{{\rm int}}(\theta)U_{\pi}U_{{\rm int}}(\theta)
+\end{equation}
+leads to the evolution $U_{{\rm DEE}}=\exp(i\pi I_{2}^{y})U_{1}$,
+where
+\begin{equation}
+  U_{1} = e^{-i\theta\sigma_{z}I_{1}^{x}}e^{i\pi I_{1}^{\alpha}}
+  e^{-i\theta\sigma_{z}I_{1}^{x}}
+\end{equation}
+entangles only the target nucleus with the NV electron. We can cancel
+the single-qubit operation on the second spin by repeating the
+sequence $U_{{\rm DEE}}$ twice to get
+\begin{eqnarray}
+  U_{{\rm DEE}}^{2}
+  & = & -2i(r_{x}I_{1}^{\alpha}+r_{y}I_{1}^{\alpha_{\perp}})\sigma_{z}
+        \nonumber \\
+  &  & +\cos^{2}\theta-\cos(2\alpha)\sin^{2}\theta,
+       \label{eq:Udee}
+\end{eqnarray}
+where we define
+$r_{x}=2\cos\alpha\sin\theta
+\left[\cos^{2}\alpha\cos\theta+\sin^{2}\alpha\right]$;
+$r_{y}=4\cos^{2}\alpha\sin\alpha\sin\theta\sin^{2}(\frac{\theta}{2})$;
+and $\alpha_{\perp}=\alpha+\pi/2$. The last line of
+Eq.~\eqref{eq:Udee} vanishes when
+\begin{equation}
+  \cos^{2}\alpha\sin^{2}\theta=\frac{1}{2},
+  \label{eq:PiPulseCondition}
+\end{equation}
+which can be satisfied by choosing a suitable value of $\theta$ if
+\begin{equation}
+  \left|\sin(\phi_{2}-\phi_{1})\right|\ge1/\sqrt{2}.
+  \label{eq:AngleRange}
+\end{equation}
+While we will work within the constraint of Eq.~\eqref{eq:AngleRange},
+we note that it is possible to relax this constraint by applying
+additional repetitions of $U_{{\rm DEE}}$. By using a value of
+$\theta$ which satisfies Eq.~\eqref{eq:PiPulseCondition}, we can
+implement a selective $\pi$ rotation $R_{\pi}$ on the target spin
+along a direction perpendicular to $\hat{z}$ by applying
+$U_{{\rm DEE}}^2$ followed by a $\sigma_z$ gate on the electron spin,
+i.e.
+\begin{equation}
+  R_{\pi} = \sigma_{z}U_{{\rm DEE}}^{2} = \exp(-i\pi I_{1}^{\beta}),
+  \label{eq:PiPulse}
+\end{equation}
+where the azimuthal angle $\beta$ can be determined from
+Eqs.~\eqref{eq:Udee} and \eqref{eq:PiPulseCondition}. From
+Eq.~\eqref{eq:Udee} and the definition of $\alpha$, we can see that
+the ambiguity of $\pi$ in $\phi_{1}$ and $\phi_{2}$
+[Fig.~\ref{fig:Drawing}(d)] is inconsequential as it merely introduces
+a possible global phase in the nuclear spin gate
+Eq.~\eqref{eq:PiPulse}. Using Eq.~\eqref{eq:PiPulse}, we can implement
+a selective controlled phase gate on only one spin in a Larmor pair,
+such as
+\begin{equation}
+  U_{{\rm ent}}
+  = (i\sigma_{x}R_{\pi}e^{-iH_{{\rm hf}}\tau})^{2}
+  = \exp(-2i\tau A_{1}^{\parallel}I_{1}^{z}),
+\end{equation}
+which borrows the idea from DEE of having two blocks of control-free
+evolution $e^{-iH_{{\rm hf}}\tau}$ driven by Eq.~\eqref{eq:SzIz}.
 
-When trying to address one spin in a larmor pair, the protocols for
-(\ref{H_int}) will simultaneously couple $\sigma_\NV^z$ to both
-$\v I_1\c\uv n_1$ and $\v I_2\c\uv n_2$ with identical coupling
-strength ($h_\t{int}$). So long as $\uv n_1$ and $\uv n_2$
-(equivalently, $\v A_1^\perp$ and $\v A_2^\perp$) are not parallel,
-however, it is possible to address only one of these spins at a time
-by applying additional control fields. In particular, the application
-of a magnetic decoupling field
-$\v B_\t{dec}^{\p\omega}\p{t}=\v B_\t{dec}\cos\p{\omega
-  t-\phi_\t{dec}}$ during the AXY-$n$ addressing protocol suppresses
-components of $\uv n_j$ which are perpendicular to the vector
-$\v B_\t{dec}$ projected onto the plane perpendicular to $\v\omega_j$
-and rotated about the axis $\uv\omega_j$ by the angle
-$\phi_\t{dec}$. One can therefore choose a direction $\v B_\t{dec}$
-which completely suppresses NV electron spin coupling to spin 1 (2),
-leaving only coupling to spin 2 (1).
+\begin{figure}[t!]
+  \includegraphics[width=0.95\columnwidth]{FigCoherence}
+  \caption{(Color online) Coherence of the Larmor pair, initialized in
+    the superposition state
+    $(1/\sqrt{2})\left(|\uparrow_{1}\downarrow_{2}\rangle
+      +|\downarrow_{1}\uparrow_{2}\rangle\right)$, as a function of
+    optical illumination periods ($N$). In each $10~\mu$s period, we
+    apply a $\pi$ pulse on the electron spin to simulate gate
+    operations on the electron spin, which can affect the
+    electron-nuclear spin dynamics. Blue spheres are the case of a DPS
+    with $\omega_{1}-\omega_{2}=2\pi\times6.7$ kHz, while red squares
+    are the case of a DFS.}
+  \label{fig:FigCoherence}
+\end{figure}
 
-\fixme{Give more information or details about this protocol? Reference
-  SI}
+We performed numerical simulations to demonstrate the high fidelity of
+our selective control in Eq.~\eqref{eq:PiPulse}. In these simulations,
+we consider a Larmor pair positioned on a diamond lattice at
+$[0.1785,0.1785,1.071]$ nm and $[0.1785,1.071,0.1785]$ nm relative to
+the NV defect location, each at a distance of approximately $1.1$ nm
+from the NV electron. A magnetic field of $B_{z}=0.4$ T is applied
+along the NV axis $\hat{z}=[1,1,1]/\sqrt{3}$. The two nuclear spins
+have identical hyperfine components $A^{\parallel}=2\pi\times10.2$ kHz
+and $A^{\perp}=2\pi\times22.2$ kHz. to realise the sequence in
+Eq.~\eqref{eq:PiPulse}, we use adaptive-XY-8 (AXY-8) sequences working
+at the $17$-th harmonic to generate the interaction of
+Eq.~\eqref{eq:Hint} in a robust manner. The entire protocol, during
+which the electron spin coherence is protected by the AXY-8 sequence,
+takes $\approx 504~\mu$s. Our numerical simulations include 1208
+microwave $\pi$ pulses, each with a duration of 25 ns, while to meet
+with realistic experimental conditions we considered a 1$\%$ amplitude
+and $2\pi\times2.162$ MHz detuning errors for these pulses. Under
+these conditions, we achieve a fidelity of 0.994.
 
-\section{Qubit initialization in a decoherence-free subspace}
+\emph{Nuclear spin DFS in solids.}~-- Using selective control on each
+of the spins in the Larmor pair, we can construct a DFS
+$\{|\uparrow_{1}\downarrow_{2}\rangle,
+|\downarrow_{1}\uparrow_{2}\rangle\}$ in their joint Hilbert
+space. The coherence of the state in the DFS is insensitive to optical
+and microwave control on the NV electron spin, yielding much longer
+coherence times than the case of a DPS, as shown in
+Fig.~\ref{fig:FigCoherence}.
 
-\fixme{Implement PRX\cite{reiserer2016robust} methods for initializing
-  a qubit in $\ket{\u\d}\pm\ket{\d\u}$}
+One can initialize the Larmor pair into the state
+$|\uparrow_{1}\downarrow_{2}\rangle$ within the DFS by first
+polarizing the nuclear spins to $|\downarrow_{1}\downarrow_{2}\rangle$
+via either SWAP operations with the NV electron spin or dynamical
+nuclear polarization, and then using the nuclear-selective $\pi$
+rotation in Eq.~\eqref{eq:PiPulse} to flip the first spin. Below, we
+describe protocols for quantum information storage in and retrieval
+from the DFS.
 
-The state space of larmor pairs contains a subspace free of
-decoherence via spin coupling to the NV center electron, i.e. a
-decoherence-free subspace (DFS). This DFS is spanned by the
-singlet-triplet states $\p{\ket{\u\d}\pm\ket{\d\u}}/\sqrt2$, or
-equivalently by $\ket{\u\d}$ and $\ket{\d\u}$. \fixme{prove that this
-  subspace is decoherence-free in the SI} The protocols for addressing
-an individual nucleus in a larmor pair can be used to initialize a
-qubit in this DFS. In particular, one can use the gate sequences in
-\cite{reiserer2016robust} to deterministically initialize the larmor
-pair into $\ket{\d\d}$, then probabilistically convert this state into
-$\p{\ket{\u\d}+e^{i\phi}\ket{\d\u}}/\sqrt2$ for some phase $\phi$
-determined by the choice of bases for the nuclear spins. While the
-sequences to initialize into $\ket{\d\d}$ require individually
-addressing each nuclear spin, the conversion
-$\ket{\d\d}\to\p{\ket{\u\d}+e^{i\phi}\ket{\d\u}}/\sqrt2$ can be
-performed with simultaneous coupling to both larmor pairs,
-i.e. without the magnetic decoupling field.
+\emph{Storing the electron spin state in a DFS}. -- A general quantum
+state $c_{0}|0\rangle+c_{1}|1\rangle$ of the electron spin can be
+stored in a DFS by the following steps. With the Larmor pair
+initialized to $|\uparrow_{1}\downarrow_{2}\rangle$, we apply the
+conditional evolution $U_{{\rm int}}(\frac{\pi}{2})$
+{[}Eq.~\eqref{eq:Uint}{]} to achieve the entangled electron-nuclear
+spin state
+$c_{0}|0\rangle|y_{1}^{-}y_{2}^{+}\rangle -
+c_{1}|1\rangle|y_{1}^{+}y_{2}^{-}\rangle$, where $|y_{j}^{\pm}\rangle$
+denotes $\exp(\pm i\frac{\pi}{2}I_{j}^{x})|\downarrow_{j}\rangle$.
+Then we apply a $\pi/2$ pulse on the electron spin followed by a
+projective measurement on the NV electron to get
+$|0\rangle\left(c_{0}|y_{1}^{-}y_{2}^{+}\rangle +
+  c_{1}|y_{1}^{+}y_{2}^{-}\rangle\right)$ or
+$|1\rangle\left(c_{0}|y_{1}^{-}y_{2}^{+}\rangle -
+  c_{1}|y_{1}^{+}y_{2}^{-}\rangle\right)$. The optical readout
+subsequently polarizes the NV to the state
+$|0\rangle$~\cite{Reiserer2016Robust}. Finally, we apply the
+conditional evolution $U_{{\rm int}}(\frac{\pi}{2})$ to get
+$c_{0}|\uparrow_{1}\downarrow_{2}\rangle +
+c_{1}|\downarrow_{1}\uparrow_{2}\rangle$ if the previous measurement
+outcome was $m_{s}=0$, or
+$c_{0}|\uparrow_{1}\downarrow_{2}\rangle -
+c_{1}|\downarrow_{1}\uparrow_{2}\rangle$ if it was $m_{s}=1$.
 
-\section{Coherent SWAP operation with DFS qubit}
+\emph{Retrieval of a quantum state from the DFS}. -- To retrieve the
+quantum information stored in the DFS, say,
+$c_{0}|\uparrow_{1}\downarrow_{2}\rangle +
+c_{1}|\downarrow_{1}\uparrow_{2}\rangle$, we can use the following
+steps: (i) We apply a selective $\pi$ rotation via
+Eq.~\eqref{eq:PiPulse} to flip the first spin and get
+$c_{0}|\uparrow_{1}\uparrow_{2}\rangle +
+c_{1}|\downarrow_{1}\downarrow_{2}\rangle$. (ii) We initialize the
+electron spin state to the superposition
+$|x_{e}^{+}\rangle=\left(|0\rangle+|1\rangle\right)/\sqrt{2}$. (iii)
+We apply a standard DEE protocol as in Ref.~\cite{Wang2017Delayed} to
+achieve the interaction
+$A^{\parallel}\sigma_{z}(I_{1}^{z}+I_{2}^{z})$, which implements a
+conditional phase gate on the electron spin and yields
+$c_{0}|y_{e}^{+}\rangle|\uparrow_{1}\uparrow_{2}\rangle +
+c_{1}|y_{e}^{-}\rangle|\downarrow_{1}\downarrow_{2}\rangle$, where
+$|y_{e}^{\pm}\rangle = \exp(\mp
+i\frac{\pi}{4}\sigma_{z})|x_{e}^{+}\rangle$. (iv) We apply a $\pi/2$
+pulse on the electron spin to get
+$c_{0}|0\rangle|\uparrow_{1}\uparrow_{2}\rangle -
+c_{1}|1\rangle|\downarrow_{1}\downarrow_{2}\rangle$. (v) Finally, we
+use the conditional evolution $U_{{\rm int}}(\frac{\pi}{2})$
+{[}Eq.~\eqref{eq:Uint}{]} to retrieve the state as
+$\left(c_{0}|0\rangle+c_{1}|1\rangle\right)|x_{1}^{+}x_{2}^{+}\rangle$,
+where the nuclear spin states can be reset to the state
+$|\uparrow_{1}\downarrow_{2}\rangle$ in the DFS by a $\pi$ pulse as in
+Eq.~\eqref{eq:PiPulse}.
 
-\bibliography{\jobname}
+\emph{Conclusions}. -- We proposed a scheme to selectively address
+nuclear spins that have identical hyperfine field components and
+Larmor precession frequencies. By using this scheme, we construct a
+decoherence-free subspace of nuclear spin states for reliable quantum
+storage in a solid-state platform, even in the presence of the noisy
+NV center electron spin dynamics. We provided a protocol to store
+quantum states of the NV electron in the DFS, and a complementary
+protocol to retrieve a quantum state from the DFS back into the NV
+electron spin. Our methods are general and can be applied to other
+color centers such as silicon carbide. Our results are useful for
+building robust optical interfaces for quantum networks and the
+realization of DFS quantum information processing, as well as in
+quantum sensing.
 
-\pagebreak
-\clearpage
-\widetext
-\makeatletter
+\begin{thebibliography}{10}
+\bibitem{Zhong2015Optically}M. Zhong, M. P. Hedges, R. L. Ahlefeldt,
+J. G. Bartholomew, S. E. Beavan, S. M. Wittig, J. J. Longdell, and
+M. J. Sellars, Optically addressable nuclear spins in a solid with
+a six-hour coherence time, Nature (London) \textbf{517}, 177 (2015).
+
+\bibitem{Doherty2013Nitrogen}M. W. Doherty, N. B. Manson, Paul Delaney,
+F. Jelezko, J. Wrachtrup, and L. C. L. Hollenberg, The nitrogen-vacancy
+colour centre in diamond, Phys. Rep. \textbf{528}, 1 (2013).
+
+\bibitem{Dobrovitski2013Quantum}V. V. Dobrovitski, G. D. Fuchs, A.
+L. Falk, C. Santori, and D. D. Awschalom, Quantum control over single
+spins in diamond, Annu. Rev. Condens. Matter Phys. \textbf{4}, 23
+(2013).
+
+\bibitem{Schirhagl2014Nitrogen}R. Schirhagl, K. Chang, M. Loretz,
+and C. L. Degen, Nitrogen-vacancy centres in diamond: nanoscale sensors
+for physics and biology, Annu. Rev. Phys. Chem. \textbf{65}, 83 (2014).
+
+\bibitem{Jarmola12} A.
+Jarmola, V.
+M.
+Acosta, K.
+Jensen, S.
+Chemerisov, and D.
+Budker, Temperature- and Magnetic-Field-Dependent Longitudinal Spin Relaxation in Nitrogen-Vacancy Ensembles in Diamond, Phys.
+Rev.
+Lett.
+\textbf{108}, 197601 (2012).
+
+\bibitem{vanderSar12} T.
+van der Sar, Z.
+H.
+Wang, M.
+S.
+Blok, H.
+Bernien,	T.
+H.
+Taminiau, D.
+M.
+Toyli, D.
+A.
+Lidar, D.
+D.
+Awschalom, R.
+Hanson, and V.
+V.
+Dobrovitski, Decoherence-protected quantum gates for a hybrid solid-state spin register, Nature \textbf{484}, 82 (2012).
+
+\bibitem{Taminiau14} T. H. Taminiau, J. Cramer, T. van der Sar, V. V. Dobrovitski, and R. Hanson, Universal control and error correction in
+multi-qubit spin registers in diamond, Nature Nanotech. \textbf{9}, 171 (2014).
+
+\bibitem{Gill13} N. Bar-Gill, L. M. Pham, A. Jarmola, D. Budker, and R.L. Walsworth, Solid-state electronic spin coherence time approaching one second, Nat. Commun. \textbf{4}, 1743 (2013).
+
+\bibitem{Kolkowitz2012Sensing}S. Kolkowitz, Q. P. Unterreithmeier,
+S. D. Bennett, and M. D. Lukin, Sensing distant nuclear spins with
+a single electron spin, Phys. Rev. Lett. \textbf{109,} 137601 (2012).
+
+\bibitem{Taminiau2012Detection}T. H. Taminiau, J. J. T. Wagenaar,
+T. van der Sar, F. Jelezko, V. V. Dobrovitski, and R. Hanson, Detection
+and Control of Individual Nuclear Spins Using a Weakly Coupled Electron
+Spin, Phys. Rev. Lett. \textbf{109}, 137602 (2012).
+
+\bibitem{Zhao2012Sensing}N. Zhao, J. Honert, B. Schmidt, M. Klas,
+J. Isoya, M. Markham, D. Twitchen, F. Jelezko, R.-B. Liu, H. Fedder,
+and J. Wrachtrup, Sensing single remote nuclear spins, Nat. Nanotechnol.
+\textbf{7}, 657 (2012).
+
+\bibitem{Liu2013Noise}G.-Q. Liu, H. C. Po, J. Du, R.-B. Liu, and
+X.-Y. Pan, Noise-resilient quantum evolution steered by dynamical
+decoupling, Nat. Commun. \textbf{4}, 2254 (2013).
+
+\bibitem{Taminiau2014Universal}T. H. Taminiau, J. Cramer, T. van
+der Sar, V. V. Dobrovitski, and R. Hanson, Universal control and error
+correction in multi-qubit spin registers in diamond, Nat. Nanotechnol.
+\textbf{9}, 171 (2014).
+
+\bibitem{Waldherr2014Quantum}G. Waldherr, Y. Wang, S. Zaiser, M.
+Jamali, T. Schulte-Herbr\"uggen, H. Abe, T. Ohshima, J. Isoya, J. F.
+Du, P. Neumann, and J. Wrachtrup, Quantum Error Correction in a Solid-State
+Hybrid Spin Register, Nature (London) \textbf{506}, 204 (2014).
+
+\bibitem{Casanova2016Noise}J. Casanova, Z.-Y. Wang, and M. B. Plenio,
+Noise-resilient quantum computing with a nitrogen-vacancy center and
+nuclear spins, Phys. Rev. Lett. \textbf{117}, 130502 (2016).
+
+\bibitem{Cai2013Large}J. Cai, A. Retzker, F. Jelezko, and M. B. Plenio,
+A large-scale quantum simulator on a diamond surface at room temperature,
+Nat. Phys. \textbf{9}, 168 (2013).
+
+\bibitem{Togan2010Quantum}E. Togan, Y. Chu, A. S. Trifonov, L. Jiang,
+J. Maze, L. Childress, M. V. G. Dutt, A. S. S\o rensen, P. R. Hemmer,
+A. S. Zibrov, and M. D. Lukin, Quantum entanglement between an optical
+photon and a solid-state spin qubit, Nature \textbf{466}, 730 (2010).
+
+\bibitem{Nemoto2014Photonic}K. Nemoto, M. Trupke, S. J. Devitt, A.
+M. Stephens, B. Scharfenberger, K. Buczak, T. Nobauer, M. S. Everitt,
+J. Schmiedmayer, and W. J. Munro, Photonic Architecture for Scalable
+Quantum Information Processing in Diamond, Phys. Rev. X \textbf{4},
+031022 (2014).
+
+\bibitem{Bernien2013Entanglement}H. Bernien, B. Hensen, W. Pfaff,
+G. Koolstra, M. S. Blok, L. Robledo, T. H. Taminiau, M. Markham, D.
+J. Twitchen, L. Childress, and R. Hanson, Heralded Entanglement between
+Solid-State Qubits Separated by Three Metres, Nature (London) \textbf{497},
+86 (2013).
+
+\bibitem{Pfaff2014Unconditional}W. Pfaff, B. J. Hensen, H. Bernien,
+S. B. van Dam, M. S. Blok, T. H. Taminiau, M. J. Tiggelman, R. N.
+Schouten, M. Markham, D. J. Twitchen, and R. Hanson, Unconditional
+Quantum Teleportation between Distant Solid-State Quantum Bits, Science
+\textbf{345}, 532 (2014).
+
+\bibitem{Hensen2015Loophole}B. Hensen, H. Bernien, A. E. Dr\'eau, A.
+Reiserer, N. Kalb, M. S. Blok, J. Ruitenberg, R. F. L. Vermeulen,
+R. N. Schouten, C. Abell\'an, W. Amaya, V. Pruneri, M. W. Mitchell,
+M. Markham, D. J. Twitchen, D. Elkouss, S. Wehner, T. H. Taminiau,
+and R. Hanson, Loophole-Free Bell Inequality Violation Using Electron
+Spins Separated by 1.3 Kilometres, Nature (London) \textbf{526}, 682
+(2015).
+
+\bibitem{Kalb2016Entanglement}N. Kalb, A. A. Reiserer, P. C. Humphreys,
+J. J. W. Bakermans, S. J. Kamerling, N. H. Nickerson, S. C. Benjamin,
+D. J. Twitchen, M. Markham, R. Hanson, Entanglement Distillation between
+Solid-State Quantum Network Nodes, arXiv:1610.03253.
+
+\bibitem{Maurer2012Room} P. C. Maurer, G. Kucsko, C. Latta, L. Jiang,
+N. Y. Yao, S. D. Bennett, F. Pastawski, D. Hunger, N. Chisholm, M.
+Markham, D. J. Twitchen, J. I. Cirac, and M. D. Lukin, Room-Temperature
+Quantum Bit Memory Exceeding One Second, Science \textbf{336}, 1283
+(2012).
+
+\bibitem{Wang2017Delayed}Z.-Y. Wang, J. Casanova, and M. B. Plenio,
+Delayed entanglement echo for individual control of a large number
+of nuclear spins, Nat. Commun. \textbf{8}, 14660 (2017).
+
+\bibitem{Reiserer2016Robust}A. Reiserer, N. Kalb, M. S. Blok, K.
+J. M. van Bemmelen, T. H. Taminiau, R. Hanson, D. J. Twitchen, and
+M. Markham, Robust Quantum-Network Memory Using Decoherence-Protected
+Subspaces of Nuclear Spins, Phys. Rev. X \textbf{6}, 021040 (2016).
+
+\bibitem{Yang2011Preserving}W. Yang, Z.-Y. Wang, and R.-B. Liu, Preserving
+qubit coherence by dynamical decoupling, Front. Phys. \textbf{6},
+2 (2011).
+
+\bibitem{Rosskopf2016Quantum}T. Rosskopf, J. Zopes, J. M. Boss, C.
+L. Degen, A quantum spectrum analyzer enhanced by a nuclear spin memory,
+arXiv:1610.03253.
+
+\bibitem{Mehring1983Principle}M. Mehring, Principle of High Resolution
+NMR in Solids, Springer (1983).
+
+\bibitem{Schweiger2001Principles}A. Schweiger, and G. Jeschke. Principles
+of Pulse Electron Paramagnetic Resonance, Oxford (2001).
+
+\bibitem{London2013Detecting}P. London, J. Scheuer, J.-M. Cai, I.
+Schwarz, A. Retzker, M. B. Plenio, M. Katagiri, T. Teraji, S. Koizumi,
+J. Isoya, R. Fischer, L. P. McGuinness, B. Naydenov, and F. Jelezko,
+Detecting and Polarizing Nuclear Spins with Double Resonance on a
+Single Electron Spin, Phys. Rev. Lett. \textbf{111}, 067601 (2013).
+
+\bibitem{Casanova2015Robust}J. Casanova, Z.-Y. Wang, J. F. Haase,
+and M. B. Plenio, Robust dynamical decoupling sequences for individual-nuclear-spin
+addressing, Phys. Rev. A \textbf{92}, 042304 (2015).
+
+\bibitem{Wang2016Positioning}Z.-Y. Wang, J. F. Haase, J. Casanova,
+and M. B. Plenio, Positioning nuclear spins in interacting clusters
+for quantum technologies and bioimaging, Phys. Rev. B \textbf{93},
+174104 (2016).
+
+\bibitem{Ma2016Angstrom}W.-L. Ma and R.-B. Liu, Angstrom-Resolution
+Magnetic Resonance Imaging of Single Molecules Via Wave-Function Fingerprints
+of Nuclear Spins, Phys. Rev. Applied \textbf{6}, 024019 (2016).
+
+\end{thebibliography}
+\pagebreak{}\clearpage{}\widetext
+
 \begin{center}
-  \large \bf Supplementary Information for ``\@title''
-\end{center}
-\setcounter{equation}{0}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\setcounter{page}{1}
-\renewcommand{\theequation}{S\arabic{equation}}
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\bibnumfmt}[1]{[S#1]}
-\renewcommand{\citenumfont}[1]{S#1}
+\textbf{\large{{Supplemental Material}}}{\large{ }}
+\par\end{center}{\large \par}
+
+%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
+%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
+\setcounter{equation}{0} \setcounter{figure}{0} \setcounter{table}{0}
+\setcounter{page}{1} \makeatletter \global\long\def\theequation{S\arabic{equation}}
+ \global\long\def\thefigure{S\arabic{figure}}
+ \global\long\def\bibnumfmt#1{[S#1]}
+ \global\long\def\citenumfont#1{S#1}
 
@@
 
-\section{Theory}
+\section{Simulation details}
 
-\subsection{Basic system model}
+In the simulation, the nuclear spins for the DPS are located at
+$\vec{r}_{1}=[0.08925,0.08925,0.80325]$ nm and
+$\vec{r}_{2}=[0.1785,1.071,0.1785]$ nm, giving the hyperfine
+components $A_{1}^{\perp}=2\pi\times55.4$ kHz,
+$A_{2}^{\perp}=2\pi\times22.2$ kHz, and
+$A_{1}^{\parallel}=-2\pi\times16.9$ kHz and
+$A_{2}^{\parallel}=-2\pi\times10.2$ kHz. The nuclear spins for the DFS
+are located at $\vec{r}_{1}=[0.1785,0.1785,1.071]$ nm and
+$\vec{r}_{2}=[0.1785,1.071,0.1785]$ nm, giving the hyperfine
+components $A^{\perp}=2\pi\times22.2$ kHz and
+$A^{\parallel}=2\pi\times10.2$ kHz.
 
-The Hamiltonian of the NV center system in the presence of a strong,
-static magnetic field $\v B$ can be decomposed as
-\begin{align}
-  H_\t{sys} = H_\NV^\t{GS} + H_\t{hf} + H_\t{nZ}  + H_\t{nn},
-\end{align}
-where
-\begin{align}
-  H_\NV^\t{GS} = D\p{\v S\c\uv z}^2 - \gamma_e\v B\c\v S
-\end{align}
-is the ground-state NV electron spin Hamiltonian with zero-field
-splitting $D$, spin-1 operator $\v S$, natural NV axis $\uv z$, and
-electron gyromagnetic ratio $\gamma_e$;
-\begin{align}
-  H_\t{hf} = \sum_j\f{\gamma_e\gamma_j}{4\pi r_j^3}
-  \p{\v S\c\v I_j-3\sp{\v S\c\uv r_j}\sp{\v I_j\c\uv r_j}}
-\end{align}
-is the hyperfine coupling between the NV electron spin (located at the
-origin) and nuclei indexed by $j$ located at $\v r_j$;
-\begin{align}
-  H_\t{nZ} = -\sum_j\gamma_j\v B\c\v I_j
-\end{align}
-is the Zeeman Hamiltonian for nuclei indexed by $j$ with gyromagnetic
-ratio $\gamma_j$ and spin operators $\v I_j$; and
-\begin{align}
-  H_\t{nn} = \sum_{j<k}\f{\gamma_j\gamma_k}{4\pi r_{jk}^3}
-  \p{\v I_j\c\v I_k-3\sp{\v I_j\c\uv r_{jk}}\sp{\v I_k\c\uv r_{jk}}}
-\end{align}
-is the internuclear coupling with $\v r_{jk}\equiv\v r_j-\v r_k$. We
-will hereafter neglect internuclear coupling in all analytical work,
-though we will keep $H_\t{nn}$ in any numerical results.
+In the simulation for Fig.~1 (d), we use a magnetic field $B_{z}=200$
+G and apply the AXY sequence with 200 robust composite pulses (i.e.,
+1000 elementary $\pi$ pulses). The 1st harmonic is used to address the
+nuclear spins, by using $f_{1_{{\rm DD}}}=0.2$. The RF Rabi frequency
+on the nuclear spins is $\Omega=2\pi\times1$ kHz.
 
-Changing into the rotating frame of $H_\NV^\t{GS}$ affects only the
-hyperfine Hamiltonian, which becomes
-\begin{align}
-  \tilde H_\t{hf} = S_z\sum_j \v A_j\c\v I_j,
-\end{align}
-where we define the hyperfine field
-\begin{align}
-  \v A_j = \f{\gamma_e\gamma_j}{4\pi r_j^3}\p{\uv z - 3\sp{\uv
-  r_j\c\uv z}\uv r_j}.
-\end{align}
-The system Hamiltonian is thus
-\begin{align}
-  \tilde H_\t{sys} = S_z\sum_j \v A_j\c\v I_j
-  -\sum_j\gamma_j\v B\c\v I_j.
-\end{align}
-
-When restricted to the subspace of $\set{\ket0,\ket{m_s}}$ with with
-$m_s\in\set{1,-1}$ for the NV electron spin,
-\begin{align}
-  S_z = \f{m_s}2\p{\sigma_\NV^z+\mathbf1},
-\end{align}
-where $\sigma_\NV^z\equiv\op{m_s}-\op{0}$ and
-$\mathbf1\equiv\op{m_s}+\op{0}$. Defining the interaction Hamiltonian
-\begin{align}
-  H_\t{int} = \f12m_s\sigma_\NV^z\sum_j\v A_j\c\v I_j
-\end{align}
-the effective larmor frequency
-\begin{align}
-  \v\omega_j = \gamma_j\v B - \f{m_s}2\v A_j,
-\end{align}
-and the effective Zeeman Hamiltonian
-\begin{align}
-  H_\t{nZ}^\t{eff} = -\sum_j\p{\gamma_j\v B - \f{m_s}2\v A_j}\c\v I_j
-  = -\sum_j\v\omega_j\c\v I_j,
-\end{align}
-the system Hamiltonian can be written as
-\begin{align}
-  \tilde H_\t{sys} = H_\t{int} + H_\t{nZ}^\t{eff}.
-  \label{S_H_sys_int_nZ}
-\end{align}
-
-Moving into the rotating frame of $H_\t{nZ}^\t{eff}$, the entire
-system is described by the Hamiltonian
-\begin{align}
-  \tilde H_\t{int} = \f12m_s\sigma_\NV^z
-  \sum_j\tilde{\v A_j}\p{t}\c\v I_j,
-  \label{S_H_int_no_DD}
-\end{align}
-where $\tilde{\v A_j}\p{t}$ is the vector $\v A_j$ rotated about
-$\uv\omega_j$ by an angle $\omega_jt$. Written explicitly,
-\begin{align}
-  \tilde{\v A_j}\p{t} = \v A_j^\parallel + \v A_j^\perp\cos\p{\omega_jt}
-  + \v A_j^{\perp\perp}\sin\p{\omega_jt},
-  \label{S_A_rot}
-\end{align}
-where
-\begin{align}
-  \v A_j^\parallel\equiv\p{\v A_j\c\uv\omega_j}\uv\omega_j
-\end{align}
-is the projection of $\v A_j$ along $\v \omega_j$,
-\begin{align}
-  \v A_j^\perp\equiv\v A_j-\v A_j^\parallel
-\end{align}
-is the projection of $\v A_j$ onto the plane orthogonal to
-$\v\omega_j$, and
-\begin{align}
-  \v A_j^{\perp\perp}\equiv\uv\omega_j\times\v A_j^\perp
-\end{align}
-is the vector $\v A_j^\perp$ rotated about $\uv\omega_j$ by $\pi/2$.
-
-\subsection{Dynamic decoupling and nuclear spin addressing}
-
-Dynamic decoupling schemes effectively prepend a modulation function
-\begin{align}
-  F\p{t}=\sum_kf_k\cos\p{k\omega_{DD}t-\phi_{DD}}
-\end{align}
-with fundamental frequency $\omega_{DD}$, phase $\phi_{DD}$, and range
-$\set{1,-1}$ to $\sigma_\NV^z$, so that the system Hamiltonian reads
-\begin{align}
-  \tilde H_\t{int} =
-  \f12m_sF\p{t}\sigma_\NV^z\sum_j\tilde{\v A_j}\p{t}\c\v I_j.
-\end{align}
-At a resonance $k_{DD}\omega_{DD}\equiv\omega_r\gg A_j$, the secular
-approximation allows one to neglect $\v A_j^\parallel$ and express
-\begin{align}
-  \tilde H_\t{int} = \f14 f_{k_{DD}} m_s\sigma_\NV^z
-  \sum_{j:\omega_j=\omega_r} A_j^\perp\v I_j\c\uv n_j,
-  \label{S_H_int_resonance}
-\end{align}
-where $\uv n_j$ is a unit vector in the direction of $\v A_j^\perp$
-rotated about $\uv\omega_j$ by $\phi_{DD}$, i.e.
-\begin{align}
-  \uv n_j = \uv A_j^\perp\cos\phi_{DD} +
-  \uv A_j^{\perp\perp}\sin\phi_{DD}.
-\end{align}
-One can concisely write (\ref{S_H_int_resonance}) with
-\begin{align}
-  h_j^\t{int}\equiv f_{k_{DD}}m_sA_j^\perp/4
-\end{align}
-as
-\begin{align}
-  \tilde H_\t{int} = \sum_{j:\omega_j=\omega_r}
-  h_j^\t{int}\sigma_\NV^z\v I_j\c\uv n_j.
-  \label{S_H_int}
-\end{align}
-
-When the harmonics of $F\p{t}$ are off resonance with all $\omega_j$
-and $\omega_{DD}\gg A_j$ for all $j$, the secular approximation allows
-one to neglect $\tilde H_\t{int}$ entirely. In this case, one can
-apply an auxiliary magnetic field
-$\v B_\t{ctl}^{\p\omega}\p{t}=\v
-B_\t{ctl}\cos\p{\omega_\t{ctl}t-\phi_\t{ctl}}$ and shift into the
-rotating frame of $H_\t{nZ}^\t{eff}$, much like the frame shift
-between (\ref{S_H_sys_int_nZ}) and (\ref{S_H_int_no_DD}), to realize
-the Hamiltonian
-\begin{align}
-  \tilde H_\t{sys}^\t{ctl} =
-  -\sum_j\gamma_j\tilde{\v B}_{\t{ctl},j}\p{t}
-  \cos\p{\omega_\t{ctl}t-\phi_\t{ctl}}\c\v I_j,
-\end{align}
-with $\tilde{\v B}_{\t{ctl},j}\p{t}$ defined using $\v B_\t{ctl}$ and
-$\v\omega_j$ the same way that $\tilde{\v A_j}\p{t}$ was defined using
-$\v A_j$ and $\v\omega_j$ in (\ref{S_A_rot}), i.e. as $\v B_\t{ctl}$
-rotated about $\uv\omega_j$ by an angle $\omega_jt$:
-\begin{align}
-  \tilde{\v B}_{\t{ctl},j}\p{t} = \v B_{\t{ctl},j}^\parallel
-  + \v B_{\t{ctl},j}^\perp\cos\p{\omega_jt}
-  + \v B_{\t{ctl},j}^{\perp\perp}\sin\p{\omega_jt},
-\end{align}
-where
-\begin{align}
-  \v B_{\t{ctl},j}^\parallel
-  &\equiv \p{\v B_\t{ctl} \c\uv\omega_j}\uv\omega_j \\
-  \v B_{\t{ctl},j}^\perp
-  &\equiv \v B_\t{ctl} - \v B_{\t{ctl},j}^\parallel \\
-  \v B_{\t{ctl},j}^{\perp\perp}
-  &\equiv \uv\omega_j\times\v B_\t{ctl}^\perp.
-\end{align}
-
-When $\omega_\t{ctl}\gg\gamma_jB_\t{ctl}$, the secular approximation
-allows one to neglect $\v B_{\t{ctl},j}^\parallel$ and express
-\begin{align}
-  \tilde H_\t{ctl} = -\f12\sum_{j:\omega_j=\omega_\t{ctl}}
-  \gamma_jB_{\t{ctl},j}^\perp \v I_j\c\uv m_j,
-  \label{S_H_ctl_resonance}
-\end{align}
-where $\uv m_j$ is the direction of $\v B_{\t{ctl},j}^\perp$ rotated
-about $\uv\omega_j$ by $\phi_\t{ctl}$, i.e.
-\begin{align}
-  \uv m_j = \uv B_{\t{ctl},j}^\perp\cos\phi_\t{ctl} +
-  \uv B_{\t{ctl},j}^{\perp\perp}\sin\phi_\t{ctl}.
-\end{align}
-One can concisely write (\ref{S_H_ctl_resonance}) with
-\begin{align}
-  h_j^\t{ctl}\equiv-\gamma_jB_{\t{ctl},j}^\perp/2
-\end{align}
-as
-\begin{align}
-  \tilde H_\t{ctl} = \sum_{j:\omega_j=\omega_\t{ctl}}
-  h_j^\t{ctl}\v I_j\c\uv m_j.
-  \label{S_H_ctl}
-\end{align}
-
-In both (\ref{S_H_int}) and (\ref{S_H_ctl}), one can choose
-$\phi_{DD}$ and $\phi_\t{ctl}$ such that $\uv n_j\p\phi$ and
-$\uv m_j\p{\phi_\t{ctl}}$ lie anywhere in the plane perpendicular to
-$\uv\omega_j$. One can also tune $h_j^\t{int}$ and $h_j^\t{ctl}$
-respectively via free parameters in the AXY-$n$ sequence and
-$\v B_\t{ctl}$. These controls, together with rotations of the NV
-electron spin, allow one to realize a universal set of quantum
-gates. An exception to this statement is when two or more nuclei have
-the same effective larmor frequency $\omega_j$, in which case they are
-addressed simultaneously in (\ref{S_H_int}) and (\ref{S_H_ctl}).
-
-\subsection{Addressing larmor pairs}
-
-We call two spins indexed by $j$ and $k$ elements of a \emph{larmor
-  set} if their effective larmor frequencies are equal,
-i.e. $\omega_j=\omega_k$, and refer to a larmor set with exactly two
-spins as a \emph{larmor pair}. The problem with individually
-addressing elements of a larmor set is manifest in (\ref{S_H_int}) and
-(\ref{S_H_ctl}), wherein the previously developed procedure for
-nuclear spin addressing does not single out any nuclei. Nonetheless,
-under certain conditions it is possible to individually address
-elements of a larmor set by applying additional control fields.
-
-When employing a dynamic decoupling protocol on resonance with an
-effective larmor frequency $\omega_r$, one can apply an additional
-magnetic decoupling field
-$\v B_\t{dec}^{\p\omega}\p{t}=\v B_\t{dec}\cos\p{\omega_r
-  t-\phi_\t{dec}}$ and realize, in the frame of $H_\NV^\t{GS}$, the
-system Hamiltonian
-\begin{align}
-  \tilde H_\t{sys}^\t{dec} = H_\t{int} + H_\t{nZ}^\t{eff} + H_\t{dec},
-\end{align}
-where
-\begin{align}
-  H_\t{dec} = -\sum_j\gamma_j\v B_\t{dec}\c\v I_j
-  \cos\p{\omega_rt-\phi_\t{dec}}.
-\end{align}
-
-In the frame of $H_\t{nZ}^\t{eff}=-\sum_j\v\omega_j\c\v I_j$, the
-decoupling Hamiltonian becomes
-\begin{align}
-  \tilde H_\t{dec} = -\sum_j\gamma_j\tilde{\v B}_{\t{dec},j}
-  \c\v I_j \cos\p{\omega_rt-\phi_\t{dec}}
-  \label{S_H_dec_eff_full}
-\end{align}
-with
-\begin{align}
-  \tilde{\v B}_{\t{dec},j} = \v B_{\t{dec},j}^\parallel
-  + \v B_{\t{dec},j}^\perp\cos\p{\omega_j t}
-  + \v B_{\t{dec},j}^{\perp\perp}\sin\p{\omega_j t}
-\end{align}
-and
-\begin{align}
-  \v B_{\t{dec},j}^\parallel
-  &\equiv \p{\v B_\t{dec} \c\uv\omega_j}\uv\omega_j, \\
-  \v B_{\t{dec},j}^\perp
-  &\equiv \v B_\t{dec} - \v B_{\t{dec},j}^\parallel, \\
-  \v B_{\t{dec},j}^{\perp\perp}
-  &\equiv \uv\omega_j\times\v B_\t{dec}^\perp.
-\end{align}
-If $\omega_r,\omega_j\gg \gamma_jB_\t{dec}$, then we can neglect
-$\v B_{\t{dec},j}^\parallel$ in (\ref{S_H_dec_eff_full}) by the
-secular approximation, and by the rotating approximation express
-\begin{align}
-  \tilde H_\t{dec} = -\sum_{j:\omega_j=\omega_r}
-  \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_\t{dec} +
-  \v B_{\t{dec},j}^{\perp\perp}\sin\phi_\t{dec}}\c\v I_j.
-\end{align}
-Defining
-\begin{align}
-  \v\nu_j = \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_\t{dec}
-  + \v B_{\t{dec},j}^{\perp\perp}\sin\phi_\t{dec}},
-\end{align}
-we can express
-\begin{align}
-  \tilde H_\t{dec} = -\sum_{j:\omega_j=\omega_r}\v\nu_j\c\v I_j.
-\end{align}
-The system Hamiltonian in the frame of $H_\t{nZ}^\t{eff}$ thus takes
-the form
-\begin{align}
-  \tilde H_\t{sys}^\t{dec} = \tilde H_\t{int} + \tilde H_\t{dec}
-  = \sum_{j:\omega_j=\omega_r}
-  \p{h_j^\t{int}\sigma_\NV^z\v I_j\c\uv n_j - \v\nu_j\c\v I_j}.
-\end{align}
-
-In the frame of $\tilde H_\t{dec}$, the entire system is governed by
-the Hamiltonian
-\begin{align}
-  \tilde H_\t{int}^\t{dec} = \sum_{j:\omega_j=\omega_r}
-  h_j^\t{int}\sigma_\NV^z\v I_j\c\tilde{\v n}_j\p{t},
-  \label{S_H_int_dec_full}
-\end{align}
-where $\tilde{\v n}_j\p{t}$ is the unit vector $\uv n_j$ rotated about
-$\uv\nu_j$ by $\nu_jt$, i.e.
-\begin{align}
-  \tilde{\v n}_j\p{t} = \v n_j^\parallel +
-  \v n_j^\perp\cos\p{\nu_jt} + \v n_j^{\perp\perp}\sin\p{\nu_jt},
-\end{align}
-with
-\begin{align}
-  \v n_j^\parallel &\equiv \p{\uv n_j\c\uv\nu_j}\uv\nu_j, \\
-  \v n_j^\perp &\equiv \uv n_j - \uv n_j^\parallel, \\
-  \v n_j^{\perp\perp} &\equiv \uv\nu_j\times\uv n_j.
-\end{align}
-If $\omega_j\gg\nu_j\gg h_j^\t{int}$, the secular approximation allows
-us to neglect $\v n_j^\perp$ and $\v n_j^{\perp\perp}$ in
-(\ref{S_H_int_dec_full}), leaving
-\begin{align}
-  \tilde H_\t{int}^\t{dec}
-  = \sum_{j:\omega_j=\omega_r}
-  \tilde h_j^\t{int}\sigma_\NV^z\v I_j\c\uv\nu_j,
-  \label{S_H_int_dec}
-\end{align}
-where
-\begin{align}
-  \tilde h_j^\t{int} = h_j^\t{int}\uv n_j\c\uv\nu_j.
-\end{align}
-
-In words, the decoupling field $\v B_\t{dec}^{\p\omega}\p{t}$ modifies
-$\tilde H_\t{int}$ in (\ref{S_H_int}) by suppressing the components of
-$\uv n_j$ (i.e. $\uv A_j^\perp$ rotated about $\uv\omega_j$ by
-$\phi_{DD}$) which are perpendicular to the respective $\uv\nu_j$
-(i.e.  $\uv B_{\t{dec},j}^\perp$ rotated about $\uv\omega_j$ by
-$\phi_\t{dec}$). The utility of this decoupling field lies in the fact
-that when $\uv n_j$ and $\uv\nu_j$ are orthogonal, the interaction
-with spin $j$ is suppressed as $\tilde h_j^\t{int}=0$. Considering a
-single larmor pair, one can therefore apply a decoupling field to
-eliminate one of the two terms in (\ref{S_H_int_dec}) and realize an
-effective Hamiltonian which couples the NV electron spin to only one
-nuclear spin. This scheme fails for larmor pairs with mutually
-parallel $\v A_j^\perp$.
-
-The tools developed in this paper do not allow for single-spin
-operations on elements of a larmor pair. Such operations must
-therefore be either forgone, or else realized via composite operations
-making use of (\ref{S_H_ctl}) and (\ref{S_H_int_dec}). The same is
-true of spin-spin coupling between the NV electron spin and a single
-element of a larmor set with more than two nuclei.
-
-\subsection{Coherent SWAP with a singlet-triplet qubit}
-
-For the following analysis, we will consider a single addressable
-larmor pair, i.e. a pair of nuclei indexed by 1 and 2 with effective
-larmor frequencies $\omega$ and for which $\v A_j^\perp$ are not
-mutually parallel. We will use the basis
-$\set{\ket\u\equiv\ket 0, \ket\d\equiv\ket{m_s}}$ for the spin states
-of the NV electron, and the standard basis
-$\set{\ket{\u\u}, \ket{\u\d}, \ket{\d\u}, \ket{\d\d}}$ for the spin
-states of the nuclei. We will refer to the logical qubit consisting of
-the basis states $\set{\ket{\u\d},\ket{\d\u}}$ as the anti-correlated
-(AC) qubit, and the logical qubit consisting of the basis states
-$\set{\ket\S,\ket\T}$ as the singlet-triplet (ST) qubit, where
-\begin{align}
-  \ket\S &\equiv \f1{\sqrt2}\p{\ket{\u\d}-\ket{\d\u}}, \\
-  \ket\T &\equiv \f1{\sqrt2}\p{\ket{\u\d}+\ket{\d\u}}.
-\end{align}
-
-A SWAP operation between two qubits indexed by 1 and 2 can be realized
-via the composite operation
-\begin{align}
-  \SWAP^{1,2} = \cNOT^{2\to1}\cNOT^{1\to2}\cNOT^{2\to1},
-\end{align}
-where $\cNOT^{j\to k}$ is the controlled-NOT gate, which flips the
-state of qubit $k$ conditionally on the state of qubit $j$. The
-$\cNOT^{j\to k}$ gate is realized via
-\begin{align}
-  \cNOT^{j\to k} = \exp\p{-j\f\pi2I_j^z} \exp\p{-j\f\pi2I_k^x}
-  \exp\p{j\pi I_j^z I_k^x}.
-\end{align}
-
-If we wish to perform a SWAP operation between the NV electron spin
-and an ST qubit, it is easier to first realize the operation
-\begin{align}
-  \SWAP^{\NV,\AC}
-  = {\cNOT^{\AC\to\NV}}^\dagger\cNOT^{\NV\to\AC}\cNOT^{\AC\to\NV},
-  \label{S_SWAP_NVAC_sketch}
-\end{align}
-where
-\begin{align}
-  \cNOT^{\AC\to\NV} = \cNOT^{1\to\NV}
-\end{align}
-and
-\begin{align}
-  \cNOT^{\NV\to\AC} = \cNOT^{\NV\to2}\cNOT^{\NV\to1}.
-\end{align}
-For later convenience, (\ref{S_SWAP_NVAC_sketch}) makes use of the
-fact that ${\cNOT^{j\to k}}^\dagger=\cNOT^{j\to k}$. Therefore (with
-$\v I_\NV=\v\sigma_\NV/2$),
-\begin{align}
-  \SWAP^{\NV,\AC}
-  =& \exp\p{-j\f\pi2 I_\NV^x} \exp\p{j\f\pi2 I_1^{z'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^x I_1^{z'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_1^{x'}}
-     \exp\p{j\f\pi2 \sigma_\NV^z I_1^{x'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^z} \exp\p{-j\f\pi2 I_2^{x''}}
-     \exp\p{j\f\pi2 \sigma_\NV^z I_2^{x''}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_1^{z'}}
-     \exp\p{j\f\pi2 \sigma_\NV^x I_1^{z'}},
-  \label{S_SWAP_NVAC_full}
-\end{align}
-where we make explicit the fact that the the spin of nuclei 1 and 2
-may be given in their own respective bases
-$\set{\uv x',\uv y',\uv z'}$ and $\set{\uv x'',\uv y'',\uv z''}$. We
-can evaluate the first and last rotations of spin 1 in
-(\ref{S_SWAP_NVAC_full}) and combine factors to get
-\begin{align}
-  \SWAP^{\NV,\AC}
-  =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 \sigma_\NV^x I_1^{z'}}
-     \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z} \exp\p{j\f\pi2\sp{I_1^{y'}-I_2^{x''}}}
-     \times \tag*{} \\
-   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
-     \exp\p{j\f\pi2 \sigma_\NV^z I_2^{x''}} \times \tag*{} \\
-   & \exp\p{j\f\pi2 \sigma_\NV^x I_1^{z'}} \exp\p{-j\f\pi2 I_\NV^x}.
-\end{align}
-Letting
-\begin{align}
-  \uv x' = \uv y'' &= \uv A_1^\perp, \\
-  \uv y' = -\uv x'' &= \uv A_1^{\perp\perp}, \\
-  \uv z' = \uv z'' &= \uv\omega_1\approx\uv z, \label{S_w=z}
-\end{align}
-where the approximation in (\ref{S_w=z}) holds for
-$\gamma_1B\gg A_1/2$,
-\begin{align}
-  \SWAP^{\NV,\AC}
-  =& \exp\p{j\f\pi2 I_\NV^x}
-     \exp\p{-j\f\pi2 \sigma_\NV^x I_1^z} \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z}
-     \exp\p{j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \times \tag*{} \\
-   & \exp\p{j\f\pi2 \sigma_\NV^x I_1^z} \exp\p{-j\f\pi2 I_\NV^x}.
-  \label{S_SWAP_NVAC_sxsz}
-\end{align}
-As we cannot directly realize the coupling $\sigma_x^\NV I_z^1$,
-we must perform rotations as
-\begin{align}
-  \exp\p{-j\f\pi2 \sigma_\NV^x I_1^z}
-  =& \exp\p{-j\f\pi2 I_\NV^y} \exp\p{j\f\pi2 I_1^{y'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{x'}}
-     \exp\p{-j\f\pi2 I_1^{y'}} \exp\p{j\f\pi2 I_\NV^y}.
-\end{align}
-Substituting this identity into (\ref{S_SWAP_NVAC_sxsz}) yields
-\begin{align}
-  \SWAP^{\NV,\AC}
-  =& \exp\p{j\f\pi2 I_\NV^x} \exp\p{-j\f\pi2 I_\NV^y} \times \tag*{} \\
-   & \exp\p{j\f\pi2\sum_jI_j^{y'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{x'}}
-     \exp\p{j\f\pi2 I_\NV^y} \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z}
-     \exp\p{j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^y}
-     \exp\p{j\f\pi2 \sigma_\NV^z I_1^{x'}}
-     \exp\p{-j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
-   & \exp\p{j\f\pi2 I_\NV^y} \exp\p{-j\f\pi2 I_\NV^x},
-  \label{S_SWAP_NVAC}
-\end{align}
-where we have canceled out two rotations of the form
-$\exp\p{\pm j\pi/2~I_1^{y'}}$ and inserted two rotations of the form
-$\exp\p{\pm j\pi/2~I_2^{y'}}$ with no net effect.
-
-The $\SWAP^{\NV,\ST}$ can be realized using the $\SWAP^{\NV,\AC}$ gate
-via
-\begin{align}
-  \SWAP^{\NV,\ST} = R_\NV^\dagger \SWAP^{\NV,\AC} R_\NV,
-\end{align}
-where the rotation $R_\NV$ takes $\ket\u\to\p{\ket\u-\ket\d}/\sqrt2$
-and $\ket\d\to\p{\ket\u+\ket\d}/\sqrt2$. Written explicitly,
-\begin{align}
-  R_\NV = \exp\p{j\f\pi2 I_\NV^y}.
-\end{align}
-We therefore have that
-\begin{align}
-  \SWAP^{\NV,\ST}
-  =& \exp\p{j\pi\v I_\NV\c\uv a} \times \tag*{} \\
-   & \exp\p{j\f\pi2\sum_jI_j^{y'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{x'}}
-     \exp\p{j\f\pi2 I_\NV^y} \times \tag*{} \\
-   & \exp\p{-j\pi I_\NV^z}
-     \exp\p{j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 \sigma_\NV^z I_1^{y'}}
-     \exp\p{-j\f\pi2 \sigma_\NV^z I_2^{y'}} \times \tag*{} \\
-   & \exp\p{-j\f\pi2 I_\NV^y}
-     \exp\p{j\f\pi2 \sigma_\NV^z I_1^{x'}}
-     \exp\p{-j\f\pi2\sum_jI_j^{y'}} \times \tag*{} \\
-   & \exp\p{-j\pi\v I_\NV\c\uv a},
-  \label{S_SWAP_NVST}
-\end{align}
-where $\v a = \uv x - \uv y$ and we have used the fact that
-\begin{align}
-  \exp\p{j\f\pi2 I^y} \exp\p{-j\f\pi2 I^x}
-  \exp\p{j\f\pi2 I^y}
-  = \exp\p{-j\pi\v I\c\uv a}.
-\end{align}
-
-In the subspace of interest, we have thus constructed the
-non-entangling SWAP operation
-\begin{align}
-  \SWAP^{\NV,\ST} = \op{\u\S}{\S\u} + \op{\u\T}{\d\S}
-  + \op{\d\S}{\u\T} + \op{\d\T}{\d\T}.
-\end{align}
-If $\gamma_1=\gamma_2$, i.e. if nuclei 1 and 2 are of the same
-species, all factors in (\ref{S_SWAP_NVST}) can be realized directly
-via the protocols for (\ref{S_H_ctl}), (\ref{S_H_int_dec}), and
-rotations of the NV electron spin.
-
-Realizing $\SWAP^{\NV,\AC}$ by switching the cNOT operations in
-(\ref{S_SWAP_NVAC_sketch}) is seemingly impossible, as doing so
-requires rotating one spin in the larmor pair without rotating the
-other. It is possible to realize $\SWAP^{\NV,\ST}$ via cNOT operations
-between the NV and ST qubits directly, but this method requires
-performing many more individual spin addressing operations, and
-therefore has a substantially lower fidelity.
-
-\fixme{when we wish to read out the ST qubit, it is possible to do so
-  without performing the full coherent SWAP operation so long as we no
-  longer need the larmor pair as a resource for the time being. Talk
-  about this.}
-
-\subsection{Robustness against noise}
-
-Talk about the robustness of the ST qubit against dephasing via the NV
-center, as well as its robustness against slowly varying (frequencies
-$\nu\ll\gamma_jB$) external magnetic noise.
-
-\section{Simulations and Results}
-
-\subsection{Abundance of larmor pairs}
-
-For any given hyperfine cutoff $A_\t{min}$ and an isotopic abundance
-$n$ of $^{13}$C, we can compute exactly the probability
-$P\p{A_\t{min},n}$ of finding an addressable larmor pair for which
-$A_j\ge A_\t{min}$. The simulations developed for this paper can also
-be used to test the computation of $P\p{A_\t{min},n}$ via the Monte
-Carlo method of simply generating many NV systems and counting the
-proportion of them which contain an addressable larmor pair.
-
-\subsection{SWAP fidelities via AXY-$n$}
-
-Discuss simulations and any relevant nuances therein. Present
-histograms of $\SWAP^{\NV,\ST}$ fidelities and net operation times.
-
-Note: the same simulations can also be used to generate similar
-histograms (as well as other info) about other operations,
-e.g. single-spin $\SWAP$ or $i\SWAP$ operations. Furthermore, the
-simulations can, without any modification, reproduce results such as
-Figure 2 in \cite{wang2016positioning} (``Positioning Nuclear Spins in
-Interacting Clusters for Quantum Technologies and
-Bio-imaging''). Minor additions to the codes might make them useful
-for comparing the efficacy of different spin-addressing protocols. Is
-there any interest in doing any of these things (for this paper or
-elsewhere)?
-
-\section{Conclusions}
-
-\section{Acknowledgments}
-
-\bibliography{\jobname}
+In the simulation with optical illumination for
+Fig.~\ref{fig:FigCoherence}, we adopt the 11-levels Lindblad model of
+the experimental paper Ref.~\cite{Maurer2012Room-1}. The illumination
+power is 1.5 $\%$ of the saturation power  \cite{Maurer2012Room-1} and
+the magnetic field $B_{z}=0.4$ T.
+\begin{thebibliography}{10}
+\bibitem{Maurer2012Room-1} P. C. Maurer, G. Kucsko, C. Latta, L.
+Jiang, N. Y. Yao, S. D. Bennett, F. Pastawski, D. Hunger, N. Chisholm,
+M. Markham, D. J. Twitchen, J. I. Cirac, and M. D. Lukin, Room-Temperature
+Quantum Bit Memory Exceeding One Second, Science \textbf{336}, 1283
+(2012).\end{thebibliography}
 
 \end{document}
-
-notes:
-
-prove DFS
-
-how to locate spins?
-- identify larmor frequencies for C-13 nuclei
-- identify a frequency with two spins
-- locate two spins
-
-perform elementary gate on one spin
-implement PRX gates
